\chapter{Chapter 4 - Enemy Unmade to Dust}
\label{chap:chapter4}

\setcounter{section}{-1}
\section{Running This Chapter}

Kholinar is under siege by Singer forces. The characters will play their part and use an ancient Unmade fabrial to tip the balance for their favor. But before that, they must plan their escape!

Depending on characters' allegiance they will be able to help either Singer or the Kholinar forces. Either a Thunderclast or a gate barricade can be annihilated with the \lootDustcaster{} and it is up to the PCs to choose.

\subsection{Character Advancement}

The characters start this chapter at level 4. Advance them to level 5 at the end of the chapter.

The following events may affect their path to radiance:
\begin{itemize}
	\item Careful planning before the mission
	\item Heroic deeds to protect their allies
	\item Talking with \npcSjaAnat can expedite an Enlightened Lightweaver
	\item Using ancient artifacts of the Unmade can expedite an Enlightened Dustbringer
\end{itemize}



\subsection{Forging Alliances}

The following actions can help the characters to become allies with Kholinar fractions:
\begin{itemize}
	\item Eliminate a Thunderclast to earn Wall Guards' gratitude.
	\item Breach the city walls to prove your loyalty to the Singer forces
	\item Characters' attempts to get invited to the \npcFractionCult{} may bring them closer to that fraction
\end{itemize}



\subsection{Weather Conditions}

The Weeping is over. The rain stopped and a clear sky can finally be seen through the clouds. It is possible for a highstorm to appear, though the book does not include them in the nearest chapters. Add them, if you believe they will enrich your story or enable the Radiants.

\input{chapter_4/briefing.tex}
\input{chapter_4/sneakToTarget.tex}
\input{chapter_4/dustcasting.tex}
\input{chapter_4/runAway.tex}

\section{Journeying Onward}

After the characters successfully escape into Kholinar, advance them to level 5 and proceed to \nameref{chap:chapter5}.