\section{Running Away}
\label{sec:dustcastingFlee}

The characters must flee the guards alerted by their dustcasting. You can run it as a slightly modified pursuit endeavor:

The party must run from Singer Camp to the city walls (assuming they were starting from there), then they must reach the Monastery. During all that time they will be chased by the guards.

During the pursuit scene, keep track of two Current Distances - one between the party and the Singer Camp an the second between them and the guards. The endeavor ends, when the party reaches Escape Distance of 9 from the Singer Camp (or 6 from the Gates, see below). When the Distance between them and the guards is reduced to 0, the chase does not end, but the guards can make a free attack against them.

\begin{tabular}{p{3cm} p{4cm}}
	\color{black} Location 			& \color{black} Distance to the next \\ \hline
	\color{black} Singer Camp 		& \color{black} 3 \\
	\color{black} City Gates 		& \color{black} 1 \\
	\color{black} Slumps			& \color{black} 3 \\
	\color{black} Rich Neighborhood & \color{black} 2 \\
	\color{black} Monastery 		& \color{black} \textit{(target reached)}
\end{tabular}

\subsubsection{Starting Distance}

Cloud of dust risen after the dustcasting is enough for the characters to allow them start with a distance of 1. If they succeeded to sneak without alerting the guards before that, add 1 to that distance (Starting Distance of 2) as the guards need more time to get there.

\subsubsection{Singer Guards}

If the party decided to dustcast a Thunderclast, they will start from the Singer Camp (Escape Distance 9 to the Monastery) and they will be chased by \enemySingerHaevenlyOne{}s. They can be deadly in the open space, but once the characters reach the city it might be easier for them to hide in narrow alleyways - allow for some advantages against the guards in there (or disadvantages for their rolls).

\subsubsection{Wall Guard}

If the party decided to remove gate barricade, they will need to outrun \enemyWallGuard{} lead by \enemyWallGuardHighmarshal{}. \npcHighmarshal{} will bolster her men, but she will not attack the PCs unless they strike her first. Escape Distance from the gates is shorter - only 6, but the guards know the city well.



\subsection{No Man's Land}

The area between the Singer Camp and the Kholinar (total Distance of 3) is a vast, empty area. The characters can find a few laits here to hide in (\skillStealth{}), they can also sprint the distance (\skillAthletics{}). However, watch out for a rockbuds growing here and there as well as for the rubble after the recent Everstorm.



\subsection{At the Gates}

If the characters flee from the Singer Camp, they will need to enter the city through the gates. If they made an alliance with the \npcFractionWall{}, they will let them pass without any problems.

However, if the characters fought them before, they might not be eager to let them through the gates. That may introduce another challenge during the pursuit. They might even join the chase themselves.

From there it is not that far (total Distance of 1) to the slumps.


\subsection{An Odd Fellow}

When the party reaches the gate barracks, you can optionally red the following:

\quoteBox{
	You can see tall and thin figure in a black coat, sitting at the chull cart full of a metal sheets. \\ \\
	"...on the walls, yes. And then you can soulcast inside that room, they won't be able to sense it", you can hear him explaining to \npcHighmarshal{}.
}

When the characters run past him, you can add the following:

\quoteBox{
	"Hey, don't rush like that!", he shouts at you. "It's pointless. No matter how fast you run, you cannot outrun your stench!"
}

On the cart there is \npcHoid{}. If the characters stop to talk with him, he might even help them a little - but his help comes at a price of a few juicy insults.

\reasonBox{
	Perhaps it's not the best moment for such a scene, but it was the only moment that I know for sure the party is at the gates. If in your game the characters reach this area on another occasion after \fullref{sec:monastery}, you can run this scene then.
}

\reasonBox{
	\npcHoid{} has little impact on this story. However, it is mentioned in the \bookOB{} that he was in the city during those events, so if you wish to roleplay him, introduce his cameo or just insult the characters - there is a perfect opportunity to do so.
}

\spoilerBox{
	\npcHoid{} helping \npcHighmarshal{} to prepare a room for soulcasting is referenced in \bookOB{}, Chapter 81: Ithi and Her Sister.
}



\subsection{The Slumps}

The slumps are a big part of the city (total Distance of 3) on the path to the palace. Though not the whole area is occupied by literal slumps and there are some decent streets in there, overall they all share some qualities that differentiate them from the nobles' mansions from the next area:

The alleys here are narrow, and it's easy to get lost in this labyrinth. The characters must navigate the tangled streets (\skillDeduction{}), but it is also easier to hide in here (\skillStealth{}). They might also find a few folks who will eagerly help them... for the right price!


\subsection{Rich Neighborhood}

Closer to the palace (total Distance of 2) the nobles have their houses. This area is nice and tidy, and the lighteye lords often deploy their own guards. It is easier to sprint than in the slumps (\skillAthletics{}), and perhaps the guards will be nice enough to help (\skillPersuasion{})... unless they decide to join the chase themselves.



\subsection{Monastery Gates}

The PCs made it! The gates are here! The Fused know better than to break into the area controlled by \npcHeartRevel{}, and \npcHighmarshal{} does not seek fight with \npcFractionCult{}. The chase is over!
