\section{Sneaking at Night}
\label{sec:dustcastingSneaking}

Before they can perform Dustcasting, the characters must sneak close enough to their target. You can run it as an endeavor. 

\scriptedOption{Sneaking to the Singer Camp}{
	If the characters want to annihilate the Thunderclast, they will need to enter the Singer Camp. It is guarded by \enemySingerWarform{}s, and the endeavor tests will be done against their Defenses.
}

\scriptedOption{Sneaking to Kholinar Gates}{
	If the characters wish to break the barricade at the gates, they will need to get close enough the wall, guarded by \enemyWallGuard{}s. The endeavor tests will involve their Defenses.
}



\subsection{Possible Approaches}

The characters are free to suggest their ideas how would they approach the endeavor. Potential proposals may include:

\scriptedOption{Being close to target.}{
	If the party is already nearby their target (eg. they spent the night in the Singer Camp and they want to unmake the Thunderclast), immediately award them with 2 successes to their endeavor progress.
}

\scriptedOption{Hiding in the cover of the night.}{
	A character can make a \skillStealth{} test against the guards' \skillPerception{} test to attempt approaching without being spotted.
}

\scriptedOption{Melding with the surrounding.}{
	A character can attempt a \skillSurvival{} test against the guards' \skillPerception{} test if they want to use a camouflage.
}

\scriptedOption{Pretend to belong.}{
	A character may deceive guards by making a \skillDeception{} test against their \skillInsight{}.
}

\scriptedOption{Threaten the guards.}{
	A \skillIntimiation{} test against guard's \skillDiscipline{} test may be attempted if a character wants to scare them away.
}

\scriptedOption{Work out guards' patrol patterns.}{
	A character may attempt a \skillCheck{15}{\skillDeduction{}} to learn the paths and time the guards take during their patrols.
}


\subsection{\pursuitResolveHeader}

\pursuitReq{6}{3}

Even if the party gathers failures, they will be able to reach their target. The only question is - will they be seen?

\scriptedOption{Success!}{
	If the party completes the endeavor, they can approach their target without being noticed by anyone.
}

\scriptedOption{1 Failure}{
	A guard notices something. They are now on high alert and their future \skillPerception{} tests are made with an advantage.
}

\scriptedOption{2 Failures}{
	The guard now sees you. "Stop! Who goes there?", he shouts at you.
}

\scriptedOption{3 Failures}{
	It's over, they now know you are not supposed to be here. The guards raise an alarm. The party will be attacked during \fullref{sec:dustcasting}.
}