\chapter{Chapter 1 - Fool Revealed}
\label{chap:chapter1}

\setcounter{section}{-1}
\section{Running This Chapter}

This chapter is loosely structured, allowing the PCs for an introduction, meeting with other PCs, and bonding with the NPCs.

At the end of the chapter the PCs will witness \npcRebelArdent{} accusing \npcQueen{} in the People's Hall - an event that will trigger all of the story.

\subsection{Character Advancement}

The characters start this chapter at level 1. Advance them to level 2 at the end of the chapter.

The following events may affect their path to radiance:
\begin{itemize}
	\item Helping to capture \npcRebelArdent{}
	\item Attempting to defend \npcRebelArdent{}
	\item The PCs' reaction to the encounters in the city.
\end{itemize}


\subsection{Forging Alliances}

The following actions can help the characters to become allies with Kholinar fractions:
\begin{itemize}
	\item Condemning \npcRebelArdent{}'s accusations may be noticed by Ardents and the Palace Guards.
\end{itemize}



\subsection{Weather Conditions}

The story starts during the Weeping, after the Lightday. Heavy overcast and constant rain are expected during first three chapters of the story. There will be no highstorms in that time.

\subsection{Scarce Food}

Recently it is difficult to acquire food in Kholinar. If any merchant has anything to sell, the price will be higher and higher as the time progresses.

For each chapter, add food value to it's final cost.\textit{(eg. during chapter 3. the price will be 4 times higher than normal: to the base price of 1x add it 3 times more because of the progressed time)}



\input{chapter_1/lifeInKholinar.tex}
\input{chapter_1/sweetHome.tex}
\input{chapter_1/peoplesHall.tex}

\section{Journeying Onward}

After the characters witness the arrest of \npcRebelArdent{}, advance them to level 2 and proceed to \nameref{chap:chapter2}.