\newpage
\section{Comments and Acknowledgments}
\label{sec:corruptedRulesAcknowledgments}



\subsection{Spren Appearance}

Enlightened Mistspren's appearance is described several times in \bookSA{}. For the purpose of those rules I used those visuals for them and I didn't attempt to add anything from myself.

Enlightened Criptics are briefly described in \bookWAT{}. I attempted to extrapolate from their Physical Realm description there and I hope my Cognitive Realm ideas fit Brandon Sanderson's vision.

I found Enlighened Inkspren's appearance on coppermind wiki. I did not try to change anything from that version.

All other Enlightened spren described in this book cannot be considered cannon. While creating them I tried to make them fit the others with their nightmarish creepiness and similarities to their non-Enlightened cousins, but they are not an official lore. You can modify those if my ideas don't fit the story you want to tell.



\subsection{Abilities}

As you know, \handbook{} provides an Enlightened Truthwatcher talent tree. This book presents a slightly modified alternative to the original, but overall the players should be familiar with them and I cannot take a credit for that part.

I also noticed that those talents align with one of the Singer's Forms of Power. Using this formula, I designed other talent trees presented here based on other Odium minions. You might notice that some of the talents are heavily inspired with those stat blocks.

For a few Orders I did not find applicable abilities or the abilities I found were not appealing enough for me. In those cases I attempted to provide my own proposals for them. I hope you will enjoy those.



\subsection{Unmade Relation}

While reading \bookSA{} books, I had a strong impression that Enlightened Truthwatchers' abilities look oddly similar to what one of the Unmade - \npcMoelach{} - can do. I always wondered if that's just a coincidence or something more...

When I considered other Unmade and their traits, I was able to identify more similarities with other Radiant Orders. For the purposes of my fan-made rules I decided to assume this is intentional and represents deeper connection to Odium and his powers.

However, this idea is never officially confirmed and cannot be considered a cannonical piece of lore.



\subsection{Drawbacks and Complications}

Enlightened Truthwatcher talents presented in \handbook{} seem to be working as an optional set of abilities a Radiant can opt to have. I honestly am not a great fan of that approach, for me it seems lacking and unbalanced - from the game mechanics point of view there is no downside of choosing the Enlightened variant, making a standard option always an inferior, and therefore - wrong, choice.

I decided to address that issue with \textbf{Drawbacks and Complications} section. Access to additional abilities always comes at a cost. It can be unpredictable and depended on the GM's approach, but the players need to be aware of the risk. 

I hope this rule will make standard Radiant Orders still a valid choice for players who prefer safer builds, while allowing an Enlightened alternative to provide more abilities.



\subsection{Ties to Scarlet Sprouter}

Those who are familiar with "The Lost Expedition of Chi-Ltik" may notice some similarities between the Red Vines presented there and an Enlightened Edgedancer talent tree from this book.

I will be honest - I like how this set of abilities enriches available trope range by adding Necromancy to the world of Roshar. I designed Scarlet Sprouter with \npcSjaAnat{}'s influence in mind and though Chi-Ltik does not explore its origins in detail, I believe such spren would be a good counterpart for the usual cultivationspren.

% It also ties quite nicely with the whole Unmade relation idea. As \npcMidnightMotherTitle{} is known for her nearly-liquid legions, it makes sense for water-like Edgedancers to summon their own troops after \npcSjaAnat{}'s Enlightenment.


\subsection{Suggested Adventure}

Those homebrew rules for Enlightened Radiant Knights can be used in any campaign you wish. However, if you are looking for some suggestions, they were designed for "Children of the Unmade" homebrew adventure that featured \npcSjaAnat{} and her corrupted children.

If you wish to play this adventure with your group, you can find it on my github: \\

~~~~\url{https://github.com/pether-pg/CosmereRPG_Books_byPether/releases}


\subsection{Special Thanks}

To discord user Sharei, for long and inspiring discussions about potential updates to the Enlightened Radiants' talents. 
