\newpage
\section{General Rules}

Enlightened Radiants are still Radiants, and all the rules from the \handbook{} are still in place. However, on top of them, the following applies:

\subsection{Philosophy Changes}

Enlightening touch of \npcSjaAnat{} expands not only the powers granted by the spren, but also their belief system. Each of the Enlightened Orders has a short description suggesting such changes. Those can be used to better understand the new values of the Order and help players with their roleplay.

\subsection{Neither Good Nor Evil}

Despite being created with Voidlilght by one of the Unmade, the spren are not inherently evil, nor are their Radiants. They are not forced onto the path of moral goodness, neither. Enlightened by the touch of \npcSjaAnat{}, the spren recognize the world is not black and white and it is up to their Radiants to determine what choices will they make.

\subsection{Enlightened Talents}

On top of standard talents available to each Radiant Path, Enlightened spren grant access to 5 additional talents from the Enlightened talent tree. Those are unique for each of the Orders. They follow the same rules as other talents.

\subsection{Drawbacks and Complications}

No great power comes without a cost. Each of the Enlightened Orders has listed some negative effects or events that can occur as a consequence of meddling with too much of Odium's powers. Some of them affect the scenes in a clearly defined rules, while others are less rigid. They can be an inspiration of complications to be used in a case of rolled \iconComp{}, but in the end it is up to GM how often they will affect the characters.

\subsection{Unmade Influence}

Each of the nine Enlightened Radiant Orders is strangely connected to one of the Unmade. Perhaps it was only a pinch of inspiration that \npcSjaAnat{} took when creating her children, perhaps the connection is rooted more deeply in the laws governing the powers of Voidlight...

Whenever an Enlightened Radiant shares a scene with the Unmade (or something deeply connected with one) related to their Order, they are rewarded with expedited progress of their powers - they can immediately develop one of their talents from Enlightened talent tree. If there are no more talents left in that tree, they can develop another Radiant talent instead. In total, that can take effect up to 3 times in the entire game.

It is up to the GM to determine how many talents award to the player at once - while 1 would be a suggested number, the GM may decide that the Unmade will not make an appearance in the future story, making this last scene with them even more impactful.

\vspace{0.3cm}
\noindent
\begin{tabular}{p{2.5cm} p{6cm}}
	\color{black} Order 			& \color{black} The Unmade 											\\ \hline
	\color{black} Windrunners 		& \color{black} \npcThrill{}, the \npcThrillTitle{} 				\\
	\color{black} Skybreakers 		& \color{black} \npcYeligNar{}, the \npcYeligNarTitle{} 			\\
	\color{black} Dustbringers 		& \color{black} \npcDustmother{}, the \npcDustmotherTitle{} 		\\
	\color{black} Edgedancers 		& \color{black} \npcMidnightMother{}, the \npcMidnightMotherTitle{} \\
	\color{black} Truthwatchers 	& \color{black} \npcMoelach{} 										\\
	\color{black} Lightweavers		& \color{black} \npcSjaAnat{}, the \npcSjaAnatTitle{} 				\\
	\color{black} Elsecallers		& \color{black} \npcBlackFisher{}, the \npcBlackFisherTitle{}		\\
	\color{black} Willshapers 		& \color{black} \npcHeartRevel{}, the \npcHeartRevelTitle{} 		\\
	\color{black} Stonewards		& \color{black} \npcMishram{} 										\\	
\end{tabular}

\subsection{Speak the Words}

With changed philosophy, the Oaths of the Knights Radiant are also different. This ruleset do not impose any specific Words - those are for you to find! 
