\newpage
\section{Enlightened Dustbringer}

\corruptedBelief{I will seek self-mastery.}{I will be the master.}

\subsection{Philosophy Changes}

Dustbringers enlightened by \npcSjaAnat{} believe that no self-growth or self-mastery can be done without glorious ambition shaping the whole process. They often focus on grand projects and they never hesitate to use others to achieve it.

At their best they are grand leaders, aiming for legendary deeds that will benefit entire kingdoms of populace.

At their worst they become selfish and ruthless tyrants, abusing others to achieve their own vain desires.

\subsection{Enlightened Ashspren}

In the Physical Realm, Enlightened ashspren manifest as blood veins, scarlet and branching, leaving bloody smears behind when they move.

In the Cognitive Realm their gray bodies rot and decay, showing bloodied flesh and sometimes even their bones. Their gums always bleed, painting their sharp teeth red and sometimes dripping smears of blood from their mouths. 

\subsection{Drawbacks and Complications}

While focusing on mastering the others, Enlightened Dustbringers sometimes fail to properly control their own powers.

The GM may ask a Dustbringer for a Discipline check (\corruptedResistanceDC{}). On a failure an item they hold slips or even turns to dust.


\subsection{Enlightened Talents}

\talent{\talentDustbringerDecayName{} (Key)}
		{Bond an Enlightened ashspren}
		{\iconSpecial}
		{Under your touch, the wounds refuse to heal.}
		{Before a character within your reach recovers health or focus, you can spend 1 Focus or 1 Investiture to prevent them from doing so. The character does not regain that Health or Focus, but any actions, Investiture, or other resources they spent still remain spent.}
	
\newpage
\talent{\talentDustbringerDrainName}
		{Speak the First Ideal, \talentDustbringerDecayName{} key talent}
		{\iconActionDouble}
		{Dying flesh cannot hold the Light.}
		{A character you touch loses 1d4 Investiture. You regain the same amount of Investiture up to your maximum value. Characters in Shardplates cannot be targeted.}
		
\talent{\talentDustbringerLifestealName}
		{\talentDustbringerDrainName{} talent}
		{\iconConstant}
		{Weakness of your enemies is your strength.}
		{Your attacks heal you for half the damage dealt.}
		
\talent{\talentDustbringerUnhealableName}
		{Speak the First Ideal, \talentDustbringerDecayName{} key talent}
		{\iconConstant}
		{One cannot heal what was chopped of by your hand.}
		{Whenever your attack, skill, or talent reduces enemy's Health or Focus, their maximum of those is also reduced by the same amount until the character's next Long Rest.}
		
\talent{\talentDustbringerAfflictionName}
		{\talentDustbringerUnhealableName{} talent}
		{\iconAction}
		{The rot and decay slowly spread through the flesh, consuming their victim alive.}
		{Spend 1 Investiture to make a Division attack against a Physical Defense of an enemy you can touch. The attack deals 2d4 vital damage. On a hit, the target becomes Afflicted [1d4 vital] for 2 rounds. Once per turn you can extend duration of the Afflicted condition for 1 round as a \iconFreeAction{} for 1 Investiture.\\
		The size of this attack’s and affliction's damage dice increases with your ranks in Division; at 2 ranks,  use d6s (instead of d4s), and so on. As usual, on a hit, add your Division modifier to damage, and on a miss, you can spend 1 focus to graze with the attack.}