\newpage
\section{Enlightened Elsecaller}

\corruptedBelief{I will reach my potential.}{I will reject imperfection.}

\subsection{Philosophy Changes}

Aiming for ones full potential is never enough for Elsecallers influenced by \npcSjaAnat{}. Instead their goal is absolute perfection. They despise anything imperfect, rejecting it from their lives.

At their best, they reach an excellence in each task they set for themselves.

At their worst, they grow hateful and resentful towards everyone and everything, including themselves. They can never be satisfied by anything and they will punish any imperfection in themselves and others.

\subsection{Enlightened Inkspren}

In the Physical Realm, the Enlightened inkspren manifest as a small iridescent person, capable of changing their size at will.

In the Cognitive Realm they look very similar, though they are always in their full size.

\subsection{Drawbacks and Complications}

Abilities granted by Enlightened talents cause the Elsecaller to be split between Physical and Cognitive Realms. At most of the time they can control it, but the GM may request a Discipline test from them (\corruptedResistanceDC{}). On a failure, they are lost for a few moments in the Shadesmar, unable to assist the rest of the team and exposed to feral spren attacks.

After a few rounds they are always transported back to the Physical Realm.

\subsection{Enlightened Talents}

\talent{\talentElsecallerKeyName{} (Key)}
		{Bond an Enlightened inkspren}
		{\iconSpecial}
		{Your physical body is full of imperfections. Reject it!}
		{At the beginning of each round you can assume a shadowy, incorporeal form by spending 1 Investiture. While you're in this form, all attacks against your Physical Defense gain disadvantage, you can ignore difficult terrain and you can travel through any gaps with a diameter of 6 inches or greater, but you can attack only if you are in a darkened area. You may return to your physical form at the beginning of subsequent rounds.}
	
		
\talent{\talentElsecallerDirgeName}
		{First Ideal; \talentElsecallerKeyName{} key talent}
		{\iconAction}
		{Perfection terrifies those of a weak mind. Present it to them, and watch them suffer! Punish their weakness!}
		{Spend 2 Investiture to make an Intimidation test against the Spiritual defense of a target you can influence within 30 feet of you. On a success, the target becomes \exhausted[-1]. \\If you are in your incorporeal form, this action costs 1 less Investiture.}
		
\talent{\talentElsecallerStealLightName}
		{First Ideal; \talentElsecallerKeyName{} key talent}
		{\iconAction}
		{Darkness is your friend, awaiting your call.}
		{Spend 1 Investiture and choose an area you can see that doesn't exceed your Transformation Surge Size. That area becomes darkened by unnatural, pitch black shadows. The effect lasts until the end of the scene or until you decide to end it.}
		
\talent{\talentElsecallerMistyStepName}
		{\talentElsecallerStealLightName{} talent}
		{\iconAction}
		{Embrace the shadows, walk through them, allow them to hide your imperfections.}
		{If you are standing in a darkened area, spend 1 Investiture to move to any other darkened place you can see within 60 feet. Until end of turn you may return to your starting location as \iconFreeAction{}. This does not trigger Reactive Strikes. \\
		If you are in your incorporeal form, this action does not require spending Investiture.}
		
\talent{\talentElsecallerDragName}
		{\talentElsecallerMistyStepName{} talent}
		{\iconConstant}
		{Nobody can run away from the perfection!}
		{When you are using \talentElsecallerMistyStepName{} talent, you can also transport 1 character standing 5 feet from you. If the target is unwilling, you must first succeed on an Agility test against the target’s Physical defense. \\
		A transported target appears in an unoccupied space of your choice within 5 feet of you.}
		
		