\section{Enlightened Lightweaver}

\corruptedBelief{I will speak my truth.}{I will uncover their lies.}

\subsection{Philosophy Changes}

After the Enlightenment, the cryptic's love for secrets is only magnified. They relish in uncovering the lies and decrypting hidden information, often discovering things seemingly impossible to gather.

At their best, Lightweavers bonding those spren make an excellent spies and agents with amazing attention to details.

At their worst, they pursue personal secrets without any regard to other peoples' privacy, often damaging reputation and spreading lies, gossip and misinformation in the process.

\subsection{Enlightened Cryptic}

In the Physical Realm Enlightened cryptics manifest as bone-white scribbles rotating around the center.

In the Cognitive Realm the rotating scribbles form the head of the cryptic. The rest of the body looks like of robes made of old parchment, with tears and bends in many places.

\subsection{Drawbacks and Complications}

The cryptics love discovering secrets so much, they will often do it without Radiant's instructions. They will always share their findings, but due to errors or spren's spite they can sometimes be misleading or false. On top of that, they enjoy dark secrets the most, so the character can be overwhelmed with gloomy reality uncovered by their spren.

The GM can make the Radiant roll for a Discipline check (\corruptedResistanceDC{}). On the failure, the character cannot contain newly learned secrets and must confront their owner about them, spreading possibly false information and damaging their reputation.

\newpage
\subsection{Enlightened Talents}

\talent{\talentLightweaverKeyName{} (Key)}
		{Bond and Enlightened cryptic }
		{\iconConstant}
		{You can read people like an open book.}
		{You gain an advantage on Insight tests made to interpret the desires or intentions of others.}
		
\talent{\talentLightweaverReadSecretsName}
		{\talentLightweaverKeyName{} key talent}
		{\iconAction}
		{With a little help from your spren you can find out much more than the person is willing to share.}
		{Spend 1 Focus to learn one secret of another person.}
		
\talent{\talentLightweaverDetectThoughtsName}
		{\talentLightweaverReadSecretsName{} talent}
		{\iconAction}
		{If you try hard enough, you can even read people's thoughts out of their faces.}
		{Spend 1 Investure and choose a character. You can determine what exactly that character is thinking about in this very moment. If used in combat, that character's actions against you gain disadvantage. Lasts for a number of rounds equal to your rank.}
		
\talent{\talentLightweaverDetermineOthersName}
		{\talentLightweaverKeyName{} key talent}
		{\iconAction}
		{You can always determine the right words to motivate others.}
		{An allay you can influence becomes Determined until the ally benefits from that condition or until the scene ends.}
		
\talent{\talentLightweaverSuggestionName}
		{\talentLightweaverDetermineOthersName or \talentLightweaverDetectThoughtsName{} talent}
		{\iconActionDouble}
		{When you can read the people this well, manipulating them is just a child's play.}
		{Spend 1 Investure and make a Deception or Persuasion test against the Spiritual Defense of an enemy you can influence. You gain an advantage on that roll if you know target's secrets, goals or intentions that are relevant. If you succeed, you can suggest a reasonable action - they will be forced to enact it.}