\newpage
\section{Enlightened Skybreaker}

\corruptedBelief{I will seek justice.}{I will seek vengeance.}

\subsection{Philosophy changes}

Skybreakers influenced by \npcSjaAnat{} recognize that all laws and legal systems exist to fulfill human desire for revenge - they may call it just and fair, but it's only to make them feel better while they aim to hurt others just like they were hurt. Those Skybreakers discard complex and inefficient legal procedures and instead focus on the core of the issue - avenging.

At their best, those Skybreakers are just and righteous warriors fighting in a name of weak and hurt.

At their worst they are blinded with their desire to punish everyone around them, without thinking about the consequences.

\subsection{Enlightened Highspren}

In the Physical Realm, Enlightened highspren manifest as small cavities filled with amethyst, looking like the inside of a purple geode.

In the Cognitive Realm, the geode-like cavity takes a shape of a man. Their silhouette's looks like a concave cluster of amethysts no matter at what angle you look at them.

\subsection{Drawbacks and Complication}

Consumed by their desire for revenge, the Skybreakers often deal massive collateral damage they might not be aware of. When they are using their Division or Enlightened talents, the DM may make them a Discipline check (\corruptedResistanceDC{}). On a failure, they lose control over their abilities, dealing damage to their allies or NPCs on top of the enemy they were aiming for.

\subsection{Enlightened Talents}

\talent{\talentSkybreakerGraspName{} (Key)}
		{Bond an Enlightened highspren}
		{\iconAction}
		{Your hands are sparkling with small electrical discharges.}
		{Spend 1 Investiture and make a Division skill check against a Spiritual Defense of an enemy you can touch. On a success, the enemy becomes Stunned. On a failure they cannot use \iconReaction{} until your next turn.}

\newpage
\talent{\talentSkybreakerLeapName}
		{Speak the First Ideal, \talentSkybreakerGraspName{} key talent }
		{\iconAction}
		{You fall from the skies, as the lightning made flesh.}
		{Spend 1 Investiture to jump up to 60 feet. If you land within 5 feet of an enemy, the you can use the Gain Advantage action as \iconFreeAction{}.}

\talent{\talentSkybreakerShieldName}
		{\talentSkybreakerLeapName{} talent}
		{\iconFreeAction{}}
		{Lightning arcs envelop you, shielding from the enemies.}
		{After you use the Move action, you become electrically charged until the start of your next turn. While charged, you’re immune to energy damage, and whenever the you are hit with an attack by an enemy within 5 feet of you, the attacker takes 1d4 energy damage. The size of the damage die increases with your ranks in Division.}

\talent{\talentSkybreakerBoltName}
		{Speak the First Ideal, \talentSkybreakerGraspName{} key talent }
		{\iconActionDouble}
		{The lightning dances at the tips of your fingers, waiting to have pointed purpose.}
		{Spend 1 Investiture to make a Division attack against a Physical Defense of a target within 60 feet. That attack gains Disadvantage unless you spend 1 Focus to ignore it. The attack deals 2d4 energy damage; the size of the damage dice increases with your ranks in Division. \textit{(As usual, if you hit, add your Division modifier. On miss, you can graze for 1 Focus.)}}
		
\talent{\talentSkybreakerStormName}
		{\talentSkybreakerBoltName{} talent}
		{\iconActionDouble}
		{Dark clouds gather and the Everstorm yearns to be called down.}
		{Spend 3 Investiture to summon a lightning storm. As long as the storm is active, at the end of each round, choose N random characters within 60 feet from you (enemies, allies or NPCs), where N is twice your ranks in Division. Each of them is attacked with a \talentSkybreakerBoltName{} \textit{(see above)}, but you cannot spend Focus to remove the disadvantage from the attack. \\
		During your subsequent turns you can sustain the storm as \iconActionDouble{} by spending 1 Investiture. If you don't, the storm ends. }

