\newpage
\section{Enlightened Stoneward}

\corruptedBelief{I will be there when I'm needed.}{I will prove myself needed.}

\subsection{Philosophy Changes}

With the enlightening touch of \npcSjaAnat{}, the Stonewards no longer passively wait for a time of need. Instead they take proactive actions to seek areas for improvements and show their skills.

At best they are always engaged in their communities, constantly seeking ways to improve things, even if everybody already believed them perfect.

At their worst, they are fabricating calamity after crisis with only goal to prove that they are the best person to fix them.

\subsection{Enlightened Peakspren}

In the Physical Realm, Enlightened peakspren manifest as a small puddles of crem-like mud. Occasionally, they emerge from the puddle as a small man, fully made of constantly dripping crem.

In the Cognitive Realm, their size is much bigger and they are taller than most of the men. They still look like they were made of crem, with their faces being shapeless cremy mass. They tend to leave stains on everything they touch.

\subsection{Drawbacks and Complications}

\talentStonewardKeyName{}, key talent of the Enlightened talent tree tends to generate \iconComp{} more often for the Stonewards, allowing for unfortunate series of events around the Radiant.

Additionally, the GM can request a Discipline check from the Stoneward (\corruptedResistanceDC{}). On a failure, the character is overcame by the temptation to cause some disaster - release their prisoner, destroy their food supplies, leave the door opened, etc.

\newpage
\subsection{Enlightened Talents}

\talent{\talentStonewardKeyName{} (Key)}
		{Bond an Enlightened peakspren}
		{\iconConstant}
		{You seem to be cursed with a bad luck, with strange unlucky accidents happening around you.}
		{Whenever you roll with one or more Plot Dice, add additional Plot Die to the roll. You must use \iconComp{} result if it is rolled on one of them.}
		
\talent{\talentStonewardAddOwnPlotName}
		{\talentStonewardKeyName{} key talent}
		{\iconSpecial}
		{With a little daring, you can now push your luck.}
		{Whenever you make a roll, you can spend 1 Investure to add a Plot Die to it. \textit{(That roll is affected by \talentStonewardKeyName{} talent.)}}
		
\talent{\talentStonewardAddOthersPlotName}
		{\talentStonewardKeyName{} key talent}
		{\iconSpecial}
		{You are always eager to offer an advice, though it's not always a good advice.}
		{Whenever another character is making a roll, you can spend 1 Investure. If you do, you add an advantage or disadvantage on their Plot Die.}
		
\talent{\talentStonewardSilveryBarbsName}
		{\talentStonewardAddOthersPlotName{} talent}
		{\iconReaction}
		{Your presence can distract even the most focused minds.}
		{After an enemy makes a roll, you can spend 1 Investure before it takes an effect. If you do, the enemy is forced to repeat the roll and use the newest result.}
		
\talent{\talentStonewardDisadvantageOthersName}
		{\talentStonewardAddOthersPlotName{} talent}
		{\iconConstant}
		{Your tendency of bad luck seems to affect more and more people around you.}
		{\talentStonewardKeyName{} talent's effects are added to all rolls made by your allies and enemies.}