\newpage
\section{Enlightened Truthwatcher}

\corruptedBelief{I will seek truth.}{I will reveal bleak sooth.}

\subsection{Philosophy Changes}

Past is long gone and irrelevant - only the future matters. Enlightened Truthwatchers are so obsessed with uncovering the upcoming fate they often forget about the presence.

At their best they are skilled advisors, always ready for anything. Or rather - for the one thing that is bound to happen.

At their worst, they become hopeless doomsayers, spreading despair with their prophecies of inevitable end.

\subsection{Enlightened Mistspren}

In the Physical Realm, Enlightened mistspren manifest as red crystaline structures that drip red light upwards.

In the Cognitive Realm, they look like a red mist shaped into a humanoid form. Instead of faces, their heads are marked with swirling red void.

\subsection{Drawbacks and Complications}

The visions that Enlightened Truthwatchers experience are often too much for a mortal mind to handle. After showing the vision, the GM can request a Discipline check from the Truthwatcher (\corruptedResistanceDC{}). On a failure they loose 1 Focus. If they have no Focus left, they become Stunned for 1 round.

The GM can send them visions without Knight's active attempts to see anything.

\subsection{Enlightened Talents}

\talent{\talentTruthwatcherFutureSightName{}(Key)}
		{Bond an Enlightened mistspren}
		{\iconSpecial}
		{Cryptic visions descend upon you, showing you what might happen.}
		{Once before a rest you can ask the GM about a specific event in the future. The GM can show you a vision containing most probable outcome, abstract symbolic images, mere impressions or feelings, or even some false information. It is up to the GM how truthful or specific the vision will be, though they can ask you for Illumination test (to determine how well you can control your powers) or for Deduction test (to see if your character was able decipher the meaning).}

\newpage		
\talent{\talentTruthwatcherGlimpseFutureName}
		{Speak the First Ideal; \talentTruthwatcherFutureSightName key talent}
		{\iconSpecial}
		{Your visions allow you to determine what is not supposed to happen.}
		{Once per round after you roll the dice for a test, you can spend 1 or more Investiture to reroll that many of the test’s dice.}

\talent{\talentTruthwatcherAlterFortuneName}
		{\talentTruthwatcherGlimpseFutureName{} talent}
		{\iconReaction}
		{You see the outcome of the events before they could even start.}
		{Each time you finish a long rest, roll a number of d20s equal to 1 + your tier, and record each result. \\
		When an enemy or willing ally you can sense makes a test, you can use a reaction to replace the test’s d20 roll with one of your recorded numbers. You can replace that number after you see their die roll and after they apply any advantages, but you must do so before the effects of the test are resolved. \\
		Each recorded number can be used only once. When new set of numbers is rolled, all previous ones are lost.}
		
\talent{\talentTruthwatcherSearchPastName}
		{Speak the First Ideal; \talentTruthwatcherFutureSightName key talent}
		{\iconSpecial}
		{Sometimes to uncover the future one must unravel the past long forgotten.}
		{Once before a long rest you can choose a past event you know of and make a Lore skill check (DC set by the GM based on how long ago the event happened and on how familiar you are with it).\\
		If you succeed, you are shown the vision of the event as though you were there. You are only the observer and you cannot affect the events of the vision.}
		
\talent{\talentTruthwatcherVisionVoidName}
		{\talentTruthwatcherGlimpseFutureName{} talent or \talentTruthwatcherSearchPastName{} talent}
		{\iconConstant}
		{Your powers shield you from the enemy's sight.}
		{You and each ally within your spren bond range are immune to any enemy effect that would reroll or replace the result of any die rolled by you or those allies.\\
		Additionally, if you’re present in or strongly influencing an event, no enemy can ever see visions of that event.}