\newpage
\section{Enlightened Willshaper}

\corruptedBelief{I will seek freedom.}{I will revel in freedom.}

\subsection{Philosophy Changes}

What is the point of freedom if you don't indulge yourself in the pleasures of free people? Enlightened Willshapers celebrate every day to feel they are truly alive.

At their best they are jovial and joyful, capable of lifting anyone's spirit even in the gloomiest of times.

At their worst they are unreliable addicts wasting their lives and fortunes in an endless indulgence.

\subsection{Enlightened Lightspren}

In the Physical Realm, the Enlightened lightspren manifest as small black balls pulsing with darkness and leaving a smoke trail as they move.

In the Cognitive Realm, their matte metallic skin is covered in rust and patina. Streams of black smoke rise from the rusty tears in the metal.

\subsection{Drawbacks and Complications}

Enlightened Willshapers are slaves to their own desires. The GM can ask a Willshaper for a Discipline check (\corruptedResistanceDC{}). On a failure, the Willshaper loses \iconAction{} this round as they are indulging themselves if revelry activities (e.g. feasting on food) and they cannot contribute in a conversation or an endeavor scenes this round.

\subsection{Enlightened Talents}
\talent{\talentWillshaperFreeMoveName{} (Key)}
		{Bond an Enlightened Lightspren}
		{\iconConstant}
		{Nobody will tell you where you can or can't go!}
		{You are immune to being Slowed and Exhausted, and you are unaffected by difficult terrain caused by rocks, crem, or similar obstacles. You can spend 1 Investiture to grant the same bonus to a character you touch as an \iconAction{}.}


\newpage		
\talent{\talentWillshaperCallName}
		{First Ideal; \talentWillshaperFreeMoveName{} key talent}
		{\iconActionDouble}
		{Come! Join us! We have wine!}
		{Make a Persuasion test opposed by a Discipline test of a character you can influence within 90 feet. If you succeed, the target loses 2 Focus, and the first action the target takes on their next turn must be the Move action to approach you by the most direct route. They can’t willingly move away from you on that turn.}
		
\talent{\talentWillshaperImpulseName}
		{\talentWillshaperCallName{} talent}
		{\iconAction}
		{Hey! What do we have here?}
		{Chooses up to two targets you can influence within 60 feet. Those characters must each make a Discipline test (\corruptedResistanceDC{}). On a failure, they lose \iconActionDouble{} during their next turn as they indulge themselves in revelry activities (searching for food, feasting, etc).}

\talent{\talentWillshaperFiremossName}
		{\talentWillshaperCallName{} talent}
		{\iconActionDouble}
		{You grind the firemoss and inhale its smoke.}
		{Spend 1 Investiture to regain up to 6 Focus. Can be used only once per scene.}
	
\talent{\talentWillshaperInhibitionsName}
		{\talentWillshaperCallName{} talent}
		{\iconConstant}
		{Come on! Just one more glass...}
		{Your attacks cause the target to lose 1 Focus on hit. At any time you can spend 1 Investiture to cause all characters who have remaining Focus equal to 1 + 1 for each of Enlightened Talents you have (including yourself and your allies) to have disadvantage on Discipline tests until the end of next round.}