\newpage
\section{Enlightened Windrunner}

\corruptedBelief{I will protect.}{I will eliminate threat.}

\subsection{Philosophy Changes}

Enlightened Windrunners recognize that focusing on defense and protection is doomed to failure - sooner or later they are bound to make a mistake and someone will pay an ultimate price for that. Instead, they focus on quick and efficient threat elimination to ensure safer world for everyone.

At their best they are formidable warriors who eagerly deal with the biggest dangers on the battlefield.

At their worst, they turn violent, hostile to everyone and unable to stop themselves from bloodshed.

\subsection{Enlightened Honorspren}

In the Physical Realm, the Enlightened honorspren manifests like a small man made from an orange light, leaving red glow behind as they move.

In the Cognitive Realm, they keep that appearance, though they grow to a size of a grown man. Their eyes look like pools of blood dripping streams of scarlet tears on their cheeks.

\subsection{Drawbacks and Complications}

Enlightened Windrunners tend to loose themselves in the heat of battle. If they seem to avoid fighting during a battle, the GM may request a Discipline check (\corruptedResistanceDC{}). On a failed check, the Windrunner cannot move away from their enemies and they must make a Strike action this turn (even if that would mean striking an allay).

\newpage
\subsection{Enlightened Talents}

\talent{\talentWindrunnerKeyName{} (Key)}
		{Bond an Enlightened honorspren}
		{\iconReaction}
		{Don't stop! Don't think! Fight! Keep the momentum!}
		{Spend 1 Focus to prevent from being moved or knocked Prone.}
		
\talent{\talentWindrunnerLashOutName}
		{Speak the First Ideal; \talentWindrunnerKeyName{} key talent}
		{\iconReaction}
		{Are you threatening me?!?}
		{Spend 1 Focus after the you are attacked by an enemy within 5 feet of you. You can attack that enemy.}
		
\talent{\talentWindrunnerBerserkName}
		{\talentWindrunnerLashOutName{} talent}
		{\iconFreeAction}
		{I WILL KILL YOU ALL!!!}
		{Spend 2 Focus. Your next Strike targets each character within 5 feet of you and deals an extra 3 (1d6) damage on a hit.}
		
\talent{\talentWindrunnerEnhanceName}
		{Speak the First Ideal; \talentWindrunnerKeyName{} key talent}
		{\iconAction}
		{This light will be the last thing you will see before your death.}
		{Spend 1 Investure to become Enhanced [Strength +1] and Enhanced [Speed +1] until the end of your next turn. This temporarily increases each of your Physical skills by 1, including attack and damage rolls. At the end of each of your turns, you can spend 1 Investiture to maintain this effect for an additional round.}

\talent{\talentWindrunnerStrikeName}
		{\talentWindrunnerEnhanceName{} talent}
		{\iconConstant}
		{Just! Die! Already!}
		{You can strike an additional time on your turn.}		
