\section{Execution}
\label{sec:execution}

Start this section by reading the following:

\quoteBox{
	You see \npcTroublemaker{} rushing towards you. "The ardent!", she gasps. "They are executing her!", she adds before running towards the execution stage. You see more and more people rushing in that direction.
}

The PCs are expected to follow the crowd, in which case, proceed to \fullref{ssec:executionExcitement}.

If the characters decide to ignore this event, the next thing they know are riots starting in the city. Proceed to \fullref{sec:riotsStarting}, but don't describe things that could be experienced only at the gallows.

\subsection{Excited Populace}
\label{ssec:executionExcitement}

when the characters reach the execution site, read the following:

\quoteBox{
	The crowd here is growing with every minute. \\ \\
	"Finally, something is happening in this city", says someone. "We haven't got any proper execution since that meat thief guy!" \\ \\
	"Nah, they cannot kill her!", someone answers. "She did nothing wrong, she was right, actually..."
}

Give the characters some time to react to the crowd or perhaps come with some plan. Their attempts to stop the execution will not succeed, but they might help them attract spren or complete other goals.

Once there is nothing more the players wish to do, proceed to \fullref{ssec:executionVerdict}.

\reasonBox{
	\npcRebelArdent{}'s execution is a pivotal moment in the story, sparking the riots and as a result all future events. Reward players' planning and good rolls, but do not allow them to free \npcRebelArdent{} or stop the hanging.
}



\subsection{Queen's Verdict}
\label{ssec:executionVerdict}

Once it seems the characters are ready for the situation to unfold, read the following:

\quoteBox{
	The ardent is brought by palace guards and queen's faithful. She is placed right below the gallows' noose, while a fat ardent unrolls a scroll and starts reading the verdict: \\ \\
	
	"We are here to resolve a case of Ardent \npcRebelArdent{} from the Devotary of Denial. She is charged with crimes of l\`ese-majest\'e, heresy, and an attempt to refound the Hierocracy. \\ \\
	
	"The queen in her mercy decided to grant a royal pardon for all the insults from the mouth of the charged. However, the crimes of heresy and Hierocracy affiliation are too severe to be ignored. Therefore, you are sentenced to death by hanging. May the Allmighty have a mercy on your soul!"
}

The crowd is unhappy with the verdict. Some of them boo, others throw rotten food on the guards. However, they are not actively hostile yet.

Give the characters some time to react. They won't be able to stop the execution, but their actions may affect their future story.

After a brief moment, read the following:

\quoteBox{
	One of the ardents escorts \npcRebelArdent{} on the box, another puts a noose on her neck. She is calm and serene, accepting her fate with pride. Soon after, the rope jerks, and ardent \npcRebelArdent{} is no more...
}

\spoilerBox{
	Hanging \npcRebelArdent{} by the order of \npcQueen{} is referenced in \bookOB{}, Chapter 62: Research.
}



\subsection{Aftermath}

Immediately after hanging of \npcRebelArdent{} proceed to \fullref{sec:riotsStarting}.