\section{Growing Unrest}

After the events of \fullref{sec:peoplesHall}, give the characters full day before starting \fullref{sec:execution}. The PCs can follow their goals, continuing encounters from \fullref{sec:kholinarLife}, with small changes in the general atmosphere:

\begin{itemize}
	\item Common folk discuss the accusations \npcRebelArdent{} painted in the People's Hall
	
	\item Some people declare \npcRebelArdent{} a sower of discord, accusing her of being irresponsible and her manifesto groundless (see \fullref{ssec:unrestLoyal})
	
	\item Some people blame incompetent ardents who lost their faith for all of this situation (see \fullref{ssec:unrestHeretic}) 
	
	\item Others, very carefully, agree with the ardent, blaming \npcQueen{} for all the problems in the city (see \fullref{ssec:unrestTreason})
\end{itemize}

Allow at least one comment from each group slip into PC's encounters with NPCs, to show various range of opinions spreading through the city. After that, when full day have passed, proceed to \fullref{sec:execution}.



\subsection{Blaming \npcRebelArdent{}}
\label{ssec:unrestLoyal}

When roleplaying NPCs believing \npcRebelArdent{} was wrong, you can use the following quotes:

\begin{itemize}
	\item She shouldn't have written that... No, she shouldn't have...
	\item That girl must have something wrong with her head...
	\item Unbelievable... To write such things...
	\item We're at war, doesn't she know that? We cannot turn on each other now...
	\item All this Weeping without the Highstorms must have made her insane!
\end{itemize}

\subsection{Heretic Thoughts}
\label{ssec:unrestHeretic}

When roleplaying NPCs loosing their faith in the city ardents, you can use the following quotes:

\begin{itemize}
	\item Those ardents should be locked in their monastery, I tell you!
	\item The ardents play the nobles' game far too long, they don't care about us, the common folk!
	\item It is Hierocracy all over again, mark my words!
	\item They can't control their own people, someone should show them where's their place!
	\item She blames the queen, but I blame the ardents. They are supposed to guide her, aren't they?
\end{itemize}

\subsection{Treasonous Whispers}
\label{ssec:unrestTreason}

When roleplaying NPCs who blame the queen, you can use the following quotes:

\begin{itemize}
	\item That ardent is right, the queen has forgotten us...
	\item \npcDeadKing{} at least cared about this city...
	\item Where are the Beggars' Feasts, hm? Where are they...?
	\item I'm hearing some rumors, the palace steals our food just to throw it away! No, really, it's true!
	\item I was told the queen is not faithful - neither to the Allmighty, nor to her husband!
\end{itemize}
