\section{Riots at the Gallows}
\label{sec:riotsStarting}

After \npcRebelArdent{} is executed, read the following:

\quoteBox{
	"She was innocent and you know it!", someone from the crowd shouts to the ardents. Another throws something disgusting at the guard, who gets hit right in the face. \\ \\
	"That's enough, you scum!", he bellows as he draws his sword and approaches the commoner.
}

Riots started at the Kholinar gallows. Play a few scenes from the list bellow, before you proceed to the next section: \fullref{sec:stormingPalace}.



\subsection{Guard's Blood}

You can start with the scene below:

\quoteBox{
	With one slash of the sword, the guard cuts helpless men in half, his blood gathering in a scarlet pool on the stone. Everyone around is shocked, but only for a second. In the next moment angry mob is charging the guard standing in their midst.
}

One \enemyQueensGuard{} is attacked by five \enemyRioter{}s. It is too late to calm any of the sides down, they are ready to kill each other and they will not run from the fight. The characters can join the fight to help one of the sides.



\subsection{Ardent in Danger}

Nearby, the PCs can witness another scene:

\quoteBox{
	You can see furious rioters pulling one of the ardents from the gallows stand. Another man of the faith wanted to pull him back, but in the end both of them ended up falling from the wooden platform. Now, they are surrounded. "You will die just like her!" one of the rioters shouts.
}

Two Ardents (use \enemyCultistOfMoments{}, no variant, stat block) are surrounded by six \enemyRioter{}s ready to dismember them. One of them is Prone. If the PCs wish, they can join the fight for any of the sides. The \enemyRioter{}s will not stop, until the Ardents are slain.



\newpage
\subsection{Dangerous Accusation}

If the PCs have sided with the Ardents or \enemyQueensGuard{}s since their arrival at the gallows, read the following:

\quoteBox{
	"Hey, and who are you?!?", one of the rioters shouts to you. "Are you with them???" \\ \\
	Soon more of them turn towards you, hatred in their eyes.
}

The PCs are attacked by eight \enemyRioter{}s who will fight until death. Any character who wishes to flee may attempt a \skillCheck{12}{\skillStealth} test to hide in the crowd.



