\section{Storming the Palace}
\label{sec:stormingPalace}

Once there was enough encounters played at the gallows, read the following:

\quoteBox{
	Through the chaos rising at the plaza, suddenly you hear angry voices: \\
	"It's all queen's fault!" \\
	"She stole our food!" \\
	"Down with the queen!"\\
	Suddenly, whole shapeless mass of people moved, running towards the palace.
}

Angry mob is storming the Kholinar Palace. If the PCs don't join them immediately, add the following:

\quoteBox{
	From the moving crowd one hand reaches to you. \npcTroublemaker{} catches your arm: \\
	"Come on! We're gonna get her!", she manages to shout before the wave of people pushes her forward.
}

If the characters wish to protect \npcTroublemaker{}, they should follow the crowd towards the palace - proceed with the events of \fullref{ssec:stormingPalaceGates}. 

If they decide they should probably flee somewhere safer, skip the palace part and proceed to \fullref{ssec:stormingPalaceFlee} (just make it happen on the streets of Kholinar, not inside the palace).



\subsection{Palace Gates}
\label{ssec:stormingPalaceGates}

When the PCs reach palace gates, read the following:

\quoteBox{
	You arrive with the mass of rioters at the palace entrance. The angry mob charged without thinking at fully armed guards, while the others forced the gates open. For a short moment, you think you see \npcTroublemaker{} rushing inside with the others
}

There are two \enemyQueensGuard{}s here, each of them is fighting with numerous \enemyRioter{}s. The PCs may join the fight if they wish to gather better weapons. They can also rush after \npcTroublemaker{} inside the palace - in that case, proceed to \fullref{ssec:stormingPalaceHalls}.



\subsection{Palace Halls}
\label{ssec:stormingPalaceHalls}

When the PCs enter the palace to find \npcTroublemaker{}, read the following:

\quoteBox{
	You find \npcTroublemaker{} deep inside the palace corridors. She's standing over the dead guard and dozen of dead rioters, bloodied sword in her hand. \\ \\
	"Hey, over here!", she waves and grins to you, her face red with blood. "We've got one". \\ \\
	Her joy is short-lived. Soon after, another guard runs in from behind the corner.
}

If the characters decide to flee, continue to \fullref{ssec:stormingPalaceFlee}.

If the characters decide to stay, they will face \enemyQueensGuard{}. Every round or two, allow another \enemyRioter{} to join the fight. Once the combat is resolved, if it wasn't enough to scare the PCs off, read the following:

\quoteBox{
	You hear more heavy steps running from the inside of the palace. "Over there!", you hear the guard's voice "More of those filth is in this corridor!" \\ \\
	You realize there is too many of them. "Oh storms!", pale \npcTroublemaker{} cries, drawing fearspren. "They will storming kill us all...!"
}

The party must grab \npcTroublemaker{} and run away. Proceed to \fullref{ssec:stormingPalaceFlee}.

\subsection{Run For Your Life!}
\label{ssec:stormingPalaceFlee}

The characters must flee from the incoming palace forces. Run this as an Pursuit Endeavor with starting distance of 2 and escape distance of 5. Once the party reaches the escape distance, they will need to find some safe room to hide inside.

If the Pursuit distance is reduced to 0, allow \enemyQueensGuard{} one free attack against one of the characters, but don't end the scene - allow them to still run away.

If at least one of the players started attracting an Enlightened Radiant spren, they will actively help during this scene. Award the party one free success in the endeavor. Also, at the end of the Pursuit, they will show the party the best room to hide in.

Once the characters are safely hidden from the palace guard, proceed to \fullref{sec:sjaanatIntroduction}.

\reasonBox{
	This entire scene is a setup for a meeting with Sja-Anat. The players cannot fail here, the meeting must happen as it enables all future events. If your players are having a bad luck in this scene, give them some help in a form of additional rioters appearing or simply spawning the proper room behind a corner, and allowing the guards to never see the party entering it, regardless of the Pursuit results.
}

