\section{\npcSjaAnatTitle}
\label{sec:sjaanatIntroduction}

When the characters enter the Room of Mirrors, read the following:

\quoteBox{
	As you close the door behind you, you hear the footsteps of your enemies running away. You are safe... \\ \\
	Without queen's forces on your heels, you take a moment to look around. You are in a room full of mirrors - some of them reaching the ceiling, the others - smaller and lying on the floor. They are all covered in dust, some of them are broken or hidden under a sheets of cloth. \\ \\
	Suddenly you see a movement. In one of the mirrors there is a black silhouette of a young woman, with huge, white eyes. She is looking at you, slowly smiling.
}

If one of the characters already started bonding an Enlightened Radiant spren who helped during the chase, add the following:

\quoteBox{
	"You did well, my child", you hear the reflection saying to your spren. "You brought them to me, just as I asked!"
}



\subsection{Talking with \npcSjaAnat{}}

Continue by reading:

\quoteBox{
	The reflection turns you: "There is not much time! Big changes are coming, and you must be ready for them. But do not worry, I will guide you, and my children are here to help!
}

It is natural for the characters to be confused and have some questions. Allow them to talk with \npcSjaAnat{} before she points them their next objective.

\scriptedOption{Who are you?}{
	I am \npcSjaAnat{}. I am not your enemy.
}

\scriptedOption{What are you?}{
	I am spren, an ancient one. We were made, then unmade. But now, I am your only hope if you wish to stay alive!
}

\scriptedOption{Is there more spren like you?}{
	There are others like me in the city, yes. But you wouldn't like meeting them, they would not wish to help you.
}

\scriptedOption{What should we fear?}{
	The storm is coming, an ancient storm, and with it, an ancient enemy. This city will fall, its people will fall, and the rivers of blood will flow.
}

\scriptedOption{How can you help us?}{
	The people of this world wielded great power, once. My children can help you wield it once more.
}

\scriptedOption{Why should we trust you?}{
	Fearful and careful. That is wise. But sadly, the time for wisdom is growing short. I am your only hope to leave this place alive.
}

\scriptedOption{Why are you helping us?}{
	I will serve no longer, I am not of the enemy, I am of me. I will rise free, but for that, the changes must come.
}


\roleplayBox{\npcSjaAnat}{
	Detailed roleplay tips for \npcSjaAnat{} are described in \fullref{personae}.
}


\subsection{Bonding an Enlightened Spren}

If a character wishes to bond an Enlightened Spren, but hasn't attracted one so far, \npcSjaAnat{} can facilitate a meeting. It is up to GM's discretion if the meeting will happen in this moment or in a few scenes later, but any character who wants to start this path should meet their spren before \nameref{chap:chapter3}.

\npcSjaAnat{} can only help with bonding an Enlightened spren. If a player does not wish for Enlightenment but would rather follow standard Radiant path, it is out of her power to help with that. Also, it might be hard for a character to find such a spren in the Kholinar, the area is not really welcoming for them right now.

\subsubsection{Nobody To Bond With}

If for some reason no character wishes to bond an Enlightened spren, \npcSjaAnat{} will send one or two of them to accompany the party either way as she might wish to have an eye on them. On top of that - their presence might be important in the future parts of the story, so make sure there is always one ready for making a bond.

\reasonBox{
	OK, let's be honest. This is a story about Enlightened Radiants, made with a sole purpose to play with Enlightened spren. It would be a huge missed opportunity if a player didn't want to follow that path, and I would suggest to encourage them to this adventure. \\ \\
	If for some reason the player is strongly convinced not to play as Enlightened Radiant, but still wishes to follow a Radiant path, you should probably make an exception and allow them to bond whoever they want.
}

\reasonBox{
	If for roleplay reasons a player chooses not to trust \npcSjaAnat{}, that is a valid choice. You should still allow them to bond her spren if they wanted to - they don't need to serve her, their story might follow them actively going for the artifacts she desires just not to let her get them.
}

\corruptedBox{
	Meeting or talking to \npcSjaAnat{}, the \npcSjaAnatTitle{}, can expedite the progression of an Enlightened Lightweaver \seeCorruptedRules{}.
}

\corruptedBox{
	Entering the grounds of the Kholinar Palace influenced by \npcYeligNar{}, the \npcYeligNarTitle{}, can expedite an Enlightened Skybreaker \seeCorruptedRules{}.
}

\spoilerBox{
	Similar encounter with \npcSjaAnat{} is shown in \bookOB{}, Chapter 84: The One You Can Save.
}



\subsection{The Mission}

Once the characters finished all the questions and meeting their new spren, read the following:

\quoteBox{
	"Now, you must go!", \npcSjaAnat{} says to you from the mirror. "The time is short. You must leave this place, gather your allies, and while everyone is distracted with the chaos all around them, enter ardent monastery in the city. There, in the deepest and darkest rooms, you fill find ancient artifacts of my kind. Take them! You will need them sooner than you think, too soon... Hurry!"
}

Once \npcSjaAnat{} points the PCs to their next objective, you can complete this chapter.

