\section{Worried Woman}

If you need a plot hook for the characters to proceed to the main part of the adventure, you can read the following:

\quoteBox{
	A young Irali woman approaches you. Her eyes are dark and tired.
	\\ \\
	"Excuse me, are you a sailor?", she asks. "Have you seen my husband? He sailed with Thaylen expedition and should be back by now, but all contact with his ship was lost..."
}

\npcWorriedWife[s] is worried about her husband, \npcCapturedExplorer{}. She offers 50 marks for each character if they can find him and bring to safety. This should give the party a nudge they need to board the ship and start the main part of the adventure. 

\npcCapturedExplorer{} is currently captured by Reshi people and can be found in their village (see \fullref{ssec:imprisonedSailor}).

Players can persuade \npcShinCaptain{} to take them north for expedition search, or they can find another ship sailing in that direction. It is up to you (and players) what solution will be applied to continue the adventure.

Whatever means of travel are secured, this book does not use any NPCs from Kasitor in later chapters. Remember to include them and secure story continuity if there are strong reasons to believe they should appear (eg. ship captain and the crew).


\roleplayBox{\npcWorriedWife{}}{
	\roleplayTips
	{Worried, fearful.}
	{Find her husband.}
	{\npcWorriedWife[s] is an Iriali woman with golden skin and eyes and tattoos. Her golden hair are in messy state, so is her dress.}
	{\npcWorriedWife{} lives in Kasitor. Her husband, \npcCapturedExplorer{} works as a sailor for a Thaylen expedition, but contact with them was lost some time ago. She is terrified about the fate, that could meet the expedition.}
}

\reasonBox{
	You can use another plot hook that would fit better the story of your characters.
	\\ \\
	You can also scatter more information about the lost expedition in this chapter - some gossip in the tavern, or inpatient NPCs in the port.
}
