\section{Landing on \theIsland}

Once the party reaches the Reshi Island, read the following:

\quoteBox{
	You swim slowly though a mist, thick like a crem. You are following a trail of floating wood and once every time, a wave rocks your ship - you are getting closer.
	\\ \\
	And then, you see it. The most breathtaking view you've ever seen in your life. An island before you raised one of it rocks and made... a step? And then another... 
	\\ \\ 
	Soon, you realized the truth - this is not a land. This is a giant beast, tall as a mountain, slowly strolling through the ocean. With each step, waterfalls cascade from his legs, waves crash and the trees shake.
}

\subsection{Fauna and flora}

After the characters disembark, they can have a moment to examine surrounding fauna and flora. Run this part for as long you decide is best for the party. Some characters may be fascinated by exotic life, while others may not pay much attention to it.

Once you believe enough time has passed for characters to enjoy this newly found island, proceed to \fullref{sec:whitespine}.

Before that, the most notable examples for fauna and flora exploration may include:

\scriptedOption{Tai-Na itself}{
	Even after landing, the island makes a big impression. Every few minutes, Tai-Na takes a huge step, whole island shakes, giving birth to enormous waves. Swarms of luckspren fly around its legs all the time.
}

\scriptedOption{Strange red vines}{
	Characters can see thin red vines squeezing through other plants. No skill check can determine what are they, only guesses may come to their minds and none of them correct.
}

\reasonBox{
	The Red Vines will play a major role in the future plot, you can start gently foreshadowing them at this moment.
}

\scriptedOption{Massive trees}{
	No character have ever seen a tree like that! Their strong trunks give perfect support for creeping vines and exotic shalebark, providing food and shelter for various cremling species. Their roots follow the pattern of Tai-Na shell.
}

\scriptedOption{Poisonous rockbuds}{
	Very rare in the east, those rockbuds have vibrant violet coloring. \skillCheck{10}{Lore or Survival} can determine they are poisonous, so it's better not to eat them.
}

\scriptedOption{Clicking and buzzing}{
	While clicking is a pretty common sound for a cremling, wing buzzing is not. \skillCheck{15}{Lore} allows to recall legends about larkins spotted on one of the Reshi Island. Perhaps there are more of them here?
}

\scriptedOption{Clounds of lifespren}{
Lifespren are pretty common around the world. But not in such quantities!
}

\scriptedOption{Pearl-like cremlings}{
	Very small and very pretty, with a carapace shining with a rainbow light, like a small pearl.
}

\reasonBox{
	You can randomize more encounters with fauna and flora if characters are showing more interest in it. You can add some skill checks for some of them, allow for more roleplay, or even introduce some trivial combat encounter if your party enjoys this part of the story.
}

