\section{Wild Whitespine}
\label{sec:whitespine}

Once the characters complete their initial exploration of the Island, read the following:

\quoteBox{
	Angry roar and screams of pain fill the air. On the nearby glade, you see a pack of axehounds in their desperate fight against a furious whitespine. Both sides are wounded and you can see several axehounds lying around, tossed by the beast. Their carapace is broken, blood painting the ground as they are whimpering, waiting for death.
	\newline \newline
	Nearby, a herdazian man is crawling away from the battle, his leg badly hurt. "Help me!", he begs.
}

Fighting in the lush glade, \enemyWhitespine{} and a pack of 5 \enemyAxehound{}s can be spotted. Behind the pack \npcMedic[s]{} takes cover, clearly wounded in the leg. Start a combat scene, with Axehounds and \npcMedic{} fighting on the side of the players. \enemyWhitespine{} fights to the death.

\roleplayBox{\npcMedic{}}{
	\roleplayTips
	{Ambitious, compassionate.}
	{Heal his patients, no matter the cost.}
	{\npcMedic[2] is a Herdazian man with broken leg. He wears dirty and ragged cloths.}
	{\npcMedic{} is stranded on a Reshi Island along with \npcBabsk{} and \npcSickGirl{}. He is determined to heal the sick girl, regardless the price. \\
		His second priority is to improve his medical skills to make sure his patients won't need to suffer anymore.
	}
}

\subsection{Battlefield Effects}

The following effects are active for this combat:

\scriptedOption{Vine Overgrowth}{
	The area is covered in thick overgrowth, making most of the battlefield a difficult terrain.
}

\scriptedOption{Jungle Trees}{
	Characters can climb the nearby trees to avoid the dangers of the fight (\skillTreeClimb{}). While on a tree, a character makes all attacks with disadvantage, but attacks against them are also made with disadvantage.
}

\subsection{Opportunities And Complications}

\oppCompTable{
	\oppCompRow{\iconOpp[15pt]}{Axehounds disorient the Whitespine. It will attack one of them next time. }
	\oppCompRow{\iconComp[15pt]}{Whitespine's attention shifts towards you. It will attack you next. }
}

\newpage % manual newpage to micromanage page layout
\subsection{Larkin Threat}

If a player tries to spend Investure for their ability, read the following:

\quoteBox{
	The man turns his sight toward you, eyes wide in terror. "Don't!", he shouts. "It will attract them!"
}

If a player doesn't heed the warning, read the following before spawning \enemyLarkin{}, attacking the player:

\quoteBox{
	Suddenly, the air is filled with whirring sound. The next second, a Larkin darts towards you from the tree crown, its jaw clicking frantically as it starts feasting on your Stormlight.
}

\reasonBox{
	\npcMedic{} suffering a leg wound is taking major part in the plot ahead. Players can cover it and try to help with it, but do not allow to fully heal it, eg. with Radiant powers. Use \enemyLarkin{}s if you need to interrupt supernatural healing.
	\newline \newline
	Even if players don't attempt healing the wound with Investure, but try to spend it in any other way, spawn \enemyLarkin{} regardless. That will teach them about consequences of using Investure and will discourage them from healing attempts in the future.
}

\subsection{Afermath}

\enemyWhitespine{} fights to the death. \npcMedic{} survives, as well as a few of \enemyAxehound{}s from the pack.

\npcMedic{}'s leg is clearly broken, with a white bone piercing through the bloodied skin. It cannot be fully healed due to \enemyLarkin{}s waiting to drain the Stormlight, but characters can attempt to bandage it to prevent blood loss.

\npcMedic{} thanks the characters for their help and invites them to his camp. Proceed to "Safe Camp".

\reasonBox{
	\enemyWhitespine{} could be a lethal challenge for low-level characters alone. This fight is not designed to kill any of the PCs. When one of the players takes too much damage, allow the enemy to focus on the \enemyAxehound{} pack.
	\newline \newline
	The same \enemyWhitespine{} appears later in the adventure as a \enemyReanimatedWhitespine{}, so make sure it is slain. If the fight goes poorly for the players, consider ending the fight with one of the NPCs killing the creature, probably adding to the damage dealt before players entered the scene. For similar reason, make sure the players see some of the slain \enemyAxehound{}s
}

\ptrBox{
	Rushing to protect \npcMedic{} may attract a honorspren. Attempts to heal or bandage his leg may attract a cultivationspren.
}