\section{Final Confrontation}

When the party returns to the camp with the specimen samples, \npcMedic{} rushes to study it, listening to what the characters learned from the Reshi. After some time (eg. while the characters rest a moment after), read the following:

\quoteBox{
	You hear heated argument nearby \npcSickGirl{}'s bed. \npcMedic{} stands above her with a vial of red liquid, thin vine reaching towards the edge of the glass. Between him and the sick girl stands \npcBabsk{} with a knife drawn.
	\\ \\
	"You can't do it to her!", he shouts. "There must be another way!"
	\\ \\
	"You fool, there is no other way! She will die without my help!"
}

Characters can enter the argument, supporting either of the sides. When they do, the person they choose to help will not attempt any skill checks. If characters choose to stay neutral, assume that \npcMedic{} was able to succeed and follow with his idea.


\conversationDefence{\npcMedic{}}{16}{13}{5}
His motivation is to help suffering people and to learn more about ways of helping them.
\conversationEnd{\npcMedic{}}{2}


\conversationDefence{\npcBabsk{}}{13}{16}{4}
He deeply cares about \npcSickGirl{} and he wants to respect her dignity.
\conversationEnd{\npcBabsk{}}{2}

\reasonBox{
	There are no good choices for this dilemma, whatever the players do will turn against them. Do not let them think they accomplished something here. Instead, motivate them to do even more.
}

\subsection{Siding with \npcBabsk{}}

If the party convinces \npcMedic{} to abandon his idea, \npcSickGirl{} will not be saved. Read the following:

\quoteBox{
	\npcSickGirl{} growls silently. You turn towards her to see her exhaling her last breath. Her chest stops moving, her eyes stop twitching with pain. 
	\\ \\ 
	Her loyal axehound pokes her with her nose, clicking sadly with mandibles. She tries to wake her up, but the girl will wake up no more...
}

\npcMedic{} is furious that the characters allowed the poor girl to die when they could save her. He walks away and does not wish to speak with the party anymore.

\subsection{Siding with \npcMedic{}}

If the party convinces \npcBabsk{} to trust \npcMedic{}, read the following:

\quoteBox{
	\npcSickGirl{}'s fingers twitch gently. Soon, she opens her eyes while a thin red vine pierced her skin, entwining with her Thaylen eyebrows. She slowly sits up, with another vine blooming through her eyes. 
	\\ \\
	She looks around, but in her eyes there is no recognition of the people around her, only black emptiness. Her loyal axehound clicks nervously with her mandibles and readies herself to pounce on her former mistress.
}

Soon, dying \npcSickGirl{} turns into \enemyReanimatedPerson{} and attacks the party. Due to young age of the girl, consider the enemy to start with only half of the health. \npcBabsk{} cannot forgive you that you turned his pupil into a monster.
