\chapter{Chapter 7 - TODO - Kharbranth}
\label{chap:chapter7}

\setcounter{section}{-1}
\section{Running This Chapter}

The characters reached \locationKharbranth{}. They will need to solve a mystery lurking in the city hospitals. When they reach \npcTaravangian{}, they will need to convince him to let them travel together to Urithiru.

Run the entire chapter as a big, ongoing Discovery Endeavor. The party will need to investigate a web of clues to reach their final goal. Since the web is not linear, there will be several paths leading there.



\subsection{Character Advancement}

The characters start this chapter at level 8. Advance them twice in this chapter: once after they enter the Palanaeum and once at the end of the chapter.

The following events may affect their path to radiance:
\begin{itemize}
	\item Remembering fallen citizens of \locationKharbranth{}
	\item Unveiling lies and secrets of the Diagram hospitals
	\item Ddeath Rattles and the presence of \npcMoelach{} may expedite an Enlightened Truthwatcher.
\end{itemize}

Killing a Soulcaster in \fullref{sec:vorinMonastery} will allow a PC to use his fabrial.

In \fullref{sec:conclaveHospital}, the PCs can obtain \abilityFutureKnowledgeName[1]{}.



\subsection{Forging Alliances}

During the events of this chapter, the party will have an opportunity to increase relations with more powerful allies. However, gaining one ally will mean gaining one enemy as well...

\begin{itemize}
	\item Saving Ghostblood agent will help to secure alliance with this organization
	\item Assisting Diagram operatives may grant access to their knowledge
\end{itemize}



\subsection{Storm Patterns}

The party starts this chapter without any Investure available. However, in one of first scenes a Highstorm will renew their reserves.

This book will not offer more Highstorm scenes. You can assume they appear regularly now, blowing from east every 1d6~+~6 days (roll new value after each passing storm). You can also skip tracking them and just assume the Stormlight will be available in abundance.

Similarly, this book will not provide information about the Everstorms. Assume they appear every 9 days and that the next one is expected in 1d8 days.

\reasonBox{
	In \bookOB{}, Highstorms return right before \npcTaravangian{} arrives to \locationUrithiru{}, which aligns with the story of \nameref{chap:chapter8}. However, it feels wrong to limit Radiant potential two chapters in a row and therefore, for the gameplay reasons, I decided to include them in this chapter. If you want to stick to the lore, feel free to skip them in here.
}


\subsection{Language Barrier}

In \locationKharbranth{} not everyone speaks alethi. The elites (nobles, surgeons, scholars) recognize Alethkar as a major power and decided to learn their language, but common folk speak only \locationKharbranth{}ian. 

If no PC in the party has an expertise in this culture, they might have trouble communicating without a hired translator.


\subsection{Policing Forces}

\locationKharbranth{} is patrolled by small groups consisting of four \enemyDiagramMuscle{}s each. When the party attack a citizen for any reason, they will appear on the scene during the next round of fight, defending the civilian and allowing them to flee.

\newpage

% \input{chapter_7/theWeb.tex}

\input{chapter_7/pathToKharbranth.tex}
\input{chapter_7/kharbranth.tex}
\input{chapter_7/cityHospital.tex}
\input{chapter_7/theManor.tex}
\input{chapter_7/vedenCamp.tex}
\input{chapter_7/vorinMonastery.tex}
\input{chapter_7/graveyard.tex}

\input{chapter_7/palanaeum.tex}
\input{chapter_7/conclaveHospital.tex}
\input{chapter_7/taravangian.tex}




\section{Journeying Onward}

After the events of \fullref{sec:conclaveHospital}, reward the party:

If they joined the Diagram, each of them will be granted \abilityFutureKnowledgeName[2] by \npcTaravangian{}. He will invite them to join him in his journey to \locationUrithiru{}.

If they saved \npcGhostbloodWounded{} instead, he will give each of them a \lootScadrialCoin{} and say that his boss will respect those as a currency. They can meet him in \locationUrithiru{} - luckily, it seems that \npcTaravangian{} is traveling there any time soon and the Ghostbloods can help the party to sneak in.

In any case, advance the PCs to level 10 and proceed to the next chapter.


