\section{Common Hospital}
\label{sec:cityHospital}

When the PCs enter the hospital, read the following:

\quoteBox{
	A man in a surgeon apron approaches you. "Hello, I am dr \npcDiagramSurgeon{}. How can I help you?"
}

In here the surgeons of \locationKharbranth{} triage and treat their patients. If a PC is wounded or injured, the healers will invite them to stay for a treatment - see \fullref{sec:cityHospitalTreatment}.

\reasonBox{
	\npcDiagramSurgeon{} will appear in the chapter finale. To make the final scene more impactful, the NPC can appear in other scenes during party's investigation. In general, if a scene contains a \enemyDiagramSurgeon{}, assume it is \npcDiagramSurgeon{}, unless there is a good reason for him not to be there.
}

\subsection{Hospital Treatment}
\label{sec:cityHospitalTreatment}

While in the hospital, all injuries heal twice as fast. If a character needs prolonged medical care, consider suggesting them playing as a temporary mercenary character.

If a PC enters the hospital alone, they will be triaged as eligible for transfer to \fullref{sec:conclaveHospital}. It is up to you how to handle this thread as this book assumes the party travels together and the surgeons will not risk transferring someone with many connections.



\subsection{Hospital Logs}

Logs of the hospital patients are held by a \enemyDiagramScribe{}. They are accessible only to the hospital personnel and the PCs will be denied access to them.

However, if the party enacts some scheme, heist or con they may gain access to the following logs:

\quoteBox{
	You see a list of patients accepted to the hospital: \\ \\
	Arivish (Port District) - rash - healed \\
	\npcOrphanSick{} (?) - transferred \\
	Korvetal (Bell District) - fever - healed \\
	Lervitar (Guild District) - bad tooth - healed \\
	Ovelgish (Port District) - cold - healed \\
	Lord \npcKharbranthNoble{} - transferred \\
	Navian (Dawn District) - broken arm - healed \\
	Harnial (Star District) - burn - healed \\
	\npcGhostbloodWounded{} (?) - transferred \\ 
	Trilam - (Dawn District) - fever - healed \\
	Baranal (Dusk District) - stab wounds -  \\
	\npcWoundedTrader{} (Trader) - whitespine wounds - 
}

\subsubsection{Clues}

\npcOrphanSick{}, \npcGhostbloodWounded{} and lord \npcKharbranthNoble{} were transferred to another hospital - see \fullref{sec:conclaveHospital}.




\subsection{Tense Surgeon}

As the party is visiting the hospital, allow them for single \skillCheck{15}{\skillInsight{}}. On a failure ignore this section. On a success, read the following:

\quoteBox{
	When you talk with the hospital surgeons, you notice one of them is more tense than the others. It's more than just a concern for their patient's health - your questions are making him nervous.
}

The surgeon knows some secrets he wants to share, but he is terrified of the Diagram's punishment. If prompted by the players, he will say only:

\quoteBox{
	I'm sorry, I cannot talk, my patients need me. Please ask in the apothecary about the next shipment. Now, excuse me, I must go back to work.
}

If the PCs will press the issue, the surgeon will tell no more. Soon after, \enemyDiagramMuscle{}s will intervene and ask politely but firmly not to overstay the hospital's welcome and allow the surgeons to do their work.




\subsection{Following The Surgeon}
\label{ssec:cityHospitalFollowSurgeon}

If the PCs wish to learn more about \npcDiagramSurgeon{}, they might attempt to follow him after his work in the hospital. If they do, they can reach his home in the Bell District.

\subsubsection{Sneak In}

If a PC decides to sneak inside the house, they must make a \skillCheck{TODO}{\skillStealth{}}, rolling against the \enemyDiagramSurgeon{}'s Spiritual Defense. On a failure, \npcDiagramSurgeon{} will rise an alarm - proceed to \fullref{ssec:cityHospitalFollowSurgeonAssault}.

When successfully inside, the PC will see that \npcDiagramSurgeon{} is napping on a bed, while holding a stack of papers he was reading before sleep. The PC can attempt to steal them with \skillCheck{TODO}{\skillThievery{}}, rolling against the \enemyDiagramSurgeon{}'s Spiritual Defense. Again, failure will trigger an alarm.

If the PC passes both tests, they will collect surgeon's notes. Proceed to \fullref{ssec:cityHospitalFollowSurgeonLogs}.

\subsubsection{Assault}
\label{ssec:cityHospitalFollowSurgeonAssault}

The party may decide to attempt intimidation or brute force as a means to extract additional information from \npcDiagramSurgeon{}. Either that or a failed stealthy approach will make him shout in alarm.

When he does, four \enemyDiagramMuscle{} will arrive for the rescue. The surgeon will flee, leaving his notes behind in a rush. After the party wins the fight, they can collect them - proceed to \fullref{ssec:cityHospitalFollowSurgeonLogs}.

If the party ignores the guards and attempts to slain the surgeon, \enemyMalata{} will join the fight protecting the man. Allow the surgeon to run with his life.

\reasonBox{
	\npcDiagramSurgeon{} has a role in the finale of this chapter. While he can be replaced with any other surgeon, it would be nice to have one NPC reappearing in the entire arc of the story, so try to keep him alive.
}

\subsubsection{Conclave Logs}
\label{ssec:cityHospitalFollowSurgeonLogs}

When the party successfully obtains the notes of \npcDiagramSurgeon{}, they will be able to read the following:

\quoteBox{
	Conclave Logs \\ \\
	Patient: \npcOrphanSick{} \\
	Extraction \sout{scheduled} completed. \\
	Deceased. Handed over to ardents. \\ \\
	Patient: Lord \npcKharbranthNoble{} \\
	Extraction \sout{scheduled} completed. \\
	Deceased. \sout{Handed over to ardents.}  \\ 
	Coffin handed over to Lady \npcKharbranthNoble for burial. \\ \\
	Patient: \npcGhostbloodWounded{} \\
	Extraction scheduled
}

\quoteBox{
	Experiment Logs \\ \\
	Sample Quality: \\
	Experiment \#1 - failure. \\
	Experiment \#2 - failure. \\
	Experiment \#3 - failure. \\
	\\
	Radiance: \\
	Experiment \#1 - failure. \\
	Experiment \#2 - failure. \\
	Experiment \#3 - failure. 
}

\subsubsection{Clues}

\npcOrphanSick{} died in the Conclave Hospital. Her body was given to the ardents from \fullref{sec:vorinMonastery}.

\npcKharbranthNoble{} died in the Conclave Hospital - his body was buried on the \fullref{sec:graveyard}.

\npcGhostbloodWounded{} is alive and can be found in \fullref{sec:conclaveHospital}.

The Conclave Hospitals run experiments on Radiance and Sample Quality - see \fullref{ssec:conclaveHospitalBlinding} and \fullref{ssec:conclaveHospitalRadiant}.



\subsection{Conclave Transfer}
\label{ssec:cityHospitalConclaveTransfer}

If the party fails to obtain the \locationPalanaeum{} access during \fullref{ssec:palanaeumPetition}, they will need to find another way to enter the \fullref{sec:conclaveHospital}. One of the ideas may be to wait for another transfer of patients to the Conclave and either track it or sneak inside.

The Diagram uses medical carts to transfer the patients during the nighttime. Each of such carts is filled with sick people (homeless, orphans, drunks and other people  nobody would miss) and is guarded by 4 \enemyDiagramMuscle{}s. Also, one \enemyDiagramSurgeon{} accompanies them each time.

If the party manages to defeat and impostor the guards, or if they successfully sneak behind their watch inside the wagon, the driver will approach the cart soon after. He will drive them up to \fullref{sec:conclaveHospitalEntrance}.