\section{Conclave Hospitals}
\label{sec:conclaveHospital}

The party enters the grounds of the Conclave Hospital. You can run this part of the adventure as a dungeon crawl, though the party might decide not to attack every NPC found in here.

There are two entrances to this area: a heavily guarded \fullref{ssec:conclaveHospitalEntrance} that can be found nearby the \locationPalanaeum{}, and a hidden \fullref{ssec:conclaveHospitalBackdoor} that require some more investigation from the PCs to find.

The goal for the party is to find \fullref{ssec:conclaveHospitalPatient} encounter, which triggers the end of the crawl and completes the story of this chapter.

\reasonBox{
	\textbf{NOTE:} Some of the scenes in this area contain graphic descriptions of violence performed by \locationKharbranth{} surgeons. You can skip them if you find them too gruesome for your players. Please follow the guidelines from \fullref{ssec:playersExpectations} to ensure a comfortable experience for all around the table.
}

\spoilerBox{
	\npcTaravangian{} shows the hospital to Szeth in \bookWOK{}, Chapter 71. Recorded In Blood.
}


\subsection{Guarded Entrance}
\label{ssec:conclaveHospitalEntrance}

As the PCs approach the hospital gate, read the following:

\quoteBox{
	You walk through the dark corridors of the Conclave until you reach a guarded door. The orange glyph indicates it must be the entrance to the hospital. \\ \\
	"You cannot enter here", the guard says. "Go away!"
}

There are four \enemyDiagramMuscle{}s guarding the gate. To enter the Conclave Hospital this way, the party must either defeat the guards or talk their way in.

This entrance leads to \fullref{ssec:conclaveHospitalCorridor}.




\subsection{Backdoor Entrance}
\label{ssec:conclaveHospitalBackdoor}

This entrance is well hidden and the party would need some creative ideas on how to find it. Following the surgeon, a cart transferring patients or the soulcaster might work.

The entrance is guarded by four \enemyDiagramMuscle{}s, but the guards in here don't expect any troubles and they will assume you are working for the Diagram if you know about this entrance.

Through this door, the party can enter \fullref{ssec:conclaveHospitalCorridorOil}.





\subsection{Barrel Corridor}
\label{ssec:conclaveHospitalCorridorOil}

As the party enters this location, read the following:

\quoteBox{
	You enter a long corridor illuminated with a light from sparse spheres. There are barrels of oil standing everywhere, ready for future shipments.
}

There is little to do in here. The corridor connects with \fullref{ssec:conclaveHospitalCorridor}. In the midle, there is \fullref{ssec:conclaveHospitalOil} room.




\subsection{Oil Barrels}
\label{ssec:conclaveHospitalOil}

As the party enters this area, read the following:

\quoteBox{
	You walk through the corridor full of oil barrels until you reach a big room with a huge, barrel-like vessel in the middle, entirely made of stone and surrounded with open, empty oil barrels. Ladders and scaffolding are built around it. \\

	There are people working here to carry corpses on top of the ladders and toss them into the stone barrel. "We must send for the Soulcaster soon", one of them says. "We will reach the top by tomorrow."
}

The party should soon realize that the oil in the city is made by Soulcasters who transform corpses of the dead patients.

There are three \enemyDiagramMuscle{}s in this room. They are focused on their work. If they notice the PCs, they will assume they are here to help them.



\newpage
\subsection{Hospital Corridor}
\label{ssec:conclaveHospitalCorridor}

As the PCs enter this area, read the following:

\quoteBox{
	Long, winding corridor twists and turns under the mountain the Conclave was built in. A few ruby spheres illuminate it with a red light. There are smears of blood on the floor.
}

The corridor is connecting all of the most important rooms in this location:
\begin{itemize}
	\item \fullref{ssec:conclaveHospitalEntrance}
	\item \fullref{ssec:conclaveHospitalArchive}
	\item \fullref{ssec:conclaveHospitalMainRoom}
	\item \fullref{ssec:conclaveHospitalBlinding} \\ \textit{(locked)}
	\item \fullref{ssec:conclaveHospitalRadiant} \\ \textit{(locked)}
	\item \fullref{ssec:conclaveHospitalCorridorOil}
\end{itemize}

There are people walking in here - \enemyDiagramMuscle{}s, \enemyDiagramSurgeon{}s and \enemyDiagramScribe{}s, but nobody pays attention to the players unless they act weird.




\subsection{Sample Archive}
\label{ssec:conclaveHospitalArchive}

When the party enters this room, read the following:

\quoteBox{
	It is a small room, full of files and notebooks cataloged on countless shelves. As you enter, you hear a clerk behind the desk reporting to a man standing before her: \\ \\
	"... and here are the samples from this week. I marked the most promising ones. Those two reinforce the Diagram's predictions. \\ \\
	"I added a note for the king next to this one, I believe it suggests by allying with the Kholins, \npcTaravangian{} will be able to slain Odium. I'm not sure, can a god be slain...?" 
}

Sitting behind a desk, there is \npcDiagramAarchivist{}, a \enemyDiagramScribe{} who manages and archives the collected Death Rattles. A \enemyDiagramMuscle{} is about to carry them to the king.

The PCs can talk with the clerk to find more about the NPCs they are looking for. They can also get access to some of the most promising Death Rattles archived in here. 

In both cases, \npcDiagramAarchivist{} will help them only for as long she believes they work for the king and the Diagram. She will call guards at the first sign if the PCs doing something suspicious.

\reasonBox{
	The Diagram is doing terrible things in the hospitals. But they believe their actions are necessary for the greater good of Roshar. Use this room to show the PCs a Death Rattle proving the Diagram may gain an upper hand in the conflict with Odium so they could consider helping them. Without it, their organization is presented as irredeemably evil, giving the players no real choice while dealing with them. 
}

\subsubsection{Asking about \npcOrphanSick{}}

When the party asks about \npcOrphanSick{}, \npcDiagramAarchivist{} will say:

\quoteBox{
	"One second..., she was from dr \npcDiagramSurgeon{}? We sent her sample a week ago, is there any problem with it?"
}

\subsubsection{Asking about Lord \npcKharbranthNoble{}}

When the PCs ask about Lord \npcKharbranthNoble{}, read the following:

\quoteBox{
	"Yes, I remember this mess... dr \npcDiagramSurgeon{} marked him incorrectly as a commoner. As a result of this confusion we could not provide his wife with a body. I'm sorry, there is nothing we can do at this point, just make sure she doesn't open the coffin... Do you need his sample?"
}

\subsubsection{Asking about \npcGhostbloodWounded{}}

When asked about \npcGhostbloodWounded{}, \npcDiagramAarchivist{} will say:

\quoteBox{
	"Let me check... yes, his extraction is scheduled for today, by dr \npcDiagramSurgeon{}. We should have his sample in a few hours. Can you wait for it?
}

\newpage
\subsubsection{Busy as Ever}

Every now and then, a \enemyDiagramScribe{} will enter with new set of notes. When she does, read the following:

\quoteBox{
	Suddenly, a young woman enters the room, interrupting your Conversation. She carries several sheets of paper. \\ \\
	"Next set of samples?", the woman sitting in the room asks. "Thank you dear, put it in the box with a name of the leading surgeon. Now, where were we...?"
}

\subsubsection{Forbidden Knowledge}

Every PC who gets access to the gathered Death Rattles receive \abilityFutureKnowledgeName[1]{}:

\abilityFutureKnowledge[1]{}




\subsection{Sample Quality Experiments}
\label{ssec:conclaveHospitalBlinding}

The room is locked. A PC must pass \skillCheck{20}{\skillThievery{} or \skillAthletics{}} to open the door. When they do, read the following:

\quoteBox{
	A single, bloodied bed is standing in the middle of the room. Next to it, there is a desk with a quill, some notes and multiple jars. When you come closer you see that all of the jars are filled with eyeballs.
}

There is nobody in the room. The PCs can read the surgeon’s notes from the desk to get a bit more insight of what was being done in here.

\subsubsection{Experiment Notes}

When the PCs investigate the notes, read the following:

\quoteBox{
	As we continue to gather the samples, one must ask a question: is the result dependent on the person’s eyesight? Can their vision influence or obscure the samples? Must design an experiment to prove this hypothesis.
}

\quoteBox{
	Experiment 1: \\
	I created a beam of light from 250 diamond marks enhanced by a system of mirrors and prisms. \\ 
	Test group size: 100. \\
	Results: \\
	No improvement of the gathered sample set observed. Must design another experiment.
}

\quoteBox{
	Experiment 2: \\
	I surgically removed the ocular organs of the patients in the test group. \\ 
	Test group size: 100. \\
	Results: \\
	No improvement of the gathered sample set observed. Must design another experiment.
}

\quoteBox{
	Experiment 3: \\
	I transplanted the ocular organs from the patients yielding promising samples to the testing group.  \\ 
	Test group size: 100. \\
	Results: \\
	No improvement of the gathered sample set observed. Must design another experiment.
}

\reasonBox{
	In the \bookSA{} series, the scene revealing the true purpose of the hospital is shocking and terrifying. My goal is to recreate those emotions in here, even for the players who are familiar with the books and already know that the patients are being killed in here to gather the Death Rattles.
}

\reasonBox{
	This scene is designed for shock factor, but contributes little to overall story. You can cut it if you believe it is too strong for your table, who might not be comfortable with it.
}




\subsection{Radiance Experiments}
\label{ssec:conclaveHospitalRadiant}

The room is locked. A PC must pass \skillCheck{20}{\skillThievery{} or \skillAthletics{}} to open the door. When they do, read the following:

\quoteBox{
	You see a small room with a single desk inside. On the desk, there lies a log book and a chalice full of glowing ruby marks. On the opposite wall, there is another door leading to the next room.
}

There is nobody in this room. The party can read the log notes or proceed to the next room.

\subsubsection{Experiment Notes}

When the PCs investigate the book on the desk, they read the following:

\quoteBox{
	The king believes some people may hold an unimaginable power. "Radiants", he calls them. They are told to command the forces of nature and to be healed by the Stormlight. Any of such individuals may change the tides of the upcoming conflict. We must design an experiment to find or create more of them.
}

\quoteBox{
	Experiment iddeas: \\
	Assuming the Radiants can use Stormlight to heal their injuries, we must provide enough light for them to use. We must also create prolonged conditions of external stimulus that would encourage them to use or develop their powers. Include psychological stimulus by preventing the removal of failed experiments from the chamber.
}

\quoteBox{
	Experiment 1: Flames \\\
	Test group size: 100. \\
	Results: \\
	No Stormlight absorbed. It is possible that the patients expire too fast. Sample collection disturbed. Must design another experiment.
}

\quoteBox{
	Experiment 2: Nails \\
	Test group size: 100 \\
	Results: \\
	No Stormlight absorbed. It is possible that the patients expire too fast. Sample collection disturbed. Must design another experiment.
}

\quoteBox{
	Experiment 3: Spikes \\
	Test group size: 100 \\
	Results: \\
	No Stormlight absorbed. It is possible that the patients expire too fast. Sample collection disturbed. Must design another experiment.
}

\newpage
\subsubsection{Experiment Room}

If the party enters through the door on the opposite wall, read the following:

\quoteBox{
	The room is full of corpses nailed to the walls or impaled on spikes. Many of them are children. Some of them are burned. The bright red light of many ruby spheres illuminates the whole scene.  \\ \\
	As you enter, one young man impaled on a stake whispers to you: "Please... Kill me..."
}

\reasonBox{
	In the \bookSA{} series, the scene revealing the true purpose of the hospital is shocking and terrifying. My goal is to recreate those emotions in here, even for the players who are familiar with the books and already know that the patients are being killed in here to gather the Death Rattles.
}

\reasonBox{
	This scene is designed for shock factor, but contributes little to overall story. You can cut it if you believe it is too strong for your table, who might not be comfortable with it.
}




\subsection{The Bleeding Room}
\label{ssec:conclaveHospitalMainRoom}

When the party enters this room, read the following:

\quoteBox{
	You enter the main room of the hospital: a huge cavity with a balcony above it and many alcoves on both sides. In some of the them, you see a patients being watched closely by the nearby pairs of a surgeon and a scribe. From time to time, the echo in this room carries muffled whispers of the dying.
}

In here the sick are being bled to death in order to obtain their Death Rattles, called "samples" by the personnel of the hospital. Sometimes a \enemyDiagramScribe{} rushes to the archive with the newest sample or a pair of \enemyDiagramMuscle{}s bring another patient on a stretcher.

When the PCs approach any of the alcoves, proceed to \fullref{ssec:conclaveHospitalPatient}.




\newpage
\subsection{Marked for Death}
\label{ssec:conclaveHospitalPatient}

When the PCs reach this area, read the following:

\quoteBox{
	You see an unconscious man lying on a stone bed. His right sleeve is cut off, showing a triangular tattoo, like a three overlapping diamonds. Next to him on the table stands a clean knife and an empty bowl. \\ \\
	"The king predicted we would meet in here. I have waited for you", says \npcDiagramSurgeon{} standing with a female scribe next to the patient. 
}

The party can see \npcGhostbloodWounded{}, a man they were asked to find in \fullref{ssec:kharbranthDarkAlley}. He is about to have his veins cut in order to gather a Death Rattle upon his death.

In the room there are also two people: \npcDiagramSurgeon{}, a \enemyDiagramSurgeon{} and a \enemyDiagramScribe{}. When the PCs approach them, \npcDiagramSurgeon{} will say:

\quoteBox{
	"Their sacrifice is great, but we must do this for the people of Roshar. By the order of the king. And he knew you would find out about this place. You are capable. Do the honor, make the cut, know the future and join the Diagram in our quest of protecting the humanity."
}

\npcDiagramSurgeon{} offers the party to kill \npcGhostbloodWounded{} and join the Diagram, the organization running the hospitals. This is the final confrontation in this dungeon.

The party may accept the offer and kill the helpless man. It is also possible they will kill the surgeon on sight, instead. In any of those case, after an NPC dies, proceed to \fullref{ssec:conclaveHospitalPatientDeathRattle}. 

They can also attempt talking to the surgeon in a Conversation, trying to show him the error of his methods. When they do, proceed to \fullref{ssec:conclaveHospitalPatientConversation}.

If the PCs refuse to participate in the deed without stopping the healer from it, \npcDiagramSurgeon{} will cut the arm of the man himself. Proceed to \fullref{ssec:conclaveHospitalPatientDeathRattle}.

\subsubsection{Conversation with \npcDiagramSurgeon{}}
\label{ssec:conclaveHospitalPatientConversation}

The party may attempt to convince \npcDiagramSurgeon{} that the Diagram is evil and killing the people like this is evil. Run this scene as a Conversation.

\conversationDefence{\enemyDiagramSurgeon{}}{18}{15}{5}. 

He believes that the True Desolation is coming and their actions are the key to finding a way to save the humanity, however evil they were.

\conversationEnd{\npcDiagramSurgeon{}}{1}

If the party fails to convince him, he will again insist that the PCs should join the Diagram and kill \npcGhostbloodWounded{}. If they refuse, he will kill him himself.

If the party convinces him, read the following:

\quoteBox{
	\npcDiagramSurgeon{} looks at you, terrified. "You... you are right...", he says. "Almighty have mercy on us, we killed so many... I killed so many..." \\ \\
	With a smooth motion he grabs the surgical knife and plunges it into his own heart. A moment after, he dies.
}

Once the conversation is over, proceed to \fullref{ssec:conclaveHospitalPatientDeathRattle}.

\reasonBox{
	There is no saving both of them. Someone must die in this scene.
}

\subsubsection{Death Rattle}
\label{ssec:conclaveHospitalPatientDeathRattle}

Either way, the scene ends when an NPC is killed. In that case, read the following:

\quoteBox{
	You see the last remains of life fleeing from the dying man. Soon, his eyes go wide, and you hear his voice: \\ \\
	"I stay on top of the tower, above the Storms. From here, I will unite them! From here, I will rule!"
}

Every PC who could hear the Death Rattle gains \abilityFutureKnowledgeName[1]{}: 

\abilityFutureKnowledge[1]{}

\corruptedBox{
	Hearing the Death Rattle, a prophetic vision granted by \npcMoelach{}, can expedite an Enlightened Truthwatcher \seeCorruptedRules{}.
}

\newpage
\subsection{Aftermath}

After the PCs hear the Death Rattle of the dying man, read the following:

\quoteBox{
	When everything goes quiet again, you hear a voice from the balcony overseeing the hospital room: \\ \\
	"Terrible. Terrible fate, indeed. But as you hear - a necessary evil, an act we must commit to ensure the humanity weathers the storm that is coming..."
}

From the balcony, \npcTaravangian{} was watching over the encounter with \npcDiagramSurgeon{}. In order to complete the story of this chapter, proceed to \fullref{ssec:taravangianDiagram}.

