\section{Graveyard}
\label{sec:graveyard}

In here, the party can ask about the missing people an investigate the most recent deaths. The gravedigger will require some encouragement, though... 




\subsection{The Gravedigger}

The gravedigger is not a chatty man. When asked detailed questions, he will claim that he "cannot recall that, huh!". Some solid bribe might improve his memory though - at that moment, he will be able to answer:

\scriptedOption{Do you have much work?}{
	Nah, less than I'd have in other cities. Healers do their job too well...
}

\scriptedOption{Did you bury a girl named \npcOrphanSick{}?}{
	Nah, there was nobody like that recently...
}

\scriptedOption{Any information about a person named \npcGhostbloodWounded{}?}{
	Nah, there was nobody like that either...
}

\scriptedOption{What about Lord \npcKharbranthNoble{}?}{
	Oh yeah, I remember him! Heavy coffin, terrible weather. We got him over there! Nice fellow, I like his grave.
}

\scriptedOption{Don't you soulcast your nobles?}{
	Yeah, sometimes. He wasn't best friends with the ardents though, he wanted go this way. What a nice guy!
}

\subsubsection{Clues}

Lord \npcKharbranthNoble{} is buried in here.

\npcOrphanSick{} is not buried on the graveyard. Neither is \npcGhostbloodWounded{}. What happened to them...?





\subsection{Dig the Grave}
\label{ssec:graveyardEmptyGrave}

The gravedigger does not allow messing with his work. He won't allow to dig the coffin of Lord \npcKharbranthNoble{}... Not without a proper bribe, at least.

If the party ignores him he will scream for alert. The same will happen if the PCs try and fail to dig the coffin silently. When alerted, four \enemyDiagramMuscle{}s will rush to help the citizen.

If the party manages to dig up Lord \npcKharbranthNoble{}'s coffin, they will see it is filled with rocks. There is no sign of \npcKharbranthNoble{}'s body...

\subsubsection{Clue}

The body of Lord \npcKharbranthNoble{} is not here...