\section{\locationKharbranth{}, the City of Bells}
\label{sec:kharbranth}

The party can freely walk on the city streets, visit shops and other NPCs. This book does not list every possible location the PCs can see, but everything expected to be located in a big city can be found in here.

You can assume the prices here are normal. All traders accept spheres from Alethkar, even if they are dun. There is one exception - by the king's order, all oil is free and provided by state. \npcTaravangian{} hopes this will help people suffering after the Everstorm.

\reasonBox{The source of the free oil will be revealed later in \fullref{ssec:conclaveHospitalOil}.}


\subsection{Rumors and Gossips}
\label{ssec:kharbranthRumors}

The PCs can ask around about \npcTaravangian{}, the hospitals and overall mood of the citizens of \locationKharbranth{}. They can also search for more clues an rumors. When they do, they will learn:

\scriptedOption{People love the king.}{
	Between free healthcare, free oil and the alliance with Vedenar, people love the king and his policies.
}

\scriptedOption{Hospitals helped many people.}{
	Everyone either was healed by the surgeons or knows someone who was. People are very satisfied with the care they get in the hospitals.
}

\scriptedOption{Only a few deaths.}{
	The surgeons do what they can, but sometimes death is inevitable. The most recent one was lord \npcKharbranthNoble{} living in the manor outside the city. However, the surgeons saved multiple hopeless cases, so nobody blames them.
}

\scriptedOption{Veden refugees.}{
	There is a veden camp in the city outskirts. They sailed to \locationKharbranth{} after their civil war- wounded and their families. They say a very skilled artifabian lives there.
}

\scriptedOption{Oil Source}{
	If, after the request from \fullref{ssec:vedenCampArtifabrian}, the party asks about the source of the free oil, no merchant will know what is it made from. However, they will point it comes from the Conclave.
}

\subsubsection{Clues}

The party can investigate the case of lord \npcKharbranthNoble{}'s death - see \fullref{sec:theManor}.

The PCs can also visit the veden refugee camp to learn more from them - see \fullref{sec:vedenCamp}.

Free oil comes from the Conclave, but nobody knows what variance is it.


\subsection{Dark Alley}
\label{ssec:kharbranthDarkAlley}

As the party explores the city, at some time, read the following:

\quoteBox{
	You walk on the city streets, when suddenly you hear a whisper: \\ \\
	"Psst, you! With the strange spren! Over here! The boss told we should expect you in here, and now you can prove your worth! We've got a job for you."
}

The PCs are stopped by a \enemyGhostbloodScout{} who says he has a quest for them. If the party shows interest, he will clarify the details:

\scriptedOption{You know about us? How?}{
	Our agent has seen you in the darkness, a few days ago. Quite a journey you had, hadn't you?
}

\scriptedOption{What happened?}{
	We were working in a team, \npcGhostbloodWounded{} and I. One day, they took him from the street. Told people about some plague symptoms. You must find him?
}

\scriptedOption{Who took him? Where?}{
	The surgeons! Took him to the hospital. He was perfectly healthy!
}

\scriptedOption{How can we recognize him?}{
	He had the tattoo. We all have. \textit{(pulls up his sleeves to show a triangle tattoo made out of free diamond shapes)}
}

\scriptedOption{What exactly do you want us to do?}{
	Find him, and bring him back. If you can't, make sure he will never talk, understood? But even then, after all of that, you must bring his body. As a proof and a precaution. They can't learn his secrets!
}

\scriptedOption{What we will have out of it?}{
	Friends. Powerful friends, with wide connections. You would be surprised what secrets can we share with our allies...
}

\subsubsection{Clue}

Ghostblood agent \npcGhostbloodWounded{} was kidnapped from the streets and taken to \fullref{sec:cityHospital}.




\subsection{Homeless Orphan}
\label{ssec:kharbranthOrphan}

When the party is about to enter the hospital, read the following:

\quoteBox{
	A small, dirty boy wearing old clothes approaches you. \\ \\
	"Um.... Excuse me", he says. "Have you seen my sister...?"
}

The characters can talk with the boy to ask him for more details:

\scriptedOption{What is your name?}{
	Um... \npcOrphanHomeless{}, sir... And my sister, she's \npcOrphanSick{}. Have you seen her?
}

\scriptedOption{What happened to your sister?}{
	She got very sick. She got hot, and weak, and got ugly rash on her face, and her head got big and bloated. I think a cremlik bit her... The doctors took her.
}

\scriptedOption{When did \npcOrphanSick{} got sick?}{
	Um... that a couple of weeks I think... Before that scary red storm...
}

\scriptedOption{Have you asked in the hospital?}{
	They won't let me in... they say it's not a place for small kids... I'm not small!
}

\scriptedOption{Where are your parents?}{
	\textit{You see a flash of sadness on the boy's face. You don't think he's got any family other than the sister...}
}

\subsubsection{Clues}

The party should ask about the boy's sister in \fullref{sec:cityHospital}.

They can also investigate symptoms of her sickness in \fullref{sec:palanaeum} - see \fullref{ssec:palanaeumOrphan}.




\subsection{The Apothecary}
\label{ssec:kharbranthApothecary}

In here, the party can acquire salves, medicine and overall medical supplies. Also, if the PCs as the right questions, they can learn:

\scriptedOption{How many hospitals are there in \locationKharbranth{}?}{
	There are two: one open to the people and one in the Conclave, for the king and the nobles.
}

\scriptedOption{Do you supply both of the hospitals?}{
	Not really... The common hospital orders most of the supplies, but the one in the Conclave is having less requests and only for some basic items.
}

\scriptedOption{Is the quality of your goods too low for the king?}{
	I doubt it. We have the best medical supplies in the city! We import some of the stock from Shinovar and Azir, the rest is freshly made by myself! You cannot ask for anything more!
}

\scriptedOption{Who is then supplying the Conclave Hospital?}{
	I don't know... Ardents, perhaps?
}

\scriptedOption{How can we enter the Conclave Hospital?}{
	Oh, you cannot... The Conclave is closed for the foreigners... But you can petition to the king to get access to \locationPalanaeum{}... It's the library in the Conclave, perhaps that will help you...
}

\subsubsection{Clues}

The apothecary does not supply the Conclave Hospital. Perhaps the \fullref{sec:vorinMonastery} does?

The Conclave Hospital is closed for the commoners. But the party can petition to the king for an access to the \locationPalanaeum{} - see \fullref{ssec:taravangianPetition}.

