\section{\locationPalanaeum{}}
\label{sec:palanaeum}

\locationPalanaeum{} is the greatest library on Roshar. If a book exists, it can be found in here. If the party needs to learn some lore or information, it is the best place to search in.

The library is located inside the Conclave. If the party is looking to enter \fullref{sec:conclaveHospital}, it would be a good place to start.

\subsection{Restricted Access}
\label{sec:palanaeumAcess}

Unfortunately, the access to the library is currently restricted. If the party manages to enter, they will be denied as only selected few are allowed inside.

Luckily for the party, in those days \npcTaravangian{} is allowing for petitions to hear for his subjects' needs. The party can try their luck with him - perhaps he will grant them access.

If the party decides to try this path, proceed to \fullref{ssec:taravangianPetition}.

Once the party obtained proper documentation from the king, they will be welcomed to learn from the knowledge gathered here.




\subsection{The Great Library}
\label{ssec:palanaeumLibrary}

The \locationPalanaeum{} is the greatest library in the known world - the PCs can find knowledge on most of the topics, including: medicine, economics, geography, cuisine and even ancient lore (though in limited amount). Same of them are listed in the sections below:

\begin{itemize}
	\item \fullref{ssec:palanaeumOrphan}
	\item \fullref{ssec:palanaeumImport}
	\item \fullref{ssec:palanaeumDeathRattles}
\end{itemize}

There are some topics the party will not be able to find the answers to: the Everstorm, Odium, Enlightened Radiant Spren, Cosmere beyond Roshar, Ghostbloods, Scadrial, etc. Use your own judgment for topics that are not listed in here.



\subsection{\locationPalanaeum{} Rumors}

When the party is investigating one of the topics in an alcove of the \locationPalanaeum{}, at some point they will hear  a nearby conversation:

\quoteBox{
	"Man! That storming surgeon! I have never seen anyone so sloppy... That history with Lord \npcKharbranthNoble{}? That was close! \npcDiagramSurgeon{} is on thin ice, I'm telling you!" \\ \\
	"Sloppy? That is nothing, have you seen his experiments...? With no finesse or elegance to it... I cannot understand why the king sees any value in them, either! He provided no meaningful results in weeks! Storming waste of resources! We should have never allowed him in the Conclave!"
}

\subsubsection{Clues}

There is more to investigate in the Conclave Hospital. Lord's \npcKharbranthNoble{} case is more complex than it seems, and the surgeon is said to make sloppy work in that topic - whatever that means....





\subsection{Orphan's Sickness}
\label{ssec:palanaeumOrphan}

The party can search for more information about the sickness of \npcOrphanSick{}, the sick orphan. When they do, sooner or later they will find the following information:

\quoteBox{
\sicknessOrphanName{} \\ \\
Contagion: \\
Carried by \textit{Lutumia Fletus} cremlings emerging during the Weeping. \\ \\
Symptoms: \\
Fever, rash, swollen lymph nodes, fatigue, red eyes. \\ \\
Treatment: \\
Plenty of rest and hydration. Keep the patient comfortable. The sickness will fade after several days. The sickness is not lethal.
}

\reasonBox{
	\sicknessOrphanName{} is not a real sickness, but you can think of it as something similar to rubella.
}

\subsubsection{Clue}

\npcOrphanSick{} should not succumb to the sickness, especially if taken care by doctors. She might be still alive...




\subsection{Import and Export}
\label{ssec:palanaeumImport}

If the party searches information on trade history in the city in order to determine the source of free oil, they will not find any tracks of recently imported oil shipments. 

They might however find increased slave purchase by the state in the recent years. If the party digs deeper, they will find most of those slaves were assigned to hospital works. There were none in \fullref{sec:cityHospital}, so they probably work in the Conclave Hospital.

\subsubsection{Clue}

Free oil is not imported via trade.



\subsection{Death Rattles}
\label{ssec:palanaeumDeathRattles}

If the party searches information about the Death Rattles, they will finally find a book by Hessi titled "Mythica", describing all nine Unmade, including \npcMoelach{}.

The book will provide information about the Unmade granting visions of the future at the time of soul's transition between realms. Many of them are prophetic in their nature, allowing nearby people to glimpse into the future.

\spoilerBox{
	Hessi's "Mythica" entries treating about \npcMoelach{} can be found in \bookOB{}, Chapters 101. Deadeye and 102. Celebrant.
}



\subsection{Path to the Conclave Hospital}

If the party sneaks out from the \locationPalanaeum{} to search for an entrance to the Conclave Hospital, they will find a corridor leading to \fullref{ssec:conclaveHospitalEntrance}.
