\section{Path to \locationKharbranth{}}
\label{sec:pathToKharbranth}

The party successfully escaped the perils of the Shadesmar. Now they find themselves in a relatively safe area nearby the City of Bells, \locationKharbranth{}.



\subsection{Out from the Darkness}

Start the chapter by reading the following:

\quoteBox{
	You step out from the light into a light breeze. The grass retracts under your step and you finally see the shimmering light of the sun. Normal, golden sun! After so many days, you finally feel... home. \\ \\
	You are standing on a mountain path, leading to the nearby city - \locationKharbranth{}.
}

Using \lootGateOpener{} consumed all of the party's Investiture - both from the PCs and their spheres. They will need to resupply before they can use their Radaint abilities.

Once the party is ready to move on the path, proceed to \fullref{ssec:pathToKharbranthTrouble}.

\reasonBox{
	Depleting the Stormlight is to made the next scene a bit more balanced for PCs on this level. Also - it is to prevent any Progression users to heal the NPCs too quickly - we need them to set the party on the path to the hospital.
}



\subsection{What's the Next Step?}

If the PCs are wondering about their next goal, either now or in some future scenes in this chapter, read the following to them:

\quoteBox{
	Your Enlightened Spren becomes visible to your friends and explains: \\ \\
	"Our Mother did not specify the next phase of her plan. However, she was very interested in the human ruling over this city, \npcTaravangian{}. We should probably scout the city, see how he runs it, perhaps even meet the man himself?"
}

In this chapter, the party will not have a clear, specified end goal. Instead, they should follow the clues of Discovery Endeavor to see where will they lead them.



\newpage
\subsection{Trouble on the Road}
\label{ssec:pathToKharbranthTrouble}

While the PCs are walking on the road to \locationKharbranth{}, read the following:

\quoteBox{
	As you are walking, suddenly you hear screams of pain and terror. As you rush towards it, you see a whitespine massacring a merchant caravan: barrels of wine lie shattered everywhere, their sweet content mixing with a blood of a dying merchant. The beast looks at the second person, ready to charge.
}

The party enters in a middle of a fight. \enemyWhitespine{} is attacking helpless caravan. One of the merchants is as good as dead, the other will die unless the PCs intervene. \enemyWhitespine{} will fight until slain.

\subsubsection{Treasure}

There is nothing left from the caravan. The chull was slain, all the goods are destroyed.

\subsubsection{Death Rattle}

After the fight, or at the moment when one of the PCs attempts to help the dying merchant, read the following:

\quoteBox{
	You approach the merchant lying in his own blood. His wounds are too severe... He is struggling for each breath, his face painting suffering. \\ \\
	Suddenly his eyes go wide, and he whispers: "They love me and in my hand I'm holding their fate: who will live, who is destined for more?" \\ \\
	After those words, the merchant dies.
}

\corruptedBox{
	Hearing a Death Rattle, a vision sent by \npcMoelach{}, can expedite an Enlightened Truthwatcher \seeCorruptedRules{}.
}

\subsubsection{The Survivor}

If the party managed to save the second merchant, they will be able to talk with him. 

\scriptedOption{Who are you?}{
	I'm \npcWoundedTrader{}, a merchant traveling from the Shattered Plains. When we survived the strange storm we thought the worst is behind us. Little did we know...
}

\scriptedOption{Where were you heading?}{
	We hoped to reach \locationKharbranth{} before the Storm... It should hit tonight... But there should be a stormshelter on the road as well... We better hurry towards it!
}

\scriptedOption{What about your wounds?}{
	I'm lucky the whitespine only scratched me. I will live, thanks to you. And the surgeons in \locationKharbranth{} will take care of the rest.
}

\scriptedOption{Surgeons?}{
	Don't you know? Everybody everywhere knows! \npcTaravangian{} runs free hospitals in the city. His surgeons help everyone in need.
}

\scriptedOption{Can we heal you?}{
	How? Old magic? Voidbringers? No, thank you, I will trust the professionals with it, no offense! Just take me to the hospital.
}

\subsubsection{Clues}

The Highstorm is comming, but there is a stormshelter nearby - see \fullref{ssec:pathToKharbranthShelter}.

In the city, there are hospitals tending to sick and wounded - see \fullref{sec:cityHospital}.




\subsection{Stormshelter}
\label{ssec:pathToKharbranthShelter}

As the party reaches this point, read the following:

\quoteBox{
	As you reach the stormshelter, you see dark clouds gathering in the east. You made it safely in time. You enter through the door to a dark, stony room. \\ \\
	There are a few people inside. One of them, a man in a white apron, approaches you and says in a broken alethi: "Hello! The king predicted you will be here. I'm glad you made it in time."
}

The person greeting the party is a \enemyDiagramSurgeon{}. He can tend to the wounded. He will not charge for his help. After the Storm is over, he will take \npcWoundedTrader{} to the city hospital. Two \enemyDiagramMuscle{}s will help him carry the man in the stretcher.

After the Storm passes, the party can easily reach the city with their Investiture reserves renewed. Proceed to \fullref{sec:kharbranth}.

\reasonBox{
	\bookSA{} never shows the Diagram having access to information with such precision and timeframe details. If you believe \npcTaravangian{} predicting PCs arrival bends the lore too much, you can skip the greeting. I added it to evoke a feeling of eerie mystery.
}

\subsubsection{Healing the Party}

\enemyDiagramSurgeon{} can use his abilities to heal the PCs and remove their negative conditions from injuries. When they do that for the first time, read the following:

\quoteBox{
	As your pain fades away, you feel a surge of gratitude and kinship towards the surgeon. At the same time, you know - if you ever find yourself in an opposite camp, it would be hard for you to argue against your savior...
}

\reasonBox{
	In this chapter, the party will have multiple opportunities to resolve conflicts in a Conversations with the surgeons. You can introduce them to their unique abilities by running one of those at the end of the scene. E.g., allow the PCs to argue against taking \npcWoundedTrader{} to the hospital if they are not sure about the idea.
}