\section{The Manor}
\label{sec:theManor}

Lady \npcKharbranthNoble{}, a widow after Lord \npcKharbranthNoble{}'s death, lives in a manor beyond the city. The party will need to take a hike if they wish to talk to her. It is not hard to find the estate, everyone in \locationKharbranth{} can point a way to it.




\subsection{Ambush at the Road}

As the party travels this road for the first time, read the following:

\quoteBox{
	You travel to the \npcKharbranthNoble{}'s Manor as you realize how quiet is it in here. The city is left far behind you and you are surrounded by silent rocks and sparse verdant leits. \\ \\
	It is the last moment as you realize - it is too quiet, and the place is perfect for an ambush...
}

The party is attacked by \enemySingerHaevenlyOne{}, four \enemySingerDireform{}s and four \enemySingerStormform{}s. They are lead in here by their leader's hate for the party and they will fight to the end.

\reasonBox{The type of the enemies is not important for the plot and can be changed for anything that would fit your PCs' story more. The number of enemies should be high enough to make it a dangerous fight for the party.}

\subsubsection{Diagram's Reinforcements}

Once a PC gets injured due to low Health, the total Health of the party members drops to roughly 25\%, or the party finds themselves in other dire conditions, read the following:

\quoteBox{
	Suddenly you hear a sound of hoofs galloping on the stone. A small force from \locationKharbranth{} is riding your way. \\ \\
	"The King has predicted this. We are here to help you. Do you need a medical attention?"
}

Two \enemyDiagramSurgeon{}s and several \enemyDiagramMuscle{}s join the fight. Most of them will focus on the Regals, fighting them off-screen. The party continues their fight against \enemySingerHaevenlyOne{} and they are joined by \enemyDiagramMuscle{}. 

If the PCs need healing, the surgeons will also join the fight to help them, but they will retreat once there is nobody else they could tend to.

If the party is still having trouble to defeat their enemy, allow more \enemyDiagramMuscle{}s to join them in the following rounds as they defeat their enemies off-screen.

\reasonBox{
	Events of this entire chapter may paint the Diagram in a bad light. This scene proves that their methods might be necessary to prevent bigger disasters and possibly gives the party an argument to join them if the players would like to do so.
}

\reasonBox{
	"The King has predicted this" is used for the same reason as in \fullref{ssec:pathToKharbranthShelter}. You can skip this line if you don't like the lore implications that it carries.
}




\subsection{The Widow}

When the party reaches the \npcKharbranthNoble{}'s Manor, read the following:

\reasonBox{
	You arrive at the \npcKharbranthNoble{}'s Manor. It's western wing shows marks of the Everstorm hitting it recently and the surrounding gardens are destroyed. \\ \\
	After you knock the door, an old lady opens you. "Oh, hello dear! What brings you here?"
}

Lady \npcKharbranthNoble{} is a nice old woman. After the PCs introduce themselves she will invite them inside the empty manor. She will gladly talk with the party:

\scriptedOption{It's empty in here... Where are your servants?}{
	The parshmen changed and left after the Red Storm. And I had to let the rest go after my husband died...
}

\scriptedOption{Why didn't the surgeons help him?}{
	They did the best they could, but nobody can heal an old age... 
}

\scriptedOption{How old was he?}{
	Oh, he would be 100 next year. He really looked forward to this... Such a holy number, he was always saying...
}

\scriptedOption{Why didn't he want to be soulcast?}{
	Oh, he wanted that really much. He was such a religious man... But the surgeons, they said no.
}

\scriptedOption{Why did they forbid the soulcasting?}{
	My husband was very weak in the end... It was plague that killed him... The surgeons said his coffin must remain closed not to risk a spread of the disease. I buried him in the ground.
}

\scriptedOption{In which hospital was he treated?}{
	They moved him to the Conclave, of course! We are lighteyes after all. He was treated by this lovely young surgeon, \npcDiagramSurgeon{} was his name I believe.
}

\scriptedOption{Where is his grave?}{
	Oh, that would be the graveyard nearby the city, my dear. If you ever visit him, can you burn him this prayer from me? I would appreciate it a lot.
}

\subsubsection{Clues}

Lord \npcKharbranthNoble{} is buried in \locationKharbranth{}  graveyard - see \fullref{sec:graveyard}.

He was treated in the Conclave Hospital by \npcDiagramSurgeon{} - see \fullref{sec:conclaveHospital}.

He wanted to be soulcast, but the surgeons told his wife not to open the coffin - it could spread the plague, they said.





\subsection{Bad News}

Lady \npcKharbranthNoble{} is fully convinced that \npcTaravangian{} and his surgeons are working for the good of the city and all it's people. She believes they are impeccable saviors and will not accept any accusation against them.

If the party discovers her husband missing body in \fullref{ssec:graveyardEmptyGrave} and bring her the news about it, she will not believe it. Instead, she will name the PCs "filthy storming liars" and throw them out of her estate.
