\section{Veden Refugees}
\label{sec:vedenCamp}

As the party approaches Veden Camp, read the following:

\quoteBox{
	Refugee camp is located on the outskirts of the city. It's hard to tell if the entire district was heavily damaged by the Everstorm or the architecture here is just... well... messy.
}

It is said a brilliant Artifabrian works in here. Also, the party can talk with local people to learn a bit more about the situation in the city.





\subsection{Rumors and Gossips}

If the party decides to talk with the people from Vedenar, they will respond to the questions:

\scriptedOption{What are you doing in \locationKharbranth{}?}{
	Our new king rules this city as well... Some of us is here for the treatment in the hospitals. Some came with the families in hopes for a better life...
}

\scriptedOption{What do you think of the surgeons?}{
	I think they want good, but the people of \locationKharbranth{} overstate their skills a lot... They are not half as good as they say... Well, at least they are free...
}

\scriptedOption{How many of you have been healed?}{
	Hard to say... maybe half? Yeah, the mortality is much higher than they say... But at least it's better than in our homeland...
}

\scriptedOption{Why don't you return home?}{
	It's not safe to travel, right now. And in here, in the city of our new king, we can hope for some opportunity for a better life...
}





\subsection{Artifabrian}
\label{ssec:vedenCampArtifabrian}

When PCs enter artifabrian workshop, read the following:

\quoteBox{
	Compared to the rest of the district, the shop looks tidy and well managed. Cogs, springs, bolts and other mechanical parts lie on the shelves. In the middle of all of those, a veden woman sits next to her workshop table, tinkering with some contraption.
}

\npcVedenArtifabrian[s]{} is the only NPC in this place. In her workshop, the party can trade or discuss about their fabrials. 

\npcVedenArtifabrian{} arrived to \locationKharbranth{} with her family who got treated in the hospital, but now they believe it is unsafe to return back home. She is not interested in local news and has little information for the PCs.

\subsubsection{Artifabrian's Request}

If the party is about to leave the workshop, read the following:

\quoteBox{
	As you are leaving, \npcVedenArtifabrian{} calls you to stop. \\ \\
	"Hey, can you do me a favor?", she asks. "When you are in the city, can you ask what oil is freely distributed? Is it from Red Lavis or Western Lavis? Both are good for as a lamp fuel or for culinary purposes, but Red Lavis Oil would tint the metals if I were to impregnate with it..."
}

\npcVedenArtifabrian{} requests the party to learn what kind of grain is used to produce free oil. She offers 50 marks for this information on top of some discount in her shop.

\subsubsection{Clue}

The party must learn more about the origin of the oil. They should probably ask local merchants for more information - see \fullref{ssec:kharbranthRumors}.
