\section{\locationKharbranth{} Monastery}
\label{sec:vorinMonastery}

When the party arrives at the monastery, read the following:

\quoteBox{
	You enter a stone building with ten steined glass windows. The western wall got damaged during the Everstorm, but the inside remained mostly intact. Now illuminated with oil lamps, the monastery is a bastion of peace during the times of chaos.
}

There is one major Vorin Monastery in \locationKharbranth{}, located in the Dawn District. In here, the party can find a bit of respite, serenity, piety, and perhaps - some answers to their questions.




\subsection{Talking with Ardent}

When the PCs talk to the ardents in the monastery, they will learn the following:

\scriptedOption{Are you supplying the Conclave Hospital?}{
	"No, we do not deal with medical supplies, that is the calling of the apothecaries". \skillCheck{15}{\skillInsight{}} will reveal the ardent knows more than they are saying.
}

\scriptedOption{Have you visited the Conclave Hospital?}{
	Of course! We visit all sick who desire to pray with us to the Almighty.
}

\scriptedOption{Did you help with any funerals?}{
	Lord \npcKharbranthNoble{} did not wish for our Soulcast Service, but we did pray for him. He rests now at the city graveyard.
}

\scriptedOption{What about small girl, \npcOrphanSick{}?}{
	No, there was no funeral of her.
}

\scriptedOption{What about \npcGhostbloodWounded{}?}{
	Don't know anyone by this name... It's a strange name, isn't it? Where is he from...?
}

\subsubsection{Clues}

Lord \npcKharbranthNoble{} is buried, he did not wish for a soulcaster - see \fullref{sec:graveyard}.

The ardents know something about the Conclave Hospital they do not share...

Neither \npcOrphanSick{}, nor \npcGhostbloodWounded{} are known by the ardents.





\subsection{The Soulcaster}

The monastery houses a soulcaster, but they are never shown to a public. If the party manages to sneak inside their chambers or break there with force and violence, read the following:

\quoteBox{
	The chamber is illuminated with the light of infused topaz spheres, casting yellow light on the gray, stony walls. In the middle there is and ardent with long, greasy hair. \\ \\
	"Who are you?", he demands. "You are not supposed to walk in here!"
}

The ardent in this chamber is a Soulcaster. He does not share the essence he is working with, but you can assume he transforms into oil. He is employed to produce oil in \fullref{ssec:conclaveHospitalOil}.

If a PC succeeds on \skillCheck{20}{\skillDeduction{}} they will be able to determine he is an Oil Soulcaster. That test gains an advantage if the PC has an expertise in Vorin Religion or has Transformation surge skill.

\subsubsection{Talking with the Soulcaster}

The Soulcaster does not wish to talk with the party. He will talk with them only if they manage to fool him into believing they are sent by the surgeon, the Diagram or the King himself. If that happens, he will expect to be called again to the Conclave for the soulcasting.

If the party demands answers from him without posing as someone he would obey, they will be asked to leave. I they don't comply, he will call for help, triggering a fight with \enemyDiagramMuscle{}s at his side.

\subsubsection{Fighting the Soulcaster}

If attacked, he will defend and fight to the end. You can use \enemySoulcaster{} stat block for this fight, but replace the visuals of his actions with a liquid theme. After the first round of the combat, five \enemyDiagramMuscle{}s will join to protect him.

After the fight, the party can collect his Soulcaster as a reward. A PC in possession of the Soulcaster gains access to Transformation skill and can develop talents from Transformation talent tree, but they cannot use them if they are separated from the Soulcaster.

\subsubsection{Clues}

The monastery houses an Oil Soulcaster. He is employed at the Conclave to transform oil - see \fullref{ssec:conclaveHospitalOil}.


