\section{Ghostbloods}
\label{sec:enemyFractionGhostbloods}

Worldhopping from another world, the Ghostbloods live by a simple creed - to do whatever is best for Scadrial, their home planet. Right now it means finding means extracting enormous amounts of Investure from Roshar and transporting it back to Scadrial.

The entire organization excels in gathering and managing information. Their awareness of the Cosmere and secrects it hides turns them into very dangerous and unpredictable foes.

\subsubsection{Scadrial Magic}

Allomancy, the magic from Scadrial, allows its users to drink metal flakes and burn them for a specific bonus effect. That makes them independent from Rosharn Highstorms as a source of Investure.

\subsubsection{Scouts and Spies}

Ghostbloods understand that knowledge is power. They employ a wide network of scouts and spies, who gather the critical information to use against their enemies. Using \lootSeonTube{}s, a technology from yet another world, they can quickly communicate with their leader, even from the Shadesmar.

\tacticsBox{
	\enemyGhostbloodThug{}s are the ones that feel the most comfortable with the fighting. Their allomancy allows them to burn pewter, making them stronger, faster and more deadly. They will not hesitate to fight dirty if that's what it takes to win.
}


\newpage
\input{appendices/enemies/enemyGhostbloodScout.tex}
\newpage
\input{appendices/enemies/enemyGhostbloodSmoker.tex}
\newpage
\input{appendices/enemies/enemyGhostbloodThug.tex}
\newpage
\input{appendices/enemies/enemyGhostbloodBoss.tex}
\newpage
\input{appendices/enemies/enemyGhostbloodMraize.tex}
\newpage
\input{appendices/enemies/enemyGhostbloodIyatil.tex}




