\section{Wild Beasts}
\label{enemyFractionBeasts}

The wilderness of Roshar is full of dangerous beasts. When traveling, make sure not to anger one of them, as they can be brutal opponents with no mercy.

\subsubsection{\enemyAxehoundName}

Not only the people are subjected to the hunger troubling the city. Lack of food is affecting also the animals. Axehounds are not exception - without proper nourishment, their packs scour the city in hopes to find anything edible. Once they pick up the scent, they won't be stopped by any obstacle.

Kholinar breed of the Axehounds is slightly bigger and more aggressive than their cousins. Their carapace has more vibrant, red hue, marked with black and orange spots.


\subsubsection{\enemySkyeelName}

Though most Skyeel species can be found nearby the large pools of water - like seas and oceans - some of them adapted to the mountainous environment. They lost their ability to swim, but they are still a vicious hunters.

Their gray and white coloring allow them to camouflage easier in the snowy mountain ranges nearby \locationUrithiru{}, making it easier to sneak on their prey.


\subsubsection{\enemyWhitespineName}

A Whitespine is one of the most dangerous predators on Roshar. They tend to live alone, but even without a pack they can easily eliminate a whole group of nobles who wanted to hunt a whitespine for sport.

\newpage
\input{appendices/enemies/enemyAxehound.tex}
\newpage
\input{appendices/enemies/enemySkyeel.tex}
\newpage
\input{appendices/enemies/enemyWhitespine.tex}
