\label{enemyQueenAesudan}


\enemyStatBlockDouble{
	\enemyStatBlockHeader{\enemyQueenAesudanName{}}{3}{Boss}{Large Humanoid}
}{
	\enemyStatBlockStats{4}{5}{4}{4}{4}{5}{200 (180–220)}{6}{9}
}{
	\enemyStatBlockSkills[
	\enemyStatblockSkillsDeflect[1 (crystal)] \\
	\enemyStatblockSkillsMovement[40 ft.]	
	\enemyStatblockSkillsSenses[50 ft. (sight)]	
	\enemyStatblockSkillsImmunities[Exhausted, Stunned, Surprised]
	\enemyStatblockSkillsPhysical[Agility +9, Athletics +8]
	\enemyStatblockSkillsCognitive[Intimidation +8]
	\enemyStatblockSkillsSpiritual[Perception +8, Leadership +9]
	\enemyStatblockSkillsSurges[Abrasion +9 (4 ranks), Adhesion +9 (4~ranks) Cohesion +8 (4 ranks), Division +8 (4 ranks), Gravitation +8 (4 ranks), Illumination +9 (4 ranks), Progression +8 (4 ranks), Tension +9 (4 ranks), Transformation +8 (4 ranks), Transportation +8 (4 ranks)]
	\enemyStatblockSkillsLanguages[alethi, thaylen, veden]
	]
}{
	\enemyStatblockFeatureBoss{} \\
	
	\enemyStatblockFeature{Crystal Carapace}{Before \enemyQueenAesudanName{} is hit by an attack, she can spend 1 Focus to turn it into a graze (no action required). Additionally, she can use her carapace like a shield, allowing her to use the Brace action.} \\

	\enemyStatblockFeature{Growing Crystal}{At the end of each combat round, increase Deflect value of \enemyQueenAesudanName{} by 1. If the value reaches 10, \enemyQueenAesudanName{} becomes overwhelmed by the Unmade and dies.} \\
}{
	\enemyStatblockAction{Strike: Crystal Claws}{Attack +9, reach 5 ft., one target. Graze: 4 (1d8) keen damage. Hit: 13 (1d8 + 9) keen damage, and \enemyQueenAesudanName{} can spend 1 Investure to deal an additional damage equal to her Deflect value.} \\
	
	\enemyStatblockAction[\iconFreeAction]{Unmade Abrasion (Costs 1 Focus)}{\enemyQueenAesudanName{} moves up to her movement rate in a straight line.}
	
	\columnbreak
	\enemyStatblockAction[\iconActionDouble{}]{Unmade Division (Costs 1 Investiture)}{Attack +8 vs. Spiritual, reach 5 ft., one target. Graze: 16 (3d10) energy damage. Hit: 24 (3d10 + 8) energy damage, and the target becomes \exhausted[-1].} \\
	
	\enemyStatblockAction{Unmade Cohesion (Costs 1 Investiture)}{\enemyQueenAesudanName{} chooses a Huge (15-foot) space within 30 feet of her, turning all stone in it to liquid. Each enemy standing on stone within that area sinks into the ground and becomes Slowed for as long as they’re in the liquid stone. \\
	At the start of each round, \enemyQueenAesudanName{} can spend 1 Investiture to maintain this effect for another round. If she doesn’t, the stone hardens and any characters in it are Immobilized. A trapped target or a character who can reach them can Use a Skill to make an DC 20 Athletics test, freeing the trapped target on a success; otherwise, the target remains trapped until they’re dug out of the stone.} \\	
	
	\enemyStatblockAction[\iconActionDouble{}]{Unmade Transformation (Costs 1 Investiture)}{\enemyQueenAesudanName{} chooses a Huge (15-foot) space within 60 feet of her, transforming all air in it to fire. Each character in that area takes 11 (2d10) energy damage, and unaccompanied flammable objects in that area catch on fire.} \\
	
	\enemyStatblockAction{Unmade Illumination (Costs 1 Investiture)}{\enemyQueenAesudanName{} Lightweaves an illusion of herself. Until an attack misses her, her attacks gain an advantage and attacks against her gain a disadvantage and can’t graze.} \\
	
	\enemyStatblockAction{Unmade Adhesion (Costs 1 Investure)}{\enemyQueenAesudanName{} makes an Adhesion test against a Physical Defense of a target within 20 ft. On a success, the target is Immobilized until her next turn.} \\
	
	\begin{center} \MakeUppercase{\textbf{Opportunities and Complications}} \end{center}
	{\color{goldStats} \hrule \vspace{0.5cm} }
	
	The following options are available when an enemy gains an Opportunity or Complication during a scene with \enemyQueenAesudanName{}:
	
	\scriptedOption{Opportunity}{An enemy can spend \iconOpp{} to increase \enemyQueenAesudanName{}'s Deflect value by 1 and make her Slowed.}
	
	\scriptedOption{Complication}{The GM can spend \iconComp{} from an enemy’s test to increase \enemyQueenAesudanName{}'s Deflect value by 1 and to restore her 1 Investure.}
}
~~ 