\section{\enemyRioterName}
\label{enemyRioter}

Hunger and unrest in the city of Kholinar made plenty people angry and desperate. At some point, enough is enough and those people - bakers, tailors and merchants - will grab whatever is nearby to fight for any glimmer of hope for a better tomorrow.

On their own, each \enemyRioter{} is timid an cowardly. In a group, however, they loose all traces of any rational behavior, turning into mindless incarnation of mayhem. Do not try to reason with them or find any logic in their actions - they are way beyond that. Now, there is only riot!

\tacticsBox{
	Not much a threat when they are alone. Fighting in larger groups gives them courage, however. A gang of \enemyRioter{}s will attempt to rain stones and rubble on their enemies with a hope to keep a safe distance. If that fails, they will use some wooden planks as a maces to defend. 
}

\newpage
% From Bandit
\enemyStatBlock{
	\enemyStatBlockHeader{\enemyRioterName}{1}{Minion}{Medium Humanoid}
}{
	\enemyStatBlockStats{1}{1}{1}{0}{2}{1}{11 (8-14)}{2}{0}
}{
	\enemyStatBlockSkills[
	\enemyStatblockSkillsDeflect[1 (leather)] \\
	\enemyStatblockSkillsMovement[25 ft.]
	\enemyStatblockSkillsSenses[10 ft. (sight)]
	\enemyStatblockSkillsPhysical[Agility +3, Athletics +3, Light Weaponry +2]
	\enemyStatblockSkillsCognitive[Discipline +1, Intimidation +3]
	\enemyStatblockSkillsSpiritual[Perception +3, Survival +3]
	\enemyStatblockSkillsLanguages[alethi]
	]
}{	
	\enemyStatblockFeature{Momentum}{If the \enemyRioterName{} moves at least 10 feet in a straight line toward a target then makes a Mace attack against them on that turn, the \enemyRioterName{} gains an advantage on that attack.} \\
	
	\enemyStatblockFeatureMinion{} \\
}{
	\enemyStatblockAction{Strike: Mace}{Attack +2, reach 5 ft., one target. Graze: 3 (1d6) impact damage. Hit: 5 (1d6 + 2) impact damage.}\\
	
	\enemyStatblockAction{Strike: Throw Rubble}{Attack +2, range 20/60 ft., one target. Graze: 3 (1d6) keen damage. Hit: 5 (1d6 + 2) impact damage. This attack gains an advantage if another \enemyRioterName{} used the same action this round.} \\
	
	\enemyStatblockAction{Trip (1 Focus)}{The \enemyRioterName{} makes an Athletics test against a target within 5 feet of them, opposed by the target’s choice of Athletics or Agility. If the \enemyRioterName{} succeeds on this test, the target is knocked Prone.}
}