\label{enemyGhostbloodBoss}

% From Ghostblood Enforcer + Crime Boss
\enemyStatBlockDouble{
	\enemyStatBlockHeader{\enemyGhostbloodBossName}{2}{Boss}{Medium Humanoid}
}{
	\enemyStatBlockStats{3}{3}{2}{3}{5}{5}{116 (106-126)}{5}{7}
}{
	\enemyStatBlockSkills[
	\enemyStatblockSkillsDeflect[1 (leather)] \\
	\enemyStatblockSkillsMovement[30 ft.]
	\enemyStatblockSkillsSenses[20 ft. (sight)]
	\enemyStatblockSkillsPhysical[Athletics +5, Heavy Weaponry +6, Light Weaponry +6]
	\enemyStatblockSkillsCognitive[Deduction +6, Intimidation +6]
	\enemyStatblockSkillsSpiritual[Deception +7, Perception +8, Persuasion +8]
	\enemyStatblockSkillsLanguages[defined by region]
	]
}{
	\enemyStatblockFeatureBoss{} \\
	
	\enemyStatblockFeature{Compelling Leader}{When the boss successfully uses the Gain Advantage action or gains an Opportunity, they can grant that advantage or Opportunity to one of their allies within 60 feet of them.} \\

	\enemyStatblockFeatureInurePoison{} \\
	
	\enemyStatblockFeature{Ruthless}{After the boss knocks an enemy Prone, they can make an additional Strike against that target as \iconFreeAction{} on that turn (even if they’ve already used that Strike action).} \\
	
	\columnbreak
}{
	\enemyStatblockAction{Strike: Dueling Cane}{Attack +6, reach 5 ft., one target. Graze: 3 (1d6) impact damage. Hit: 11 (1d6 + 8) impact damage, and the boss can spend 1 Focus to knock the target Prone.}\\
	
	\enemyStatblockAction{Strike: Obsidian Dagger}{Attack +6, reach 5 ft., one target. Graze: 2 (1d4) keen damage. Hit: 10 (1d4 + 8) keen damage, and if the boss had at least one advantage on the attack, it deals an extra 5 (2d4) keen damage. On a Complication, this weapon breaks.} \\
	
	\enemyStatblockAction[\iconFreeAction{}]{Burn Zinc (Costs 1 Investure)}{The boss chooses one of the effects below to be active until the start of their next turn. At the start of each of their turns, the boss can spend 1 Investiture to maintain this effect for an additional round.
		
	\textbf{Riot Prowess.} Another allied character can make an additional strike during their next turn. 
	
	\textbf{Riot Panic.} Make a Persuasion test against the target's Spiritual Defense. On a success, the target gains disadvantage on their attack rolls and must start their next turn by moving away from the boss.
	} \\
	
	\enemyStatblockAction{Disquiet}{The boss manipulates their knowledge of an enemy they can influence to unnerve them. If the boss knows one or more of the target’s goals, their purpose, or their obstacle, the target loses 1d4 Focus; otherwise, the target loses 1 Focus.} \\
	
	\enemyStatblockAction[\iconActionDouble{}]{Intimidate (Costs 1 Focus)}{The boss makes an opposed Intimidation test against the Discipline of a target they can influence. If the boss succeeds, the target loses 1 Focus and is no longer Focused.} \\
	
	\enemyStatblockAction[\iconActionDouble{}]{Drink Vial}{The boss drinks a vial with metal flakes, regaining 6 Investure.}
}
\newpage
~~ 