\section{\npcFractionCult}

Ardents indulging in a life full of comfort quickly become a prime target for \npcHeartRevel{}, the \npcHeartRevelTitle{} and it's corruption. After the Everstorm, those ardents founded the \npcFractionCult{}.

During the day, the \enemyCultist{}s are walking in processions, each wearing a different costume of a spren. They preach the upcoming end and call for the spren worship. At nights they all gather at the Monastery, where the revelry starts.

\subsection{Spren Cultists}

When they are out in the city, each \enemyCultist{} wears a costume made of white ardent robes decorated with ribbons or other ornaments to reassemble one of the spren. The most common are:

\scriptedOption{Windspren}{
	The \enemyCultistName{} attaches light blue ribbons to their robes. They move quickly to make them flap on the wind. During fight, they cut with their knives before running to another enemy.
}

\scriptedOption{Firespren}{
	With short, bright red straps of ribbons attached to their white robes, those cultists often carry a flaming torch or a censer, which they can use as a weapon.
}

\scriptedOption{Painspren}{
	Robes of those \enemyCultistName{}s remain white, but they additionally wear orange gloves ended with sharp, steel claws. If attacked, they will use them to make deep, bleeding cuts.
}

\scriptedOption{Shockspren}{
	Those \enemyCultistName{} attach plenty of strings with yellow glass shards to their robes. If needed, they can rip one off and fling it like with a slingshot. They are seldom lethal, but they can cut painfully.
}

\scriptedOption{Anticipationspren}{
	They wear white robes with one, long, red ribbon around their arm. During fight, they use it as a whip and they can entangle their enemies with a precise strikes, restraining their movements.
}

\tacticsBox{
	When drawn to combat, each \enemyCultist{} will attempt to enact the spren they are representing: those with windspren ribbons will quickly move between multiple targets, the ones with painspren gloves will scratch their foes, while shockspren cultists will use slings to rain glass shards on their enemies.
}


\input{appendices/enemies/statblockCultist.tex}



\subsection{Revelers of the Heart}

After the set of sun, the revelry begins. All cultists return to the Monastery where they indulge in food, drinks, dance and other pleasures. 

But the former ardents are not alone - with food being scarce in the city and the enemy army threatening with carnage any day now, many lost all hope and responded to the inviting call of \npcHeartRevel{}. In here, all their desires come true: \\

\scriptedOption{\enemyRevelerMaskedName{}}{
	One of the most devoted servants of \npcHeartRevel{} - former ardent, now making sure the revelry continues undisturbed. Those revelers hide their faces behind pale blank masks without any features.
}

\scriptedOption{\enemyRevelerDrinkingName{}}{
	Desperate lighteyes and starving people ready to give everything for one more sip of vine, one additional bite of meat. They don't care about anything else, their clothes are often in shreds and food stains.
}

\scriptedOption{\enemyRevelerMusicalName{}}{
	Broken people finding their last glimpse of joy in music and dance. Some of them are haunted with an eerie tune nobody else can hear. They are eager to share the musical rapture with other characters who do not follow the steps of the dance.
}

\scriptedOption{\enemyRevelerWealthyName{}}{
	While you can't eat your money, some revelers desire wealth above all else. When they are surrounded by delicious food and exotic wine, they see only spheres and jewelry which they proudly wear, presenting to the world.
}

\scriptedOption{\enemyRevelerSadisticName{}}{
	Those do not care about money or whatever it can buy. Instead they hunger for sensations and experiences - they seek thrill of pleasure, scream of pain, they are longing for fear and anticipation, each one unique and exceptional.
}

\tacticsBox{
	The revelers do not wish to fight, they only want to relax and revel. They will invite the others to the revel to share the celebrations, but they will avoid physical conflict for as long as possible.
}


\input{appendices/enemies/statblockRevelerMasked.tex}
\input{appendices/enemies/statblockRevelerDrinking.tex}
\input{appendices/enemies/enemyRevelerMusical.tex}
\input{appendices/enemies/statblockRevelerWealthy.tex}
\input{appendices/enemies/statblockRevelerSadistic.tex}


\subsection{\enemyHeartOfTheRevelName{}}

\npcHeartRevel{}, the \npcHeartRevelTitle{} is the Unmade whose influence corrupted the ardents until they formed \npcFractionCult{}. It resides in the very center of the revelries in the Ardent Monastery - on top of the control building of the Kholinar Oathgate.

\npcHeartRevel{}'s body is a huge mass of black flesh. It beats in uneven rhythm, which earned it a name of \npcHeartRevelTitle{}. However, there is nothing familiar in its form - if it really reassembles a heart, it is no heart of a human.

Despite being a powerful Unmade, it is not very intelligent. One cannot expect a meaningful conversation with it. Instead, it will try to enact its nature - calling weak and troubled to join the endless revel.

\tacticsBox{
	\npcHeartRevel{} cannot be killed and any attempts will fail. To defeat it, one must show unyielding determination and a steel will. \\ \\
	In a conversation it will attempt to shake the resolve of its opponents with constant calls to the revel. It will use its thralls for help if that's what it takes. \\ \\
	If \npcHeartRevelTitle{} would see it has no power over a person, it will retreat.
}  

\input{appendices/enemies/statblockHeartOfTheRevel.tex}