\label{enemyMishram}

\enemyStatBlockDouble{
	\enemyStatBlockHeader{\enemyMishramName}{4}{Boss}{Medium Humanoid}
}{
	\enemyStatBlockStats{5}{5}{4}{5}{3}{9}{42 (34–50)}{5}{7}
}{
	\enemyStatBlockSkills[
	\enemyStatblockSkillsDeflect[3 (carapace)] \\
	\enemyStatblockSkillsMovement[30 ft.]
	\enemyStatblockSkillsSenses[50 ft. (sight)]
	\enemyStatblockSkillsPhysical[Agility +10, Athletics  +10, Light Weaponry +10]
	\enemyStatblockSkillsCognitive[Intimidation +10, Lore +8]
	\enemyStatblockSkillsSpiritual[Leadership +14]
	\enemyStatblockSkillsLanguages[all]
	]
}{
	\enemyStatblockFeatureBoss{} \\
	
	\enemyStatblockFeature{Compelling Leader}{When Mishram successfully uses the Gain Advantage action or gains an Opportunity, she can grant that advantage or Opportunity to one of their allies within 60 feet of them.} \\
	
	\enemyStatblockFeature{Glimpses of the Future (Costs 1+ Investiture)}{Once per round, after Mishram rolls the dice for a test, Mishram can spend 1 Investiture or more to reroll that number of dice.} \\
	
	\enemyStatblockFeature{Spiked Carapace}{Mishram can use her carapace like a shield, allowing her to use the Brace action. When Mishram either is hit or grazed by a melee attack or is successfully Grappled or Shoved by an enemy, that enemy takes 3 (1d6) keen damage.}	\\
	
}{
	\enemyStatblockAction{Strike: Scepter}{Attack +10, reach 5 ft., one target. Graze: 3 (1d6) impact damage. Hit: 13 (1d6 + 10) impact damage. This attack gains an advantage if Mishram moved at least 10 ft. in straight line toward the target this turn.} \\
	
	\vfill
	\columnbreak
	
	\enemyStatblockAction{Strike: Carapace Claws}{Attack +10, reach 5 ft., one target. Graze: 4 (1d8) keen damage. Hit: 14 (1d6 + 10) keen damage. Mishram can use this action multiple times per turn by spending 1 Focus for each of those actions beyond the first. } \\

	\enemyStatblockAction[\iconActionDouble{}]{Bolt of Lightning (Costs 1 Investiture)}{Attack +10, range 60 ft., one target. Graze: 8 (2d8) energy damage. Hit: 18 (2d8 + 10) energy damage.} \\

	\enemyStatblockAction{Grieving Dirge (Costs 2 Investure)}{Mishram makes an Intimidation test against the Spiritual defense of a target she can influence within 30 feet of her. On a success, the target becomes \exhausted[-1].} \\

	\enemyStatblockAction{Swift Charge (Costs 3 Investiture)}{Mishram moves up to her movement rate in a straight line without triggering Reactive Strikes. When she does, Mishram can move through the spaces of Medium and smaller characters. Mishram can make an Agility attack against the Physical defense of each enemy in this line, rolling 1d6 impact damage. On a hit, the enemy is also knocked Prone.} \\

	\enemyStatblockAction{Granter of Forms (Costs 1 Investure)}{An allied tier 1 Singer Mishram can sense becomes Unconscious. That condition cannot be removed. At the end of the next round, the Unconscious condition ends and the target assumes chosen Regal Form of Power. That form recovers all Health, Focus and Investure. If the target dies before assuming the new Form, the ability ends with no effect, and Mishram regains all Investure spent to use it.} \\

	\enemyStatblockAction{Healing Touch (Costs 1 Investure)}{An allied Singer within 5 ft. recovers 11 (2d6 + 5) Health.} \\
	
	\enemyStatblockAction[\iconActionDouble{}]{Draw from the Well}{At the end of the round, Mishram recovers all Investure.} \\
	
	\enemyStatblockAction[\iconReaction{}]{Decaying Touch (Costs 1 Focus or Investure)}{Before a character within Mishram's reach recovers health or focus, she can spend 1 Focus or 1 Investiture to prevent them from doing so. The character does not regain that health or focus, but any actions, Investiture, or other resources they spent still remain spent.} \\
}
\newpage
~~ 