\section{\npcFractionWall}
\label{enemyWall}

When \npcQueen{} closed the gates of the Palace, it became clear that she has no intention to defend the people of the city. Lead by \npcHighmarshal{}, men of \npcFractionWall{} took that duty on themselves.

Despite being a woman - unprecedented in alethi culture - \npcHighmarshal{} shows great leadership skills and martial prowess, both desperately needed in those difficult times. She assumed command after the previous guard leader fell in riots and quickly ordered to assault the Monastery to secure a Soulcaster.

Despite their skilled and righteous leader, the \npcFractionWall{} cannot protect everyone... In the end, they decided to focus their attention on the city wall to defend from the Singers, leaving the streets of the city to various criminals and the \npcFractionCult{}.

\tacticsBox{
	When fighting against other Kholinar citizens, the guards seek to incapacitate and disarm their opponent instead of killing them. They will knock enemies Prone with their longspear attacks. If their opponent does not yield, they will proceed to more drastic measures. \\ \\
	A guard manning the wall will use crossbow to shoot the enemies below.
}

\tacticsBox{
	\npcHighmarshal{} wields a great power few people can recognize. However, she refuses to use it against other people. In battle, she will focus on leading an bolstering her troops, but she will never strike other humans with her blade - at least as long she doesn't feel threaten. 
}

\input{appendices/enemies/statblockWallGuard.tex}
\input{appendices/enemies/statblockSoulcaster.tex}
\input{appendices/enemies/statblockHighmarshal.tex}