\section{Midnight Essence}
\label{enemyFractionMidnight}

Deep under \locationUrithiru{} an ancient evil lurks - \npcMidnightMotherFull{}. She was tasked with one job millennia ago - to kill humans.

However, after many years of slaughter, she became curious of her prey. Now she sends her minions - black spawns made seemingly from a tar-like liquid held in a waterskin-like vessel - to learn more about humans and their cruelty. 

Her smallest children - \enemyMidnightBeast{}s are not big enough to impersonate people. Instead they can be found mimicking wild animals, often assuming a form of predators.

\enemyMidnightAssassin{} are sent into the halls of \locationUrithiru{} to observe and learn people. If a crime is committed, those creatures seek to reenact it within days. Though they try to appear as humans, they often look... wrong.

Every child of \npcMidnightMother{} is scary, but none is more terrifying than \enemyMidnightTwin{}. Those abominations look like two people sharing one twisted body with four arms and legs and two hideous faces. When one is slain, it often splits into two smaller creatures.

\tacticsBox{
	Midnight Essence creatures prefer combat in a close-range, where they can use their Formed Weapon and Mimic Violence to imitate the attack of their foes. If endangered, they will flee into the darkness to lick their wounds.
}

\newpage
\input{appendices/enemies/enemyMidnightBeast.tex}
\newpage
\input{appendices/enemies/enemyMidnightAssassin.tex}
\newpage
\input{appendices/enemies/enemyMidnightTwin.tex}