\subsubsection{\abilityTaravangianBoonName{}}
\label{enemyDiagramTaravangian}

Due to an influence of the Old Magic, the king's abilities change every day. This is represented by the following ability:

\abilityTaravangianBoon{}

To avoid unnecessary calculations, the table below captures final values of Intelligence (Int), Awareness (Awa), Cognitive and Spiritual Defenses (C.D and S.D) in relation to the result of 2d6 roll.

Please note, roll 2d6 only once and derive all the results from that singular roll. \\

\noindent
\footnotesize
\begin{tabular}{l l l l l l l l l l l l}
	2d6: & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 & 12 \\ \hline
	Int: & 0 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\ 
	Awa: & 10 & 9 & 8 & 7 & 6 & 5 & 4 & 3 & 2 & 1 & 0 \\
	C.D.: & 15 & 16 & 17 & 18 & 19 & 20 & 21 & 22 & 23 & 24 & 25 \\
	S.D.: & 25 & 24 & 23 & 22 & 21 & 20 & 19 & 18 & 17 & 16 & 15 \\
\end{tabular}
\normalsize


\subsubsection{Recognize Brilliance}

The consequences of \abilityTaravangianBoonName{} roll extend beyond the attributes, but also shape how the conversation with \enemyTaravangian{} will look like.

Whichever part of the kings personality is dominant at the moment will determine which arguments are harder to resist - both for the king and his adversaries in the Conversation. If any character succeeds a test against their enemy Defense, if that Defense is the highest one of \enemyTaravangian{}, it costs 2 Focus instead of 1 to resist it.

That works for both king and the PCs - eg. if \enemyTaravangian{} has higher spiritual attributes, his \skillPersuasion{} is harder to resist, but when an enemy successfully uses \skillPersuasion{} against him, it is more effective and costs \enemyTaravangian{} 2 Focus to resist.


\newpage
\enemyStatBlock{
	\enemyStatBlockHeader{\enemyTaravangianName{}}{3}{Boss}{Medium Humanoid}
}{
	\enemyStatBlockStats{2}{2}{5}{5}{5}{5}{76}{7}{0}
}{
	\small
	\enemyStatBlockSkills[
		\enemyStatblockSkillsMovement[25 ft.] \\		
		\enemyStatblockSkillsSenses[25 ft. (sight)]	
		\enemyStatblockSkillsCognitive[Deduction (Int +4), Dyscipline +8, Lore (Int +4)]
		\enemyStatblockSkillsSpiritual[Deception +8, Insight (Awa +4), Leaership +9, Persuasion +9]
		\enemyStatblockSkillsLanguages[kharbranthian, alethi]
	]
}{
	\enemyStatblockFeatureTaravangianBoon{} \\
	
	\enemyStatblockFeature{Recognize Brilliance}{During a Conversation, all characters must spend 2 Focus to resist an influence of a tests rolled against the Defense that is the highest of Taravangian's Defenses.} \\
	
	\enemyStatblockFeatureFutureKnowledge[4]{} \\ 
	
	\enemyStatblockFeatureBossConversation{}
}{
	\enemyStatblockAction{Control the Conversation}{Choose an attribute. Until the end of the next round, no character can use skills of that attribute while contributing to the Conversation. You cannot choose the same attribute twice in a row.}\\
	
	\enemyStatblockAction{Know Thy Enemy}{Taravangian makes a \skillDeduction{} or \skillInsight{} test against the target's respective Defense. On a success, during the target's next turn, resisting their influence costs 1 fewer Focus and if Taravangian doesn't need to resist their influence, the target looses 2 Focus instead.}
}
\normalsize