\label{enemyWindrunnerThird}


\enemyStatBlock{
	\enemyStatBlockHeader{\Large \enemyWindrunnerThirdName{}}{3}{Rival}{Medium Humanoid}
}{
	\enemyStatBlockStats{4}{4}{4}{3}{4}{2}{56 (46-66)}{5}{6}
}{
	\small
	\enemyStatBlockSkills[
	\enemyStatblockSkillsDeflect[1 (leather)] \\
	\enemyStatblockSkillsMovement[30 ft.]
	\enemyStatblockSkillsSenses[20 ft. (sight)]
	\enemyStatblockSkillsPhysical[Agility +8, Heavy Weaponry +8, Light Weaponry +8]
	\enemyStatblockSkillsCognitive[Deduction +6, Discipline +7, Lore +5]
	\enemyStatblockSkillsSpiritual[Insight +7, Perception +6]
	\enemyStatblockSkillsSurges[Gravitation +7 (3 ranks)]
	\enemyStatblockSkillsLanguages[all]
	]
}{
	\enemyStatblockFeature{Sworn to Protect}{The Windrunner's attacks gain an advantage if they target an enemy who damaged their ally during this round of combat.} \\
}{
	\enemyStatblockAction{Strike: Shardblade}{Attack +8, reach 5 ft., one target. Graze: 11 (2d10) spirit damage. Hit: 19 (2d10 + 8) spirit damage.}\\
	
	\enemyStatblockAction{Lashing Shot (Costs 1 Investiture)}{Attack +7, range 30 ft., one target. The Windrunner touches a Medium or smaller unattended object and launches it at the target. Graze: 9 (2d8) impact or keen damage. Hit: 16 (2d8 + 7) impact or keen damage.}\\
	
	\enemyStatblockAction{Offensive Gravitation (Costs 1 Investiture)}{The Windrunner makes a Gravitation test against the Physical defense of a target within reach. On a success, the Windrunner moves the target up to 25 feet in any direction, and the target becomes Restrained until the start of the Windrunner’s next turn. If the target hits an object or surface, they take 9 (2d8) impact damage. If the target passes within reach of an object that they aren’t going to hit, they can make a DC 16 Agility test, grabbing the object and stopping this forced movement on a success.}\\
	
	\enemyStatblockAction[\iconFreeAction{}]{Regenerate (Costs 1 Investiture)}{The Windrunner recovers 6 (1d6 + 3) health. They can use this free action even while Unconscious or otherwise prevented from using actions.}\\
}
\normalsize
