\section{True Spren}
\label{enemyFractionTrueSpren}

Spren who bond with Knights Radiant are called True Spren. In the Cognitive Realm they have a humanoid shape, their own culture, cities and communities. 

\tacticsBox{
	In the fight, a True Spren will choose their weapon based on a distance to the enemy. When at sea, they will attempt tho throw the enemy overboard to quickly remove them from the combat.
}


\subsubsection{Splinter of a God}

There are nine types of True Spren. Each of them gains an additional ability based on their family: \\

\ability{Honorspren}{If a melee attack misses the spren, they can strike the attacker as \iconReaction{}.}

\ability{Highspren}{All attempts to influence the spren during a Conversation gain disadvantage.}

\ability{Ashspren}{As \iconFreeAction{}, the spren can recover 1d4~Health.}

\ability{Cultivationspren}{Once per round, the spren can use Aid action as \iconFreeAction{}.}

\ability{Mistspren}{The spren does not trigger Reactive Strikes.}

\ability{Cryptic}{As \iconAction{}. the spren can advantage on all actions against the target until the end of the scene.}

\ability{Inkspren}{As an \iconAction{} the spren can spend 1~Focus to become Focused.}

\ability{Lightspren}{Keen damage against the spren is rolled with disadvantage.}

\ability{Peakspren}{The spren gains +2 Deflect. Allies can use them as a cover.}



\newpage
\input{appendices/enemies/statblockSprenTrue.tex}
\newpage
\input{appendices/enemies/statblockSprenPirate.tex}
\newpage
\input{appendices/enemies/statblockSprenCaptain.tex}

