\section{Knights Radiant}
\label{sec:enemyFractionRadiants}


People who bond with the true spren are granted the powers of surgebending and become Knights Radiant. Their knightly Orders are gathered in the Urithiru and respond to the Bondsmith. The current one, \npcDalinar{} Kholin, is doing everything in his power to unite their scattered numbers.

Each of the Orders has its own power, philosophy and traditions. Knights from each of them differ much from each other and not always get along, but they are united in one thing - their service to the humanity.

\scriptedOption{Windrunners}{
	Sworn to protect those in need, the Windrunners are the most honorable warriors to be found on the battlefield. They are excellent fighters and they often form the most efficient Radiant strike forces.
}

\scriptedOption{Lightweavers}{
	Masters of illusion and deception, the Lightweavers make great spies, agents, or assassins. They can be rarely found on the front lines of the conflict, but should they ever be in this situation, they would use their cunning and wits to their advantage.
}

\tacticsBox{
	The Knights will attempt to utilize their Radiant abilities go give them an edge in battle. However, they will always make sure to have some spare Investiture to heal their wounds.
}


\newpage
\input{appendices/enemies/enemyWindrunnerThird.tex}
\newpage
\input{appendices/enemies/enemyTruthwatcherRlain.tex}
\newpage
\input{appendices/enemies/enemyTruthwatcherRenarin.tex}
\newpage
\input{appendices/enemies/enemyLightweaverShallan.tex}



