\label{enemyGhostbloodIyatil}

\enemyStatBlockDouble{
	\enemyStatBlockHeader{\enemyGhostbloodIyatilName}{3}{Boss}{Medium Humanoid}
}{
	\enemyStatBlockStats{3}{5}{5}{4}{4}{3}{180 (160 - 200)}{6}{6}
}{
	\enemyStatBlockSkills[
	\enemyStatblockSkillsDeflect[1 (leather)] \\
	\enemyStatblockSkillsMovement[30 ft.]
	\enemyStatblockSkillsSenses[20 ft. (sight)]
	\enemyStatblockSkillsPhysical[Agility +9, Light Weaponry +9, Stealth +9]
	\enemyStatblockSkillsCognitive[Deduction +9, Intimidation +9]
	\enemyStatblockSkillsSpiritual[Deception +7, Perception +8, Persuasion +7]
	\enemyStatblockSkillsSurges[Transportation +8 (3 ranks)]
	\enemyStatblockSkillsLanguages[all]
	]
}{
	\enemyStatblockFeatureBoss{} \\
	
	\enemyStatblockFeature{Compelling Leader}{When Iyatil successfully uses the Gain Advantage action or gains an Opportunity, she can grant that advantage or Opportunity to one of her allies within 60 feet of her.} \\
	
	\enemyStatblockFeatureInurePoison{} \\
	
	\enemyStatblockFeature{\talentElsecallerKeyName{}}{At the end of her turn, Iyatil can switch between her physical form and a formless, shadowy form by spending 1 Investiture. While in her incorporeal form, all attacks made against her Physical Defense gain disadvantage, but she can attack only if she stands in a darkened area.} \\
	
	\enemyStatblockFeature{Ruthless}{After Iyatil knocks an enemy Prone, she can make an additional Strike against that target as \iconFreeAction{} on that turn (even if she has already used that Strike action).} \\
	
	\vfill
	\columnbreak
}{
	\enemyStatblockAction{Strike: Shortsword}{Attack +9, reach 5 ft., one target. Graze: 3 (1d6) keen damage. Hit: 12 (1d6 + 9) keen damage.}\\
	
	\enemyStatblockAction{Strike: Anti-Stormlight Knife}{Attack +9, reach 5 ft., one target. Graze: 2 (1d4) keen damage. Hit: 11 (1d4 + 9) keen damage. That attack ignores Deflect value of Shardplates. Once per scene, after hitting an enemy, Iyatil can infuse them with Anti-Stormlight - until the next Long Rest, if that enemy uses Stormlight Investiture, they immediately die. } \\
	
	\enemyStatblockAction{\talentElsecallerDirgeName{} (Costs 2 Investiture)}{Iyatil makes an Intimidation test against the target's Spiritual Defense. On a success, the target becomes \exhausted[-1]. \\
	While Iyatil is in her incorporeal form, that action costs only 1 Investiture.} \\
	
	\enemyStatblockAction{\talentElsecallerMistyStepName{} (Costs 1 Investiture)}{If Iyatil is standing in a darkened area, she can move to any other darkened place you can see within 60 feet. This does not trigger Reactive Strikes.\\
	While Iyatil is in her incorporeal form, that action does not require spending Investiture.} \\
	
	\enemyStatblockAction[\iconFreeAction{}]{Regenerate (Costs 1 Investiture)}{Iyatil recovers 1d6 + 3 Health.} \\
	
	\enemyStatblockAction[\iconActionDouble{}]{Intimidate (Costs 1 Focus)}{Iyatil makes an opposed Intimidation test against the Discipline of a target she can influence. If Iyatil succeeds, the target loses 1 Focus and is no longer Focused.} \\
	\\
	
	\begin{center} \MakeUppercase{\textbf{Opportunities and Complications}} \end{center}
	{\color{goldStats} \hrule \vspace{0.5cm} }
	
	The following options are available when an enemy gains an Opportunity or Complication during a scene with \enemyGhostbloodIyatilName{}:
	
	\scriptedOption{Opportunity}{An enemy can spend \iconOpp{} to prevent \enemyGhostbloodIyatilName{} from using \lootAntiStormlightDagger{} during her next turn.}
	
	\scriptedOption{Complication}{The GM can spend \iconComp{} from an enemy’s test to increase the number of charges in \enemyGhostbloodIyatilName{}'s \lootAntiStormlightDagger{} by 1.}
}
\newpage
~~ 