\label{enemyLightweaverShallan}

\enemyStatBlockDouble{
	\enemyStatBlockHeader{\enemyLightweaverShallanName}{4}{Boss}{Medium Humanoid}
}{
	\enemyStatBlockStats{3}{5}{5}{3}{4}{5}{200 (180-220)}{5}{7}
}{
	\enemyStatBlockSkills[
		\enemyStatblockSkillsDeflect[1 (leather)] \\
		\enemyStatblockSkillsMovement[30 ft.]
		\enemyStatblockSkillsSenses[20 ft. (sight)]
		\enemyStatblockSkillsPhysical[Athletics +8, Heavy Weaponry +8, Light Weaponry +10]
		\enemyStatblockSkillsCognitive[Deduction +10, Lore +10]
		\enemyStatblockSkillsSpiritual[Deception +10, Perception +9, Persuasion +9]
		\enemyStatblockSkillsSurges[Illumination +9 (4 ranks)]
		\enemyStatblockSkillsLanguages[alethi, veden]
	]
}{
	\enemyStatblockFeatureBoss{} \\
	
	\enemyStatblockFeature{Infiltrator}{Shallan can spend 1 Focus to gain an advantage on a Deception, Insight, or Persuasion test.} \\
	
	\enemyStatblockFeature{Reflexive Illusion}{At the start of a scene, if Shallan is not Surprised, she can use her Illusory Disguise (no action required).} \\
	
	\vfill
	\columnbreak
}{
	\enemyStatblockAction{Strike: Knife}{Attack +10, reach 5 ft., one target. Graze: 2 (1d4) keen damage. Hit: 12 (1d4 + 10) keen damage, and if Shallan had at least one advantage on the attack, it deals an extra 5 (2d4) keen damage. }\\
	
	\enemyStatblockAction{Strike: Shardblade}{Attack +10, reach 5 ft., one target. Graze: 11 (2d10) spirit damage. Hit: 21 (2d10 + 10) spirit damage.}\\
	
	\enemyStatblockAction{Illusory Disguise (Costs 1 Investiture)}{Shallan creates an illusion to disguise herself as another character. While disguised, Shallan has an advantage on attack tests against enemies unaware of their ruse. This disguise continues until they end it as \iconFreeAction{} or use this action to change it.} \\
	
	\enemyStatblockAction[\iconActionDouble{}]{Cunning Tongue}{Shallan weaves manipulative words around an enemy they can influence, making a Deception or Persuasion test opposed by the target’s Insight. Shallan gains an advantage on this test if they know one or more of the target’s goals, their purpose, or their obstacle. If Shallan succeeds, the target loses 1d4 Focus.} \\
	
	\enemyStatblockAction{Spiritual Illumination (Costs 2 Investiture)}{Shallan or her ally becomes Determined and Focused.} \\
	
	\enemyStatblockAction{Painful Truth (Costs 2 Investiture)}{Shallan tests Illumination vs. Spiritual of a target. On success, they are Slowed and must Move away on their next turn or spend Focus to avoid doing so.} \\
	
	\enemyStatblockAction[\iconFreeAction{}]{Regenerate (Costs 1 Investiture)}{Shallan recovers 7 (1d6 + 4) health. They can use this free action even while Unconscious or otherwise prevented from using actions.}\\
	
}
\newpage
~~
