\section{The Diagram}
\label{enemyFractionDiagram}

In the past, during a day of godlike intelligence, \npcTaravangian{} written down "The Diagram" - a set of enigmatic notes, graphs and ciphers describing his prophetic predictions for the future events. 

The king's secret society, named after the Diagram, now works in shadows of \locationKharbranth{} to do whatever is necessary to ensure the survival of humanity in the upcoming Desolation.

\tacticsBox{
	Diagram forces rely on their knowledge about future events. Both in combat and conversations, they will reach for that knowledge to use their \abilityFutureKnowledgeName{} abilities, allowing them to re-roll unwanted roll results.}


\subsubsection{\abilityFutureKnowledgeName{}}

Due to the access to predictions written down in "The Diagram" reinforced by Death Rattles gathered in \locationKharbranth{} hospitals, the Diagram has a limited knowledge about the future events. This is represented by \abilityFutureKnowledgeName{} feature:

\abilityFutureKnowledge{}

At the beginning of a Combat or a Conversation scene with the Diagram, roll specified number of d20s for each of the adversaries in the scene and note the results. Those characters can use them to replace unwanted rolls during the scene.

To simplify the management, note only the results of the rolls, but you can refrain from tracking which value is owned by which NPC. Instead allow them to share the pool, just make sure no NPC can use their ability more times than specified in their stat block.



\newpage
\input{appendices/enemies/enemyDiagramSurgeon.tex}
\newpage
\input{appendices/enemies/enemyDiagramScribe.tex}
\newpage
\input{appendices/enemies/enemyDiagramMuscle.tex}
\newpage
\input{appendices/enemies/enemyDiagramMalata.tex}
\newpage
~~ \newpage
\input{appendices/enemies/enemyDiagramTaravangian.tex}
