\section{\enemyAxehoundName{}}
\label{enemyAxehound}

Not only the people are subjected to the hunger troubling the city. Lack of food is affecting also the animals. Axehounds are not exception - without proper nourishment, their packs scour the city in hopes to find anything edible. Once they pick up the scent, they won't be stopped by any obstacle.

Kholinar breed of the Axehounds is slightly bigger and more aggressive than their cousins. Their carapace has more vibrant, red hue, marked with black and orange spots.

\tacticsBox{
	\enemyAxehound{}s often work in a group and they gladly accept human leadership over their pack. They focus their efforts on one enemy, attempting to knock them prone and surround it with their On the Hunt reaction. They prefer sticking close to each other to benefit from their Pack Instincts.
}

\newpage
\enemyStatBlock{
	\enemyStatBlockHeader{\enemyAxehoundName{}}{1}{Minion}{Small Animal}
}{
	\enemyStatBlockStats{2}{2}{0}{0}{3}{0}{12 (9-15)}{2}{0}
}{
	\enemyStatBlockSkills[
		\enemyStatblockSkillsMovement[40 ft.]\\
		\enemyStatblockSkillsSenses[40 ft. (smell)]
		\enemyStatblockSkillsPhysical[Agility +4, Athletics +4, Stealth +3]
		\enemyStatblockSkillsSpiritual[Perception +5, Survival +4]
		\enemyStatblockSkillsLanguages
	]
}{
	\enemyStatblockFeature{Enhanced Senses}{The axehound gains an advantage on non-attack tests that rely on smell.} \\
	
	\enemyStatblockFeature{Hungry}{The axehound gains an advantage on \skillPerception{} tests to sense food.} \\
	
	\enemyStatblockFeatureMinion{}
}{
	\enemyStatblockAction{Strike: Bite}{Attack +4, reach 5 ft., one target. Graze: 2 (1d4) keen damage. Hit: 6 (1d4 + 4) keen damage, and if the target is Medium or smaller, the axehound can spend 1 focus to knock the target Prone, then move up to 10 feet while dragging the target behind them.}\\

	\enemyStatblockAction[\iconFreeAction{}]{Pack Instincts}{While within 5 feet of an ally, the axehound can use the Gain Advantage action as \iconFreeAction{}.} \\
	
	\enemyStatblockAction[\iconReaction{}]{On the Hunt}{After an enemy within 30 feet of the axehound falls Prone, the axehound moves up to 15 feet toward them.}
}
