\label{enemyWallGuardHighmarshal}

% From Brightlord
\enemyStatBlock{
	\enemyStatBlockHeader{\enemyWallGuardHighmarshalName}{2}{Boss}{Medium Humanoid}
}{
	\enemyStatBlockStats{2}{4}{6}{3}{6}{4}{54}{5}{8}
}{
	\enemyStatBlockSkills[
	\enemyStatblockSkillsDeflect[4 (Full Plate)] \\
	\enemyStatblockSkillsMovement[30 ft.]
	\enemyStatblockSkillsSenses[50 ft. (sight)]
	\enemyStatblockSkillsPhysical[Agility +7, Light Weaponry +7]
	\enemyStatblockSkillsCognitive[Deduction +4, Discipline +6, Intimidation +7]
	\enemyStatblockSkillsSpiritual[Insight +9, Leadership +7, Persuasion +6]
	\enemyStatblockSkillsLanguages[all]
	]
}{	
	\enemyStatblockFeature{Nalthian Awareness}{\enemyWallGuardHighmarshalName{} gains an advantage on all Awareness skill tests. She can sense spren and invisible characters.} \\
	
	\enemyStatblockFeature{BioChromatic Sword}{The Highmarshal wields \lootHighmarshalsBlade{}.}
		
}{
	\enemyStatblockAction{Shield Up}{Target ally increases their Physical Defense by 2 until the end of the next round. This action can be used multiple times in a single round.}\\
	
	\enemyStatblockAction{Strike True}{Target ally gains and advantage on their next attack. This action can be used multiple times in a single round.} \\
	
	\enemyStatblockAction[\iconActionDouble]{Form a Line}{All allies can each spend 1 Focus to move up to their speed as \iconReaction{}. Until the end of the next round, all attacks targeting Azure's allies standing within 5 ft. of a friendly character gain disadvantage.}\\
	
	\enemyStatblockAction[\iconFreeAction]{Invested Healing}{Azure can spend 1 Investiture to recover 5 (1d6 + 2) Health.} \\
	
	\enemyStatblockAction[\iconReaction]{Parry, Riposte}{Before Azure is hit with a melee attack, she can add her Light Weaponry skill to her Physical Defense. If the attack misses as a result, she can strike the attacker: Attack +7, reach 5 ft., one target. Graze: 13 (2d12) spirit damage. Hit:~20~(2d12~+~7) spirit damage.}
}