\label{enemySoulcaster}

% From Soulcaster Savant
\enemyStatBlock{
	\enemyStatBlockHeader{\enemySoulcasterName}{2}{Rival}{Medium Humanoid}
}{
	\enemyStatBlockStats{1}{2}{2}{4}{5}{3}{32 (25–39)}{6}{0}
}{
	\enemyStatBlockSkills[
	\enemyStatblockSkillsMovement[25 ft.] \\
	\enemyStatblockSkillsSenses[50 ft. (sight)]
	\enemyStatblockSkillsCognitive[Discipline +7, Intimidation +6, Lore +4]
	\enemyStatblockSkillsSpiritual[Insight +8, Survival +8]
	\enemyStatblockSkillsLanguages[alethi, herdazian, veden]
	]
}{	
	\enemyStatblockFeature{Soulcaster Essences}{The Soulcaster’s fabrial is set with three emeralds. If one of the Soulcaster’s attacks reduces an enemy to 0 Health, the enemy is killed and transforms into the corresponding Essence.} \\
		
}{
	\enemyStatblockAction{Wood}{Attack +7 vs. Spiritual, reach 5 ft., one target. Graze: 3 (1d6) spirit damage. Hit: 10 (1d6 + 7) spirit damage, and the Soulcaster can spend 1 Focus to make the target Slowed until the end of the target’s next turn.}\\
	
	\enemyStatblockAction[\iconActionDouble]{Moss}{Attack +7 vs. Spiritual, reach 5 ft., one target. Graze: 7 (2d6) spirit damage. Hit: 14 (2d6 + 7) spirit damage.}\\
	
	\enemyStatblockAction[\iconActionDouble]{Vines}{The Soulcaster transforms ground into thorny vines. Each enemy within 5 feet of them takes 9 (2d8) keen damage. The Soulcaster can spend 1 Focus per enemy in range to make that enemy Restrained. As \iconActionDouble{}, they can make a DC 17 Agility test to remove that condition.}\\
	
	\enemyStatblockAction[\iconActionDouble]{Soulcasting}{The Soulcaster touches a Medium or smaller object and makes a DC 17 Discipline test. On a success, they transform the object into one of their Essences. They can spend 2 Focus to target a Large object instead.}\\
	
	\enemyStatblockAction[\iconReaction{}]{Soulcast Protection (Costs 2 Focus)}{Before a ranged attack hits the Soulcaster or an ally within 5 feet of them, the Soulcaster makes a Discipline test. If their result is greater than the triggering attack test, the Soulcaster causes the attack to miss.}
}