\chapter{Chapter 5 - Revel of Fools}
\label{chap:chapter5}

\setcounter{section}{-1}
\section{Running This Chapter}

The PCs reached the gates of the Monastery controlled by \npcFractionCult{}. To reach the Circle of Memories, they will need to enter the ongoing Revel conducted by \npcHeartRevel{}.

\reasonBox{
	Festivities influenced by \npcHeartRevelTitle{} are the most indecent and scandalous events of indulgence in the entire \bookSA{} series or perhaps even in the whole grand Cosmere. In this book I will not dare to go much further than family-friendly descriptions of tattered sleeves on a safehand, but it is possible go much further and darker than that. \\ 
	\textbf{IMPORTANT:} If you do, please make sure beforehand that you do not exceed the boundaries of a comfortable roleplay for everyone on the table! \textit{(see \fullref{ssec:playersExpectations})}
}

\reasonBox{
	\textbf{IMPORTANT:} If you find some of the encounters here too intense for your group, please modify them or straight up remove the from this chapter.
}

\subsection{Character Advancement}

The characters start this chapter at level 5. Advance them to level 6 at the end of the chapter.

The following events may affect their path to radiance:
\begin{itemize}
	\item Solution to enter through the Revel gates.
	\item Joining or resisting the Revel.
	\item Helping or eliminating the revelers.
	\item The proximity of \npcHeartRevel{}, the \npcHeartRevelTitle{} may expedite an Enlightened Willshaper.
	\item Seeing \npcMidnightMother{}, the \npcMidnightMotherTitle{} in the Spiritual Realm vision may expedite an Enlightened Edgedancer.
	\item Seeing \npcMishram{} in the Spiritual Realm vision may expedite an Enlightened Stoneward.
\end{itemize}

\newpage
\subsection{Forging Alliances}

The following actions can help the characters to become allies with Kholinar fractions:
\begin{itemize}
	\item Joining \npcFractionCult{} is a sure way to make an alliance with them.
	\item Joining forces with \npcFractionCrime{} can lead to an alliance with them.
\end{itemize}


\input{chapter_5/revelryGates.tex}
\input{chapter_5/cultRevelry.tex}
\newpage
\input{chapter_5/heartOfTheRevel.tex}
\input{chapter_5/spiritualVisions.tex}

\section{Journeying Onward}

Once the characters are transported to Shadesmar, advance them to level 6 and proceed to the next chapter.