\section{Revelry}
\label{sec:revelry}

The characters are entering the Revelry of \npcFractionCult{}. If they entered through the gates, the party will start at \fullref{ssec:revelryStairs}.

\subsubsection{Loosing Oneself in the Indulgence}

Each time a character freely chooses to participate in revelry activities (by eg. eating food, enjoying drinks, joining the dance, etc), they slowly loose their resolve as they are more and more influenced by \npcHeartRevel{}.

Each time that happens, they loose 1 Focus and Maximum Focus and they cannot regain it as long as they are in the area influenced by \npcHeartRevelTitle{}.


\spoilerBox{
	\npcShallan{} entering the revel is described in \bookOB{}, Chapter 78. The Revel.
}




\subsection{Steps to Enlightenment}
\label{ssec:revelryStairs}

When the PCs approach the stairs, read the following:

\quoteBox{
	Just behind the gates, there are long stairs leading to the Monastery Dais. Up above, at the top of them, you can see a red glow of an ongoing revelry.
}

Each PC climbing the stairs must do \skillCheck{10}{\skillAthletics{}}. On a failure, the character is \exhausted{} until the next short rest.

After reaching the top of the stairs, the characters enter \fullref{ssec:revelryVillage}.




\subsection{Monastery Village}
\label{ssec:revelryVillage}

Once the party reaches this location, read the following:

\quoteBox{
	In here, the Monastery buildings are smaller, looking like a village inside the city. On your right you can see a blazing bonfire. On your left the Sunwalk leads to the Kholinar Palace.
}

From here, the characters could go to \fullref{ssec:revelrySunwalk}, though there is little to do there. Another path leads to \fullref{ssec:revelryBonefire}.

If the party was invited by the \npcFractionCult{} to join them, there will be a \enemyCultist{} waiting for them. In that case, read the following:

\quoteBox{
	In the middle of a path between the buildings you can see a man in a dirty, greased ardent robes. \\
	"Welcome! I am your guide tonight!", he says. "You can call me... \npcRevelerGuide{} I believe...? It doesn't matter, really..."
}

\npcRevelerGuide{} will accompany the party. He will show them the revelry, but he won't allow them to enter \fullref{ssec:revelryInner} - the party will need to get rid of him before reaching the Circle of Memories, though it shouldn't be a very hard task for them.



\newpage
\subsection{The Sunwalk}
\label{ssec:revelrySunwalk}

When characters enter the Sunwalk, read the following:

\quoteBox{
	You step on the Sunwalk, a long stone walkway leading to the Kholinar Palace. From here you can see the majestic royal residence, but there is nothing for you to find there. Your path leads to the center of the Revelry.
}

There is nothing to do here, the characters should go back. If they persist on walking the Sunwalk, they will soon meet \enemyQueensGuard{}s guarding the palace. They will be friendly for anyone approaching from the Revelry, but they will deny them entrance.

\reasonBox{
	There is nothing important in here to do, this location is added only to align with the official lore.
}




\subsection{The Bonefire}
\label{ssec:revelryBonefire}

When characters reach this place, read the following:

\quoteBox{
	In the center of the revelry, huge bonfire blazes away the darkness of the night. A few flamespren - jagged and blue - dance in its flames. Around it, the revelers in rich clothing dance to the shrieking sounds of flutes playing. \\ \\
	A bit further, there is a ring of tables full with food and wine. A women in purple havah, with her safehand sleeve torn and tattered, walks between them, enjoying the feast. 
}

This is the central part of the Outer Ring revelry. There is delicious food, expensive wine, music, dance and laughter.

From here the PCs can quickly reach \fullref{ssec:revelryStatues}. To reach the Circle of Memories, they will need to walk next to \fullref{ssec:revelryPrivate}.

\corruptedBox{
	Being present on the revelry influenced by \npcHeartRevel{}, the \npcHeartRevelTitle{}, can expedite the progression of an Enlightened Willshaper.
}

\subsubsection{Food Tables}

The tables around the bonfire are laid with an abundance of food. A hungry PC can feast on it to remove any related penalties.

Between the tables walks \enemyRevelerDrinking{}. A bit further there are five \enemyCultist{}s. They are indulging in food and wine. \enemyRevelerDrinking{} will invite characters to join, turning hostile if refused. \enemyCultist{}s will join her, but other revelers will be oblivious to the fight.

\subsubsection{Dancing Floor}

Some of the revelers are dancing around the bonfire, including two \enemyRevelerWealthy{}s, two \enemyRevelerMusical{}s and three \enemyCultist{}s. A character can join the dance to attempt stealing riches or breath Stormlight from them.

The dancers will ignore the party, unless a character enters their midst without proper dance, at which point they will turn hostile. \enemyRevelerWealthy{} will also attack anyone he suspects of stealing his glowing rings (either by taking the rings or breathing their Investure).





\subsection{Herald's Statues}
\label{ssec:revelryStatues}

When characters approach the statues, read the following:

\quoteBox{
	You see a reveler facing a statue of Jezerezeh, standing one foot from a splattered stone surface. With a bottle risen high, he drinks straight from it. Next to him, another one lies on the floor, paying no heed to the puddle soaking his clothes.
}

The party finds two \enemyRevelerDrinking{}s in here (one of them lies Prone). They will ignore the PCs, but they will turn hostile when attacked, fighting to the end.

There is nothing beyond this place - only the edge of the platform and a long way down.




\subsection{Meditation Rooms}
\label{ssec:revelryPrivate}

When party enters this location, read the following:

\quoteBox{
	You step into relatively quiet rooms. Once, ardents used to meditate in here. Now it is occupied by revelers seeking a bit of privacy. Most of the doors are closed; a few of them - invitingly opened.
}

The party can rest shortly in here. However, they can see that long rest is not safe in here. If they decide for one regardless, after roughly an hour (once the short rest is completed) three \enemyRevelerSadistic{}s will approach them from the nearby rooms. They will invite the PCs to share the ecstasy of the revel and will turn hostile if the PCs refuse.

If a character investigates the nearby rooms, they will see one of them is unexpectedly quiet. Behind a locked doors (\skillCheck{15}{\skillThievery} to open, \skillCheck{20}{\skillAthletics} to break), they will find \fullref{ssec:revelryPrison}.

Path from this location leads straight to \fullref{ssec:revelryInner}.




\subsection{Imprisoned \npcRevelerGeneral{}}
\label{ssec:revelryPrison}

If the characters investigate this location, read the following:

\quoteBox{
	You see a dark room, with almost no sounds of the revelry coming from the outside. In the middle there is a young woman sitting on the cold stony floor.
}

The party can talk with the NPC. She will be thankful for freeing her and will join the party, though she will not be very helpful. If the characters decide to talk with the girl, she will share the following information:

\scriptedOption{Who are you?}{
	They named me \npcRevelerGeneral{}, I believe...? I'm not sure... I don't remember?
}

\scriptedOption{What is your real name?}{
	My real name...? I don't think I have one, I don't remember...
}

\scriptedOption{What are you doing here?}{
	The heart... I was hearing its beating... Calling me, inviting me in... I was curious. I joined them, but they locked me up.
}

\scriptedOption{Why were you locked?}{
	I told them nobody will tell me what to do... I am my own master, I will not follow orders from a spren. They did not like that.
}


\reasonBox{
	\npcRevelerGeneral{} is an inspiring Enlightened Dustbringer, though she did not develop any significant powers yet. She will keep away from danger, but if everything else fails, you can use her to activate the Oathgate. The main reason for her to be in this part of the story is to have a backup solution if the party looses all of their Radiant Knights before reaching the Circle of Memories. 
}

\reasonBox{
	\npcRevelerGeneral{} has no ties to this story. You can insert any NPC that would be significant for the players. Perhaps \npcTroublemaker{} survived? Or maybe someone from a PC's backstory can be found in here?
}




\newpage
\subsection{Inner Ring}
\label{ssec:revelryInner}

When the PCs enter the Inner Ring, read the following:

\quoteBox{
	In the unnatural darkness, you can see a people crawling on the floor. Once lighteyes, now filthy, in tattered rags and madness in their eyes. All of them are giggling or muttering, enslaved by their twisted emotions. \\ \\
	Everywhere around lie heaps of spoiled food, rotspren crawling all around them. One of the revelers grabs a handful of it and pushes it into her mouth, smiling at you with her bleeding mouth.
}

The scenery in unnaturally unnerving. Each character must pass a \skillCheck{20}{\skillDiscipline} or loose 1 Focus. PCs who bonded an Enlightened spren gain an advantage on this roll. Each time a character chooses to interact with any of the Revelers, they must repeat the \skillDiscipline{} test.

Crawling on the floor there are two \enemyRevelerDrinking{}s, one \enemyRevelerWealthy{}, one \enemyRevelerMusical{} and five \enemyCultist{}s. They are ignoring the PCs. If attacked, they will turn hostile for one turn, before they return to giggling and crawling.

From here there is a short path to \fullref{ssec:revelryCenter}. 







\subsection{Circle of Memories}
\label{ssec:revelryCenter}

When the characters reach the center of the platform, read the following:

\quoteBox{
	You approach the Circle of Memories, the very place \npcSjaAnat{} instructed you to find. However, your path is blocked - a huge black mass of flesh overgrows the central building. It beats with a slow and deep rhythm, like a giant heart. \\ \\
	"Give in! \\
	Join the revel!" 
}

The party reached the Circle of Memories, but it is blocked by \npcHeartRevelTitle{}. Proceed to \fullref{sec:heartOfTheRevel}.

