\section{\npcHeartRevelTitle}
\label{sec:heartOfTheRevel}

When the PCs face \npcHeartRevelTitle{}, read the following:

\quoteBox{
	Thundering, irregular rhythm echoes in your skull. So loud... entire city must hear it, entire Alethkar! \\ \\
	And this alluring voice... "Give up your pain! Give up your loss! Embrace the end, and relish in it!"
}

The party stands against \enemyHeartOfTheRevel{}. The foe it is invulnerable to most weapons, but the characters must defeat it to get inside the building. Run this encounter as a conversation.

\conversationDefence{\enemyHeartOfTheRevel{}}{18}{22}{9}
It recognizes and respects essence of Odium - it might be more responsive to actions of characters influenced by other Unmade.

It is more a force of nature than a intelligent opponent - it is unable to be persuaded and it won't bargain, but if the characters present will strong enough, it might be weakened enough to unblock the path. 

\conversationEnd{\enemyHeartOfTheRevel{}}{1}

\reasonBox{
	Despite being run as a conversation, this is final boss fight of the act I. Try to make it as epic as possible, even if there is little sword swinging.
}

\corruptedBox{
	Seeing \npcHeartRevel{}, the \npcHeartRevelTitle{}, can expedite the progression of an Enlightened Willshaper \seeCorruptedRules{}.
}

\subsubsection{Little Eloquence}

\npcHeartRevelTitle{} does not possess human level of intelligence. It is more a force of nature made manifest, a huge and terrifying beast of a spren, but still - only a beast. 

It will not ask or answer questions, it will not present well-formed arguments, nor will it show any nuance or finesse in this conversation. Instead, it's voice will carry simple thoughts and concepts:

\quoteBox{
	\centering
	Give in! \\
	Join us! \\
	Embrace the end! \\
	Feast! Drink! Dance! \\
	Revel! Indulge! Relish! \\
	Give me your pain! Your longing! \\
}

\subsubsection{Battlefield Effects}

The following items can be found nearby. A character may interact with any of them if they so wish.

\scriptedOption{Rotten Food.}{
	Heaps of food, once delicious, now spoiled and infested with rotspren.
}

\scriptedOption{Shards of Glass.}{
	Wine Glasses lie shattered on the floor. It can painfully hurt, but is not dangerous.
}

\scriptedOption{Ruined Art.}{
	Paintings, sculptures and other works of art lie under the rotten food. All of them are ruined and worthless.
}

\subsubsection{Opportunities and Complications}

You can use following table as an inspiration for ideas for the Plot Die rolls: \\

\oppCompTable{
	\oppCompRow{\iconOpp}{In the heaps of rotten food you find a sphere infused with Stormlight. Regain 1 Investure.}
	\oppCompRow{\iconComp}{One of the Inner Ring revelers joins the fight for the next round.}
}

\subsubsection{Out of Focus}

If during the conversation with \enemyHeartOfTheRevel{} a character has no more Focus to spend when they're being influenced by the Unmade, they are consumed by the overwhelming desire to indulge and they loose themselves in the revel, becoming \unconscious{}.

\reasonBox{
	Depending on the difficulty level your group wants to play on, this may either affect them until the end of the scene, or it can be equivalent of mental death of the character. Please talk with your players beforehand how hardcore should the game be (see \fullref{ssec:playersExpectations}).
}

\subsubsection{Hour of Need}

If the battle goes poorly, consider unexpected reinforcements helping the party in the crucial moment. 

If freed, allow \npcRevelerGeneral{} to step in with heroic determination, aiding a PC and granting them an advantage on their next test.

If \npcRevelerGeneral{} is unable to join, consider similar help from \npcSjaAnat{} herself, appearing as a PC's shadow pointing towards the source of light.




\subsubsection{Conversation's End}

If \enemyHeartOfTheRevel{} is out of focus, it will retreat inside the stony platform, allowing the characters to enter the Circle of Memories. Proceed to \fullref{ssec:heartOfTheRevelOathgate}.

If all characters loose themselves in the revel, the scene ends. They can wake up the following morning - proceed to \fullref{ssec:heartOfTheRevelTPK}.

\reasonBox{
	If your players are here to accept consequences of their failures and would find it insulting to Deus-Ex-Machina them back to life, you can also consider this TPK an epic end to the adventure. 
}



\subsection{The Morning After}
\label{ssec:heartOfTheRevelTPK}

If the party lost their conversation with \npcHeartRevel{}, read the following:

\quoteBox{
	You wake up the following morning... Or was it an entire eternity...? Your heads are pounding, your skulls feel like a wine glasses shattered to a myriad tiny shards. Your clothes are torn to pieces and most of your possessions are gone. \\ \\
	"I did expect better from my children", you hear the voice of \npcSjaAnat{} forming out of your shadow. "Nevertheless, the spren of Odium was a formidable foe. It wasn't easy to bring your mind back..."
}

\npcSjaAnat{} brings the PCs back to consciousness. They are \exhausted[-2] and stripped of most of their possessions. Luckily, \lootGateOpener{} can be found nearby - the characters can continue to \fullref{ssec:heartOfTheRevelOathgate}.




\subsection{The Oathgate}
\label{ssec:heartOfTheRevelOathgate}

When the characters enter the Circle of Memories, read the following:

\quoteBox{
	You enter a round building. Light from the spheres illuminates mosaics that decorate the walls. On the other side of the building you can see a metal device, looking like a keyhole.\\ \\
	"We made it!", your spren says. "The~Gate, it's here! Summon me, I can open it!"
}

Any Radiant can summon their spren as a Shardblade to activate the Oathgate. When they do, all characters standing in the room are transported away from the Physical Realm - proceed to \fullref{sec:visionsEnterShadesmar}.

\reasonBox{
	If your player's Radiant did not develop a talent to summon their Shardblade yet, please don't wait for that. Allow them for one-time Shardblade summon not to hinder the flow of the story.
}

\reasonBox{
	Any Radiant can activate the Oathgate - Enlightened or not - but it must be a Radiant. If the party has lost their Radiant in the recent events, consider a helping hand from \npcRevelerGeneral{} or allow a PC for a last-minute bonding. Enlightened Lightspren should lurk nearby, attracted by the revel.
}