\section{Hateful Vision}
\label{sec:visionsEnterShadesmar}

When any Radiant activates the Oathgate, read the following:

\quoteBox{
	In a flash of blinding light you are transported to a different place, different time, different self... \\ \\
	You wear a body of a Singer, standing in a ranks of a Singer army. The commander - a femalen with a proud and regal face streaming shadowy smoke behind her - approaches you and lays her carapaced hand on your shoulder. \\ \\
	"I am proud of you, my children, all of you!", she says. "But the fighting is not done, and will never be done while the children of Honor live", she adds, pointing upwards. Human figures are flying there, leaving streams of pale blue light behind them.
}

Allow PCs for some quick interactions with other characters in the vision. After a few moments, proceed to \fullref{sec:visionsEnterShadesmarMidnight}.

\reasonBox{
	If your party prefers combat encounters more and you believe they might feel unsatisfied with the conversation as a final boss fight, you can expand the vision to include a proper battle. However, to keep the chapter pacing, I decided not to do that.
}

\corruptedBox{
	Seeing \npcMishram{} can expedite the progression of an Enlightened Stoneward \seeCorruptedRules{}.
}



\subsection{Midnight Reinforcements}
\label{sec:visionsEnterShadesmarMidnight}

After a moment, continue the vision with the following:

\quoteBox{
	"Your gods may have abandoned you...", \npcMishram{} continues. "But I will never! I am standing with you, and so are our allies!" \\ \\
	You look around and you see them: troops black as a tar, glistening like oil, moving through your ranks with a nightmarish grace. One turn to you and smiles with a terrifying sneer, before squeezing its body to move forward.
}

Again, you can give the PCs a few moments to interact with the scene. Once you are ready to end the vision, proceed to \fullref{sec:visionsEnterShadesmarHate}.

\reasonBox{
	\npcMishram{} and \npcMidnightMother{} appearing in the visions have two purposes. For one, they foreshadow the future chapters. But more important is a possibility to expedite Enlightened Stonewards and Enlightened Edgedancers - the Unmade related to their Orders appear much later in the story, and it would feel bad and unbalanced to keep that bonus away from the players for most of the game.
}

\corruptedBox{
	Seeing the children of \npcMidnightMother{}, the \npcMidnightMotherTitle{} can expedite the progression of an Enlightened Edgedancer \seeCorruptedRules{}.
}


\newpage
\subsection{Flash of Hatred}
\label{sec:visionsEnterShadesmarHate}

As a final part of the vision, read the following:

\quoteBox{
	Suddenly, \npcMishram{}'s face changes: her pride and determination vanished, replaced by a tormented visage of spite and hatred. \\ \\
	"I will destroy you!", she screams at you. "I will skin you alive! I will break every bone in your body, and your cries will be a music for my ears!" \\ \\
	The vision starts to unravel into misty streams, everything turning pale, but you still hear her threats for some more time: "I will pull every tooth and nail! I will boil your tortured body! I will..."
}

With the vision ending, proceed to \fullref{sec:visionsEnterShadesmarEnd} before completing the chapter.

\spoilerBox{
	\npcMishram{} appearing in Spiritual Realm visions is described in multiple chapters in \bookWAT{}.
	Her similar changes of personality are shown in Chapter 76. Concessions.
}



\subsection{Shadesmar}
\label{sec:visionsEnterShadesmarEnd}

When the vision ends, read the following:

\quoteBox{
	You are thrown out of the vision into the realm of darkness. You land on a stony platform under a black sky. When you stand up, you see that the platform is just a small island on the endless sea of small glass beads.
}

The characters find themselves in the Cognitive Realm - the Shadesmar. Take a moment to describe their spren in here, then proceed to the next chapter.