\chapter{Chapter 4 - Aid for the Desperate} 

\setcounter{section}{-1}
\section{Running This Chapter}

In this chapter, the characters will have an opportunity to prepare for their final confrontation with \npcSprenVines{}. 

The book suggests three separate paths on which the PCs may get help. You can run those in any order. Characters may decide to skip some of them.

Each of the paths offers easy way to get some generic support for characters' quest, but they have also an opportunity for much more unique rewards, required to unlock one of the story endings. Those are harder to earn, though, and the characters must approach each of those attempts with caution.

\reasonBox{
	Apart from support earned, the plot of this chapter has little connection to the main story. You can easily modify this chapter to better align with backstories of the PCs.
	\\ \\
	Each of the arcs in this chapter ties to one of the ways of dealing with the Red Vines at the end of the story. Before you modify this chapter, please see \fullref{sec:finalBoss} to plan for possible endings of your story.
}


\subsection{Character Advancement}

Characters start this chapter at 4th level. Advance them to 5th level once they return to the island.

The following decisions offer opportunities to introduce spren, strengthen spren bonds, or swear Ideals:

\begin{itemize}
	\item How does a character behave in artifabrian workshop.
	\item How does a character act when facing a Shardbearer.
\end{itemize}

\input{chapter_4/supportRequest.tex}
\input{chapter_4/supportRira.tex}
\input{chapter_4/supportIri.tex}
\input{chapter_4/supportReshi.tex}

\section{Journeying Onward}

If the characters believe they are ready to resolve the threat of the Red Vines, they can return to the island. Proceed to the next chapter.



