\newpage % manual newpage to micromanage page layout
\section{Threat of the Undying}

After conflict revolving around treating \npcSickGirl{} is resolved, read the following:

\quoteBox{
	You see \npcBabsk{} rushing towards you with an angry stride.
	\\ \\
	"Those Red Vines... They're an abomination! It's not natural! The heralds would demand their destruction and so shall we do! We should spread the word, gather allies and remove this damned infestation from the face of the Allmighty's world!"
}

The party should consider what do they know about the Red Vines and think of some ways of dealing with it. If nobody from the party reaches any ideas, \npcBabsk{} should suggest the below options:

\begin{itemize}
	\item Artifabrian help (see \fullref{ssec:helpArtifabrian})
	\item A Shardblade (see \fullref{ssec:helpShardblade})
	\item Help from other Reshi (see \fullref{ssec:helpReshi})
\end{itemize}

\subsection{I know an artifabrian...}
\label{ssec:helpArtifabrian}

If the party needs some suggestion to start this path, read the following:

\quoteBox{
	"I know an artifabrian", \npcBabsk{} says. "Really solid work she does! I've met her when we stopped at Kurth once, she crafts the best fabrials in this part of the world! Perhaps she had something to deal with this plague..."
}

Characters can travel to Kurth to find the artifabrian and try to get some help from her. To run this part, follow to \fullref{ssec:helpArtifabrian}.

\subsection{About the Shardblade...}
\label{ssec:helpShardblade}

If a character searches for a way to get a Shardblade, or if nobody comes with that idea, read the following:

\quoteBox{
	"What about the Shardblade, hm?", \npcBabsk{} asks. "There is no problem they can't cut through. Those wonders are tracked and guarded by kings and queens, but my crew was whispering tales about a rogue Shardbearer in Iri. If his Shardblade went missing, no war would be started as a result..."
}

The party may wish to track the \enemyRogueShardbearer{} in Iri. If they manage to slain him, the blade would be theirs. For details, proceed to \fullref{ssec:helpShardblade}.

\subsection{What abut Reshi...?}
\label{ssec:helpReshi}

Unless the party comes to an idea to ask other Reshi Islands for help, read the following:

\quoteBox{
	"And what about the other Reshi?", \npcBabsk{} continues. "Their islands are the closest and they will be first to fight those horrors. Perhaps they already have in the past? You should ask them, maybe they know a way of dealing with those vines and that god who controls them?"
}

Characters can sail to another Reshi Island to gather more information about the threat. If they do, proceed to \fullref{ssec:helpReshi}.

\subsection{Far from the island}

The characters should search for help away from the island infested with the Red Vines controlled by \npcSprenVines{}. As they are away from that location, \enemyLarkin{}s are no longer lurking in the jungle - players can use their Investure without a fear of attracting one.