\chapter{Chapter 8 - TODO - Urithiru}
\label{chap:chapter8}

\setcounter{section}{-1}
\section{Running This Chapter}
\label{sec:chapter8running}

The characters travel to Vedenar, to use Oathgate there and get to \locationUrithiru{}. They arrive there in a middle of a serial murder crisis. They need to support investigation efforts of \npcShallan{} and gain trust of the Urithiru Radiants.

Run this chapter as a two parallel plot threads and allow the party to switch between them as they wish. The first one is for the safe parts of \locationUrithiru{}, with neutral NPCs and potential allies. The second thread represents dungeon delving into the lair of \npcMidnightMother{}, the \npcMidnightMotherTitle{}.

\subsection{Character Advancement}

Advance the characters twice in this chapter. Award the party 1 level after dealing with \npcMidnightMother{}, the \npcMidnightMotherTitle{}. Award the party 1 level once they secure their first patronage of a new NPC met in the tower or otherwise complete the story of the chapter.

The following events may affect their path to radiance:
\begin{itemize}
	\item Learning secrets of the Tower.
	\item Protecting allies during the fight with Midnight Essence.
	\item Meeting \npcMidnightMother{}, the \npcMidnightMotherTitle{} and her children may expedite an Enlightened Edgedancer.
\end{itemize}

The PCs may also earn unique rewards from their patrons located in the tower.

\subsection{Forging Alliances}

While in \locationUrithiru{}, the party will have opportunity to secure patronage from various powers. Those may include, but are not limited to:

\begin{itemize}
	\item Members of the Kholin family
	\item Kaladin Stormblessed
	\item Sons of Honor
	\item Vorin Church
\end{itemize}

The book will not provide example scenes for all possible patrons. Use your own judgment to provide players with quests to secure patronage they aim for.


\subsection{Handling Canon}

Starting from this chapter, the party will interact with characters and events described in \bookSA{}. It is possible that their actions will cause consequences contradicting the official story.

Please make sure that everyone at the table is aware of your group's Canon policy. You can all agree to ensure everything happens exactly like in the books, you can also allow for some alternative histories. Please remember it is a game and its primary goal should be a fun experience for all participants.

For more guidelines, see \fullref{ssec:runningAdventureCanon} and "Canon and Continuity" section of \handbook{}.


\subsection{Event: Dark Wrongness}
\label{ssec:chapter8runningEvent}

In the deep tunnels of the Tower, an ancient evil lurks and learns.\\

\eventComplication{Dark Wrongness}{
	\iconCompEvent
	\iconCompEvent
	\iconCompEvent \\ \vspace{0.15cm}
	\iconCompEvent
	\iconCompEvent
}


\subsubsection{Progressing the Event}

Each time a complication is rolled by a PC while outside of the inhabited part of \locationUrithiru{}, you can spend it to progress the event by 1, trading an immediate Complication for the \npcMidnightMother{}'s awareness. If you do, the PC must pass \skillCheck{14}{\skillDiscipline{}} or they loose 1d4 Focus.

You can progress the event only once per Long Rest.

\subsubsection{Triggering the Event}

Once the final complication slot is filled, \npcMidnightMother{}, the \npcMidnightMotherTitle{} becomes bold enough to attack people in the tower. The PCs can be randomly assaulted by a \enemyMidnightAssassin{} using its Mimic Violence and Uncanny Nature actions before slipping into the cracks of the walls.

\subsubsection{Ending the Event}

The event finishes after the party deals with the Unmade during \fullref{sec:middnightMother}.


\input{chapter_8/urithiru.tex}
\newpage
\input{chapter_8/ghostbloodsHideout.tex}
\input{chapter_8/diagramChambers.tex}
\input{chapter_8/dalinarVsArdents.tex}
\input{chapter_8/jasnahVsSonsOfHonor.tex}
\input{chapter_8/moreAllies.tex}

\input{chapter_8/stoppingWrongness.tex}
\input{chapter_8/mysteriousViolence.tex}
\input{chapter_8/darkTunnels.tex}
\input{chapter_8/middnightMother.tex}

\section{Journeying Onward}

After the characters defeat \npcMidnightMother{}, the \npcMidnightMotherTitle{} or help her escape, allow them to complete their other goals in the Tower before proceeding to the next chapter. 

The party should have level 12 at that point of the story \textit{(unless they ignored the arc of \npcMidnightMotherFull{})}. 