\section{Tradition and Heresy}
\label{sec:dalinarVsArdents}

As the PCs arrive to the Tower, recent actions of \npcDalinar{} alienated Vorin Ardentia in \locationUrithiru{}, who cannot continue to support him.

The PCs can show their support for one of the sides of that conflict. In doing so, they may secure a powerful ally. Regardless of the side they choose, they shouldn't be able to obtain the patronage before \fullref{ssec:mysteriousViolenceBarFight} scene.



\subsection{\npcDalinar{} Kholin}

\npcDalinar{} Kholin, the Bondsmith, bonded the Stormfather, an ancient remnant of Honor. Through that bond, he received visions from Honor himself and now is spreading his learnings. Those, however, often contradict the teachings of the Ardents.

\subsubsection{Patron's Goal}

\npcDalinar{} might offer goals like the following:

\scriptedOption{Embrace Change}{Accept and spread the uncomfortable truth - Honor is dead, and he never was a god.}

\subsubsection{Patron Benefit}

As a patron, \npcDalinar{} can use his influence to greatly support Knights Radiant with any amount of Stormlight they may spend for training and battle.

When facing \npcMidnightMother{} during \fullref{sec:middnightMother}, \npcDalinar{} will support the party with one of his trusted officers.




\subsection{Vorin Ardentia}

Ardents in the Tower refuse to accept \npcDalinar{}'s heresy. They are the defenders of the holy faith of the Almighty and they will not follow anyone who threatens their dogma. Vorinism was always the source of stability and comfort, and this is what is especially needed in those times.

\subsubsection{Patron's Goal}

Ardents might offer goals like the following:

\scriptedOption{Preserve Tradition}{Defend the religion. Renounce heretic claims and actions of \npcDalinar{} Kholin.}

\subsubsection{Patron Benefit}

Ardents will not support a PC working in a party with someone supported by \npcDalinar{} and they will revoke their support once \npcDalinar{} assumes patronage of the party.

Ardentia patronage can provide the party with stability and endorsement of the most influential religion on Roshar. Through their prayers, they increase maximal Focus of the PCs by 1.

When facing \npcMidnightMother{} during \fullref{sec:middnightMother}, an Ardent will join the party to help them.