\section{Dark Tunnels}
\label{sec:darkTunnels}

Dark tunnels represent the dangerous and unknown part of \locationUrithiru{}. The party will need to descend into them to find the entrance to \fullref{sec:middnightMother} and proceed with the plot of the chapter. 

You can also use this location as a destination on various quests from potential patrons and allies.

\subsection{Traveling Through the Darkness}

You can run this part as an infinite dungeon crawl. At each point, the party has two choices: go deeper or turn back. Each time they make a move in any direction, they risk an encounter with \npcMidnightMother{}'s children.

\subsubsection{Goal - Source of the Wrongness}

You can run a search for \fullref{sec:middnightMother} as a modified Endeavor. To finish it, the party must accumulate 5 successes. There is no failing threshold and the party may attempt it as much as they want, each time  risking an encounter with enemies.

\subsubsection{Entrance Point}

The party can start their search from any place in \locationUrithiru{} that is away from uninhabited parts of the Tower. Here, the tunnels are dark, but in a wrong way...

The starting Distance of the descend is 0. Each time the party moves deeper into the Tower, increase the Distance by 1, each time they successfully go back - decrease it by 1. The party can leave the tunnels when they reach the Distance of 0 again.

\subsubsection{Action - Descend into Darkness}

The party can descend deeper into the tunnels. Each time they do, increase their Distance by 1 and ask one of the PCs how do they search for the source of evil and wrongness. 

Choose a skill that best matches the PC's attempt. That PC makes a skill test with a DC equal to 30 minus current Distance value. On a success, mark one success on their current Endeavor. On a failure nothing happens.

After the skill test, roll for a random encounter - see \fullref{ssec:darkTunnelsEncounters}.

\reasonBox{
	If you want tests' DCs more varied, use starting DC value of 27 + 1d6 instead of constant 30. Each time decrease the value by current Distance.
}

\subsubsection{Action - Return}

The PCs can decide to abandon their current attempt to investigate the tunnels as it is time to go back to safety an lick their wounds. To do that, a PC must make a \skillCheck{15}{\skillDeduction{} \textit{(or other skill)}}.

On a success, decrease their Distance by 1. If they reached the Distance of 0, they can exit the tunnels. Do not erase their Endeavor successes - allow them to continue another day.

After the skill test, roll for a random encounter - see \fullref{ssec:darkTunnelsEncounters}.

\subsubsection{Random Encounters}
\label{ssec:darkTunnelsEncounters}

To determine a random encounter, roll d20 and reduce the result by current Distance Value and the number of complications accumulated on \fullref{ssec:chapter8runningEvent}. Compare the result with the table below: \\

\small
\noindent
\begin{tabular}{c l}
	d20 & Encounter \\ \hline
	1+  & \textit{(none)} \\
	0   & Each PC loses 1 Focus. \\
	-1  & 1x \enemyMidnightBeast{} \\
	-2  & 1d4 \enemyMidnightBeast{}s \\
	-3  & 1d6 \enemyMidnightBeast{}s \\
	-4  & 1x \enemyMidnightAssassin{} \\
	-5  & 2x \enemyMidnightAssassin{} \\
	-6  & 1x \enemyMidnightAssassin{} + 1d4 \enemyMidnightBeast{}s \\
	-7  & 1d4 \enemyMidnightAssassin{}s + 1d4 \enemyMidnightBeast{}s \\
	-8  & 1d6 \enemyMidnightAssassin{}s + 1d4 \enemyMidnightBeast{}s \\
	-9  & 1d6 \enemyMidnightAssassin{}s + 1d6 \enemyMidnightBeast{}s \\
	-10 & 1d6 \enemyMidnightAssassin{}s + 1d8 \enemyMidnightBeast{}s \\
	-11 & \enemyMidnightTwin{} \\
	-12 & \enemyMidnightTwin{} + 1d4 \enemyMidnightBeast{}s \\
	-13 & \enemyMidnightTwin{} + 1d6 \enemyMidnightBeast{}s \\
	-14 & \enemyMidnightTwin{} + 1d8 \enemyMidnightBeast{}s \\
	... & \enemyMidnightTwin{} + 1d4 \enemyMidnightAssassin{}s \\
\end{tabular}
\normalsize

\subsubsection{Opportunities and Complications}

During this crawl, you can spend Opportunities and Complications on following effects: \\

\scriptedOption{Modify Distance}{
	The PCs can spend \iconOpp{} to modify Distance value by 1. The GM can spend \iconComp{} to increase it by 1.
}

\scriptedOption{Affect Encounter Chance}{
	The PCs can spend \iconOpp{} to ensure the next roll to determine random encounter gains an advantage. The GM can spend \iconComp{} to give it a disadvantage.
}

\scriptedOption{Advance Event}{
	Once per Long Rest, the GM can spend \iconComp{} to progress \fullref{ssec:chapter8runningEvent}.
}