\section{Diagram Chambers}
\label{sec:diagramChambers}

\npcTaravangian{} and his court from \locationKharbranth{} are invited to occupy some of the \locationUrithiru{} chambers. The entrance is guarded by two \enemyDiagramMuscle{}s and it would not be in a good taste to violate their space.

However, if the PCs were invited by the King to join him on his travel to the Tower, they will be allowed to enter those rooms and work with the Diagram to reach their goals.




\subsection{King's Court}

If the party ended \nameref{chap:chapter7} on a friendly terms with \npcTaravangian{} and were invited to travel to \locationUrithiru{} with him, they will be allowed to live in a chambers designated for his court.

In that case, at some point read the following:

\quoteBox{
	As you walk through the halls of \locationUrithiru{}, \npcMalata{} from the Diagram approaches you. \\ \\
	"\npcTaravangian{} is hosting a gathering tonight", she says. "You are expected to be there."
}

The party got invited for a meeting with the king. When they go there, proceed to \fullref{ssec:diagramChambersQuest}.

\subsection{Vital Task}
\label{ssec:diagramChambersQuest}

When the PCs join the meeting with the king, read the following:

\quoteBox{
	As you enter, you see the meeting already started. \\ \\
	"... and thus, our next step is clear. I must prove to the people that I am better king that \npcDalinar{} Kholin. So, how do we do that? Council me."
}

One of the solutions to this problem is to show everyone that an expedition mounted by \npcTaravangian{} resolved the dark wrongness lurking in the tower. If no PC suggests this, allow some NPC to give that idea.

When the idea is suggested, read the following:

\quoteBox{
	"Yes, that would certainly help", says the king. "You showed you are capable and resourceful. This will be your task for the upcoming days - eradicate this evil and earn the glory. For yourself and for \locationKharbranth{}."
}

\subsubsection{Support}

If the party manages to find the entrance to \fullref{sec:middnightMother} and reports it to \npcTaravangian{}, a \enemyDiagramSurgeon{} will be sent with them to aid them as a part of \fullref{ssec:middnightMotherAllies}.

\subsubsection{Reward}

After the party removes the threat of \npcMidnightMother{} from the Tower, double the number of \abilityFutureKnowledgeName[N] received from the Diagram by the PCs.

At this point, \npcTaravangian{} will also recognize them as official members of The Diagram.




\subsection{More Quests}

After a PC joins The Diagram, you can use this organization to give them more quests and tasks, rewarding them with additional access to \abilityFutureKnowledgeName[2] for the most impactful ones.

This book does not provide examples of such tasks. However, you can align them with the main story of the campaign.




\subsection{Diagram Entries}

While working for \npcTaravangian{}, the party might get access to the notes recorded in "The Diagram". If they do, once per day, each PC gets \abilityFutureKnowledgeName[1]:

\abilityFutureKnowledge[N]

The party might also enter a Conversation with \npcTaravangian{} to convince him they need more information on that day. On a success, they receive \abilityFutureKnowledgeName[2] instead.

\reasonBox{
	In the books, "The Diagram" records are shown to be sometimes written in a cipher to better convey the meaning. You can use this opportunity to give your players a puzzle. When solved, it will grant the PCs their \abilityFutureKnowledgeName{}. \\ \\
	This book will not provide any examples as the difficulty of each puzzle should be determined by the GM who knows the group.
}