\section{\npcFractionGhostbloods{}' Hideout}
\label{sec:ghostbloodsHideout}

The \npcFractionGhostbloods{} established their hideout inside the Tower. Unsuspecting PCs will not be able to find it.

However, if the party saved \npcGhostbloodWounded{} in the previous chapter, the  PCs will be included in their schemes.



\subsection{The Invitation}
\label{ssec:ghostbloodsHideoutInvitation}

When the party travels through the Tower, if they sided with the \npcFractionGhostbloods{} during \nameref{chap:chapter7}, read the following:

\quoteBox{
	As you stroll the corridors, you suddenly see a sheet of paper tugged into the rocky wall. On it, you see your names and the symbol you saw before - a three diamonds forming a triangle. \\ \\
	"Let us meet", the letter says. "Fifth level, western corridor, merchant storehouse, ask for atium."
}

If the PCs follow the letter instructions, proceed to \fullref{ssec:ghostbloodsHideoutQuest}.

\reasonBox{
	This scene assumes at least one PC can read. In other case, the \npcFractionGhostbloods{} would choose a different method to invite the party. A whisper from a dark alley, perhaps?
}


\subsection{Proof of Skill}
\label{ssec:ghostbloodsHideoutQuest}

If the party follows the instructions from the letter found in \fullref{ssec:ghostbloodsHideoutInvitation}, read the following:

\quoteBox{
	You enter a large room, filled with boxes, barrels and crates. Some of them are marked with the glyph marking them as owned by Sadeas princedom. \\ \\
	"Hello, there!", the merchant says. "What can I get you?"
}

If the party asks for atium, they will be taken to a backdoor room. Read the following:

\quoteBox{
	The next room is dark and full of shadows. One guard sits here in the corner. He wears has a green uniform and terribly scarred face. His pet chicken sits on his shoulder. \\ \\
	"The travelers from the dark", he says. "I heard a lot about you. Time to put your skills to the real test!"
}

\subsubsection{The Mission}

\npcFractionGhostbloods{} tell the PCs to find and eradicate the source of the evil wrongness lingering in the Tower. To succeed, the party must complete \fullref{ssec:middnightMotherFight}.

\subsubsection{Support}

If the party manages to find the entrance to \fullref{sec:middnightMother} and reports it to the \npcFractionGhostbloods{}, a Ghostblood Agent will be sent with them to aid them as a part of \fullref{ssec:middnightMotherAllies}.

\subsubsection{Reward}

After the party removes the threat of \npcMidnightMother{} from the Tower, the \npcFractionGhostbloods{} will formally invite them to the organization.

Any character who tattoos their symbol on their forearm will receive one \lootScadrialCoin{} to be spent for items in \fullref{ssec:ghostbloodsHideoutMarket}.



\subsection{More Quests}

After a PC joins \npcFractionGhostbloods{}, you can use this organization to give them more quests and tasks, rewarding them with \lootScadrialCoin{}s for the most impactful ones.

This book does not provide examples of such tasks. However, you can align them with the main story of the campaign.



\subsection{Black Market}
\label{ssec:ghostbloodsHideoutMarket}

If a PC is allied with \npcFractionGhostbloods{}, they gain access to their stock of unique items. Each of them costs a single \lootScadrialCoin{} to buy. Forged coins will be recognized and refused.

In here, the PC can buy:

\begin{itemize}
	\item \lootHemalurgicNail{}s \textit{(various metals)}
	\item \lootForgerySeal{}s \textit{(various kinds)}
	\item \lootSeonTube{}
	\item \lootWhiteSand{}
	\item \textit{and other...}
\end{itemize}

\reasonBox{
	In here, you can use \npcFractionGhostbloods{}' connections to introduce off-world magic systems into the setting of \bookSA{}. If at any point Brandon Sanderson introduces a new magic system, if you believe the \npcFractionGhostbloods{} would have access to it, feel free to  introduce more items to their shop.
}



