\section{Past and Future}
\label{sec:jasnahVsSonsOfHonor}

During a Highstorm several days after the events of \fullref{ssec:mysteriousViolenceBarFight}, \npcJasnah{} Kholin appears in \locationUrithiru{}. That rekindles her old quarrels with \npcAmaram{}.




\subsection{\npcJasnah{} Kholin}

A sholar and a Veristitalian, \npcJasnah{} was one of the first people to bond with a Radiant spren and joining the Order of Elsecallers.

She was also considered dead, murdered by \npcFractionGhostbloods{}, so her return to the Tower is unexpected and welcomed with glee.

\subsubsection{Patron's Goal}

\npcJasnah{} might offer goals like the following:

\scriptedOption{Reshape Alethkar}{Abolish alethi institutions and traditions that are based on injustice and inequality.}

\subsubsection{Patron Benefit}

With \npcJasnah{}'s connections, the party gains access to a wide spanreed network. The PCs can use it go gain Erudition (Scholar Key) talent for as long they have access to the network.

As an ally, \npcJasnah{} will also join the fight during \fullref{ssec:middnightMotherConfront}.

\npcJasnah{} will not support a party with a patronage from \npcAmaram{} and she will revoke any benefits when he allies the PCs.





\subsection{\npcAmaram{}}

Recently elevated to a station of the Highprince Sadeas by the wife of the previous Highprince, \npcAmaram{} is a skilled warrior and a cunning schemer. 

He also leads The Sons of Honor - a cult of religious fanatics that wanted to restart Desolations in order to see the Heralds returning and the Vorin church regaining much of the lost power.

\subsubsection{Patron's Goal}

\npcAmaram{} might offer goals like the following:

\scriptedOption{Refound Hierocracy}{Increase the influence of Vorin church, giving it more power, autonomy and political strength.}

\subsubsection{Patron Benefit}

\npcAmaram{} is widely connected and as a patron of the party can grant them access to those connections. Also, once per day he can make each PC Determined.

He will also send one of his generals to mentor and support the party during \fullref{ssec:middnightMotherConfront}.

