\section{Mysterious Violence}
\label{sec:mysteriousViolence}

While talking with inhabitants of \locationUrithiru{}, the PCs might hear some rumors about mysterious deaths happening in the Tower. 

At first, everyone is talking about assassination of Highprince Torol Sadeas and Vedekar Perel, who was killed in a very similar way. If the PCs know where to ask, they will hear darkeyes whispering about Ned, who strangled two women recently.

If the party investigates the topic more, listening to the rumors on the street, they might learn about a few more incidents that might spark their attention.

Allow the PCs to hear at most one new rumor per Long Rest. When the it appears, the party has one day to follow its lead. At the following day it is too late - Midnight creatures already managed to replicate the crime and flee into the darkness.

If the party manages to investigate a rumor, award them with one success towards the Endeavor to find the source of the crimes - see \fullref{sec:stoppingWrongness}.



\subsection{Mauled by Axehounds}

\subsubsection{Rumor}

A man was found mauled by a pack of \enemyAxehound{}s outdoor on the bottom level of the Tower. The pack was found and put down by the policing force.

\subsubsection{Investigation}

Run investigation of this rumor as an Endeavor. \pursuitReq{6}{3}

Set the average DC of skill tests of the Endeavor to 19 (or 16 + 1d6).

\subsubsection{Endeavor Succeeded}

If the party completes the Endeavor, read the following:

\quoteBox{
	You find another pack of animals. They look like axehounds, except they are jet black, with skin glistening like oil and their body proportions feel... wrong... \\ \\
	The pack looks at you and pounces, ready for a fight.
}

The PCs are attacked by 4 \enemyMidnightBeast{}s mimicking \enemyAxehound{}s. They will fight to the end.

After the fight, award the party with a progress towards the Endeavor to find the source of \locationUrithiru{} wrongness - see \fullref{sec:stoppingWrongness}.

\subsubsection{Endeavor Failed}

If the party fails the Endeavor or ignores the rumor, on the following day they will hear a news about yet another man found mauled by a pack of axehounds... which is weird, because the last pack was put down previously...




\subsection{Prey of the Skyeels}

\subsubsection{Rumor}

A scout was found dead in the snowy mountain range. She was sent to map the area around \locationUrithiru{}, but, judging by her wounds, she was attacked by a flock of skyeels defending their territory.

\subsubsection{Investigation}

Run investigation of this rumor as an Endeavor. \pursuitReq{7}{3}

Set the average DC of skill tests of the Endeavor to 20 (or 17 + 1d6).

\subsubsection{Endeavor Succeeded}

If the party completes the Endeavor, read the following:

\quoteBox{
	High in the mountains, you find a nest of the skyeels. You've never seen skyeels as black. And should their bodies twist like this...?
}

The party is attacked by 5 \enemyMidnightBeast{}s mimicking a flock of \enemySkyeel{}s. They will fight until slain.

After the fight, award the party with a progress towards the Endeavor to find the source of \locationUrithiru{} wrongness - see \fullref{sec:stoppingWrongness}.

\subsubsection{Endeavor Failed}

If the party fails the Endeavor or ignores the rumor, on the following day they will hear a news about a scribe found dead in the mountains. The wounds again suggest the flock of skyeels. But what was a scribe doing there...?



\subsection{Unfortunate Horneater}

\subsubsection{Rumor}

Last night some Ghostblood agent interrogated people in the local bar about Ned who recently killed two women. She knifed herself only to cut him. Storming maniac!

\spoilerBox{
	The rumor references the events described in  \bookOB{}, Chapter 18. "Double Vision".}

\subsubsection{Investigation}

Run investigation of this rumor as an Endeavor. \pursuitReq{7}{3}

Set the average DC of skill tests of the Endeavor to 21 (or 17 + 1d8). Endeavor tests may include search for a similar Horneater or chasing the impersonator through the halls of \locationUrithiru{}.

\subsubsection{Endeavor Succeeded}

When the party succeeds on the Endeavor, read the following:

\quoteBox{
	You are facing the maniac. She looks like a woman in a long black cloak and a hat. But her face... Distorted and black, like it was made of tar. She looks at you with hatred and disdain.
}

The party is facing against \enemyMidnightAssassin{} impersonating \npcVeil{}. Once the PCs catches up to it, it will fight until the end.

After the fight, award the party with a progress towards the Endeavor to find the source of \locationUrithiru{} wrongness - see \fullref{sec:stoppingWrongness}.

\subsubsection{Endeavor Failed}

If the party fails the Endeavor or ignores the rumor, on the following day they will hear a news about a bridgeman chef, who got assaulted in a broad daylight. Why would anyone attack him...?

\spoilerBox{
	The same incident is referenced in \bookOB{}, Chapter 25. "The Girl Who Looked Up".}




\subsection{The Impersonator}

If a PC acted in a noticeably violent manner toward an NPC in the Tower, allow \enemyMidnightAssassin{}s to replicate their crime and enact it in a very similar way on the following day.

The party might see the crime with their own eyes or hear about it. If they manage to catch the creature behind it, award them with a progress towards the main Endeavor.




\subsection{Bar Fight}
\label{ssec:mysteriousViolenceBarFight}

\subsubsection{Rumor}

A man started a bar fight last night, during which he killed his opponent with a shattered bottle. He was hung for the murder.

\subsubsection{Investigation / Ignored}

If the PCs decide to investigate this lead, they will eventually encounter a \enemyMidnightAssassin{} attempting to replicate the hanging. At that point, \npcShallan{} will also carry on with her investigation. From this point, proceed to \fullref{ssec:middnightMotherNoBacking}.

If the party decides to ignore the lead, they will hear \npcAdolin{} quickly gathering bridgemen bodyguards to get help for \npcShallan{}. Either way, proceed to \fullref{ssec:middnightMotherNoBacking}.

\reasonBox{
	If you wish, you could run the investigation as yet another Endeavor. However, is there a point? Regardless of the result, the story must lead to \fullref{ssec:middnightMotherNoBacking} anyway, so the Endeavor can be skipped in this scene.
}

\spoilerBox{
	The same crime is referenced in \bookOB{}, Chapter 29. "No Backing Down".}



\subsection{More Crimes}

If the party did not defeat \npcMidnightMotherFull{} as a result of \fullref{ssec:mysteriousViolenceBarFight}, you may consider introducing more crimes to investigate, leading to more encounters with \enemyMidnightAssassin{}s. 

However, don't think that is required to move the story forward. The party can find more clues in the endless dark tunnels below the Tower - see \fullref{sec:darkTunnels}.