\section{Stopping the Wrongness}
\label{sec:stoppingWrongness}

While spending time in \locationUrithiru{}, the PCs might notice that something is wrong with the Tower. They might hear rumors of strange murders, feel a creeping unease while walking through its tunnels and hear the people talking about it.

At some point, the PCs may decide to find the source of it and deal with it. It may be their own idea or come as a quest from their superiors.

You can run the search for the source of the wrongness as a modified Endeavor. In total, the party must accumulate 5 successes to succeed on the Endeavor. There is no failing threshold, sooner or later they will succeed, but the longer it takes, the more dangerous the situation becomes.

You should run this Endeavor in the background of the chapter events. The PCs will need to succeed in multiple scenes to find what they are looking for.




\subsection{Gathering Successes}

For this Endeavor, the PCs can gather successes in two different ways:

They can investigate the rumors of strange crime scenes (see \fullref{sec:mysteriousViolence}), with each successful investigation awarding them a single progress point for the main Endeavor.

They can also descend into the dark tunnels below the Tower (see \fullref{sec:darkTunnels}). In here they can accumulate more progress for the main Endeavor, but the crawl can be more dangerous.




\subsection{Completing the Endeavor}

After the party gathers 5 successes in their Endeavor to find the source of the wrongness in the Tower, they will find the entrance to the lair of \npcMidnightMotherFull{} (see \fullref{sec:middnightMother}).

At that point, the PCs can enter inside to fight the Unmade or return later with more allies. If they decide for more careful approach, they will need to find the entrance again, though this time they will be able to do it with an advantage.




\subsection{Midnight Essence}
\label{ssec:stoppingWrongnessMidnightEssence}

If you need to introduce enemies for a fight, either during a crime investigation (see \fullref{sec:mysteriousViolence}), or the exploration of the unknown parts of \locationUrithiru{} (see \fullref{sec:darkTunnels}), you can use Midnight Essence creatures.

\enemyMidnightBeast{}s are smaller creatures, often working in small groups, mimicking wild animals. Use them for easier fights. For more standard encounters, use \enemyMidnightAssassin{}s. For boss fights you can use a \enemyMidnightTwin{}.

\corruptedBox{
	Fighting a Midnight creature can expedite an Enlightened Edgedancer \seeCorruptedRules{}.
}