\section{\locationUrithiru}
\label{sec:urithiru}

At the end of the last chapter, the PCs learn that the next stop on their adventure is \locationUrithiru{}. Now it is time for this next step in their journey.



\subsection{Way of Kings}

In order to get to \locationUrithiru{}, \npcTaravangian{} organized a ship from \locationKharbranth{} to \locationVedenar{}. The PCs travel with the Diagram - either as full-fledged members, or as a stowaways smuggled by the \npcFractionGhostbloods{}, impersonating darkeye servants.

In \locationVedenar{} \npcMalata{} uses her Shardblade to transport everyone to \locationUrithiru{}.

The voyage takes several days with little encounters. The PCs can use this time to work on their personal goals, or the players can agree to fast-forward this part.

Once the journey is completed, proceed to \fullref{ssec:urithiruArrival}.




\subsection{Arrival}
\label{ssec:urithiruArrival}

When the PCs arrive to \locationUrithiru{}, read the following:

\quoteBox{
	You see \npcTaravangian{}'s bodyguard summon her Shardblade and push it into the wall of the small building in the middle of a lush garden. In an instant, you are transported elsewhere. \\ \\
	You brace yourself to see hateful visions and the realm of darkness. Instead, you feel a chilly breeze and see several coldspren grow around your feet.
}

The PCs successfully traveled to \locationUrithiru{}. Proceed to \fullref{ssec:urithiruTower}.





\subsection{The Tower of Radiants}
\label{ssec:urithiruTower}

The party reached \locationUrithiru{}, the ancient seat of all Radiant Orders.

You can treat this location as a functional city, with markets, artisans and artifabrians. This book does not provide every NPC an service that can be found in here, you can use your own judgment to determine what is available for the PCs.

Run this part of the story as a town full of NPCs and their quests. Allow the party to pick and choose what do they wish to do and in what order.

\subsubsection{Old Friends}

\npcFractionGhostbloods{} and the Diagram are present in the Tower. If the party is in friendly relations with one of those groups, the PCs can count on more support in this chapter. For more details, see \fullref{sec:ghostbloodsHideout} and \fullref{sec:diagramChambers}.

\subsubsection{New Alliances}

There are plenty NPCs in the Tower to interact with. Some of them are powerful enough to support the party with a patronage. See \fullref{sec:dalinarVsArdents} and \fullref{sec:moreAllies} for the goals of the potential patrons.

In about a week or two, after the next Highstorm, \npcKaladin{} and \npcJasnah{} will arrive to the city. For more patron opportunities, see \fullref{sec:jasnahVsSonsOfHonor}.

\subsubsection{Murder Investigation}

As the PCs arrive to \locationUrithiru{}, there is an investigation ongoing. Someone assassinated two lighteye nobles on the grounds of the Tower. The victims are: Highprince Torol Sadeas and Vedekar Perel.

See \fullref{sec:mysteriousViolence} if the PCs decide to investigate the murders.

\subsubsection{Tower Exploration}

Not every part of the Tower is inhabited. Many of tunnels reach deep and hide unknown perils. If the PCs wish to explore those regions see \fullref{sec:darkTunnels} for details.