\section{Avatar of Hatred}
\label{sec:avatarOfHatred}

The party is very close to reaching their goal. But there is still one enemy between them and their prize - \npcMishram{}'s hatred growing through the millennia of imprisonment now manifests in the Spiritual Realm as \enemyMishram{}.

\reasonBox{
	This is the final boss fight of the adventure. Make it epic!
}



\subsection{Well-Deserved Rest}

Allow your party for a Long Rest before proceeding to the final fight. The PCs should be able to approach the fight with all of their resources restored.

Consider a vision with a shop if one of the PCs relies on consumable items and must refresh their inventory.


\subsection{Starting the Fight}

Start the fight by reading the following:

\quoteBox{
	Suddenly, the Spiritual Realm around you grows smoky and black. From the black cloud, a femalen steps out. Her face twisted with hatred, she walks towards you. \npcMishram{}. \\ \\
	"Traitors! You cannot run from me! You will answer for your betrayal, and your suffering will be a song for my ears!"
}

The PCs might have successfully fled from the \npcMishram{}'s hatred before, but not this time. Now it's  time to end it!


\subsection{Enemy Forces}

\enemyMishram{} is accompanied by 4 \enemySingerWarform{}s. For each failed challenge in \fullref{sec:trailOfTheAges}, add an additional \enemySingerWarform{}. For each scene completed successfully, \enemyMishram{} looses 1 starting Investure.

\enemyMishram{} will fight to the end, but when she dies, the fight ends and all other forces unravel into the Spiritual Realm.



\subsection{Shifting Battlefield}

Due to instability of the Spiritual Realm, the following action is available for the PCs (the enemies do not have access to it):

\ability{Alter Battlefield}{As \iconAction{} you can attempt a \skillCheck{25}{\skillLore{}}. On a success, you may modify the battlefield by changing a part of a scenery. The change cannot trap or damage the enemies, but you can create additional obstacles, difficult terrain, elevation, or items to interact with. }



\subsection{Opportunities and Complications}

During the battle, the following options to spend Plot Dice results are available:

\scriptedOption{Prolonged Transformation}{
	A PC may spend \iconOpp{} to delay the full effect of \enemyMishram{}'s Granter of Form ability by one round.
}

\scriptedOption{An Old Friend}{
	A PC may spend \iconOpp{} to manifest a spiritual vision of their ally. The ally helps them for one action before unraveling. The PC can choose from the actions available in \fullref{ssec:middnightMotherAllies} or \fullref{ssec:kholinarPalaceOpportunities}.
}

\scriptedOption{Shifting Battlefield}{
	\iconOpp{} and \iconComp{} can be spent to alter the battlefield in a way that helps or hinders the PCs.
}

\scriptedOption{Rally Legions}{
	The GM can spend a \iconComp{} from the player's roll to spawn an additional \enemySingerWarform{} into the fight.
}




\subsection{Aftermath}

After \enemyMishram{} dies, the PCs may proceed to \fullref{sec:thePrison}.