\chapter{Chapter 10 - TODO - The Spiritual Realm}
\label{chap:chapter10}

\setcounter{section}{-1}
\section{Running This Chapter}

The characters entered the Spiritual Realm. In here, they must find \npcMishram{} and free her from her prison.

\subsection{Character Advancement}

The party starts this chapter at level 14. Advance them twice in this chapter: once after they find a lead to the \npcMishram{}'s prison, and once after their final confrontation with the Unmade.


\subsection{Encounters' Character}

This chapter will provide little descriptions of precisely designed scenes. Instead it suggests some examples what the GM could prepare for the PCs, but since the content of the encounters is heavily tied to the PCs and their stories it will not present exact scenes.



\input{chapter_10/rulesOfTheRealm.tex}
\input{chapter_10/personalScenes.tex}

\input{chapter_10/fixTheFailure.tex}
\newpage
\input{chapter_10/backstoryFlashback.tex}
\input{chapter_10/momentOfRespite.tex}
\newpage
\input{chapter_10/epicFight.tex}
\newpage
\input{chapter_10/unmadeProgression.tex}
\newpage
\input{chapter_10/familiarPast.tex}
\newpage
\input{chapter_10/learnTheLore.tex}
\input{chapter_10/completeTheirStory.tex}

\input{chapter_10/trailOfTheAges.tex}
\input{chapter_10/avatarOfHatred.tex}
\input{chapter_10/thePrison.tex}


\newpage
\section{Journeying Onward}

The story ends here. If they characters survive perils of the Spiritual Realm, advance them to level 16. They may start a new adventure.

If you wish to continue the story of the PCs, here are some ideas:

\subsubsection{Stormlight Continued}

Allow the party to influence the story of \bookSA{} books 6-10. At the time of writing this those books are not yet released, but perhaps you will play your campaign a bit later, when those are already available.

\subsubsection{Endless Realm}

The PCs can have more encounters in the depths of the Spiritual Realm. Continue fights against terrible creatures the party did not encounter before.

\subsubsection{Worldhoppers}

The PCs may exit in the Cognitive Realm and use it to travel to another world to have another adventures there. They say Scadrial is beautiful this season...

\subsubsection{Spirited City}

At this point in the \bookSA{} story, the city of \locationKharbranth{} got exiled into the Spiritual Realm. The PCs can find it in this Realm and have more adventures in it.