\section{Epic Fight}
\label{sec:epicFight}

Not every player prefers focusing on their character's story during the RPGs. Some are here for a challenging, tactical combat. You can lean on this playstyle as well during this chapter.

Use this opportunity to introduce encounters with adversaries that are inspiring you, but did not appear in the campaign so far. You can also replay some of the Combat scenes from the adventure that the players enjoyed.

You can use enemies from this book, \bookWorldGuide{}, other sources or your own homebrew. Whatever feels inspiring!

\reasonBox{
	Be cautious not to make too many difficult combat scenes in a row. Allow the PCs to have some time to rest, heal, and regain resources. Sprinkle some social encounters or Endeavors in between. \\ \\
	In other case, the stream of combat scenes may be unfairly lethal to the party.
}



\subsection{Example Scene}

You can start such a scene with something like:

\quoteBox{
	You are traveling a dirt road in the wilderness, when you notice something lying in a pool of blood ahead of you. \\ \\
	When you come closer to investigate, you recognize a carcass of an axehound. Poor thing is dead for some time now, rotspren started crawling over it.
}

The party encounters a dead axehound on the road. A PC with a proper expertise may recognize a hunting pattern of a Whitespine.

A moment later, the PCs are ambushed by the biggest Whitespine they've ever seen. Each PC starts the fight Surprised, unless they were aware or warned about its hunt strategy.

You can use \enemyWhitespine{} stat block with following changes: increase all of its attributes by 1 (as well as all of its skills and attack bonuses) and give it Boss feature. It has 200 Health and 5 Focus.