\section{Familiar Past}
\label{sec:familiarPast}

If your players have played \cosmereRPG{} previously, you may have the PCs meet their earlier characters or relive their older adventures. 

You can consider that characters' players control their roleplay, while others people control the PCs from the current adventure. In that case don't focus too much on having the most recent and correct stat block for those characters. 

Because of that, don't design this scene to center around rules-heavy encounters like e.g. combat. Instead allow the PCs to interact with their old heroes.

\reasonBox{
	If you have access to an old character sheet you can definitely play some more complex scene. However, don't try to find them in the middle of your game. If you don't have it - don't worry, but make sure it is not needed for a smooth play.
}

\subsection{Example Scene}

You may start such a scene with something like:

\quoteBox{
	You find yourself on a small boat sailing through a calm, but misty sea. In a moment you see another boat approaching you from the fog. It carries only one, but most peculiar individual. \\ \\
	The man looks like an alethi, but is wearing a reshi clothing and an armor made from a carapace. His long and braided hair flow around a characteristic scar marking his face. On a shoulder, you can see a strange red chicken perching. \\ \\
	"The gods and the kings welcome you", the man says. "My name is Mike-son-Island and I will be your guide."
}

Let the player who created Mike-son-Island for the previous campaign play as him during this scene. You can provided them with a goals and motivation the character aims to achieve during this scene. The party will have one fewer PCs for this scene.

\reasonBox{
	Of course, do not read the above description. This is just an example how can you reintroduce an old character, but I doubt I guessed correctly their name or appearance. 
}