\section{The Spiritual Realm}
\label{sec:rulesOfTheRealm}

The Spiritual Realm is a vast and unstable place. If one can even call it a place... It's more like a raging storm of memories and places.

For the purposes of this chapter, you should remember the following rules:




\subsection{Theater of the Past}

The Spiritual Realm connects the past, present and the future. Encounters here replay the past events as though it was a theater play portraying those stories, replaying them as close to the real events as possible.




\subsection{Impersonate Characters of Old}

While experiencing the scenes in the Spiritual Realm, unless a PC was present during the original events, they will appear for the NPCs as someone from that time. 

While a PC impersonates other characters, they keep all of their level, talents, equipment and abilities. NPCs form the scene will not notice it or will consider it normal.




\subsection{Can't Change the Past}

Most of the scenes played in the Spiritual Realm reenact some events of the past. However, those are just something akin to theatrical plays. Nothing happening during them can alter the reality.

If the PCs do something differently from the real events (eg. prevent the assassination on \npcDeadKing{}), it does not affect the Physical Realm. They might feel better for one scene, but the consequences of that event are not modified.



\subsection{Permanent Possessions}

For the gameplay purposes, assume all items earned by the PCs in the Spiritual Realm persist even after their scenes end as long as a PC holds them in their possession.

All items traded from merchants and all unique rewards should remain with the PCs even after they leave the Realm.


\subsection{Storm of Chaos}

The Spiritual Realm does not have it's own geography like the other Realms. Instead it swirls with constant storm of chaotic energy, feelings and memories. It is very hard to navigate, though Enlightened Spren can greatly help with that.

In brief moments between the encounters, the PCs will be exposed to those energies. However, soon after a new scene should start.


\subsection{Non-linear Time}

Time in the Spiritual Realm flows only forward, but in unspecified speed. It may happen the PCs will spend around a week in here, but upon exiting they will realize it was a whole year in the Physical Realm. Or a thousand years. 

It is up to the GM to determine how much time will pass during their adventures in here. However, the party cannot exit from the Spiritual Realm into the past.