\section{Ancient Prison}
\label{sec:thePrison}

As the PCs enter the prison of \npcMishram{}, read the following:

\quoteBox{
	From the long corridor, you enter into a children room. Their toys lie scattered around. In a middle, there is a corpse on the floor. You recognize \npcMelishi{}, the Bondsmith who betrayed and imprisoned \npcMishram{}. \\ \\
	Next to him, on the floor, lies a perfectly rounded gemstone with a small Everstorm raging inside. Above it, two Radiants are wondering what to do with it. You recognize one of them as \npcRenarin{} Kholin.
}

The PCs can choose the fate of Roshar. It will be easy for them to persuade \npcRenarin{} to agree on whatever they decide to do with \npcMishram{}.

\reasonBox{
	If you want to make this scene last longer, you can make this scene into a Conversation or a Combat scene, but for the pacing reasons I decided to avoid more challenges here. For stat blocks you can use \enemyTruthwatcherRenarin{} and \enemyTruthwatcherRlain{}.
}


\subsection{Release the Unmade}

If the PCs choose to release \npcMishram{}, read the following:

\quoteBox{
	The gem is shattered and the room is filled with a black smoke. You recognize the Unmade. She screams, her wailing echoing in your ears like a cacophony of pain, madness and despair. Soon after, you see an explosion of light and everything is gone. \\ \\
	You just released an unimaginable evil into the world. An ancient Unmade, driven by her hatred for humans, now gone mad. Yet somehow you know - this was the right thing to do.
}

\npcMishram{} is free. The quest given to the PCs is completed. 




\subsection{Keep Her Imprisoned}

If the PCs leave \npcMishram{} imprisoned, read the following:

\quoteBox{
	Your Journey was long, but now, as you reached the Destination, you know this for sure - nothing good will come from releasing this hateful spren into the world. \npcSjaAnat{}'s scheme might benefit her, but it is sure that people will suffer. And this you cannot allow. \\ \\
	You leave \npcMishram{} in her prison, loyal to the last order of Honor. You will never serve \npcOdium{} or his spren. The path to your victory in this war may be difficult, but you know one - it is the right one.
}

\npcMishram{} remains imprisoned as the party leaves the gemstone to be forever lost in the Spiritual Realm.



\newpage
\subsection{Stay on Guard}

If the PCs decide to stay here and guard the prison with their lives to prevent anyone from freeing the Unmade, read the following:

\quoteBox{
	As you gather around the \npcMishram{}'s prison, you realize how many people sacrificed their lives to keep her here. To give humanity a chance in this eternal conflict. But you also know - you are not the only ones sent by \npcSjaAnat{}, there will be others. \\ \\
	And now it is your turn to sacrifice your lives. You will die here, protecting the prison and making sure no servant of the Unmade will ever reach it. You will die as the Watchers on the Rim, a true Knights Radiant. And thought your only companion will be the hateful wail of a mad spren, you know this is the right thing to do.
}

The PCs have chosen this place to die on duty. Their story ends here.