\section{Trail of the Ages}
\label{sec:trailOfTheAges}

Finally, the party gathered enough clues to start searching for \npcMishram{} in the Spiritual Realm. In this section, they will follow her through her past, uncovering her story.

You can run this part similar to the previous scenes, except now you should focus on \npcMishram{}. The following scenes you can find in here can be treated as inspiration or examples, you can change them to better fit your story.



\subsection{Sorrowful Healer}

Start this scene with the following:

\quoteBox{
	You find yourself in a body of a dying singer. The battlefield is scattered with wounded like yourself, various spren hovering above you all. \\ \\
	Suddenly, you see a black cloud of smoke approaching you. Black arms grow out of the cloud to help it move. You recognize the Unmade... \\ \\
	As the smoke flies next to you, it transform into a regal femalen, \npcMishram{}. "Live", she says with a soothing voice. "Heal", she adds as she gently cradles you in her arms.
}

The PCs take the roles of singer troops on a bloodied battlefield. However, the battle is over - \npcMishram{} is healing the wounded singers. 

The PCs may help her. Run this scene as an Endeavor. Set the average test difficulty to 22 (or 19 + 1d6).

\pursuitReq{5}{3}

\subsubsection{Success!}

If the party completes the Endeavor with a success, make a note of that. During the fight in \fullref{sec:avatarOfHatred}, \enemyMishram{} will start with 1 fewer Investiture.

\subsubsection{Failure...}

If the party completes the Endeavor with a failure, make a note of that. During the fight in \fullref{sec:avatarOfHatred}, \enemyMishram{} will be accompanied with one additional \enemySingerWarform{}.

\subsubsection{Ending the Scene}

At the end of the Endeavor, read the following:

\quoteBox{
	Suddenly, the face of \npcMishram{} changes drastically. Instead of sorrowful and caring healer, you see a visage twisted with hatred and disdain looking at you. \\ \\
	"I see you", she hisses. "You will die in agony, begging for death! I will break every bone in your body, I will..."
}

Unless the party flees the scene at this very moment, \enemyMishram{} will strike a random PC before the vision ends. 

\corruptedBox{
	Meeting with early memory of \npcMishram{} may expedite an Enlightened Stoneward \seeCorruptedRules{}.}


\spoilerBox{
	\npcShallan{} meeting \npcMishram{} healing singers is presented in \bookWAT{}, Chapter 76. Concessions.
}




\subsection{False Desolation}

Start this scene with the following:

\quoteBox{	
	You wear a body of a Singer, standing in a ranks of a Singer army. The commander - a femalen with a proud and regal face streaming shadowy smoke behind her - approaches you and lays her carapaced hand on your shoulder. \\ \\
	"I am proud of you, my children, all of you!", she says. "But the fighting is not done, and will never be done while the children of Honor live", she adds, pointing upwards. Human figures are flying there, leaving streams of pale blue light behind them.
}

The party, taking a role of the Singers during the False Desolation, must face against Radiant forces. There are six Knights, treat each of them as \enemyWindrunnerThird{}. They will fight to the end. In the background there are more Singers fighting with more Radiants.

\subsubsection{Using Surges}

If a PC attempts to use a Surge, read the following:

\quoteBox{
	As you are about to use your powers, you hear the voice of your spren: \\ \\
	"Don't! Those Singers could not do that. If you use the Surges, the vision might unravel!" 
}

If the PCs does not change their mind, \enemyMishram{} will take over \npcMishram{} for a moment to make a strike against them. That will repeat each time any PC would use their powers.

\subsubsection{Granter of Forms}

At beginning of the 2nd round of combat, read the following:

\quoteBox{
	"Your gods may have abandoned you...", you hear \npcMishram{}. "But I will never! I am standing with you." \\ \\
	As you feel her touching your carapace, a surge of power fills your body and you hear rhythms you never knew before. You feel faster, stronger, more powerful!
}

\npcMishram{} gives the PCs the forms of power. Each of the PCs gains talents and abilities of one Regal form of your choice. You can use \enemySingerDireform{}, \enemySingerStormform{}, or other form from \handbook{} or other sources.

For easier game play, assume this only changes the talents and abilities the PCs can use, but not their Health or other characteristics that would be unhandy to track.


\subsubsection{Success!}

If the party defeats all the enemies, make a note of that. During the fight in \fullref{sec:avatarOfHatred}, \enemyMishram{} will start with 1 fewer Investiture.

\subsubsection{Failure...}

If the party fails to defeat the enemies, make a note of that. During the fight in \fullref{sec:avatarOfHatred}, \enemyMishram{} will be accompanied with one additional \enemySingerWarform{}.

If a PC would die in combat, instead pull them out from the vision.

\subsubsection{Ending the Scene}

Just like before, end this scene with the following:

\quoteBox{
	As the last enemy falls, you feel the gaze of \npcMishram{} following you. \\ \\
	"I see you!", you hear her scream. "I see you and I know you! Traitors! Voidbringers! I will bring your death, I will make you suffer!"
}

Again, unless the party flees the scene at this very moment, \enemyMishram{} will strike a random PC before the vision ends.

\reasonBox{
	This scene was foreshadowed during \fullref{sec:visionsEnterShadesmar}, try to paint the same picture as then.
}




\subsection{Price of Peace}

Start this scene with the following:

\quoteBox{
	Yet again, you enter a vision wearing a Singer's carapace. Before you stands your leader, gently holding a hand of a human. \\ \\
	"My people don't want war", you hear her pleading to other humans. "Peace is possible. We can find a way."
}

The PCs find themselves as Singers trying to end the False Desolation. They must convince a group of Windrunners they should have peace. Run this scene as a Conversation.

For the purpose of the scene, treat all Windrunners as a single character. \conversationDefence{\enemyWindrunnerThird{}}{17}{16}{5}

The Windrunners lost many friends in the war and they want to have their revenge. However, they respect \npcGarith{}, their leader, who stands beside the Singers. They also feel responsible for the fate of humanity they swore to protect.

\conversationEnd{\enemyWindrunnerThird{}}{1}

\subsubsection{Success!}

If the party completes the Conversation with a success, make a note of that. During the fight in \fullref{sec:avatarOfHatred}, \enemyMishram{} will start with 1 fewer Investiture.

\subsubsection{Failure...}

If the party completes the Conversation with a failure, make a note of that. During the fight in \fullref{sec:avatarOfHatred}, \enemyMishram{} will be accompanied with one additional \enemySingerWarform{}.


\subsubsection{\npcMishram{} and \npcMelishi{}}

Once the Conversation is ended, proceed by reading the following:

\quoteBox{
	"Those need to know it's not just a few of us", your Singer leader says. "They need to know our new god is different". \\ \\
	As she said it, you see a darkness pooling between the stones. Soon after, from  the shadows a regal femalen steps out. \npcMishram{}.
}

\npcMishram{} enters the scene. For a brief moment, allow her to speak fondly of peace. While talking, her voice overlaps with multiple rhythms at once.

Soon after, proceed with the following:

\quoteBox{
	Suddenly, \npcMishram{}'s head jolts and she turns towards the night. "Who is out there?", you hear the Unmade asking. \\ \\
	You see a lone man approaching \npcMishram{}. In his hands, he is holding a large gemstone with a soft, yellow glow. \\ 
	"I am the Bondsmith", says the man.
}

\subsubsection{Ending the Scene}

To end the scene, read the following:

\quoteBox{
	"DO IT, MELISHI", you hear Honor's voice. In this instant, the gemstone starts glowing, as \npcMishram{} gets imprisoned inside. All of the singers around drop to the ground, screaming and writhing, and you feel something being ripped out from the Roshar itself.
}

\npcMishram{} is captured. If the PCs were not fast enough and they failed the Conversation, a random PC is being hit with a strike of \enemyMishram{} before she gets imprisoned.

You can now proceed to \fullref{sec:avatarOfHatred}.


\spoilerBox{
	Capturing \npcMishram{} by the Bondsmith is described in \bookWAT{}, Chapter 87. Love and Betrayal.
}



\subsection{Deadly Rivals}

Start this scene by reading the following:

\quoteBox{
	You find yourself on an infinite stony expanse under a gray sky. There are two people standing in front of a dark corridor. \\ \\
	"Do we have to do this?", you hear \npcShallan{} asking. \\ \\
	"You just killed by babsk", he answers. It is clear to you, they are about to kill each other.
}

The party witnesses an upcoming fight between \enemyLightweaverShallan{} and \enemyGhostbloodMraize{}. They can join either of sides to help them defeat the other. Both sides will fight to kill and won't yield.

In this scene, \npcShallan{} bears \lootAntiStormlightDagger{} with no charges left (they were used to kill Iyatil a moment ago) and will not summon her Shardblade.

\subsubsection{Aftermath}

After the PCs deal with an enemy of their choice, you can proceed to \fullref{sec:thePrison}.

\spoilerBox{
	\npcShallan{}'s fight with the Ghostblood leaders is shown in \bookWAT{}, Chapter 134. The Third Way.
}

\reasonBox{
	This scene features \enemyGhostbloodMraize{} as he appeared more in the adventure. This book also provides a stat block for \enemyGhostbloodIyatil{} - you can use it to prepare similar scene with Iyatil. However, since she did not appear so far, I don't feel introducing her now would be good for the pacing.
}

\reasonBox{
	This scene is designed as a boss fight, but there are good arguments to turn the enemy into a Rival or kill them in a "cinematic" scene without real fight. Feel free to adjust based on the preferences of your players. You can also skip this scene if it doesn't fit your story, or play it after the fight with \enemyMishram{}.
}

