\section{Unmade Influence}
\label{sec:unmadeProgression}

The entire adventure focused around the Unmade. Enlightened Radiants could have their talents expedited up to three times after meeting them \seeCorruptedRules{}.

However, it might have happened that not every Radiant had an opportunity to be granted three free talents - perhaps the PCs missed some scenes or the Radiant joined the party in the middle of the adventure.

You can use the memories of the Spiritual Realm to create another encounter with the Unmade, allowing the Radiant to receive full range of available bonuses.

Or you can also introduce an Unmade just because the PCs enjoyed previous encounters with them and you believe it will make for a fun scene.




\subsection{Example Scene}

You can start such a scene with the following:

\quoteBox{
	Out of the sudden, you are thrown in the midst of battle. Men screaming, horses whinnying, steel clanging. Nearby a dying man whispers his last rattles. \\ \\
	You recognize the enemy to wear veden colors. But there is no time to think. You must push forward! Don't stop! Keep the momentum!
}

The party fights in a border war against the veden forces. They must face six Veden Troops (use \enemyQueensGuard{} stat block). They will fight to the end.

A PC might give themselves to the \npcThrillTitle{} of the Battle, gaining an advantage on each attack and grazing all characters (including allies) around themselves with each melee attack.

\corruptedBox{
	Fighting in a battle influenced by \npcThrill{}, the \npcThrillTitle{} may expedite en Enlightened Windrunner \seeCorruptedRules{}.
}

\corruptedBox{
	Hearing Death Rattles, a vision sent by \npcMoelach{}, may expedite an Enlightened Truthwatcher \seeCorruptedRules{}.
}