\chapter{Appendix \thechapter{}: Acknowledgments}
\label{chap:acknowledgments}

I poured my heart into this project, but I couldn't make it by myself alone. Here is quick thank you for all of those, who helped me do it, as well as a few other acknowledgments. \\ \\


\noindent\textbf{\Large My lovely wife} \\

My gemheart, moon of my life, the harbor of my soul’s journeying, thank you for all the help during this project! \\ \\


\noindent\textbf{\Large My fluffiest cat} \\

To Leo, the best, cutiest, fluffiest cat in the world! Thank you for your soothing purring, gentle rubs and musical meows to provide emotional support during all those evenings.

Thank you for reminding me that there is a time to write adventures, but also a time for a break, pets, belly rubs, fun and games!

Thank you for alerting me that the bowl is empty just in time to avert any disaster that could fall on our house for this transgression!

But on top of that, thank you for being so purrrfect! \\ \\


\noindent\textbf{\Large Anomer} \\

Anomer, my dear friend, thank you for all shared RPG discussions and your feedback on dungeon designing process.\\ \\


\newpage
\noindent\textbf{\Large Artists involved} \\

I cannot express my gratitude enough to all talented artists whose masterpieces show us the world of Roshar and its wonders. In particular I want to thank those, who created art for this book:

\begin{itemize}
	\item \textit{(At this moment the list is empty...)}
\end{itemize}

If you are an artist and this book inspired you to create some epic illustration, please reach out! It would be great if I could include your art in here! \\ \\


\noindent\textbf{\Large Map generation} \\ 

Maps included in \nameref{chap:exampleMaps} were created with free trial version of Inkarnate. You can find this online tool in here: 

\url{https://inkarnate.com} \\ \\


\ifthenelse{\equal{\useAI}{false}}{}{
	\noindent\textbf{\Large Image generation} \\ 
	
	Images used in this book are generated by ChatGPT. Before you will have any ideas - I used this tool only for image generation, the story and other ideas are not AI-generated. \\ \\
}

\noindent\textbf{\Large PDF Building} \\ 

This document was written in TeXstudio with MiKTeX 24.1.

