\chapter{Appendix \thechapter{}: Items}
\label{chap:items}

Following unique items can be found or earned by the characters during the adventure:

\section{\lootPerfectGemstoneName}

Gemstone perfectly cut into a round sphere. It can trap and hold a single spren forever.

In order to entice the spren into entering the gemstone, it must be exposed to something it is familiar with. As \iconAction{} a character holding the gemstone may produce a statement or present a behavior that aligns with spren's nature or philosophy. Any insincere attempts must be preceded with a successful \skillCheck{20}{Deception}

\scriptedOption{Success!}{
	If the spren approves of the statement or particular action, add 1 to the capture track.
}

\scriptedOption{Failure!}{
	If the spren does not agree with the statement or behavior, or if the Deception check failed, subtract 1 from the capture track.
}

\scriptedOption{Captured!}{
	Once the capture track reaches level of 3, the spren created enough Connection with the character to be lured into the gem. It cannot leave it unless the gemstone is shattered.
}

\section{\lootRogueShardbladeName}

A Shardblade in possession of criminal underworld. Few people know of its existence. A character claiming this item will not be pushed into the politics of the nearby realms. The Blade follows all standard Shardblade rules (see \handbook{}).\\

\noindent
% \textbf{Type:} Shardblade \\
% \textbf{Skill:} Heavy Weaponry\\
% \textbf{Damage:} 2d8 spirit \\
% \textbf{Range:} Melee\\
% \textbf{Expertise:} loses Dangerous trait\\
% \textbf{Traits and Rules:} Dangerous, Deadly, Unique: Summoning/Dismissing Spiritual Injury


\section{\lootSprenDaggerName}

An ancient Reshi dagger, forged with Reshi songs in order to fight hostile spren. Upon contact with any cognitive being, the dagger releases an enormous amount of energy, annihilating both the target and the wielder.

\section{\lootTorchShortName}

Short torch, made from metal. It is decorated with twisty, sinuous patterns, similar to vine stalks - now rusty and crumbling from the age. \\

\noindent
\textbf{Type:} Mace \\
\textbf{Skill:} Light Weaponry\\
\textbf{Damage:} 1d4 impact \\
\textbf{Range:} Melee\\
\textbf{Expertise:} gains Momentum trait\\
\textbf{Traits and Rules:} Extinguishable, Flaming [1d6] \textit{(see Below)}


\section{\lootTorchLongName}

An old and rusty torch with a 6 ft. shaft. Whole torch is made of metal decorated with twisty, sinuous patterns, similar to vine stalks. \\

\noindent
\textbf{Type:} Longspear \\
\textbf{Skill:} Heavy Weaponry\\
\textbf{Damage:} 1d4 impact \\
\textbf{Range:} Melee [+5]\\
\textbf{Expertise:} gains Defensive trait\\
\textbf{Traits and Rules:} Two-Handed, Extinguishable, Flaming [1d8] \textit{(see Below)} \\ \\

\noindent \Large \textbf{Unique Torch Traits} \normalsize \\


\scriptedOption{Extinguishable}{
	The GM can spend \iconComp{} from an attack with this weapon to extinguish it at the end of turn. As long as this weapon is extinguished, it looses Flaming trait. As \iconAction{}, a character may light the torch again to restore the trait.
}

\scriptedOption{Flaming [N]}{
	On hit, this weapon deals additional N energy damage from fire.
}


