\chapter{Chapter 6 - TODO - Shadesmar}
\label{chap:chapter6}

\setcounter{section}{-1}
\section{Running This Chapter}

The characters must travel through the Shadesmar to Kharbranth.



\subsection{Character Advancement}

The characters start this chapter at level 6. Advance them twice in this chapter: once after they depart from Celebrant and once when they reach Kharbranth.

In this chapter, the party will have an opportunity to rescue a stranded Deadeye, allowing them to earn their Shardblade when they exit Shadesmar with her. They can also encounter and tame a Mandra.

The following events may affect their path to radiance:
\begin{itemize}
	\item Trading secrets with Ghostbloods
	\item Rescuing stranded Deadeye
	\item Freeing Tukari prisoners
	\item Joining fight at Unyielding Fidelity
	\item Using \lootGateOpener{} can expedite an Enlightened Elsecaller
\end{itemize}



\subsection{Forging Alliances}

While traveling in the Shadesmar, the party will be presented with following opportunities to improve relations with other fractions:

\begin{itemize}
	\item Trading secrets with Ghostbloods agents will benefit them in future relations.
\end{itemize}



\subsection{Spren Attitude}

When traveling in Shadesmar, the party will encounter variety of spren. Each of them can have a different attitude towards the party, based on number of factors:

\subsubsection{\npcSjaAnat{}'s Touch}

The spren will not be fond to see one of them corrupted by the Unmade, especially if they see one of their kind affected. Mistspren being curious by nature will show more leniency in that matter.

\subsubsection{Radiant Bonds}

In general the spren will respond positively to another one of their kind bonding one of the PCs. However, there are exceptions to this rule: Honorspren and Inkspren refused renewing the bonds and will react negatively if they see one of their kind is bonded to a character.

\subsubsection{Traveling with a Deadeye}

Having Deadeye in the party, suggesting their corpse might be used as a weapon in the Physical Realm, might hurt relations with other spren, especially with Honorspren, Inkspren or the ones of the Deadeye's kind.

\subsubsection{Living Spren's Ideals}

Character's behavior might positively impact their relations with any spren if they enact the ideals the spren believe in. \textit{(eg. Cultivationspren will react better to a person living by Edgedancers' ideals of remembering the forgotten)}


\input{chapter_6/pathToLighthouse.tex}
\input{chapter_6/feralSprenEncounters.tex}
\input{chapter_6/sailingCelebrant.tex}
\input{chapter_6/celebrant.tex}
\input{chapter_6/sailingUnyieldingFidelity.tex}
\input{chapter_6/shadesmarSeaEncounters.tex}
\input{chapter_6/unyieldingFidelity.tex}
\input{chapter_6/toThePhysicalRealm.tex}


\section{Journeying Onward}

After the party uses \lootGateOpener{} to exit from Shadesmar and enter Kharbranth, advance them to level 8 and move to the next chapter.