\section{Path to the Lighthouse}
\label{sec:pathToLighthouse}

Start this chapter by reading the following:

\quoteBox{
	In the realm of the endless darkness, you see a figure approaching you. Their skin looks like a rusty metal with a dark smoke rising from the cracks. \\ \\
	"Greetings, travelers", he says. "The mother sends me. The mother asks to guide you to the river. The travelers will come."
}

\npcSprenGuide[s] is an Enlightened Lightspren sent by \npcSjaAnat{} to help the party traverse the sea of beads. He guides the PCs to the nearby boat. When the characters board it, he will stand at it's end and use a long pole to make it move.

\newpage
\subsection{Shadesmar Guide}
\label{ssec:pathToLighthouseGuide}

As the party swims through the sea of beads, read the following:

\quoteBox{
	Thud! The pole hits the sea floor. Click! Click! Click! Click! The beads scatter before the boat. \\ \\
	"Mother says the travelers go to Kharbranth", thud! "The travelers must go south, to \locationFidelity{}, and use the fabrial there", click, click, click! "The path will lead you to the lighthouse", thud! "There you can wait for ship to take you", click, click, click! \\ \\
	Thud! Click, click, click, the rhythm continues. Thud! click, click, click!
}

It will take a few moments to reach the shore. \npcSprenGuide{} will remain silent for the most part, unless the party asks him more questions:

\scriptedOption{Who are you?}{
	I was a Lightspren once, before the mother showed me the truth. Now, I am Enlightened. Easier to hide nearby the revelry.
}

\scriptedOption{Why are you helping us?}{
	The mother speaks highly of you. The mother asked to help you.
}

\scriptedOption{Will you travel with us?}{
	I must return before the night. They must not see I am gone. They will suspect me, they will suspect mother.
}

\scriptedOption{What is this place?}{
	It is where the spren live. It is how the people think of things. Like a reflection of your world, but more true.
}

\scriptedOption{Do you have any advice?}{
	There is little food. You can trade to buy more. You pay with light in here, dun spheres are worthless. Control your emotions, don't draw them.
}

\scriptedOption{What path should we take?}{
	Board a ship. Sail to Celebrant. It is The Rift on your side. There you will find more ships, take one sailing to Unyielding Fidelity. Some will suggest you go to the Perpendicularity. Don't go, not safe!
}

\subsubsection{Treasure}

In the boat there is some provisions for the party: just enough food to reach the Lighthouse and 100 marks worth of Stormlight. The light will slowly fade, but most of it should survive until the party reaches Celebrant. It will fade before reaching Unyielding Fidelity.

\corruptedBox{
	Investigating or prolonged holding of \lootGateOpener{} will expedite an Enlightened Elsecaller \seeCorruptedRules{}.
}




\subsection{Obsidian River}

Once the boat reaches the shore, read the following:

\quoteBox{
	You land on the black, glassy surface. It's not too wide and spreading southward. In the Physical Realm, a river flows here, but in here, the land seems to be inverted. \\ \\
	"My journey ends here", \npcSprenGuide{} says. "Your journey continues. Death before life, radiants!"
}

The path leads south. It will take 3 days of hike to reach the lighthouse, unless the characters are slowed down for some reason. Keep track of party resources (food, water, Investure) as it is not trivial to renew them in here.

There is little variety in the surrounding environment. If you wish to enrich this part of the story, you can run some of the encounters from \fullref{ssec:shadesmarFeralEncounters}.

In the middle of 3rd day of hike, the party reaches their first stop. Proceed to \fullref{ssec:shadesmarLighthouse}.

\spoilerBox{
	Journey on the same path is described in \bookOB{}, Chapter 95. Inescapable Void.}



\subsection{The Lighthouse}
\label{ssec:shadesmarLighthouse}

When the party reaches the lighthouse, read the following:

\quoteBox{
	Light-skinned man welcomes you to the tall building with light shining on top. \\ \\
	"Are you here for the fortune? You are lucky, the storm should rage tonight."
}

Lighthouse keeper \npcFortuneReader[s]{} is an \enemyExpert{} who might be looking Shin for the characters, though in truth he is from Shu-Korath on Sel. He offers fortune reading and can trade with basic supplies.

The party is welcome in the lighthouse and they can wait in here for a ship that will take them south.

\spoilerBox{Kaladin interacting with the lighthouse keeper is described in \bookOB{}, Chapter 97. Riino.}


\subsubsection{Trading with \npcFortuneReader{}}

\npcFortuneReader{} can sell canned food, full waterskins, and most of the items listed in \textbf{Equipment} section of \handbook{}. Refer to that section for item prices.

He will accept only spheres full of light as dun ones are worthless in here.


\subsubsection{Fortune Reading}

For a price of 2 marks of stormlight, \npcFortuneReader{} will read fortune for one of the characters during the next highstorm. That can be something you prepare for a specific PC or one of the Death Rattles \textit{(see \nameref{chap:deathRattles})}.

A character who received the reading will gain \abilityFutureKnowledgeName[1]{}:

\abilityFutureKnowledge{}.


\subsubsection{Ship Schedule}

\npcFortuneReader{} knows about two ships that should be sailing here soon: a Reacher vessel with accommodation for human passengers and a smaller Mistspren boat. 

He does not know how expensive would it be to board any of them, though he suspects it will be cheaper on a boat that does not provide food or water for humans.

If the characters decide to wait for the arrival of a ship, proceed to \fullref{sec:sailingCelebrant}. 