\section{Sailing to Celebrant}
\label{sec:sailingCelebrant}

The characters must choose their transport to Celebrant. \npcFortuneReader{} knows about two ships that are expected to sail there soon.

Lightspren ship is the first one to arrive at the lighthouse. They charge the party for 30 marks of Stormlight for the passage to Celebrant. The voyage should take 3 days and they have a cabin for human passengers, offering food and water for the time of the trip.

If the party chooses this option, proceed to \fullref{ssec:sailingReachers}.

If that price is too high for them, soon after mistspren arrive. They don’t charge the party for the travel, as they are intrigued by humans and wish to know them better. However, their ship does not have any human adaptations - the party will need to provide their own food and water.

The party must board their ship or they will be stranded here for many days. Proceed to \fullref{ssec:sailingMistspren}.



\subsection{Sailing with Reachers}
\label{ssec:sailingReachers}


In the middle of 2nd day, their ship is attacked by Shadesmar Pirates. The attackers aim to steal Reacher’s cargo to sell on the black market. The PCs can defend the Lightspren or step back.

Pirate's attack consists of three mistspren \enemyMandraRider{}s. Their ship looms behind them with a cryptic standing on a bow, but he doesn't give an order to join the riders. The riders fight to the end.

At the end of the trip, when the party reaches Celebrant, they will loose 50\% of their Stormlight as the Investure leaks from the imperfect gems.

\reasonBox{
	The same group of pirates can be met later in this chapter: see \fullref{ssec:sailingPirates} or \fullref{ssec:shadesmarSeaEncountersPirates}.
}



\subsection{Sailing with Mistspren}
\label{ssec:sailingMistspren}

It should take 3 days for mistspren to reach Celebrant. However, as they treat the plan with little rigor, each day will come with spontaneous idea to change the course and visit some locations around Celebrant:

\begin{itemize}
	\item day 1: Candlemore (one of them has family over there and wants to see them)
	\item day 2: The Burning Gardens (the captain always wanted to see them)
	\item day 3: Emberdark (to perhaps buy some goods for a trade in Celebrant)
\end{itemize}

Each sidetrack will add 1 day to the total travel time. The party can enter a Conversation with the captain each time to discourage them from their ideas and keep course on Celebrant. Each time they succeed in influencing the captain, the crew agrees to visit the location later.

\conversationDefence{\enemySprenCaptain{}}{17}{15}{5} Like all mistspren she is a free spirit, yearning for new experiences.

\conversationEnd{\enemySprenCaptain{}}{1}

At the end of the trip, the party will loose 50\% of their Sormlight increased by additional 10\% for each unplanned course change (up to 80\% total).



\subsection{Sailing to the Perpendicularity}

The party should be discouraged to sail in that direction. Despite being the only reliable method of exiting the Cognitive Realm, \npcSjaAnat{}'s instruction are to go south.

If the characters insist on going there, make them enter the Conversation with their ship's captain. The spren are aware of some nasty rumors about this place and do not wish to sail there. The PCs must convince them to change the course.

If that didn't stop them, proceed with an encounter with a \enemySingerHaevenlyOne{} patrolling the skies. If they win that fight, introduce more and stronger Singers ready to fight the party.

At some point, the party should agree to take the safer route and sail to Celebrant.