\section{Sailing to Unyielding Fidelity}
\label{sec:sailingUnyieldingFidelity}

The party boarded a ship on their journey to \locationFidelity{}. However, there is still a long road ahead...

Depending on the party's choice of the ship, proceed to:

\begin{itemize}
	\item \fullref{ssec:sailingPeakspren}
	\item \fullref{ssec:sailingPirates}
	\item \fullref{ssec:sailingHonorspren}
\end{itemize}

\subsection{Sailing with Peakspren}
\label{ssec:sailingPeakspren}

The party can board peakspren ship for 50 marks of Stormlight. They will be provided food and water for the time of the trip.

\subsubsection{Peakspren Crew}
\label{ssec:sailingPeaksprenCrew}

\npcPeaksprenCaptain[s]{} and her crew consisting of five \enemyTrueSpren{}s (all peakspren) man this ship. They are reliable and experienced sailors who are sailing from Cultivation's \locationPerpendicularity{} with goods to trade at \locationFidelity{}.

"Ava" is actually not her full name. It's a shorten version of "Avalanche" she uses in formal occasions (eg. when talking to honorspren sea patrol).

\subsubsection{Pirate Attack!}

Atthe 2nd day of the journey, the peakspren ship is attacked by the pirates. For details of this encounter, see \fullref{ssec:shadesmarSeaEncountersPirates}.

The characters can join either side of the combat.

If the party stays on the side of peakspren and they win, they can continue the journey on their ship. If they loose, however, they will be captured by the pirates. Proceed to \fullref{ssec:sailingPiratesCaptured}.

If they switch sides and join the pirates, proceed to \fullref{ssec:sailingPirates} after the battle, regardless of the result.

\subsubsection{Honorspren Inspection}

At the 3rd day of the journey, honorspren sea patrol demands to inspect the ship. For details of this encounter, see \fullref{ssec:shadesmarSeaEncountersHonorspren}.

If the players rise suspicions during the inspection, they will be asked to be taken by honorspren for questioning in \locationFidelity{}. If the party agrees, proceed to \fullref{ssec:sailingHonorspren}.

Failure to comply will make honorspren hostile, starting a fight. If the party wins, they can remain on the peakspren ship. If they are defeated, proceed to \fullref{ssec:sailingHonorsprenCptured}.




\subsection{Sailing with Ashspren Pirates}
\label{ssec:sailingPirates}

Boarding the ship is free, but the characters must pay in other ways for the voyage. On top of that, the pirates do not offer food and water - the PCs must have their own, or they will suffer \exhausted[1] for each day without them.

The party can show \lootScadrialCoin{}, earning the crew's respect and an expectation to participate in the fights. The PCs can also work mundane tasks on the ship with \skillCheck{15}{\skillThievery{} (or other applicable skill)}.

If the characters fail any of the above, \npcCrypticCaptain{} will deem them worthless. Their water will be drugged and they will be imprisoned in their sleep - proceed to \fullref{ssec:sailingPiratesCaptured}.

\subsubsection{Pirate Crew}

\npcCrypticCaptain{} is a rebel cryptic who commands seven \enemySprenPirate{}s: three mistspren an four ashspren. They are nasty thugs, who attack smaller ships to steal and plunder.

Their ship is fast and nimble, pulled by more mandras than one would expect for a vessel this big. During the fight, some of them are used as mounts as a few pirates ride them into battle as \enemyMandraRider{}s.

\newpage
\subsubsection{Imprisoned by Ashspren}
\label{ssec:sailingPiratesCaptured}

Start this scene by reading the following:

\quoteBox{
	You wake up in the morning, your head hurting like it was full of broken glass. You are striped of all your possessions, locked behind iron bars. \\ \\
	"Nothing personal, humans", you hear \npcCrypticCaptain{} speaking from the dark corner of the room. "You are useless as part of the crew, but we can sell you for at least some profit. Don't worry, we will take you to \locationFidelity{}, as promised..."
}

The party is imprisoned and the pirates are planning to sell them as slaves. They do not care to feed them - each PC gets \exhausted[1] for each day they go without the food. A PC can attempt \skillPersuasion{} against mistspren's Defenses to beg them for food.

The prisoners are guarded for most of the time, though they can speak freely and plan their escape. To open the lock they would need succeed on \skillCheck{20}{\skillThievery{}} (assuming they can get proper tools for the job). There will be an opportunity for escape when the pirates are in a middle of a fight, either with peakspren or honorspren.

\subsubsection{Easy Money}

At the 2nd day of journey, the pirates catch Peakspren ship, starting the attack against the crew (for details, see \fullref{ssec:sailingPeaksprenCrew}). The characters can join either side of the combat.

If the party joins the side of peakspren and they win, they can continue the journey on their ship. If they loose, however, they will be captured by the pirates. Proceed to \fullref{ssec:sailingPiratesCaptured}.

If the party chooses to fight for the pirates, they can continue the journey on their ship. What's more, if they win, the captain will share the spoils with them - d20~+~10 marks of Stormlight for each character.

\subsubsection{Honorspren Inspection}

At the 3rd day of the journey, honorspren sea patrol demands to inspect the ship. For details of this encounter, see \fullref{ssec:shadesmarSeaEncountersHonorspren}.

Honorspren quickly realize they are dealing with pirates, which starts the fight. The characters can join either side of the combat.

If the party joins honorspren, after the fight proceed to \fullref{ssec:sailingHonorspren} regardless of the result.

If the party chooses to fight with the pirates, they can remain on the ship.

\subsubsection{Rewarded Loyalty}

If the party stays on the side of the pirates during all encounters, the captain will recognize their loyalty. If at least one of them is not bonded to a spren, he will send one of the ashspren with them, securing a connection to powerful friends.



\subsection{Sailing with Honorspren}
\label{ssec:sailingHonorspren}

The party cannot board this ship, unless \npcHonorsprenCaptain{} decides there is a reason for it. When that happens, the party will be provided with food and water.

Depending on the reason why the party is on the ship, the captain may decide it will be better if one of the PCs, their spren, or the entire party are held in custody. If that happens, proceed to \fullref{ssec:sailingHonorsprenCptured}.

\subsubsection{Honorspren Crew}

\npcHonorsprenCaptain{} commands sea patrol consisting of six other honorspren \enemyTrueSpren{}s. The ship also employs mistspren crew, but in the case of fight they are ordered not to get involved. \npcHonorsprenCaptain{} believes it wouldn't be honorable to expect them to join the battle.

Their whole ship is massive, in a military design. It reassembles a small swimming fortress pulled by mandras.


\subsubsection{Imprisoned by Honorspren}
\label{ssec:sailingHonorsprenCptured}

Start this scene by reading the following:

\quoteBox{
	Honorspren soldiers drag you to the brig and lock the door behind you. Your cell is clean and relatively comfortable, but still - it's a cell. \\ \\
	"You cannot be trusted", \npcHonorsprenCaptain{} says, "and it will be better for everybody if you are contained here. Your companions are free to walk on deck, but they will join you at the first sign of trouble."
}

Honorspren treat their prisoners well, providing them with regular food and water. However, there is always one of them keeping watch - unless there is fight on the deck.

When the guard is not there, the party might attempt to lockpick the doors with \skillCheck{20}{\skillThievery{}}. They may also try other methods of freeing their companions.

\newpage
\subsubsection{Hunting Pirates}

The captain is aware of the pirates on those waters and is actively searching for them. At 2nd day of the journey, they will catch them, starting a fight (see \fullref{ssec:shadesmarSeaEncountersPirates}). The characters can join either side of the combat.

If the party chooses to fight on the side of honorspren, if they win, they will continue the journey on their ship. If they loose, they will be captured by the pirates - proceed to \fullref{ssec:sailingPiratesCaptured}.

If the party switches sides and joins the pirates, if they win, they will continue the journey on their ship - proceed to \fullref{ssec:sailingPirates}. If they loose, however, they will be imprisoned by honorspren who will demand their trial in \locationFidelity{}.

\subsubsection{Peakspren Inspection}

On the 3rd day, honorspren ship encounters the peakspren vessel. Honorspren demand to inspect the ship and peakspren comply.

It is an opportunity for PCs who don't wish to continue this travel on their ship. Each PC and accompanying NPC can attempt a \skillStealth{} check against honorspren captain's defenses.

If they succeed, they can continue the travel on peakspren ship (though it may lead to some more interactions with upset peakspren). On a failure, honorspren turn hostile against the sneaking PCs, starting a fight.



\subsection{Reaching the Destination}

After the party experienced an encounter with peakspren, honorspren and the pirates, you might consider introducing them to other events from \fullref{sec:shadesmarSeaEncounters}.

When those are over, proceed to \fullref{sec:unyieldingFidelity}.