\section{Shadesmar Sea Encounters}
\label{sec:shadesmarSeaEncounters}

While the party is traveling on see, you might consider enriching their story with following encounters. 

Some of them are mandatory when they are traveling on a specific ship and will be listed in \fullref{sec:sailingUnyieldingFidelity} section, but you can add more of them from here if you want to.

Make sure every encounter from this list is used only once. If the party traveled with peakspren, were attacked by pirates and later detained by honorspren, do not run the pirate encounter again.

When there is no more encounters you want to introduce, proceed to \fullref{sec:unyieldingFidelity}. 




\subsection{Pirate Attack}
\label{ssec:shadesmarSeaEncountersPirates}

Start this scene by reading the following:

\quoteBox{
	Suddenly, you hear more rapid bead clicking in a distance. You turn in that direction to see three figures mounted on mandra steeds rushing towards you. \\ \\ 
	Behind them, a ship is quickly approaching you. A criptic standing on its bow holds his sword high, aiming at you. It seems this battle is unavoidable...
}

The ship is attacked by pirates. Three mistspren \enemyMandraRider{}s and four ashspren \enemySprenPirate{}s are lead by cryptic \enemySprenCaptain{}. They will fight with the ship's crew until one of the sides is fully defeated.

The party can join the fight on either side or they can use the chaos as a cover for their other schemes.

\reasonBox{
	\enemyMandraRider{}s were never described in any book, but it feels like a tactic that might happen in the Shadesmar and since the adversary roaster could use some variety, I decided to introduce them.
}




\subsection{Honorspren Inspection}
\label{ssec:shadesmarSeaEncountersHonorspren}

Start this scene by reading the following:

\quoteBox{
	Your ship is being approached by a small floating fortress pulled by mandras. An honorspren captain declares: \\ \\
	"By the authority of \locationFidelity{}, I, \npcHonorsprenCaptain{}, demand that you granted me permission to enter your ship for a routine inspection."
}

An honorspren \enemySprenCaptain{} and his six honorspren \enemyTrueSpren{} enter your ship. If they find anything illegal they will demand an explanation, which might turn into a fight. When this happen, the party may join either side (unless they were the reason the combat started), or use it as a cover for their own schemes.

If the inspection finds suspicious individuals in the party (another honorspren or an enlightened spren), they will consider detaining them and transporting to \locationFidelity{} for a trial. The party will have a chance to enter a Conversation with \npcHonorsprenCaptain{} to ease his mind.

\conversationDefence{\enemySprenCaptain{}}{17}{15}{5} He is bound by duty and honor and he will aim to enact them in his decisions.

\conversationEnd{the captain}{1}

\subsubsection{Additional Complications}

If a character rolls \iconComp{} during the encounter with honorspren, the GM may spend it for them to find \lootGateOpener{}, consider it suspicious and confiscate it. The party will need to retrieve it from \npcHonorsprenCaptain{} before they can escape from Shadesmar.





\subsection{Trading Ship}
\label{ssec:shadesmarSeaEncountersTraders}

When you start this scene, read the following:

\quoteBox{
	A rich vessel approaches your ship. Its fat captain in fancy robes smiles at you. \\ \\
	"Hellooooo!", he yells loud enough to be heard a few miles away. "Would you like to trade? We have best prices on this sea, and the best quality! I'm sure something will catch your eye!"
}

The party is approached by a trader's ship. They trade with items, though the prices are less than ideal: buying costs twice as much, while selling can be done for half the price. The party can enter Conversation with ship's captain to get better prices.

Depending on what your story needs, the traders can be either spren or humans, from either Roshar or off-world.




\subsection{Fused Scouts}
\label{ssec:shadesmarSeaEncountersFused}

Start this encounter by reading the following:

\quoteBox{
	You see small red points, flying far from your ship. Soon, as they come closer, you see red ribbons trailing behind them. \\ \\
	You realize when it is too late - those are not spren, those are fused. And if you can see them, they can see you!
}

Soon after, the ship is attacked by three \enemySingerHaevenlyOne{}s. They fight with hatred and focus their attacks on the PCs, ignoring other crew members who join to defend their ship.

The singers will fight to the end. They will attempt to throw the PCs off the ship for an easy kill, but they will not refuse to use their weapons either.

If a character is thrown into the sea, they will start drowning in a round unless they grab a rope. There are plenty of those on the ship, but they require an \iconAction{} to throw them. If no PC does that, one of the crew spren will do that instead in their turn. 




\subsection{Feral Mandras}

When you start this encounter, read the following:

\quoteBox{
	On a horizon, you see a flock of beasts flying above the surface of the bead ocean. When they fly closer, you recognize they are mandras, domesticated luckspren who usually pull other ships. \\ \\
	You never consider them to be aggressive, but this pack certainly looks hostile. What riled them up? Were they corrupted by \npcSjaAnat{}?
}

The party is attacked by 1d4 + 2 \enemyLuckspren{}s. They will fight until the end.

If the party missed \fullref{ssec:celebrantLuckspren} encounter, after the fight one of the mandras may remain behind, allowing the PCs to start \fullref{ssec:celebrantLucksprenTame} arc.




