\section{To the Physical Realm}
\label{sec:toThePhysicalRealm}

Once the party decides to use \lootGateOpener{}, read the following:

\quoteBox{
	When you crack the shell of the ancient artifact, suddenly a pillar of light shoots into the sky. From within it, black tendrils of misty smoke slowly evaporate into the air. Next moment, the pillar starts to visibly shrink.
}

The party has 1 round to enter the temporal \locationPerpendicularity{}. They and their entire equipment is transported nearby \locationKharbranth{}. If they rescued deadeye spren in Celebrant, she will appear as a Shardblade on the other side.

Any characters, equipment or unfinished quests are left behind and there is no way to bring them back. For this reason, make sure the players understand the consequences of using the item when they are not grouped together.

\corruptedBox{
	Using \lootGateOpener{}, an ancient artifact of \npcBlackFisher{}, the \npcBlackFisherTitle{} will expedite an Enlightened Elsecaller \seeCorruptedRules{}.
}

\reasonBox{
	This is a last time the story references \npcBlackFisher{}. Make sure after this scene an Enlightened Elsecaller was expedited 3 times in total.
}



\subsection{Visions of Disdain}
\label{ssec:visionsExitShadesmar}

When the PCs enter the summoned pillar of light, read the following:

\quoteBox{
	When light fades away, you find yourself standing on a stony shore. The day is warm and the cremlings skitter on a lush vegetation around you. \\ \\
	You are in a city full of Singers and golden-haired people. They talk, laugh, and trade. There is no sign of war anywhere.
}

Give the PCs a short moment to walk around. A character with a proper expertise might recognize the people as Iriali and the city as Kasitor. Even if none of the PCs usually speak their language, they will be able to communicate without issues.

A moment later, read the following:

\quoteBox{
	There is one figure, that catches your attention. A feamalen Singer wearing a proud and regal form. She stands above the crowd, her arms spread in a welcoming gesture. \\ \\
	"This land is for you to thrive, my children", she says. "Live peacefully, my dearest, and forget the horrors of war, as those will never reach you again".
}

When \npcMishram{} notices the party, read the following:

\quoteBox{
	Suddenly, her face changes. Serenity gone, now replaced with a visage tormented with hate and disdain. She jerks her head to look directly at you and changes her speech: \\ \\
	"You will scream, begging for your death, when I will rip your throat! You will choke on your own blood! I will make you suffer, every day for the rest of your miserable lives! I will..." \\ \\
	With that, the vision end, but the echo of hateful screams still follows you...
}



After the vision ends, proceed to the next chapter.

\corruptedBox{
	Meeting \npcMishram{} in a vision will expedite an Enlightened Stoneward \seeCorruptedRules{}.
}