\section{\locationFidelity{}}
\label{sec:unyieldingFidelity}

When the party reaches \locationFidelity{}, read the following:

\quoteBox{
	You arrive at \locationFidelity{}, an impressive honorspren fortress. Hundreds feet tall, with rectangular walls made of blue stone that defy the laws of gravity: each wall is a separate surface, with roads, parks and fountains ignoring the true meaning of "down".
}

The party reached their destination! However, to use \lootGateOpener{} and travel back to the Physical Realm they must gather together - which may be difficult if honorspren detained one of them.

Additional complication may happen if the sea patrol confiscated the artifact. If that's the case, the PCs must work to recover it.

Allow the party to spend some time around and interact with the NPCs. Once the party is ready to proceed or they lack ideas what to do next, start the events of \fullref{ssec:unyieldingFidelityFight}.

\newpage
\subsection{Ice Gardener}

When the party approaches the fortress, they will notice a cultivationspren with a pale-blue, fern-like body. If the party accepted quest from \fullref{ssec:celebrantIceCultivationspren}, they will recognize the recipient of the letter they are carrying.

\subsubsection{Reward}

If the players deliver the letter to \npcIceCultivationsprenGardener{}, if the letter doesn't show any signs of being opened, the spren will ask the party to join them.

A PC can bond her and become a Radiant. If they do, they will receive free talent from Abrasion talent tree. However, their first Progression talent costs twice as much. Subsequent talents in those trees have standard cost.

If no player wishes to bond her, she will accompany them until she finds someone suitable. Until then, she will be supportive NPC always ready to provide a helpful comment.

If she sees the party read the letter, she won't trust them enough - she will find a Radiant to bond on her own, possibly meeting the PCs in the future chapters.

\subsubsection{\npcIceCultivationsprenGardener{} the Cultivationspren}

\npcIceCultivationsprenGardener{} is a cultivationspren from Frostland regions. Her kin have pale-blue look of their vines, and instead of crystals, their vines entangle over icicles and ice shards.

In the Physical Realm, they manifest as frost-like patterns. Most commonly they mark flat surfaces remaining flat themselves, but occasionally they can rise as three-dimensional beings.

\npcIceCultivationsprenGardener{} loves cold weathers, with sliding on ice being her favorite fun activity. She is not an expert on medicine - her remedy on any ailment is to "put an ice on it". Surprisingly, sometimes it helps!



\subsection{Tukari Prisoners}
\label{ssec:unyieldingFidelityTukari}

When the PCs approach the cages, read the following:

\quoteBox{
	You see a group of people locked in a cage next to the wall. Judging by their clothes, they are from the western part of Roshar, Tukar perhaps? \\ \\
	"Hey, you, human!", one of them calls you in a broken alethi. "Set us free! We pay!"
}

If the characters want to speak with the prisoners, they will tell the following:

\scriptedOption{Who are you? Where are you from?}{
	"Tukari. From Tukar. On the other side. Peace be to you!"
}

\scriptedOption{How much will you pay for freeing you?}{
	"20 marks. Full with Stormlight. Rare on this side, yes?"
}

\scriptedOption{Why are you locked in here?}{
	"Honorspren. Who knows their reasons? They not think like us." With a successful \skillCheck{18}{\skillInsight{}} a PC can determine they know exactly why they are imprisoned.
}

\scriptedOption{Don't lie to me, why are you here?}{
	If the PC succeeds on \skillCheck{15}{\skillIntimiation{}}, the prisoners will answer: \\
	"All right, all right! We were attacked by an ashspren on our way here. We defended ourselves. Honorspren say it's a crime in here. They lock us here."
}

\scriptedOption{How can we enter the fortress?}{
	"Not try. You enter, you leave never. Run from here if can!"
}

\scriptedOption{Who's got a key to those cages?}{
	"Honorspren. The girl. One with combat skirt."
}

\subsubsection{Releasing the Prisoners}

To open the cages, a PC must pass a \skillCheck{25}{\skillThievery{}} or use a key held by one of the honorspren. 

To pickpocket the key carried by female honorspren, a PC must succeed on \skillCheck{20}{\skillThievery{}}. This check gains an advantage during \fullref{ssec:unyieldingFidelityFight}. Pickpocket failure will make honorspren hostile.

If the tukari are released during \fullref{ssec:unyieldingFidelityFight}, they will focus on running away, attacking only those who try to stop them.

\subsection{Honorspren Trial}

If the party arrived to \locationFidelity{} with honorspren, any character held by them in the custody will be transported to the cages already occupied by tukari people.

Honorspren are claiming the characters must stay here and await the trial. For that, they need the High Judge, who is currently away. Nobody will provide a timeline when will he arrive here.

\reasonBox{
	This book does not provide any details for the trial. It is suggested the party attempted to leave this place before it happens. If they insist on staying despite all warnings it's not a good idea - improvise!
}




\subsection{Fight on the Walls}
\label{ssec:unyieldingFidelityFight}

When you start this scene, read the following:

\quoteBox{
	Suddenly, you see movement from the west - a group is approaching \locationFidelity{}. When they come closer, you see marble-white skin, with red patterns. Singers! \\ \\
	Their small force is lead by two Heavenly Ones, Fused unhinged enough to attempt this kind of attack.
}

\locationFidelity{} is being attacked by Singer forces: 2 \enemySingerHaevenlyOne{}s, 4 \enemySingerDireform{}s and 4 \enemySingerStormform{}s. During the combat they will focus on fighting honorspren forces. They will fight to the end.

The fortress is defended by honorspren guards: 8 \enemyTrueSpren{}s and single \enemySprenCaptain{}.

\subsubsection{PCs' Goals}

At the end of this fight, the party must complete the following objectives:
\begin{itemize}
	\item Reclaim \lootGateOpener{} from \npcHonorsprenCaptain{} if it was confiscated
	\item You must gather your party before venturing forth
\end{itemize}

If the party is ready with those objectives, they can use \lootGateOpener{} without waiting for the end of the fight.

If the PCs aim to reclaim the stolen artifact, they can use the fight as a distraction to pickpocket it from \npcHonorsprenCaptain{}. They can also backstab him to loot the artifact when he is weaken.

To gather the party, if one of them is locked, they can obtain the key from the guard in a similar way. They can also attempt to lockpick the cages.

An alternative would be to join the fight on the side of honorspren. If they manage to defend the Singer force together, \npcHonorsprenCaptain{} will recognize honor of their actions, allowing them to go free.

\subsubsection{Walkable Walls}

It is possible to walk on the external walls of \locationFidelity{} as though they were a floor. If a character other than honorspren or Windrunner rolls \iconComp{} while standing on a wall, the GM can spend it to give them Disoriented condition until their next round.

\reasonBox{
	In the books we are only shown that the internal walls of honorspren cities are walkable and it would make quite a poor defense if the external walls allowed for the same, but it makes an interesting battlefield, so let's allow it, shall we?
}

\subsubsection{Limited Visibility}

The edge of the wall's corner obscures vision of the 2nd part of the wall. Characters will not be able to see enemies behind the corner. Use your own judgment for any specific cases.

\subsubsection{Angerspren Pens}

There are 2 \enemyAngerSpren{}s locked in nearby pens. The PCs can open them with \skillCheck{15}{\skillThievery{}} to let them loose. Angerspren will attack the nearest character, without regards of the side their prey is fighting on.

\subsubsection{Pirates Join the Fight}

If during the previous encounters honorspren won in a fight against ashspren pirates, they might have taken some of them into the custody. If that's the case, the remaining pirates may plan a rescue mission. 

If that's the case, on the 2nd round of the combat they will drop their hooded cloaks and join the fight. They will focus on freeing their mates from the cages, but they won't hesitate to attack any honorspren or Singer standing in the way.

\reasonBox{Depending on your party's preferred plystyle, you might end this chapter with either huge and epic fight, or ignore the fighters and focus on stealth, pickpocket and backstabbing. Don't make your players do things they will not enjoy.}


