\chapter{Chapter 9 - TODO - Kholinar}
\label{chap:chapter9}

\setcounter{section}{-1}
\section{Running This Chapter}

After they proved themselves to \npcDalinar{}, the characters can join a mission he and other Radiants are planning. They want to fly to Kholinar to scout the city and rescue \npcElhokar{}'s family. However, \npcSjaAnat{} has another mission for the party - \npcQueen{} must be slain.

\subsection{Character Advancement}

The party starts this chapter at level 12. Advance them twice in this chapter: once after they find their way to the Royal Palace and once after they kill \npcQueen{}.

In this chapter, the PCs may win a Shardplate from a fight with a royal guard.

The following events may affect their path to radiance:
\begin{itemize}
	\item Rescuing \npcGavinor{} may be recognized by a Lightspren or Cultivationspren
	\item Meeting \npcSjaAnat{} may expedite an Enlightened Lightweaver
	\item Entering they Royal Palace and facing the queen may expedite an Enlightened Skybreaker
\end{itemize}



\subsection{Forging Alliances}

In this chapter, the PCs will have a final opportunity to forge and benefit from alliances with following fractions:
\begin{itemize}
	\item The Wall Guard
	\item Kholinar \npcFractionGhostbloods{}
	\item The Cult of Moments
	\item Besieging Singers
\end{itemize}

Choices made by the party in the Act I of the story should carry on to this chapter, affecting the initial attitude of the fractions towards the PCs. Some alliances may be easier to secure, some might be near-impossible...


\subsection{Event: Singer Siege}
\label{ssec:singerSiegeEvent}

In the second part of the chapter, the PCs will charge against the Royal Palace of the Kholin monarch. At the same time, the Singer forces are attacking the city. At some point they will reach the palace, meeting the PCs.

\eventComplication{Singer Siege}{
	\iconCompEvent{}
	\iconCompEvent{}
	\iconCompEvent{}
	\iconCompEvent{} \\ \vspace{0.15cm}
	\iconCompEvent{}
	\iconCompEvent{}
	\iconCompEvent{}
}

\subsubsection{Progressing the Event}

Each time a complication is rolled by a PC while they are in the Kholinar Palace, you can spend it to progress the event by 1, trading an immediate Complication for an advancement of Singer forces through the city.

Other conditions described in the relative sections may also affect the event progression.

Alternatively, if the PCs are allied with the Singers, instead of spending their complications, they can spend any opportunity they roll to advance the progress on the event.

\subsubsection{Triggering the Event}

Once the final progression slot of the event is filled, the Singer forces reach the palce. All major NPCs supporting the party will flee towards the Oathgate, leaving the PCs alone in the palace.

On top of that, Singer adversaries can be met in all Palace areas. They will attack the party on sight. If the PCs allied them, they will support them in fight instead - you can allow the Singer NPCs to fight alongside them or reduce the number of royal guard forces, assuming a guard is fighting a Singer off-screen.




\subsection{Alternative Story}
\label{ssec:alternativeStoryChap9}

From the structural point of view, this chapter serves two main purposes that must happen to keep the story cohesive:
\begin{itemize}
	\item The PCs must battle \npcYeligNar{}
	\item The PCs must enter the \locationPerpendicularity{}
\end{itemize}

It is a nice addition to place the events of the chapter in Kholinar and resolve any plot threads started in Act~I of the adventure. 

However, the same structural goals could be achieved if the party joined the Battle of Thaylen Field - the PCs could face \npcAmaram{} after he bonded \npcYeligNar{} and later enter the \locationPerpendicularity{} opened by \npcDalinar{}. 

If you wish, you can GM the story in that direction. This book will not provide detailed sections on how to GM that alternative story, but you can include:

\begin{itemize}
	\item Securing a support from azish and thaylen patrons
	\item Several Conversation scenes with the locals
	\item Several Endeavor scenes to rebuild the city \\ \textit{(allow the results to affect the battle)}
	\item A Mass Warfare scene of the battle
	\item An attempt to resist Thrill
	\item An Endeavor to retrieve the King's Drop
	\item Fight with \npcYeligNar{}
	\item Entering \npcDalinar{}'s \locationPerpendicularity{}
\end{itemize}

Make sure the PCs advance 2 times in the chapter and that they end the chapter inside the Spiritual Realm.


\input{chapter_9/returnToKholinar.tex}
\input{chapter_9/sjaAnatsPlan.tex}

\input{chapter_9/gatheringAllies.tex}
\newpage
\input{chapter_9/theWall.tex}
\newpage
\input{chapter_9/cloakAndDagger.tex}
\newpage
\input{chapter_9/theCultOfMoments.tex}
\newpage
\input{chapter_9/singerSiege.tex}
\newpage

\input{chapter_9/kholinarPalace.tex}
\newpage
\input{chapter_9/kholinarPalaceRooms.tex}
\input{chapter_9/queenFight.tex}
\newpage
\input{chapter_9/toSpiritualRealm.tex}


\section{Journeying Onward}

After the party kills the queen allowing \npcSjaAnat{} to open the Perpendicularity, the PCs can enter the Spiritual Realm. Advance them to level 14 and proceed to the next chapter.