\section{Cloak and Dagger}
\label{sec:cloakAndDagger}

One of the powers the party can ally with is the underworld of Kholinar - crews of thieves, petty scoundrels and dangerous criminals, all under the rule of \npcGhostbloodBoss{}.

There is no secret in the city that they wouldn't know and no dirty trick they shy away from. If allied, their experience could be put to a good use.




\subsection{Fraction Leader}

Kholinar underworld is ruled by \npcGhostbloodBoss[s]{}. \npcGhostbloodBoss{} (short for Alloy) is a \enemyGhostbloodBoss{}, a \npcFractionGhostbloods{} member who lost contact with other agents. He decided to fill the power vacuum after \npcQueen{}'s behavior become more erratic. 

\npcGhostbloodBoss{} already noticed the PCs in their previous struggles in the city. Now, when they returned, he will quickly attempt to recruit them and make use of their competence.



\subsection{Endeavor Requirements}

To secure an alliance with Kholinar \npcFractionGhostbloods{}, the party will need to run a series of food heists, stealing from city nobles, allowing the criminals to sell it for ludicrous prices.

You can run it as an Endeavor. Instead of the PCs making skill tests, run several scenes, each with its own Endeavor, Conversation or Combat. Award a success or a failure to the main Endeavor based on whether the party succeeded on the scene.

\pursuitReq{6}{3}



\subsection{Starting Conditions}

The Endeavor starts with an additional success if the PCs sided with the criminals during \fullref{ssec:cityEscapePlanCriminals}. It starts with additional failure if the party sided with the cult at that time.

The Endeavor starts with an additional success if the PCs joined the \npcFractionGhostbloods{} and have their mark tattooed on their arms. Lightweaving of the tattoo might also work, but the success will change to failure as soon as it is revealed to be a fake.

The Endeavor starts with an additional success if the party owns \lootSeonTube{} (or other items bought by \lootScadrialCoin{}) and gifts it to the \npcFractionGhostbloods{} in Kholinar.


\subsection{Example Scene}

The party must steal the food from the Mausoleum, a mansion owned by the Tenets. It earned the name after the statues of house servants created with Soulcasting.

You can run this as an Endeavor focusing on \skillStealth{} and \skillThievery{}. Set the average DC of Endeavor tests to 22 (or 18 + d8). 

\pursuitReq{7}{3}

\spoilerBox{
	\npcShallan{} planning a food heist in the Mausoleum is shown in \bookOB{}, Chapter 77. Stormshelter.}


\subsection{Cloak and Dagger - Final Task}
\label{ssec:cloakAndDaggerFinal}

When the PCs successfully complete the Endeavor, they will be presented with the final task to secure the alliance - they must break into the Monastery Dais and steal the food from the cultists.

You can run this scene as an Endeavor focusing on \skillStealth{} and \skillDeception{}. On a failure the party will be attacked by \enemyRevelerSadistic{}s and \enemyCultist{} of various kinds.

\subsubsection{Success!}

If the PCs manage to sneak into the Revelry and steal the food, or if they kill the cultist guards attacking them, they will secure an alliance with Kholinar \npcFractionGhostbloods{}.

That will grant them additional bonuses during their assault on the Royal Palace. However, their action will damage their relations with the \npcFractionCult{}, preventing them from allying with the party.



\subsection{Rewards}

If the party succeeded on the Endeavor, they will learn about \enemyQueensGuard{} patrol patterns as well as about \enemyQueensShardbearer{} guarding \fullref{ssec:kholinarPalaceRoomsGavinorEntrance}.

If the PCs complete \fullref{ssec:cloakAndDaggerFinal}, they will learn about an alternative entrance to the Palace - the one described in \fullref{ssec:kholinarPalaceRoomsSecretEntrance}.