\section{Gathering Allies}
\label{sec:gatheringAllies}

Breaking into \fullref{sec:kholinarPalace} will not be an easy task. It will be wise for the party to gather some allies first.

At this point of time, there are four major fractions that might be interested in moving against \npcQueen{}. You can find more about them in following sections:

\begin{itemize}
	\item \fullref{sec:theWall}
	\item \fullref{sec:cloakAndDagger}
	\item \fullref{sec:theCultOfMoments}
	\item \fullref{sec:singerSiege}
\end{itemize}




\subsection{Allying a Fraction}

Overall the process of making an alliance with a fraction is the same for all four powers: it starts with an Endeavor to run a few simple tasks for them. If succeeded, the PCs will be assigned one final task to prove their allegiance.

When running an Endeavor to befriend a fraction, do not let it be resolved with just a few test checks. Instead, allow each attempt to be a separate scene with its own Endeavor, Conversation or Combat. Award a success or a failure to the main Endeavor based on the result of the scene.

Not every fraction can be fully allied. Since they are hostile towards one another, completing a Final Task from one of them will lock the PCs from allying another one. In total they can ally only two of them.

You will find more details relating to each fraction in their respective sections.


\subsection{Starting Conditions}

To create a continuity with the first part of the campaign, allow each Endeavor to start with additional successes or failures already earned based on PCs' choices at lower levels.

The details are described in respective sections.



\subsection{Rewards}

Completing the Endeavor of each fraction will grant the PCs some small benefits during their assault on the Royal Palace.

If the party succeeds on the Final Task, they will be additionally rewarded with more benefits.

The details are described in respective sections.


\subsection{Default Alliance}

If the PCs fail to ally anyone or if they ignore the topic and focus on realizing their own goals, allow \npcKaladin{} to fully ally the Wall Guard to align with the story of \bookOB{}.



\subsection{Old Friends}

Not only major powers wish for \npcQueen{} to go down. Depending on how the story of the PCs developed, they might count on the help from other NPCs they've met earlier in the story, eg:

\begin{itemize}
	\item \npcTroublemaker{}
	\item \npcGrandma{} \npcGrandmaName{}
	\item \npcSingerWorkerGranF{} and \npcSingerWorkerGranM{}
	\item Ardent \npcLockedArdent{}
	\item Reveler \npcRevelerGeneral{}
\end{itemize}

This book will not focus on those NPCs. If they are alive in your story and friendly towards the party, allow them to give some support, eg by providing an additional success to one of the Endeavors to ally a fraction or with another favor.