\section{Palace Rooms}
\label{sec:kholinarPalaceRooms}

Kholinar Royal Palace is a vast location, full of rooms to explore and enemies to fight. 

The PCs can enter through one of the three entrances: \fullref{ssec:kholinarPalaceRoomsMainGate}, \fullref{ssec:kholinarPalaceRoomsSunwalk} and \fullref{ssec:kholinarPalaceRoomsSecretEntrance}.



\subsection{Main Gate}
\label{ssec:kholinarPalaceRoomsMainGate}

When the PCs approach the Main Gate of the Palace, read the following:

\quoteBox{
	As you approach the enormous gates of the Royal Palace, the guards reach for their arms, scarlet anticipationspren lashing around them like angry whips. \\ \\
	"Get lost!", their leader cries. "The palace is closed for the likes of you!"
}

Two \enemyQueensGuard{}s commanded by one \enemyQueensGuardLeader{} guard the entrance. The party will need to attack and defeat them to enter the Palace.

At beginning of the 2nd round of combat, two more \enemyQueensGuard{}s join the fight, arriving from the nearby \fullref{ssec:kholinarPalaceRoomGrandEntry}.

\subsubsection{Connected Rooms}

From here the PCs can proceed to \fullref{ssec:kholinarPalaceRoomGrandEntry}.




\subsection{Grand Entry}
\label{ssec:kholinarPalaceRoomGrandEntry}

When the party reaches this location, read the following:

\quoteBox{
	The long and quiet halls of the Palace stretch in every direction. Despite the spheres full of Stormlight hanged on the walls, it is unnaturally dark in here...
}

Normally, two \enemyQueensGuard{}s can be found in here. However, if the party entered from \fullref{ssec:kholinarPalaceRoomsMainGate}, they already joined the fight in there, making this location empty.

The walls of this location are illuminated with numerous spheres. The PCs can use them to restore their Investure.

\subsubsection{Connected Rooms}

This is a central location in the Palace, connecting the entrance at \fullref{ssec:kholinarPalaceRoomsMainGate} with corridors at locations of \fullref{ssec:kholinarPalaceRoomsEasternGallery} and \fullref{ssec:kholinarPalaceRoomsHighHalls}.

Also, from here the PCs can access \fullref{ssec:kholinarPalaceRoomsGarrison}, \fullref{ssec:kholinarPalaceRoomsArdentChambers} and \fullref{ssec:kholinarPalaceRoomsBallrooms}.




\subsection{Guard Garrison}
\label{ssec:kholinarPalaceRoomsGarrison}

When the PCs approach this room, read the following:

\quoteBox{
	You approach a room filled with resting guards. Their helmets are off, their swords and belts are hanging from the pegs on the wall. \\ \\
	However, the people are acting wrong. There is no chatter, no jokes, no laughter you would expect in a garrison like this. The men are just sitting, their eyes hidden in shadows.
}

The party can sneak by this location with a successful \skillCheck{20}{\skillThievery{}} test passed by each PC. On a failure, the guards will attack.

There are six \enemyQueensGuard{} in here commanded by a \enemyQueensGuardLeader{}. They are resting - a quick attack would make them Surprised. During a combat they will fight to the end.

\subsubsection{Treasure}

The room is filled with weapons. You can assume any standard weapon a PC might be looking for can be found in here. There are no special weapons in here (like Half-Shards, Warhammers, Grandbows, etc.).

\subsubsection{Connected Rooms}

This room connects only with \fullref{ssec:kholinarPalaceRoomGrandEntry}.





\subsection{Sunwalk Entrance}
\label{ssec:kholinarPalaceRoomsSunwalk}

When the PCs approach this entrance, read the following:

\quoteBox{
	You see a huge gate, ornamented with the Double Eye of the Almighty. Through the nearby window you see a narrow path towards the Monastery Dais - the Sunwalk.
}

This entrance is locked. To enter from here, the PCs would need to be allied with \npcFractionCult{}.

\subsubsection{Connected Rooms}

This gate connects \fullref{ssec:kholinarPalaceRoomsEasternGallery} with the Monastery Dais (see \fullref{ssec:revelrySunwalk}).





\subsection{Eastern Gallery}
\label{ssec:kholinarPalaceRoomsEasternGallery}

When the PCs enter this area, read the following:

\quoteBox{
	The room is full of spheres scattered on the floor. In the midst of them, several men in ardent robes are standing surrounded by palace guards. \\ \\
	One of them is looking at you, his hand fidgeting with glowing rings. "Thank the spren! You are exactly what we need! Do you want to be rich?"
}

Three \enemyRevelerWealthy{}s and six \enemyQueensGuard{}s are located in this room. The revelers bribed the guards to protect them instead of following their duties.

When the PCs enter, the Revelers will offer them 20 marks each to hire them as their guards and protect them from Singers. If the PCs accept, allow them short respite and progress \fullref{ssec:singerSiegeEvent} to the end.

If the party refuses, they will order \enemyQueensGuard{} to attack them, starting a fight.

\subsubsection{Treasure}

Scattered on the floor, there is 100 + 2d20 marks. On top of that, each \enemyRevelerWealthy{} carries their own wealth. After the PCs gather all of those, you can assume they will have unlimited access to Stormlight until the end of the chapter.

\subsubsection{Connected Rooms}

From this area, the PCs can go to \fullref{ssec:kholinarPalaceRoomsSunwalk}, \fullref{ssec:kholinarPalaceRoomsDining} or \fullref{ssec:kholinarPalaceRoomsKitchen}. Main exit in this room leads to \fullref{ssec:kholinarPalaceRoomGrandEntry}.




\subsection{Guest Dining}
\label{ssec:kholinarPalaceRoomsDining}

When the party reaches this location, read the following:

\quoteBox{
	You see a long table in the middle of a room, full with food, sweets and wine. A man in an ardent robes raises his chalice. "Cheers! For the end of the world!", he toasts.
}

Five \enemyRevelerDrinking{}s are feasting in here. They will attempt to tempt the party to join them, triggering a combat upon refusal. They will fight to the end.

\subsubsection{Feast}

Most of the food in here is spoiled, but the wine is fine. A PC may drink the wine in here to quickly gain benefits of a Short Rest. However, they loose 1 maximum Focus as a result of the influence of \npcHeartRevel{}, the \npcHeartRevelTitle{}.

Any PC may return to this location for sip of a wine any number of times, each time gaining the Short Rest benefits and maximum Focus penalty.

The maximum Focus restores to normal at the end of the next Long Rest.

\subsubsection{Connected Rooms}

From here the PCs can head towards \fullref{ssec:kholinarPalaceRoomsArdentChambers} or \fullref{ssec:kholinarPalaceRoomsEasternGallery}.




\subsection{Kitchens}
\label{ssec:kholinarPalaceRoomsKitchen}

When the PCs enter here, read the following:

\quoteBox{
	You enter the palace kitchen. Once it must have been a busy place. Now the bodies slashed with kitchen knives are scattered all around: on the table, in the corner, on the cellar trap.
}

Dead bodies belong to the royal cook and kitchen staff. Most of the food found in here is already spoiled. 

\subsubsection{Connected Rooms}

The PCs can continue to \fullref{ssec:kholinarPalaceRoomsCellar} or return back to \fullref{ssec:kholinarPalaceRoomsEasternGallery}.





\subsection{Dark Cellar}
\label{ssec:kholinarPalaceRoomsCellar}

When the party descends in here, read the following:

\quoteBox{
	The steps lead down into the darkness. You smell the horrid odor of death, rot and decay. When you rise a sphere, you see a piles of dead and rotten bodies, all in a noble clothing. \\ \\
	A moment later you see a movement. A small boy is still alive, just barely. "Have you killed them?", he asks.
}

The boy's name is \npcCellarBoy{}. He is an Enlightened Dustbringer. If the party offers him a little Stormlight, he will recover and join them with a goal to kill the queen.

\subsubsection{\npcCellarBoy{}}

\npcCellarBoy{} is too small to fight with the guards, cultists or Singers. However, as an Enlightened Dustbringer, he can use Spreading Decay.

To make him use his ability, a PC must spend \iconOpp{} (see \fullref{ssec:kholinarPalaceOpportunities}).

\npcCellarBoy{} will accompany the PCs until \npcQueen{} is killed. He will not flee when the Singers reach the Palace as a part of \fullref{ssec:singerSiegeEvent}.

\subsubsection{Connected Rooms}

The path ends here. The party must return upstairs to \fullref{ssec:kholinarPalaceRoomsKitchen}.




\subsection{Ardent Chambers}
\label{ssec:kholinarPalaceRoomsArdentChambers}

When the PCs enter this area, read the following:

\quoteBox{
	You walk through a long corridor with guest rooms on its both sides. In the middle you see some cultists in ardent robes.
}

Three \enemyCultist{}s can be met on the corridor. If attacked by the party, the noise will attract nine more \enemyCultist{}s and two \enemyRevelerSadistic{}s, who will join the fight at beginning of the second round of combat. 

Each \enemyCultistOfMoments{} impersonates a random spren and will fight to the end.

\subsubsection{Connected Rooms}

The corridor in here joins \fullref{ssec:kholinarPalaceRoomGrandEntry} and \fullref{ssec:kholinarPalaceRoomsDining}.


\subsection{Secret Entrance}
\label{ssec:kholinarPalaceRoomsSecretEntrance}

When the PCs enter through this path, read the following:

\quoteBox{
	A hole in a wall overgrown with rockbud vines, then a labyrinth of narrow corridors and forgotten rooms. No wonder nobody knows about this path...
}

This entrance is hidden and few people know about it. It will be hard for the party to learn about it unless they are allied to Kholinar criminals.

\subsubsection{Connected Rooms}

The corridor leads to \fullref{ssec:kholinarPalaceRoomsBallrooms}.



\subsection{Ballrooms}
\label{ssec:kholinarPalaceRoomsBallrooms}

When the PCs enter this location, read the following:

\quoteBox{
	You enter a wide room. Some of the walls were crudely torn down to make even more space. In the middle of all of this people in ardent robes are dancing, while others are playing some screeching instruments.  
}

Two \enemyQueensGuard{} guard the entry to the room in which six \enemyRevelerMusical{} are dancing. They will invite the PCs to the dance, attempting to force them if they refuse.

\subsubsection{Treasure}

After dealing with the cultists, the PCs can find rich clothes of Kholinar nobility lying on the floor and furniture. A character wearing those will be ignored by the guards in \fullref{ssec:kholinarPalaceRoomsGarrison} and \fullref{ssec:kholinarPalaceRoomsHighHalls}.

\subsubsection{Connected Rooms}

The main entrance of this location leads to \fullref{ssec:kholinarPalaceRoomGrandEntry}.

If the PCs know where to look, backdoor corridors lead to \fullref{ssec:kholinarPalaceRoomsSecretEntrance}.




\subsection{High Halls}
\label{ssec:kholinarPalaceRoomsHighHalls}

When the party enters this location, read the following:

\quoteBox{
	You enter halls decorated with numerous sculptures and spheres. Somehow, the darkness in here feels stronger and more wrong...
}

Those halls are patrolled by four \enemyQueensGuard{}s. A PC can attempt \skillCheck{25}{\skillStealth{}} to learn their patrol pattern and allow the party to avoid them. The test gains an advantage if the PCs learned before about the guards from allied Kholinar criminals.

\subsubsection{Connected Rooms}

The Halls are connected to \fullref{ssec:kholinarPalaceRoomGrandEntry}. On the other end there is \fullref{ssec:kholinarPalaceRoomsThroneRoomEntrance}, and if the party takes the stairs, they can find a corridor leading to \fullref{ssec:kholinarPalaceRoomsGavinorEntrance}.




\subsection{\npcGavinor{}'s Room Entrance}
\label{ssec:kholinarPalaceRoomsGavinorEntrance}

When the PCs approach this location, read the following:

\quoteBox{
	You approach a small door that would seem insignificant in other circumstances. However, the guard in a Shardplate suddenly makes this room feel much more important. \\ \\
	"Stay where you are", he says, preparing his warhammer. "By the order of the queen, nobody is to disturb the prince. Especially not you!"
}

A \enemyQueensShardbearer{} and six \enemyQueensGuard{}s are guarding the entrance. They will attack anyone who would attempt to enter the room behind them, but they will not pursue fleeing enemies.

\subsubsection{Shardplate}

If the PCs manage to kill the \enemyQueensShardbearer{}, they will be able to collect his Shardplate. Make it clear for them there will be little time to recharge it, so any damage they do to the Plate will carry on after the Plate is in their possession.

\subsubsection{Connected Rooms}

The Shardbearer was guarding \fullref{ssec:kholinarPalaceRoomsGavinorsRoom}. The party can also go back to \fullref{ssec:kholinarPalaceRoomsHighHalls}.




\subsection{\npcGavinor{}'s Room}
\label{ssec:kholinarPalaceRoomsGavinorsRoom}

When the PCs enter this room, read the following:

\quoteBox{
	You enter a cold, stark room with a broken mirror on the wall. Only a few spheres illuminate the interior. \\ \\
	In the corner, on the stony floor, you can see a small baby surrounded by red spren. They pull on his hair and force him to watch horrifying shapes they turn into.
}

\reasonBox{
	While in the books \npcGavinor{} and \npcQueen{} are met in the same place, I decided to split this scene into two locations for gaming purposes. This way the party may follow the secondary objective to rescue the baby and earn the Shardplate. Or they can ignore it and focus on main quest only.
}

\spoilerBox{
	\npcGavinor{} is met by the rescue party in \bookOB{}, Chapter 84. The One You Can Save.}

\subsubsection{Rescuing \npcGavinor{}}

\npcGavinor{} is tormented by hatespren. They can be easily slain by a Radiant with a Living Shardblade. If none of the PCs does that, they will flee after a couple of moments. The heir is safe!


\reasonBox{
	Have an NPC take care of the baby, there is no need for the PCs to take on this role. However, don't stop them if they want to go extra mile to protect the boy.
}

\subsubsection{Connected Rooms}

The path ends here. The PCs must go back through \fullref{ssec:kholinarPalaceRoomsGavinorEntrance} to return on the corridors of \fullref{ssec:kholinarPalaceRoomsHighHalls}.




\subsection{Throne Room Entrance}
\label{ssec:kholinarPalaceRoomsThroneRoomEntrance}

When the PCs reach this location, read the following:

\quoteBox{
	You approach a grand door, unmistakably leading to the throne room. Six guards are standing in front of it. \\ \\
	"Go back!", one of them orders. "The queen does not wish to see you. Leave or die!"
}

Two \enemyQueensGuardLeader{}s and four \enemyQueensGuard{}s guard the entrance. They will attack anyone attempting to enter \fullref{ssec:kholinarPalaceRoomsThroneRoom}, but they will not pursue fleeing enemies.

\subsubsection{Connected Rooms}

From here the PCs can enter \fullref{ssec:kholinarPalaceRoomsThroneRoom} or return back to \fullref{ssec:kholinarPalaceRoomsHighHalls}.




\subsection{Throne Room}
\label{ssec:kholinarPalaceRoomsThroneRoom}

When the party reaches this room, read the following:

\quoteBox{
	You enter the throne room. Enormous statues representing nine heralds reach the ceiling, the floor is decorated with precise mosaics. \\ \\
	The queen stands next to a window, but the sun couldn't reach her skin. Instead, she is covered in darkness.
}

This is the room the PCs were searching for. The party should prepare for a fight! Proceed to \fullref{sec:queenFight}.

\subsubsection{NPCs' Retreat}

If \npcElhokar{} or his Radiants are still with the PCs, read the following:

\quoteBox{
	"Oh, Elhokar...", the queen says. "You were ever so oblivious. Your father had great plans, but you... all you ever wanted to do was to sit in his shadow. It was for the best that you went off to play war. \\ \\
	"But I have solved the riddle! \npcYeligNar{} serves me! I have outgrown you, Elhokar!"
}

\npcElhokar{} will quickly realize \npcQueen{} is under the influence of the Unmade and there is no reasoning with her. They will retreat to focus on rescuing \npcGavinor{}. The PCs must face the Queen without their support.

\spoilerBox{
	\npcElhokar{} meets \npcQueen{} in \bookOB{}, Chapter 84. The One You Can Save.}

