\section{Fighting the Queen}
\label{sec:queenFight}

Start this scene by reading the following:

\quoteBox{
	A black smoke started to twist around \npcQueen{}, her nails glowing with a purple when a crystalline structure started growing over them. \\ \\
	"You should have run with the others", she whispers. "Guards! Kill the traitors!"
}



\subsection{Combat Forces}

\enemyQueenAesudan{} is accompanied by four \enemyQueensGuard{}s. All of them will fight to the end.

PCs' allies will focus on their other goals and will not interfere with the fight. The exception is \npcCellarBoy{} rescued from \fullref{ssec:kholinarPalaceRoomsCellar}, who is determined to face \npcQueen{}.

During the fight additional \enemyQueensGuard{}s or \enemySingerDireform{}s may join as a result of \iconComp{} roll. Don't do it too often not to drag the fight too much.




\subsection{Touched by \npcYeligNar{}}

\enemyQueenAesudan{} accepted the bond with \npcYeligNar{}, granting her additional powers in the fight. However, if the fight goes for too long, the power of the Unmade will consume her.

The queen starts with 1 Deflect value from \npcYeligNar{}'s crystals growing out of her body. During the scene, as the crystals grow, the Deflect value will increase. When it reaches the maximum, the queen dies and the fight ends - proceed to \fullref{sec:toSpiritualRealm}.

\corruptedBox{
	Fighting the vessel of \npcYeligNar{}, the \npcYeligNarTitle{} can expedite an Enlightened Skybreaker \seeCorruptedRules{}.
}



\subsection{Opportunities and Complications}

You can use the following examples for an inspiration on how to spend \iconOpp{} and \iconComp{} during the fight:

\scriptedOption{Call for Reinforcements}{
	Any side of a conflict may spend the result of a Plot Die to call for additional support. The queen is supported by \enemyQueensGuard{}, the Singers may have \enemySingerDireform{} appear, while the Wall Guard may send \enemyWallGuard{}. Make sure the spawned character matches currently active alliances and events.
}

\scriptedOption{\npcCellarBoy{} - Spreading Decay}{
	If the PCs rescued \npcCellarBoy{} from \fullref{ssec:kholinarPalaceRoomsCellar}, he can occasionally support them with his Spreading Decay ability (see \fullref{ssec:kholinarPalaceOpportunities}) for a cost of \iconOpp{}.
}

\scriptedOption{\npcYeligNar{}'s Surge}{
	\enemyQueenAesudan{} can immediately use one of her Unmade actions for \iconComp{}, without spending \iconAction{} or Investiture.
}

\scriptedOption{\npcSjaAnat{}'s Scheme}{
	A PC can spend \iconOpp{} to use a talent from an Enlightened Radiant talent tree without spending \iconAction{} or Investiture.
}

\scriptedOption{Modify \npcQueenName{}'s Deflect}{
	Either side of the conflict may spend their Plot Die results to increase or decrease \enemyQueenAesudan{}'s Deflect value by 1. Do it no more than once per turn. \\
}

\reasonBox{
	There is no one correct choice in here and it depends on PCs's strategy weather they wish to increase or decrease her Deflect. Smaller Deflect means easier but longer fight. Increasing it means the foe becomes more difficult to face, but might be overwhelmed by the power faster.
}



\subsection{Aftermath}

Once \enemyQueenAesudan{} is defeated, proceed to \fullref{sec:toSpiritualRealm}.

\reasonBox{
	This is the last reference of \npcYeligNar{} in this book. Make sure to expedite your Enlightened Skybreakers three times in total at this point.
}