\section{Return to Kholinar}
\label{sec:returnToKholinar}

In the days following their victory over \npcMidnightMotherFull{}, the PCs will start hearing rumors about \npcElhokar{} gathering a small force tasked with return to Kholinar to rescue \npcQueen{} and their son - \npcGavinor{}.

This is a great opportunity for the PCs to return to the city and contact \npcSjaAnat{} about the next steps in her plan.


\subsection{Additional Motivation}

If the PCs are unsure if they should return, read the following:

\quoteBox{
	"Our mother should've contact us by now", you hear your spren say. "She didn't. The enemy must watch her closely, he must suspect her... \\ \\
	"Without more information, we cannot proceed with her plan. This mission in Kholinar may be our opportunity to get closer and contact her. We must go with them!"
}

Allow Enlightened Spren bonded to the PCs to encourage them to join this mission. If that won't help, one of their patrons can task them with this quest instead.

\reasonBox{
	To progress the story, the PCs must defeat a Servant of \npcYeligNar{} and enter a \locationPerpendicularity{}. Either one of the NPCs convinces the party to take part in Kholinar mission, or you will need to improvise \fullref{ssec:alternativeStoryChap9}.
}

\subsection{Joining the Mission}

To join the mission to Kholinar, the PCs would need to be recommended by one of their patrons. Following NPCs have the say on the matter:

\begin{itemize}
	\item \npcDalinar{} \textit{(not joining himself)}
	\item \npcElhokar{}
	\item \npcAdolin{}
	\item \npcShallan{}
	\item \npcKaladin{}
\end{itemize}

If the party already secured patronage of one of those NPCs, they might ask to be assigned for the mission. If not, now it's their last chance to do it.



\subsection{Flight to Kholinar}

When the party is assigned to the mission, give them a couple of days to prepare. After that, during the next Highstorm, \npcKaladin{} will use his gravitation surges to transport the entire squad eastward to Kholinar.

Once the squad enters the city through a heavily guarded gate, \npcElhokar{} will order a reconnaissance to scout the situation in Kholinar. He will also suggest to find anyone who will support their efforts to enter the Palace.



\subsection{Without Patron's Aid}

It is possible for a party to return to Kholinar on their own, without \npcKaladin{}'s help. To do that, the party would probably need to consist of a skilled Gravitation or Transportation user, or have another means of fast travel.

However, the PCs should be aware that doing this without a patron's mandate means they'll receive less support, so it might be safer to go in a bigger group, alongside \npcAdolin{}, \npcKaladin{} and \npcShallan{}.