\section{Singer Siege}
\label{sec:singerSiege}

The Singers besieging the city represent a major force that must be respected. They could prove a formidable allies if the party convinces them to become friends.




\subsection{Fraction Leader}

The Singer camp answers to the Fused. However, the PCs are too insignificant to talk to them directly. Instead, the party should talk to \npcSingerEnvoy{}.

\npcSingerEnvoy[s]{} is a \enemySingerEnvoyform{}. Through her, the will of the Fused is made known to the entire camp, PCs included. \npcSingerEnvoy{} will not seek out the party to give them tasks, but if the PCs volunteer, she will be ready to accommodate their help.


\subsection{Endeavor Requirements}

To ally with Singer forces, the PCs will need to weaken Kholinar defenses by conducting precise strikes against the Wall Guard.

You can run it as an Endeavor. Instead of the PCs making skill tests, run several scenes, each with its own Endeavor, Conversation or Combat. Award a success or a failure to the main Endeavor based on weather the party succeeded on the scene.

\pursuitReq{6}{3}


\subsection{Starting Conditions}

The Endeavor starts with an additional success if the party helped \npcSingerWouned{} during Kholinar riots (see \fullref{sec:dyingSinger}).

The Endeavor starts with an additional success if the PCs were invited to stay in the Singer Camp.

The Endeavor starts with an additional success if the party sided with the Singers during \nameref{chap:chapter4}, using the \lootDustcaster{} on Kholinar defenses. The endeavor starts with a failure if the PCs attacked the Thunderclast instead.


\subsection{Example Scene}

The party must weaken the resources of the Wall Guard by disrupting their food production. The PCs must find and kill the Soulcasting who generates the grain.

\subsubsection{Search for the Soulcaster}

Run the search for the Soulcaster as an Endeavor focusing on \skillDeduction{}, \skillInsight{} and \skillDeception{}. The PCs must scout the grain movement and interrogate the guards.

\pursuitReq{5}{3} Set the average difficulty of each test to 20 (or 17 + 1d6)

\subsubsection{Soulcaster Elimination}

Once the PCs find the room in which the Soulcaster is producing food, they must strike at this location. At any time there is one \enemySoulcaster{} and eight \enemyWallGuard{}s protecting her. All of them will fight to the end.




\subsection{Final Task}
\label{ssec:singerSiegeFinalTask}

When the PCs successfully complete the Endeavor, they will be tasked with one final job - to eliminate \enemyWallGuardHighmarshal{}. The party will find her on the wall, accompanied by eight \enemyWallGuard{}.

When \enemyWallGuardHighmarshal{} is defeated, the remaining guards will flee.

\reasonBox{
	When \enemyWallGuardHighmarshal{} drops to 0 Health, allow her to flee. There is no need to break lore with her death. \\ \\
	When she runs, she should keep her sword with her - there will be other rewards for that task. If you want to reward the party with \lootHighmarshalsBlade{}, make the fight more challenging.
}

\subsubsection{Success!}

If the party deals with \npcHighmarshal{}, they will secure an alliance with Singer forces.

However, the wall guard will suffer heavy loses as a result. The PCs will not be able to ally \npcHighmarshal{}.



\subsection{Rewards}

If the PCs successfully complete the Endeavor, the Singer forces will consider them friendly and will not attack them during their assault on the Palace.

If on top of that, the party removes \npcHighmarshal{} from the picture during \fullref{ssec:singerSiegeFinalTask}, after reaching the Palace the Singer forces will support the PCs in their fight.
