\section{\npcSjaAnat{}'s Plan}
\label{sec:sjaAnatsPlan}

When the party is alone in Kholinar, read the following:

\quoteBox{
	Suddenly, you see your shadow twist and distort. A moment after it points towards the light, taking a shape of a tall, slender woman with a flowing hair and eyes glowing white - \npcSjaAnat{}. \\ \\
	"Well, well, well... you returned! And stronger than ever! Good... You will need strength in the days to come."
}

The PCs are approached by \npcSjaAnat{}. Use this scene to define their goals for the rest of the adventure.

\corruptedBox{
	Speaking with \npcSjaAnat{}, the \npcSjaAnatTitle{} may expedite an Enlightened Lightweaver \seeCorruptedRules{}.
}


\subsection{The Plan}

Continue with the following:

\quoteBox{
	"Now is the time to complete the plan and free all of us from \npcOdium{}'s hatred. You must enter Spiritual Realm and release \npcMishram{} from her prison. Only she can challenge him. \\ \\
	"There is only one way for you to get there. \npcQueen{}. You must kill her. She is now a puppet of \npcYeligNar{}, and  upon her death, he will claim her soul. I will use this to open the path for you."
}

The party must break into the Royal Palace and kill \npcQueen{}. After that they will need to enter the Spiritual Realm (with \npcSjaAnat{}'s help), find \npcMishram{} there and free her. 



\subsection{Find Allies}

Make sure to suggest the following:

\quoteBox{
	"You are strong, but you shall not underestimate \npcQueen{}. Her bond with \npcYeligNar{} makes her a deadly foe, like nothing you have faced before. And her troops are loyal to her. \\ \\
	"Search the city. Find others, who hate her with passion. Use them. You will need as many allies and tools as you can get. Let them fight for you, so you could focus on what really matters."
}

Suggest to the party that they should find more allies. For details, see \fullref{sec:gatheringAllies} and other sections linked there.


\subsection{Sworn to Secrecy}

If the party arrived to Kholinar with other NPCs, add the following:

\quoteBox{
	"The others. The king, the artist, the knight. They must not know your intentions. They believe the queen can be saved. She cannot be. But they will stand between you and her. Do not let that happen. \\ \\
	"Let them stumble in the dark. I will not harm them, you have my word. I will try to keep them alive. But you must allow them to take their own path. Do not warn them about the dangers ahead. They must face them as you did."
}

The PCs should not share their secrets with \npcElhokar{} and his squad of Radiants. They must follow their own path an pursue their own goals not to interfere with the quest given by \npcSjaAnat{}.

\reasonBox{
	This is an attempt to stay as close as possible to the lore of \bookOB{}. The PCs' knowledge about the situation in Kholinar could lead \npcShallan{} and the others to take different decisions. Allow them to run through the broken Oathgate, and let the PCs focus on their own path.
}


\newpage
\subsection{Summary}

After this scene, the party should know the following:

\begin{itemize}
	\item Their goal in Kholinar is to kill \npcQueen
	\item After that, they should free \npcMishram{} from Spiritual Realm
	\item They should find allies to use them in their assault on Kholinar Palace
	\item They cannot expect the NPCs to help them with the queen
	\item They must allow the NPCs to follow their own path and not try to change their plans.
\end{itemize}

\reasonBox{
	This is the last time \npcSjaAnat{} makes a bigger appearance in the history. Make sure to fully expedite your Enlightened Lightweavers with three bonus talents.
}