\section{The Cult of Moments}
\label{sec:theCultOfMoments}

With a close access to \npcQueen{} and the privileges granted by her, the Cult of Moments can be an handy tool to use against her. The PCs may attempt to gain their influence. 


\subsection{Fraction Leader}

The cult does not bother with concerns like leadership or power structure. The cultists want only to revel and forget all their worries.

However, before joining the cult, former ardent named \npcRevelerGuide{} was doing most of the leadership work and some of the old habits are still active in his new life. The PCs can talk to him, as he is the only one lucid enough to give them vaguely coherent answers.




\subsection{Endeavor Requirements}

When working for the Cult of Moments, the PCs will need to recruit new valuable members from Kholinar nobility and the common people.

You can run it as an Endeavor. Instead of the PCs making skill tests, run several scenes, each with its own Endeavor, Conversation or Combat. Award a success or a failure to the main Endeavor based on weather the party succeeded on the scene.

\pursuitReq{6}{3}



\subsection{Starting Conditions}

The Endeavor starts with an additional success if the PCs helped the cultists during \fullref{sec:gatesBattle}. The Endeavor starts with an additional failure if the PCs helped \npcHighmarshal{} instead.

The Endeavor starts with an additional success if the party joined the Cult of Moments to enter the Revelry during \fullref{ssec:cityEscapePlanJoin}. The Endeavor starts with an additional failure if the PCs bribed the criminals instead during that scene.

The Endeavor starts with an additionl success if the PCs succumbed to the temptation of \npcHeartRevel{}, the \npcHeartRevel{} during \fullref{chap:chapter5} - either willingly or as a result of failed Conversation during \fullref{sec:heartOfTheRevel}.




\subsection{Example Scene}

The PCs are tasked to recruit new cult members. Run this scene as a Conversation. The party will try to convince a noble who uses \enemyQueensGuardLeader{}'s stat block.

The Noble has 15 Cognitive Defense, 17 Spiritual Defense and 7 Focus. In the times of uncertainty, he yearns for security.

\conversationEnd{the Noble}{1}


\subsection{The Cult - Final Task}
\label{ssec:theCultOfMomentsFinalTask}

If the party successfully completes the Endeavor, they will receive one last task - to find and kill the leader of the criminals who interfere with the cult's business - the \npcGhostbloodBoss{}.

\subsubsection{Search for \npcGhostbloodBoss{}}

You can run this part as an Endeavor with an average difficulty of a skill set to 21 (18 + d6). The party will need to focus on \skillThievery{}, \skillIntimiation{} and \skillDeception{} during it.

\pursuitReq{5}{3} The party can quickly skip the entire search if they already established contact with \npcGhostbloodBoss{}.

\subsubsection{Fighting \npcGhostbloodBoss{}}

\npcGhostbloodBoss{} is a \enemyGhostbloodBoss{} protected by four \enemyGhostbloodThug{}s. They all will fight to the end.

\subsubsection{Success!}

When the PCs succeed on \npcGhostbloodBoss{}, \npcRevelerGuide{} will consider them trusted allies.

This, however, will prevent any future dealings with Kholinar Underworld - as their leader is dead, the others will start a struggle to fill the power vacuum and will not have any time to spare for the party.


\subsection{Rewards}

If the party successfully completes the Endeavor, many of the cult members will recognize them. They will no longer be hostile towards the PCs during their assault on the Royal Palace.

If on top of that they will manage to eliminate \npcGhostbloodBoss{}, \npcRevelerGuide{} will allow them to enter the Palace using \fullref{ssec:kholinarPalaceRoomsSunwalk}.