\section{The Wall Guard}
\label{sec:theWall}

The people guarding the city wall are capable soldiers under a command of someone, who understands the stakes of the conflict on Roshar.

If recruited, they would be a valuable asset during the assault on the Kholinar Palace.


\subsection{Fraction Leader}

The Wall Guard is commanded by \npcHighmarshal{}, a Nathalian Awakener and a Worldhopper, who took the mantle of the leader when the Guard needed her the most.

She remembers the party from their previous encounters. However, she is not aware the PCs are back in Kholinar and she will not initiate the talks. 


\subsection{Endeavor Requirements}

To secure an alliance with the Wall Guard the party will need to prove themselves by serving in their ranks for some time, defending the city from Singer attacks and performing other guard duties.

You can run it as an Endeavor. Instead of the PCs making skill tests, run several scenes, each with its own Endeavor, Conversation or Combat. Award a success or a failure to the main Endeavor based on whether the party succeeded on the scene.

\pursuitReq{6}{3}



\subsection{Starting Conditions}

The Endeavor starts with an additional success if the PCs helped the Guard to defend the city gates during \fullref{sec:gatesBattle}. The endeavor starts with a failure if the PCs attacked the gate instead.

The Endeavor starts with an additional success if the party supported \npcHighmarshal{} during her attack on the monastery in \fullref{sec:monastery}.

The Endeavor starts with an additional success if the party sided with the Wall Guard during \nameref{chap:chapter4}, using the \lootDustcaster{} on the Thunderclast. The endeavor starts with a failure if the PCs attacked the Guards' Defenses instead.



\subsection{Example Scene}

The PCs are ordered to protect the transport of wagons with grain sacks. Due to hunger persisting in the besieged city, there is a risk of civilians attacking the convoy.

Run this scene as an Endeavor. Set the average difficulty of the tests to 21 (or 17 + d8). \pursuitReq{5}{2}

If the characters succeed on the scene, add one success to the Endeavor to ally the Wall Guard.

If the party fails, they will be attacked by 20  \enemyRioter{}s. Add one failure to the Endeavor to ally the Wall Guard.



\subsection{The Wall Guard - Final Task}
\label{ssec:theWallFinalTask}

When the party successfully completes the Endeavor, immediately three \enemySingerHaevenlyOne{}s will attack the wall. The PCs must defend the soldiers and kill the Singers. 

\subsubsection{Success!}

If the PCs manage to kill all \enemySingerHaevenlyOne{}s attacking the wall, they will earn the respect of the Wall Guards and their alliance.

That will however enrage the Singers, who will treat the party with hostility from now on. It will not be possible to ally the Singers in this adventure.




\subsection{Rewards}

If the PCs complete the Endeavor, they will gain respect of many guards. They will agree to stand by PCs' side when they decide to attack the Palace, dealing with some of the enemies the party will face.

When the last \enemySingerHaevenlyOne{} is slain during \fullref{ssec:theWallFinalTask}, \npcHighmarshal{} will agree to personally join the party during the assault on the Palace, enabling her unique ability (see \fullref{ssec:kholinarPalaceOpportunities}).



\subsection{Default One}

If the PCs ignore the quest of gathering allies in Kholinar, at the time they decide to attack the Palace, \npcKaladin{} will ally the Wall Guard, bringing them for help. This will not happen, if the PCs already allied with Singers.
