\section{About this book}

\subsection{About me}

Hello! I'm glad to meet you :)

You can call me Pether. I am a fantasy nerd who has played RPGs since childhood. Recently I've dived even deeper into this hobby as I am GMing a campaign for my friends for the past two years. I happily enjoyed various homebrew systems, Dungeons and Dragons, Warhammer RPG, Call of Cthulhu, and now - \cosmereRPG{}.

All my content and RPG resources are free for everybody. I would be happy to play with you, but since I can't, I will gladly share my ideas and notes, perhaps you will find them helpful. You are invited to modify my work to suit your own needs and playstyles. If you share your RPG sessions on youtube please let me know when you play this adventure, I will be excited to see how the story develops for your group!

I hope you will enjoy this adventure. If you would like to virtually hang out or to fuel my various future projects, you can always buy me a coffee using the link below ;)

\url{https://ko-fi.com/pether}


\subsection{Who is it for?}

This campaign is tailored for people who are not familiar with Roshar and Brandon Sanderson’s books. The story starts in Shinovar kingdom, which is the most similar to the classic fantasy setting. Characters originating in there do not require any knowledge about Roshar, storms or spren to start roleplaying.

The story quickly moves from those familiar areas northward, so you can quickly introduce Roshar. Players who know more about the world will be able to shine there.

\subsection{Is it canon?}

No. This is a fan-made campaign and the story presented in here cannot be considered canon. While I did my best to align with official lore of the world, some of the events here might contradict Brandon Sanderson’s vision.

\subsection{How many spoilers?}

The campaign is designed to include as little spoilers as possible. No book character makes an appearance here and the campaign story does not intertwine with the events described in the books.

However, it is impossible to remain fully spoiler-free… The ecosystem of Roshar is quite unique and by playing this campaign players are bound to discover it before reading the books. In particular, the nature of Reshi Islands cannot be avoided here, potentially spoiling one of the chapters in \bookWOR{}.

\subsection{Motivation behind this book}

While browsing official \cosmereRPG{} books I noticed adversaries listed there follow the same pattern - they are either a creatures in carapace, or humans, or nearly-humans in carapace. I wanted to design an adventure with more enemy variety. This book revolves around undead, or at least something similar that could possibly work within Roshar lore.