\section{About This Adventure}
\label{sec:aboutAdventure}

\subsection{Campaign Themes}

This campaign is using themes as listed below. Use this list to determine if you are interested in running this kind of campaign. In the game, you can encounter themes of:
\begin{itemize}
	\item Jungle exploration
	\item Horror
	\item Undead
\end{itemize}

\subsection{Campaign Setting}

Most of the adventure is happening on one of the Reshi Isles. Some of the scenes are taking place in Ksitor (Iri) and players can voyage to Rall Elorim (Iri) and Kurth (Rira). You can start the adventure in Shinovar for an easier Roshar introduction to the people who are not familiar with it.

The story is hardly connected to any events described in the books. This campaign assumes it is taking place alongside the story of “The Words of Radiance”, but GMs can modify a few names of kingdoms and ruling monarchs to set this adventure in any epoch they like, eg. during Silver Kingdoms era, right before the False Desolation.

You can also run this adventure after the events described in official "Stonewalkers" book. You would probably modify a few things (most notably - difficulty level, as the characters would have 7 more levels than initially assumed), but since this adventure starts in Iri (the same kingdom where "Stonewalkers" ends), it should be rather easy to ensure story continuity.

\subsection{Radiant Warning}

Some of the campaign challenges would be trivialized by using Knight Radiant Surges, especially by the healing powers of the Progression Surge. In order to ensure that players won’t skip entire plot lines, to encourage creative problem-solving and to make the tension higher, in many scenes Knights Radiant might attract larkins while using their powers. Those little critters will drain them from the Investure, interrupting their abilities and preventing their future usage.

Bonding with spren can still occur, but please be aware that this story will focus more on Heroic Path progression - manage players’ expectations accordingly.

The threat of the larkins diminishes after completion of "\nameref{chap:sickGirlDies}". Starting from the next chapter, the characters can freely use full extent of their powers.