\section{Adventure Summary}

\subsection{Chapter 0 Summary}

Characters start their adventure on the ship from Shinovar, sailing towards Kasitor. Consider this a tutorial chapter to introduce players to the world of Roshar, mechanics of the game and roleplay in general. You can skip it if you are playing with a more experienced group.

\subsection{Chapter 1 Summary}

While in Kasitor, characters learn about a lost Reshi Isles expedition. They board a ship and sail north, to learn about the expedition's fate and search for survivors. When they reach the shore of \theIsland{} island, they notice strange red vines, unique for it. While searching the island, they meet \npcMedic{}, herdazian man leading a pack of Axehounds fighting with a Whitespine.

\subsection{Chapter 2 Summary}

\npcMedic{} leads the party to his camp. Here characters meet a sick Thaylen girl that \npcMedic{} is attending with his medical knowledge. He asks the party to find some herbs he needs to help the sick girl and perhaps find some information about the rest of the expedition he left behind. When characters return to the camp, they are attacked by a few Axehounds. They recognize the beasts that fell earlier, now returned back to life and overgrown with scarlet vines.

\subsection{Chapter 3 Summary}

After learning about the strange vines growing over slain beasts, \npcMedic{} asks characters to gather more information about them. He asks for some samples and suggests learning from the local Reshi village. Once it is discovered that the vines are revered by locals as a holy plant that can empower people and reanimate dead, \npcMedic{} suggests using them for treatment of sick Thaylen girl, without which she is doomed to die.

\subsection{Chapter 4 Summary}

Identifying red vines as a threat for nearby islands, characters may travel to gather some support to deal with the situation. Upon their return, they witness the danger growing out of hand. They must hurry to resolve the threat before it is too late…

\subsection{Chapter 5 Summary}

The party ventures deep into the ancient Reshi shrine to face the spren responsible for the plague of spreading vines, \npcSprenVines{}. Regardless of characters’ approach to the threat, the Reshi Isle will be changed forever.
