\section{Running the Adventure}
\label{sec:runningAdventure}

To run this adventure you will need \handbook{} containing all rules and guidelines on how to run \cosmereRPG{}. This book contains only adventure-specific details and suggestions on how to run it.

\quoteBox{
	You can read (or paraphrase) a text in such a box to your players. Alternatively, you can describe the scene using your own words.
}


Whenever a characters name appears in \enemy{bold}, it means there is corresponding stat block available. You can use it to get more info about the character's attributes and abilities.

Items appearing in \loot{bold italic} have special rules you can find at the end of this book.

\reasonBox{
	Boxes like this will help you understand the reason behind some of the design choices. Those have no impact on the game, but they may help you modify some elements of the adventure if you so choose.
}

\ptrBox{
	When a plot might allow for certain Radiant Spren to be attracted by player's actions, that will be indicated by such a box. However, use your own judgment whenever a players does something not accounted by this book.
}

If you are using this book in electronic version, it has also several quality-of-life improvements to make your life easier when you navigate this book:

Whenever a name of a chapter or section appears (eg. "\nameref{sec:aboutAdventure}"), you can click on it to quickly go to the chapter in question.

All characters' names (eg. \npcMedic{}) are links that lead to \hyperref[personae]{Dramatis Person\ae} chapter, where all the NPCs are listed.

Items (eg. \lootRogueShardblade{}) and adversaries (eg. \enemyDrunkenSailor{}) are also links that will lead you to the page with their unique rules. 


\subsection{Adjusting Difficulty}

This book assumes your players will form a party of 4 characters starting at 1st level. However, it is perfectly fine to have a different size of your group and/or to start playing at a different level (eg. because the characters already shared a different adventure together). Also, it is possible that challenges presented in this book are not aligning with strong suits of the party.

If you see that the balance is a bit off, feel free to adjust the difficulty. You can change a number or tier of the enemies, modify endeavors' requirements or weave some other changes into the story.

\subsection{Handling Canon}

Despite treating original source with respect, this adventure is not canon. While playing the game your primary focus should be fun. For everyone, "fun" means something different - either following official lore to the letter, creating your own touching story, or just hitting bad guys with your sword. Make sure you know what is fun for you and your group and make it your primary objective. If that means modifying this adventure or straying away from the canon - go for it!

You can find more information on that topic in “Canon and Continuity” section of \handbook{}.

\subsection{Playing with Radiants}

Please keep in mind, that this adventure greatly limits Radiants' abilities with larkins swarming the area. However, if a player wants to play as Knight Radiant despite it (for example - to tell a story about their relationship with the spren) this book will provide some opportunities to enable this kind of story. Just make sure your players are aware of the limitations that might hinder some of their abilities.

\subsection{Playing with Singers}

This story does not focus on conflict with Singers. If a player wants to play with a Singer heritage, it is perfectly acceptable. This book assumes the story is happening sometime along \bookWOR{}, but it provides little details related to Singer mechanics and it leaves it up to you to fill those gaps if required.

If one of your players wants to play as a Singer, please discuss with them what kind of story do they want to tell and adjust this adventure accordingly. You can run it before, after, or just at the moment of the Everstorm reawakening, or in another era entirely - the core of this story will remain unchanged, but various NPCs may react to the singer differently depending on the date you choose.



