\section{Unique Rules and Events}

The game follows original \cosmereRPG{} rules with a few unique additions, specific for this campaign:


\subsection{Ravenous Larkins}

The Reshi Island, where most of the adventure is taking place, is swarming with larkins. Each time a character uses Investure, spawn \enemyLarkin{} into the scene. The larkin attacks the character, feasting on their Investure, until there is nothing left. When no player can be targeted with larkin's Drain Light ability, the creature flee.

If a player repeats Investure usage later, spawn more larkins and/or make them more aggresive each time.

If a larkin appears outside of combat, there is no need to start the fight - allow it to Drain Light and fly away. If spawned during combat, however, those creatures are more aggressive: while their focus is on using Drain Light and staying alive, they can also attack player characters with their Bite action.

All larkins are immune to Red Vines influence (see below).

\reasonBox{
	Limiting Investure abilities can create unique challenges for the players and make the game more interesting. However, the main reason for this feature is to prevent healing NPCs using Progression Surge in later chapters - Radiant abilities would make that part of the plot boring and trivial. 
	\newline
	Despite real significance in the future parts of the story, introduce Larkins earlier to properly warn the players about that threat to Radiant abilities.
}


\newpage % manual newpage to micromanage page layout

\subsection{\abilityVinesName}
\label{ssec:ruleVines}

During the adventure, the PCs can encounter strange, red vines growing on the island. If they are allowed to overgrow a living creature, that creature gains the following ability:

\abilityVines{}

If you add this feature to an existing stat block, remember that Strength affects Physical Defense, Health and some of the skills - those in turn can affect attack and damage bonuses. Pay attention, that Strength affects total Health once every tier - enemies on higher tiers will receive Health bonus several times.

Unknown to everyone, the Vines are a variety of rockbuds without their own shells - instead they inhabit carapaces of slain creatures. They are controlled by a spren from the ancient temple, \npcSprenVines{}. Creatures affected by this ability are influenced by the spren and want to follow its will. Given time, the Vines will creep inside host's body, causing more and more pain, and, in the end - gruesome death, giving birth to a new Husk.

\reasonBox{
	Red Vines are an alluring promise of strength, power and immortality that leads the desperate to their doom. They are the magic that goes horribly wrong because the caster did not fully understand it. Reveal any information relating to it slowly, in the pace of whole story.
	\newline
	If players are desperate to use the scraps of knowledge they have, they can invite the Red Vines enhancement. However, be prepared to introduce negative consequences slowly creeping in as the Vines themselves.
}


\subsection{\abilityHuskName}
\label{ssec:ruleHusk}

Red Vines are a rockbud variant that lacks it's own protection. Instead, the plant uses carapace of dead animals as a shell. While overgrowing the corpse, the Vines can animate it like a puppet, allowing for locomotion and self-defence. Creatures under this effect gain following ability:

\abilityHusk{}
\newpage % manual newpage to micromanage page layout

Such husks loose all their previous identity and cognitive abilities. They cannot communicate nor understand any communication attempts. They are driven by anger and desire to create more corpses for the Vines to grow into. They fight mercilessly without any will to preserve own existence. While not fully alive, it is difficult to kill them, and any attempts may just cause their body to split into smaller parts. 

\reasonBox{
	Reanimated Husks are my attempt to bring undead into the world of Roshar. They are mindless and deadly. Their existence is a huge threat to the Island and eliminating it will eventually be players' main goal. Try to make them as gruesome, hideous, grotesque and dangerous as possible.
}