\section{\enemyWhitespineName{}}
\label{enemyWhitespine}

Born and raised in the jungles of Reshi Islands, \enemyWhitespine{}s are perfectly adapted for hunting in lush environment. They often tread the jungle alone, stalking smaller prey.

In combat, they are fierce and dangerous. They are deadly when they fight an enemy restrained by reshi plants which they can easily trample. Then can get confused when surrounded by more enemies, though.

\enemyWhitespine{}s are more pale carapace than their cousins from other parts of Roshar - only the edges of carapace plates are marked with violet patterns. 
\\

\tacticsBox{
	\enemyWhitespine{} prefers to stalk its prey and wait until it enters an area with a lush reshi overgrowth, constraining its movement and making it harder to escape. At this moment it charges, making use of its Goring Tusks. If required, the whitespine will use its claws or will back out for another charge. They often focus single prey, stunning other foes with its Pheromone Release.
}


\newpage
\enemyStatBlock{
	\enemyStatBlockHeader{\enemyWhitespine}{2}{Rival}{Large Animal}
}{
	\enemyStatBlockStats{4}{3}{0}{2}{4}{0}{42 (33–51)}{4}{0}
}{
	\enemyStatBlockSkills[
	\enemyStatblockSkillsDeflect[1 (carapace)]\\
	\enemyStatblockSkillsMovement[60 ft.]
	\enemyStatblockSkillsSenses[40 ft. (smell)]
	\enemyStatblockSkillsPhysical[Agility +6, Athletics +7, Stealth +6]
	\enemyStatblockSkillsCognitive[Intimidation +5]
	\enemyStatblockSkillsSpiritual[Perception +6, Survival +6]
	\enemyStatblockSkillsLanguages
	]
}{
	\enemyStatblockFeature{Enhanced Senses}{The whitespine gains an advantage on non-attack tests that rely on smell.} \\
	
	\enemyStatblockFeature{Spined Carapace}{After an enemy within 5 feet of the whitespine grazes them with a weapon attack, that enemy takes 3 (1d6) keen damage} \\

	\enemyStatblockFeature{Reshi-Born}{The whitespine can ignore negative effects of a difficult terrain caused by plants.} \\
	
}{
	\enemyStatblockAction{Strike: Claws}{Attack +7, reach 5 ft., one target. Graze: 3 (1d6) keen damage. Hit: 10 (1d6 + 7) keen damage, and the whitespine can spend 1 focus to make the target Afflicted [1d4 vital] until the target regains at least 1 health.} \\
	
	\enemyStatblockAction{Goring Tusks}{Attack +7, reach 5 ft., one target. Graze: 5 (1d10) impact damage. Hit: 12 (1d10 + 7) impact damage. If the whitespine hits with this attack immediately after moving at least 15 feet, the target takes an extra 5 (1d10) impact damage and must succeed on a DC 14 Athletics test or be knocked Prone.}\\
	
	\enemyStatblockAction[\iconActionDouble]{Pheromone Release (Costs 1 Focus)}{The whitespine releases foul pheromones. Each non-whitespine character within 10 feet of them must succeed on a DC 15 Discipline test or become Stunned until the end of the whitespine’s next turn.} 
}
