\section{\enemyAxehoundName{}}
\label{enemyAxehound}

This axehound breed was adapted by herdazians for the sole purpose of expedition missions. Those axehounds are very curious creatures, love open spaces and relish in discovering new areas. You can always find their pack scattered in a search for something new that might interest them.

Raised in herdazian communities, those axehounds are very social. They grow attached to humans and enjoy spending time with them. Walking together and seeing new places is of course their favorite activity, but they also love playing games or getting carapace rubs.

Extremely loyal, they always obey their masters and never leave their side. Their friendship lasts forever and is very easy to earn. In a face of danger, they will gladly sacrifice themselves to protect their pack.

\enemyAxehound{}s' carapace is a bit darker than in other axehound breeds. On their sides it is marked with golden-brown dots. Their antennae are slightly longer than normal and also a bit darker.

If \enemyAxehound{} dies on \npcSprenVines{}'s island, it can later return as \enemyReanimatedAxehound{}.
\\

\tacticsBox{
	\enemyAxehound{}s often work in a group and they gladly accept human leadership over their pack. Their focus their efforts on one enemy, attempting to knock it prone and surround it with their On the Hunt reaction. They prefer sticking close to each other to benefit from their Pack Instincts.
}

\newpage
\enemyStatBlock{
	\enemyStatBlockHeader{\enemyAxehound}{1}{Minion}{Small Animal}
}{
	\enemyStatBlockStats{2}{2}{0}{0}{3}{0}{12 (9-15)}{2}{0}
}{
	\enemyStatBlockSkills[
		\enemyStatblockSkillsMovement[40 ft.]\\
		\enemyStatblockSkillsSenses[40 ft. (smell)]
		\enemyStatblockSkillsPhysical[Agility +4, Athletics +4, Stealth +3]
		\enemyStatblockSkillsSpiritual[Perception +5, Survival +4]
		\enemyStatblockSkillsLanguages
	]
}{
	\enemyStatblockFeature{Enhanced Senses}{The axehound gains an advantage on non-attack tests that rely on smell.} \\
	
	\enemyStatblockFeature{Herdazian Breed}{The axehound gains an advantage on Survival tests.} \\
	
	\enemyStatblockFeatureMinion{}
}{
	\enemyStatblockAction{Strike: Bite}{Attack +4, reach 5 ft., one target. Graze: 2 (1d4) keen damage. Hit: 6 (1d4 + 4) keen damage, and if the target is Medium or smaller, the axehound can spend 1 focus to knock the target Prone, then move up to 10 feet while dragging the target behind them.}\\

	\enemyStatblockAction[\iconFreeAction{}]{Pack Instincts}{While within 5 feet of an ally, the axehound can use the Gain Advantage action as \iconFreeAction{}.} \\
	
	\enemyStatblockAction[\iconReaction{}]{On the Hunt}{After an enemy within 30 feet of the axehound falls Prone, the axehound moves up to 15 feet toward them.}
}
