\chapter{Appendix \thechapter{}: Death Rattles}
\label{chap:deathRattles}

In most cases, when a character dies, there is no need to invoke Death Rattles as their final words. However, if you wish to indicate a close proximity of \npcMoelach{} and you don't feel particularly creative at the moment, you can choose something from the pool below - either as a quote or an inspiration.


\section{Foreshadowing Death Rattles}
\label{sec:deathRattlesForeshadowing}

This pool refers to various events from the story. Make sure to always refer a future chapter, never the one that was completed by the players.

\begin{itemize}
	\item Screams of pain, broken bones, blood flowing in rivers. Finally, the suffering ended!
	\\ \textit{(refers to \nameref{chap:chapter3})}
	
	\item So grand! So majestic! Oh, Allmighty... now it rains with ash and dust... 
	\\ \textit{(refers to \nameref{chap:chapter4})}
	
	\item Come! Sing! Dance with me! Let us relish in the world ending! 
	\\ \textit{(refers to \nameref{chap:chapter5})}
	
	\item Sea of darkness, sky of void. How much longer must we run...? 
	\\ \textit{(refers to \nameref{chap:chapter6})}
	
	\item One cut to heal. Two to betray. Three to speak with the gods.
	\\ \textit{(refers to \nameref{chap:chapter7})}
	
	\item I am the nightmare, and we are myriad. Oh mother, how can you love us?
	\\ \textit{(refers to \nameref{chap:chapter8})}
	
	\item Crystal broken, armor shattered, soul erased. We won! Let us step into death!
	\\ \textit{(refers to \nameref{chap:chapter9})}
	
	\item I hate you, child of lies and betrayal. I hate you and your kind! And I will have my revenge!
	\\ \textit{(refers to \nameref{chap:chapter10})}
\end{itemize}




\newpage
\section{Random Death Rattles}

This pool does not reference anything specific. To avoid easy to deduce spoilers, use them in between the Rattles from \fullref{sec:deathRattlesForeshadowing}.


\begin{itemize}
	\item Cold! So much cold... Was the sun ever warm?
	
	\item No... No! This cannot be! This cannot come! NO!
	
	\item They told us we won! They promised peace! We loved them! They lied to us all...
	
	\item Who are you? Why are you staring at me? What have you done to me...?
	
	\item The song! The rhythm! So beautiful! How could we not hear it...?
	
	\item The stick! Burn the stick! Why can't you wish to live?
	
	\item Wield them high, mighty and glorious! The sword, the spear, the dining fork!
	
	\item Sky aflame, earth to ash, souls to despise!
	
	\item No eyes to cry, no voice to lament, the suffering is eternal!
\end{itemize}