\chapter{Appendix \thechapter{}: Items}
\label{chap:items}

\section{\lootDustcaster{}}

An ancient fabrial of \npcDustmother{}, the \npcDustmotherTitle{}. It looks similar to the Soulcasters, though it's more jagged and not as ornamental. It allows its wearer to perform single dustcasting, after which the fabrial turns to dust itself.

\subsubsection{Dustcasting}

As a \iconActionDouble{} you can touch another character or an object. For the next three rounds neither of you can move or take any other actions. After three rounds the target you touched an the item itself turn to dust and are annihilated. 

At the end of each of those three rounds, make a \skillCheck{10}{Division} or \skillCheck{20}{\skillDiscipline{}}. Each failure causes you to take damage as parts of yourself become dustcasted as well. If you drop to 0 Health, you are also annihilated and you cannot be healed, though it doesn't stop the dustcasting process.

\scriptedOption{1+ Failures}{
	The PC looses the tips of their fingers on the dustcasting hand. They take 1d6 Spirit damage.
}

\scriptedOption{2+ Failures}{
	Whole dustcasting palm is gone. The PC takes additional 1d8 Spirit damage.
}

\scriptedOption{3 Failures}{
	Entire arm of the PC is turned to dust. Its owner takes additional 1d10 Spirit damage.
}




\newpage
\section{\lootGateOpener{}}

An ancient fabrial of \npcBlackFisher{}, the \npcBlackFisherTitle{}. It looks like a black scallop shell with purple markings. Once per game, the shell can be forced open.

\subsubsection{Opening the Shell}

As a \iconAction{} you can open the fabrial. That will open a small perpendicularity lasting until the end of the next round. Any character stepping inside can travel to any other Realm (eg. to the Physical Realm from the Cognitive Realm).

Once the fabrial is opened, it looses its properties and cannot be used again.




\section{\lootHighmarshalsBlade}

This sword is one of a kind. It's a masterpiece equaling a Shardblade, though it's shorter and cannot be dismissed. It is owned by \npcHighmarshal{} and there is small chance she will ever choose to part with it.

Due to it's small size, either a Shardblade expertise or a Side Sword expertise can be used for wielding this weapon. 

Characters killed with this blade wither, their skin turning ashen gray.\\

\noindent
\textbf{Type:} Shardblade / Side Sword \\
\textbf{Skill:} Heavy or Light Weaponry\\
\textbf{Damage:} 2d12 spirit \\
\textbf{Range:} Melee\\
\textbf{Expertise:} loses Dangerous trait\\
\textbf{Traits and Rules:} Dangerous, Deadly, Unique: Spiritual Injury, Bane of the Weak

\scriptedOption{Bane of the Weak}{
	When an adversary with a \textbf{Minion} trait is hit with this weapon, the blade kills them immediately.
}



\section{\lootScadrialCoin}

A strange metal disc covered with sharp symbols. It looks like a flat necklace without a chain. It can be used as a proof of allegiance or a currency paid for favors and equipment from those who respect it.




\section{\lootSeonTube}

Hollow metal tube closed from all sides. The spren inside will carry your voice to any other character who owns a similar item.




\section{\lootHemalurgicNail}

A long, spiky earring, looking like a nail or a needle. The box it comes with is laid with some wet, red cloth.

As long a character is wearing the earring piercing their skin, they receive a bonuses based on the material, the earring is made of:

\begin{itemize}
	\item Iron: Enhanced [Str +1], Enhanced [Spd +1], \\Physical Defense +2
	\item Copper: Enhanced [Int +1], Enhanced [Wil~+1], Cognitive Defense +2
	\item Zinc: Enhanced [Pre +1], Enhanced [Awa +1], Spiritual Defense + 2
\end{itemize}



\section{\lootForgerySeal}

When the Seal is imprinted on a character’s skin, the character receive an expertise set based on the history written in the Seal, eg.:

\begin{itemize}
	\item Martial Training: \\Expertise on all weapon and armor types
	\item Traveler’s Voyages: \\Expertise on all cultures of the world
	\item Assassin’s Training: \\Expertise on poisons, subterfuge and anatomy
\end{itemize}



\section{\lootWhiteSand}

A small glass vial of a black sand. The sand turns white when in the presence of a character with Investure.



\section{\lootAntiStormlightDagger}

\noindent
\textbf{Type:} Knife \\
\textbf{Skill:} Light Weaponry\\
\textbf{Damage:} 1d4 keen \\
\textbf{Range:} Melee\\
\textbf{Expertise:} gains Offhand, Thrown (20/60)
\textbf{Traits and Rules:} Discreet, Shardplate Piercer, Anti-Stormlight Weapon

\scriptedOption{Shardplate Piercer}{
	This weapon ignores Deflect value of all armors with Shardplate type.
}

\scriptedOption{Anti-Stormlight Weapon}{
	This weapon contains 1 charge. \\
	When you hit an enemy with this weapon you my spend its charge to infuse the enemy with Anti-Stormlight. Until that enemy finishes a Long Rest, if they spend Stormlight Investure for any of their abilities, they immediately die.
}