\section{About This Book}

\subsection{About me}

Hello! I'm glad to meet you :)

You can call me Pether. I am a fantasy nerd who has played RPGs since childhood. Recently I've dived even deeper into this hobby as I am GMing a campaign for my friends for the past two years. I happily enjoyed various homebrew systems, Dungeons and Dragons, Warhammer RPG, Call of Cthulhu, and now - \cosmereRPG{}.

All my content and RPG resources are free for everybody. I would be happy to play with you, but since I can't, I will gladly share my ideas and notes, perhaps you will find them helpful. You are invited to modify my work to suit your own needs and playstyles. 

I hope you will enjoy this adventure. If you would like to virtually hang out or to fuel my various future projects, you can always buy me a coffee using the link below ;) \\

~~~~\url{https://ko-fi.com/pether} \\

You can find all of my \cosmereRPG{} homebrew content below: \\

~~~~\url{https://github.com/pether-pg/CosmereRPG_Books_byPether/releases}

\subsection{Who is it for?}

Though everyone is invited to play this adventure, it is designed for people familiar with the world - the story starts in Kholinar and expects players to be able to roleplay in that environment. This adventure does not include tutorial chapter and the plot may reveal some events and secrets from \bookSA{}.

\subsection{Is it canon?}

No. This is a fan-made campaign and the story presented in here cannot be considered canon. While I did my best to align with official lore of the world, some of the events here might contradict Brandon Sanderson’s vision.

\subsection{How many spoilers?}

This book contains heavy spoilers of Kholinar arc from \bookOB{}. On top of that there are spoilers of \bookWAT{} and minor spoilers of one of interludes from \bookWOR{}.

Please make sure that everyone on your table is fine with those.

\subsection{Motivation behind this book}

I always believed that desperate dark deals with ominous entities could greatly enhance the story. While other RPG systems do a good job of including this trope, \bookSA{} focuses on Radiants following their ideals to become the best versions of themselves, leaving less space for "deal with the devil" storyline.

This book addresses this issue by introducing opportunity to bond a spren Enlightened by \npcSjaAnat{}'s touch. Those offer access to more powerful abilities that come at a cost. How much will the characters be willing to pay for this kind of power? And how desperate will they be before making another step on that path...?