\section{About the Adventure}


\subsection{Campaign Themes}

This campaign is using themes as listed below. Use this list to determine if you are interested in running this kind of campaign. In the game, you can encounter themes of:
\begin{itemize}
	\item Corrupted spren
	\item Deals with the devil
	\item Lesser evil
\end{itemize}

\subsection{Campaign Setting}

The story starts in Kholinar ruled by \npcQueen{}, shortly before the arrival of Everstorm. The characters will spend roughly half of the story in here. Later, they will travel through Shadesmar to reach Kharbranth and later - Urithiru.

\subsection{Missing Chapters}

You might notice that entire Act II (chapters from 6. to 10.) is missing. Initially my idea for the adventure assumed only 5 chapters in Kholinar. However, as I started working on it, it became obvious that the book will be much better with 5 more chapters.

Enlightened Radiant rules prepared for this book \seeCorruptedRules{} assume there are 9 Unmade that can influence those Radiants. If I wanted to balance that influence fairly without excluding any of the Orders, it would make sense to have all 9 of the Unmade in the story - preferable each featured in one Chapter focusing on them.

Also, the entire point of new talent trees is to use them. It makes little sense to finish the adventure before the PCs can properly play with their new toys - that was the entire goal of this book! Adding more chapters, advancing to higher tiers and having more challenges to face is just the way to go!

Therefore, I decided to expand the initial idea beyond Act I and introduce Act II. However, this book is already long in the making and I know some of you wait to play it... That's why I decided to share Act I while I'm still working on Act II. And that's why you might still find some TODO notes here and there.

You can enjoy Act I as it is fully playable and I consider it completed. Hopefully, before you reach Act II, I will have more to complete it and share with you. If not, I left some general info how would I see the story progressing so you could improvise from there.

Good luck and I hope you will enjoy it!