\section{Adventure Summary}

Here is a brief summary of the plot of the story. You can use it to quickly familiarize yourself with the adventure events.

\subsubsection{Shorter Options}

All chapters form together a long, cohesive story. However, each of the chapters 6-10 is large enough to be played by itself as a smaller adventure. 

You should be able to pick any one of them and run it as a one-shot adventure with minimal changes to the plot. Just make sure to adjust the starting level of the PCs accordingly.

You can also cut the adventure after chapter 5, ending the story with a cliffhanger.

\subsection{Chapter 1 Summary}

In the People's Hall, the characters discover glyphs accusing \npcQueen{} of the ten foolish attributes. \npcRebelArdent{}, the responsible ardent, is imprisoned for the crime.

\subsection{Chapter 2 Summary}

After the execution of \npcRebelArdent{}, riots start in the city. The rioters storm the Kholinar Palace. In the palace halls, the characters find a room full of mirrors with \npcSjaAnat{} reflected in one of them. She urges the characters to bond her children to prepare for the coming storm.

\subsection{Chapter 3 Summary}

The riots continue. \npcHighmarshal{} organizes defenses and storms the monastery with goal to secure a Soulcaster located there. The characters, instructed by \npcSjaAnat{}, aim to retrieve different artifacts from there. Finally, the Everstorm wakes Kholinar Parshmen.

\subsection{Chapter 4 Summary}

Newly awaken Singers gather around the city, laying a siege to it. The characters will need to use a \lootDustcaster{} retrieved from the monastery to tip the scales of that conflict.

\subsection{Chapter 5 Summary}

The characters must flee the city. The only path leads through the Kholinar Oathgate, currently occupied by reveling ardents.

\subsection{Chapter 6 Summary}

The party is stranded in the Shadesmar. They must travel through it to Kharbranth.

\subsection{Chapter 7 Summary}

While in Kharbranth, the party must negotiate with \npcTaravangian{} and convince him to let them travel to Urithiru.

\subsection{Chapter 8 Summary}

While in Urithiru, the party hears about \npcShallan{}'s investigation to uncover the mystery of a series of murders. Their help could secure their connections inside the Tower. 

\subsection{Chapter 9 Summary}

\npcDalinar{} and \npcElhokar{} are mounting a rescue mission to Kholinar. This is a perfect opportunity to travel back and face \npcQueen{}.

\subsection{Chapter 10 Summary}

The characters are tasked with their final quest - they must travel to Spiritual Realm and find \npcMishram{} as she is the only one who can overrule \npcOdium{}'s reign.


\reasonBox{It might be hard to proceed with  your campaign on Roshar after chapter 10. If your players want to continue playing as their PCs, you should probably consider worldhopping somewhere else. Due to some Ghostbloods NPCs coming from Scadrial, you can consider going over there.}