\section{Dramatis Person\ae}
\label{personae}

Following NPCs and fractions appear in the adventure:

\begin{itemize}
	\item \npcTroublemaker[s]{} - adolescent woman, most probably friend or family of the PCs; enthusiastic and impulsive, prone to getting into trouble.
	
	\item \npcGrandma[s]{} - \npcTroublemaker{}'s grandmother, grumpy and fast to insult.
	
	\item \npcRebelArdent[s]{} - ardent of Devotary of Denial, accused \npcQueen{} of ten foolish attributes; her execution sparks the riots in Kholinar.
	
	\item \npcLockedArdent[s]{} - ardent, friend of \npcRebelArdent{}, got locked up after her imprisonment.
	
	\item \npcHoid[s]{} - nobody really important...
\end{itemize}



\subsubsection{Royal Palace}

The Palace closed its doors to the hardships troubling the city. Only queen's most trusted allies have access inside.

Following NPCs are related to this fraction:

\begin{itemize}
	\item \npcQueen[s]{} - wife of \npcElhokar{}, at his absence she rules the city; bonded to \npcYeligNar{}, the \npcYeligNarTitle{} she got her soul corrupted and her judgment clouded.
	
	\item \npcElhokar[s]{} - king of Alethkar, currently located in the Shattered Plains.
	
	\item \npcDeadKing[s]{} - former king of Alethkar, father of \npcElhokar{}, killed by the Assasin in White.
\end{itemize}



\subsubsection{\npcFractionCult{}}

Ardents close to \npcQueen{} herself, whose lives full of excess lead to drawing the sight of \npcHeartRevel{}, the \npcHeartRevel{}. Now their minds are lost, following only the beating of the terrible heart.

Following NPCs can be found in this fraction:

\begin{itemize}
	\item \npcRevelerGuide[s]{} - guides new cultists to their first revelry.
	
	\item \npcRevelerGeneral[s]{} - got attracted to the revelry in the Monastery; her unwillingness to follow \npcHeartRevel{} got her imprisoned.
\end{itemize}



\subsubsection{\npcFractionWall{}}

With \npcQueen{} secluded in her Palace, the responsibility to defend the city fell to the \npcFractionWall{}. 

Following NPCs are included here:

\begin{itemize}
	\item \npcHighmarshal[s]{} - took charge once the previous commander fell in the city riots; now she does her best to protect the city and its people.
	
	\item \npcSoulcaster[s]{} - an Emerald Soulcaster from the city Monastery, got rescued by \npcHighmarshal{} during the city riots to soulcast food for them.
\end{itemize}



\subsubsection{Singers}

During the Everstorm, Kholinar parshmen are transformed into Singers who devastate the city before establishing a camp beyond its walls.

Following NPCs are included in this group:

\begin{itemize}
	\item \npcSingerWorkerGranM[s]{} - malen worker at \npcGrandma{}'s.
	
	\item \npcSingerWorkerGranF[s]{} - femalen worker at \npcGrandma{}'s.
	
	\item \npcSingerWouned[s]{} - wounded during the fights in Kholinar.
	
	\item \npcSingerEnvoy[s]{} - Envoyform Singer at the camp.
\end{itemize}



\subsubsection{Shadesmar}

In Shadesmar, also known as the Cognitive Realm, true spren built their own civilization, with cities, craftsmen, travelers and merchants. 

Following NPCs are included in this group:

\begin{itemize}
	\item \npcSprenGuide[s]{} - an Enlightened Lightspren, sent by \npcSjaAnat{} to help the party with their journey.
	
	\item \npcFortuneReader[s]{} - a lighthouse keeper and an oracle.
	
	\item \npcIceCultivationsprenTrader[s]{} - frosty Cultivationspren, trader. Travels with his Coldspren.
	
	\item \npcIceCultivationsprenGardener[s]{} - frosty Cultivationspren, sister of \npcIceCultivationsprenTrader{}. She tends to the gardens at \locationFidelity{}. Always wanted to bond with a human.
	
	\item \npcCultivationsprenPainter[s]{} - Cultivationspren painter and art merchant.
	
	\item \npcHonorsprenCaptain[s]{} - Honorspren, ship captain.
	
	\item \npcPeaksprenCaptain[s]{} - Peakspren, ship captain.
	
	\item \npcCrypticCaptain[s]{} - Cryptic, pirate captain.
\end{itemize}



\subsubsection{The Ghostbloods}

Ruthless organization from a world of Scadrial, wielders of Allomancy - a magic unknown to anyone on Roshar. 

Following NPCs are included in this group:

\begin{itemize}
	\item \npcGhostbloodScout[s]{} - scouts the Shadesmar for anything interesting.
	
	\item \npcGhostbloodWounded[s]{} - wounded in \locationKharbranth{}, gone missing.
	
	\item \npcGhostbloodBoss[s]{} - leader of Kholinar network, lost contact with the rest of the organization.
	
	\item \npcMraize[s]{} - Ghostbloods' leader on Roshar. Bonds with an Enlightened Cryptic.
	
	\item \npcIyatil[s]{} - mentor of \npcMraize{}. Mysterious and elusive, with access to off-world magic. Bonds with an Enlightened Inkspren. 
	
	\item \npcVeil[s]{} - \npcShallan{}'s persona, spy and assassin, Ghostblood initiate.
\end{itemize}



\subsubsection{\locationKharbranth{}}

Also known as the City of Bells is a home to the best surgeons in the world. The medical care is free for everyone in the  city and the \locationPalanaeum{} allows for the highest quality of medical training.

Following NPCs can be met here:

\begin{itemize}
	\item \npcWoundedTrader[s]{} - trader, wounded on the road to the city.
	
	\item \npcKharbranthNoble[s]{} - noble family. Lady \npcKharbranthNoble{} recently lost her husband.
	
	\item \npcOrphanSick[s]{} - sick orphan, taken to the hospitals.
	
	\item \npcOrphanHomeless[s]{} - homeless orphan, is searching for \npcOrphanSick{}.
	
	\item \npcVedenArtifabrian[s]{} - artifabrain from Vedenar.
\end{itemize}


\newpage
\subsubsection{The Diagram}

Several years ago, during a day of godlike intelligence, \npcTaravangian{} created the Diagram - a set of prophetic notes, predicting the future of Roshar. Ever since, a group named after it uses the Diagram to their advantage with hopes to save humanity from the aftermath of the Last Desolation.

Following NPCs are included in this group:

\begin{itemize}
	\item \npcDiagramSurgeon[s]{} - surgeon.
	
	\item \npcDiagramAarchivist[s]{} - archivist, gathers recorded samples.
	
	\item \npcMalata[s]{} - Dustbringer, guards \npcTaravangian{}.
	
	\item \npcTaravangian[s]{} - king of \locationKharbranth{} and leader of the Diagram.
\end{itemize}



\subsubsection{\locationUrithiru{}}

An ancient city of Knights Radiant was recently rediscovered by alethi forces under the command of \npcDalinar{}. Now the alethi colonized the tower, making it a seat of alethi power.

Following NPCs can be met here:

\begin{itemize}
	\item \npcDalinar[s]{} - the Bondsmith, leader of alethi forces.
	
	\item \npcShallan[s]{} - artist, scholar and a Lightweaver, uses \npcVeil{} and \npcRadiant{} personas to deal with non-academic problems.
	
	\item \npcRadiant[s]{} - \npcShallan{}'s persona, skilled warrior accustomed with military life.
	
	\item \npcAdolin[s]{} - son of \npcDalinar{}, Shardbearer and excellent duelist.
	
	\item \npcRenarin[s]{} - son of \npcDalinar{}, a Truthwather bonded to an Enlightened spren.
	
	\item \npcNavani[s]{} - wife of \npcDalinar{}, artifabrian and a patron to scholars.
	
	\item \npcJasnah[s]{} - daughter of \npcNavani{}, scholar of a world renown, an Elsecaller with much experience.
	
	\item \npcGavinor[s]{} - son of \npcElhokar{} and \npcQueen{}, 3-year old baby.
	
	\item \npcKaladin[s]{} - \npcDalinar{}'s bodyguard, a Windrunner.
	
	\item \npcAmaram[s]{} - alethi highlord, leader of the Sons oh Honor.
\end{itemize}




\subsubsection{The Unmade}

Following Unmade are referenced or make an appearance in the adventure:

\begin{itemize}
	\item \npcSjaAnat{}, the \npcSjaAnatTitle{} - eerie, mysterious and secretive, \npcSjaAnat{} subtly arms and leads the PCs, arming them and manipulating them to achieve her own agenda.
	
	\item \npcThrill, the \npcThrillTitle{} - violent and brutal, relishes in the sounds of battle, fueling the rage of rioters and warriors fighting in Kholinar.
	
	\item  \npcDustmother{}, \npcDustmotherTitle{} - gone for millennia, now only \lootDustcaster{} remains as a memento of her terrible power.
	
	\item \npcHeartRevel{}, the \npcHeartRevel{} - drawn to indulgence and excess, influences \npcFractionCult{} in Kholinar.
	
	\item \npcBlackFisher{}, the \npcBlackFisherTitle{} - since the Scouring of Aimia, only tales and \lootGateOpener{} remain of him.
	
	\item \npcMoelach{} - often found near the dying people, showing them visions of the future known as Death Rattles.
	
	\item \npcMidnightMother{}, the \npcMidnightMotherTitle{} - lurks in the deeps of Urithiru, spawning creatures of horrors to torment its new inhabitants.
	
	\item \npcYeligNar{}, the \npcYeligNarTitle{} - capable of bestowing the power of Surges, he is now bonded to \npcQueen{}, corrupting her soul.
	
	\item \npcMishram{} - once carrying the power to rival \npcOdium{} himself, captured by ancient Radiants, she is now imprisoned in the Spiritual Realm plotting her revenge.
\end{itemize}

\roleplayBox{\npcSjaAnat}{	
	\roleplayTips{Eerie, mysterious, ancient}
		{Release \npcMishram{} to break free from Odium}
		{Slender woman with black, long, flowing hair, appearing as a reflection in mirrors}
		{\npcSjaAnat{} is very secretive and will not share her motivations with the party, telling them only as much they must know at the moment. She doesn't want to serve Odium anymore, but to break free she must ensure he is defeated and removed from the scene. Her best hope is \npcMishram{} who already once proved she can replace their master. \\ \\			
		However, \npcMishram{} is imprisoned and hidden away. \npcSjaAnat{} must find agents who can be manipulated into entering the Spirit Realm to release \npcMishram{}, and she must ensure they are strong enough for the job. A group of Radiants bonding her Enlightened children seem to be perfect candidates.
		}
}


