\section{Battle at the Gates}
\label{sec:gatesBattle}

If the players managed to reach this location before completing \fullref{sec:monastery}, they will see \npcHighmarshal{} and her \enemyWallGuard{}s defending the gate from the \npcFractionCult{}. The PCs can join either side of the conflict. Start the encounter from  \fullref{ssec:gatesMain}.

If they decided to complete \fullref{sec:monastery} first, \npcHighmarshal{} successfully defended the gate by the time the characters reach it. In this case there is nothing more to do in here and you can skip the events of this section.

\roleplayBox{\npcHighmarshal{}}{
	\roleplayTips
		{Determined, inspiring, resourceful}
		{Protect the people of Kholinar}
		{Orange eyes and short, straight, black hair. Lean and grim, with couple scars on her face. Wears shining chainmail and an azure cloak.}
		{\npcHighmarshal{} didn't ask for that - she just was around when Kholinar needed a Wall Guard commander and she stepped up to take the responsibility. She is not even from Alethkar, but this does not matter - there are people who need her and she will defend them!}
}

\spoilerBox{
	\npcHighmarshal{} leading the defense of the city gates against the Cult of Moments is referenced in \bookOB{}, Chapter 70: Highmarshal Azure.
}



\subsection{Main Gate}
\label{ssec:gatesMain}

Start this encounter by reading the following:

\quoteBox{
	"Form the line! Shields high! Don't give them an inch!" - you hear orders shouted from a small group of defenders surrounded by an assault of cultists in white.
}

\enemyWallGuardHighmarshal{} leads a small squad of four \enemyWallGuard{}s against an assault of eight \enemyCultist{}s (each \enemyCultistOfMoments{} of a random kind). \npcHighmarshal{} will retreat once all her troops are dead, but all others will fight to the end.

From here, the characters can take the stair to join the fight in \fullref{ssec:gatesWalls}. They can also enter the gate tower to fight in \fullref{ssec:gatesBarracks}.

\npcHighmarshal{} and other combatants form this location will remain here, it is up to the players to drive off the enemies.




\subsection{Guard Barracks}
\label{ssec:gatesBarracks}

When the PCs enter this room, read the following:

\quoteBox{
	You enter the barrack room to see the last of the cultists being overwhelmed by the defenders.
}

Six \enemyWallGuard{}s are fighting here, and only two \enemyCultist{}s (random kinds) are remaining. All of them will fight to the end.

Both sides are vaguely familiar with the character's involvement during the fight in \fullref{ssec:gatesMain}, so the PCs cannot change sides now.

From here the characters can take an exit to reach \fullref{ssec:gatesWalls}.




\subsection{City Walls}
\label{ssec:gatesWalls}

When the PCs enter the walls, read the following:

\quoteBox{
	You enter just in time to see more cultists approaching on the walls. The lone guard will soon be overwhelmed...
}

Single \enemyWallGuard{} is about to be attacked by six \enemyCultist{}s (random kinds). All will fight to the end.

Both sides are vaguely familiar with the character's involvement during the fight in \fullref{ssec:gatesMain}, so the PCs cannot change sides now.

From here the characters can enter \fullref{ssec:gatesBarracks}.




\subsection{Aftermath}

The fighting stops once the PCs defeat all enemies in all three locations. The gates are now under control of the fraction the PCs were supporting during the fight.

\npcHighmarshal{} is gathering people to storm the Cultist Monastery (see \fullref{sec:monastery}). She invites the characters to join her.

If \npcHighmarshal{}'s forces were defeated by the PCs, she will retreat to recover and attack the Monastery alone.