\chapter{Chapter 3 - Enemy Reborn}
\label{chap:chapter3}

\setcounter{section}{-1}
\section{Running This Chapter}

In this chapter, the riots continue on the streets of Kholinar. \npcHighmarshal{} defends city gates and storms the monastery, while helpless parshmen are slaughtered on the streets by queen's orders.

In this chaos, the characters follow their own agenda - they must reclaim ancient artifacts of the Unmade from the Ardent Monastery.

\reasonBox{
	Starting from this chapter, this book assumes \npcTroublemaker{} might have died in the riots and she is referenced no more. If in your game she survived, it is up to you how to tell her story - she may die from the hands of newborn Singers during \fullref{sec:enemyReborn}, or she may live to meet the PCs again during \nameref{chap:chapter9}. Who knows, she might even bond an Enlightened spren (knowing her personality, probably a lightspren)
}

\subsection{Character Advancement}

The characters start this chapter at level 3. Advance them to level 4 at the end of this chapter.

\reasonBox{
	Depending on the player choices, this chapter may be encounter-rich, or finish quicker if the party remains focused to complete their objective as soon as possible.
	\\ \\
	If you feel the chapter is getting longer, consider advancing the party to level 4 as you trigger \fullref{sec:enemyReborn} events. If you do so, do not award them additional level at the end of the chapter, they should start \nameref{chap:chapter4} at level 4 no matter how many encounters did they have during the riots.
}

\newpage
The following events may affect their path to radiance:
\begin{itemize}
	\item Calming angry mob or leading them to riot against queen's herald
	\item Defending helpless parshmen or helping to execute them
	\item Fighting with \npcThrill{} nearby can expedite an Enlightened Windrunner
	\item Seeing ancient artifacts of the Unmade can expedite an Enlightened Dustbringer or Elsecaller
\end{itemize}



\subsection{Forging Alliances}

The following actions can help the characters to become allies with Kholinar fractions:
\begin{itemize}
	\item Helping \npcHighmarshal{} to defend the gates and secure the monastery
	\item Fighting alongside the \npcFractionCult{} against \npcHighmarshal{} and the parshmen
	\item Defending helpless parshmen and newly born Singers
\end{itemize}



\subsection{Event: The Thrill of Battle}

As the fights rise in the city, \npcThrill{}, the \npcThrillTitle{} gets attracted by the screams of battle and the blood of the wounded. \\

\eventComplication{The Thrill of Battle}{	
	\iconCompEvent
	\iconCompEvent
	\iconCompEvent
	\iconCompEvent\\ \vspace{0.15cm}
	\iconCompEvent
	\iconCompEvent
	\iconCompEvent
	\iconCompEvent\\ \vspace{0.15cm}
}

\subsubsection{Progressing the Event}

Each time a complication is rolled during a fight in Kholinar, you can spend it to progress the event by 1, trading an immediate Complication for the \npcThrill{}'s attention.

Each time a PC kills a foe in Kholinar while there are other enemies still alive, they must pass \skillCheck{15}{\skillDiscipline{}}. On a failure, progress the event by 1.


\subsubsection{Triggering the Event}

Once the final complication slot is filled, \npcThrill{} arrives to Kholinar. From now on, during all combat scenes, all characters (PCs and NPCs) are affected by the following rules:

\scriptedOption{Thrill of Murder}{
	Raise Stakes each time a melee attack is made. On a \iconComp{}, add +3 to that d20 roll and that attack grazes all characters adjacent to both the attacker and the defender (without spending focus).
}

\scriptedOption{Keep Fighting!}{
	If a character wishes to move away from the enemy or stop fighting (e.g. when there are no enemies left), they must make a \skillCheck{15}{\skillDiscipline}. On a failure they must keep fighting and attempt an attack against any character in the scene, including an ally. If the character passes the test, they no longer repeat it during next rounds of this combat scene.
}

\corruptedBox{
	Fighting in the battle influenced by \npcThrill{}, the \npcThrillTitle{}, can expedite the progression of an Enlightened Windrunner \seeCorruptedRules{}.
}



\subsection{Death Rattles}

When a nearby NPC dies, you can consider marking his death with a Death Rattle, especially if there is an Enlightened Truthwatcher in the party.

You can make up your own Death Rattles (either random nonsense or foreshadowing prophecy), or you can pick one from the examples presented in \nameref{chap:deathRattles}.

\corruptedBox{
	Hearing a Death Rattle sent by a \npcMoelach{} can expedite the progression of an Enlightened Truthwatcher \seeCorruptedRules{}.
}

\reasonBox{
	\npcMoelach{} will have its own arc dedicated for its influence in \nameref{chap:chapter7}. Do not expedite an Enlightened Truthwatcher more than once in this chapter.
}


\input{chapter_3/proclamation.tex}
\input{chapter_3/bloodyStreets.tex}
\input{chapter_3/closedPalace.tex}
\input{chapter_3/battleAtTheGates.tex}
\input{chapter_3/stormingMonastery.tex}
\input{chapter_3/enemyReborn.tex}
\input{chapter_3/dyingSinger.tex}

\section{Journeying Onward}

Once you complete encounters with reborn Singers, advance characters to level 4 and proceed to \nameref{chap:chapter4}.