\section{The Palace}
\label{sec:closedPalace}

At this point in the story, there is little to be gained in the palace. If characters attempt to enter the palace, they will find closed and heavily guarded gates.

\quoteBox{
	Two knights guard the bared palace gates. Their armors shine in the sun, but there is a shadow falling over their eyes and the sense of wrongness to them. Their leader approaches you. "The palace is closed for the likes of you.", he says. "Go back where you belong!"
}

Two \enemyQueensGuard{}s keep watch on both sides of the gates. Their commander - \enemyQueensGuardLeader{} will not allow the characters to enter. If the characters stay here too long, they will be attacked by palace forces. When the fight starts, two more \enemyQueensGuard{} will reinforce palace forces after the first round of combat. All guards will fight to the end.

\corruptedBox{
	Approaching the gates of the Kholinar Palace influenced by \npcYeligNar{}, the \npcYeligNarTitle{}, can expedite an Enlightened Skybreaker \seeCorruptedRules{}.
}


\subsection{Talking Their Way In}

The characters may wish to persuade the guards to let them in - run it as a conversation.
\conversationDefence{\enemyQueensGuardLeader{}}{15}{18}{5}

His loyalty to the \npcQueen{} is incredible and he will positively respond to people with similar values.
All tests against him are made with disadvantage unless the character has very good reason to be allowed inside.

\conversationEnd{\enemyQueensGuardLeader{}}{1}



\subsection{Sneaking Inside}

The characters may decide to avoid the guards and sneak inside the palace behind their backs. You can run it as an endeavor.
\pursuitReq{6}{2}
All tests of the endeavor made against the palace guards are made with disadvantage as they are on high alert.

If the characters succeed, they can enter the palace without the guards knowing. Otherwise, they are attacked by them. They will fight to the death, but they will not pursue fleeing characters.



\subsection{Inside the Palace}

If the characters convinced the guards to let them in, they will be escorted by two \enemyQueensGuard{}s. They will be allowed to the throne room to swear devotion and loyalty to \npcQueen{} (or whatever was the reason the guards let them in). 

After that they will be escorted back to exit. Any sign of disobedience or lack of cooperation will turn the guards hostile and may result in lethal encounter.

\reasonBox{
	Do not allow \npcQueen{} to participate in a fight in this chapter - she will have her own boss fight in Act II.
}