\section{Dying Singer}

When characters complete their objective for this chapter, end it with following:

\quoteBox{
	You see a badly wounded Singer sitting on the ground. "I must reach the others, beyond the walls", she mumbles to herself.
}

The characters can help the wounded or finish her off. If they choose to be friendly, she will introduce herself as \npcSingerWouned{}. She will invite them to the camp next to the city, where all other Singers gather, and she will ask them to help her get there.

\subsection{Singer Camp}

If the characters travel to the Singer camp, read the following:

\quoteBox{
	You reach the camp that is setup in an alethi fashion. Two massive Singers stay on watch, accompanied with one sleek one standing behind. \\ \\
	"Stop! Who goes there?", one of them asks, raising his weapon.
}

Two \enemySingerWarform{}s and one \enemySingerEnvoyform{} named \npcSingerEnvoy{} stay at the gates. If the party wishes to enter the camp, they must convince them to let them through. Run this as a conversation encounter.

\conversationDefence{\npcSingerEnvoy{}}{15}{18}{6}
Her goal is to grow Singer's camp in strength and she will welcome every potential ally, but she is wary of traitorous humans. 

All tests done by the party have advantage if they are accompanied by a Singer. Also, if during \fullref{sec:bloodyStreets} the characters stood in the defense of parshmen, one of them will step from the camp and vouch for the party, counting as one successful test.

\conversationEnd{\npcSingerEnvoy{}}{2}
If the Singers fail to believe the characters, they will turn hostile at the end of the conversation.

If the party chooses violent solution, more Singers will soon join the fight. There is a full camp of them, the characters can't defeat them all and will soon need to flee back to the city.