\section{The Everstorm}
\label{sec:enemyReborn}

Introduce events of this section after the party completes \fullref{sec:monastery}.

\quoteBox{
	The sky darkens as the thick, black clouds gather from the west. The wind raises, blowing with unnatural speed. Soon after, a red lightning strikes a building. More of them follows soon after.\\ \\
	In the midst of this, the usually quiet parshmen fell to their knees, screaming a soul-piercing wails of unimaginable anguish. Their bones break, their skin tears to shreds as dozens of spikes puncture through their bodies. Soon after, they all lie in pools of their own blood, with enough life in them to suffer agony.
}

The party faces two\enemySingerWarform{}s and three \enemySingerNimbleform{}s. They are Prone, lying in blood, Stunned for two rounds and Surprised for one. Once they are back on their feet they will attack the characters or nearby NPCs.

If the party decides not to take shelter to hide from the Everstorm and hostile Singers you can run the following encounters:



\subsection{Ungrateful Servants}
\label{ssec:enemyRebornServants}

If the party returns to \npcGrandma{}'s home, read the following:

\quoteBox{
	The household you enter is unnaturally quiet. No shouting, no complaining, no insults or empty threats. The building sounds empty...
}

If the characters rushed here just after the Everstorm arrived, they will see \enemySingerWarform{} and \enemySingerNimbleform{} standing above terrified \npcGrandma{}, savoring their revenge and preparing for the kill. If someone enters the room, they will attack them instead.

If the characters are late, they will find \npcGrandma{} brutally murdered by her own servants. They joined other Singers spreading mayhem in the city - the house is empty now.



\subsection{Raging Everstorm}

You can run this encounter multiple times and/or in pair with other events.

\quoteBox{
	Gusts of wind grow heavier. Soon after, a series of lightning strikes from the sky, flashing red light on otherwise dark street.
}

Lightning bolts of Everstorm hit the area. For each character in the scene, roll as if \enemySingerStormform{} attacked them with Bolt of Lightning while having a disadvantage. If the attack misses the character, the bolt lands nearby, destroying the surrounding environment.



\subsection{Clash With the Singers}

Read the following:

\quoteBox{
	In the howling wind you could not hear them, before you walked just into them: a group of Singers, still covered in their own blood after the transformation, fighting a terrified group of people. Red flashes of lightning flare every few seconds, but in between everything is black.
}

A group of Singers (\enemySingerDireform{} or \enemySingerStormform{}, 1d4 \enemySingerWarform{}s and 1d4 \enemySingerNimbleform{}s) fight against some humans (2d6 \enemyCultist{}s or 2d6 \enemyRioter{}s or 2d4 \enemyWallGuard{}s). Both groups ignore the party, but the characters may join on any side if they wish. All involved will fight to the end.



\subsection{Massacre the Weak}

Read the following:

\quoteBox{
	You see a few Singers standing above a crying mother. One of them grabbed her infant and smashed it into the stone wall of a building. Another one lunged to the devastated woman soon after.
}

A \enemySingerDireform{} and two \enemySingerWarform{}s are committing the atrocities. They did not notice the party yet, allowing them to sneak away. If they fail to do so, the singers will turn hostile towards them soon after. They will fight to the end.


\subsection{Unfortunate Artifabrian}

You can start similar encounter when a PC uses a fabrial or a non-Enlightened Radiant surgebends.

\quoteBox{
	You see a group of guards fighting against two Singers with sparks of lightning dancing around their arms. One of the guards aims with her fabrial to one of them. Soon after a bright light flashes the street and the Singer falls to the ground, twitching. \\ \\
	
	Cheers don't last long - moments later a vicious, screaming spren darts from the above towards the fabrial. A majestic figure appeared shortly after. The singer rammed one of the guards with a lance and send another one flying in the air. With the fabrial secured, the figure flied away, its unnaturally long red robes flapping behind it on the wind.
}

\enemySingerHaevenlyOne{} ignores the characters as long as they are not using fabrials, but two wounded \enemySingerStormform{} (with roughly half of their Health) remain. Unless the characters flee right away, they will turn hostile towards them. 

