\section{Proclamation}

Start the events of this chapter by reading the following:

\quoteBox{
	You see small crowd gathering around a woman wearing queen's colors who stands on some box in the middle of a street. She is accompanied by royal guards and is holding a piece of parchment. \\ \\
	The crowd around grows agitated with each passing moment.
}

Female herald is an \enemyExpert{} guarded by two \enemyQueensGuard{}s. The crowd throws rotten food at them, but they are ignoring it.

The characters can lead the riot against them or try to calm the people. If the fight starts, the herald flees, leaving her scroll behind for the PCs to find, but the guards will stand and fight against the people. If no fighting starts, after a few moments the herald reads the content of the scroll:

\quoteBox{
	We, \npcQueenName{}, by the grace of Allmighty and His Heralds, Queen of the Alethkar, do herby proclaim that all parsh people are the Voidbringers in hiding and therefore enemies to the realm and our faith. It is our order to exterminate all parsh people taking shelter behind the walls of Kholinar.
}

After reading the proclamation, the herald and the guards walk away, leaving angry and confused people behind.

If the riots start before the herald can read the order, she leaves the scroll behind in a hurry. Any character who can read in alethi will be able to learn its contents.

\spoilerBox{
	\npcQueen{} proclaiming parsmen to be Voidbringers and ordering their execution is referenced in \bookOB{}, Chapter 62: Research.
}
