\section{Ardent Monastery}
\label{sec:monastery}

Sooner or later, the characters are bound to attempt entering the Monastery. When they arrive to the location, they will start from \fullref{ssec:monasteryYard}.

\subsubsection{\npcHighmarshal{}'s Assault}

If the party was quick to get here, they will find mostly Ardents and \enemyCultist{}s here. If they stopped to help one of the sides during \fullref{sec:gatesBattle}, \npcHighmarshal{} will also storm the Monastery, and she will bring \enemyWallGuard{}s with her (if enough of them survived). 

The party will meet her in \fullref{ssec:monasterySoulcasters}, unless they are attacking the place together, allowing them to share most of the scenes.

\subsubsection{Past Actions}

Depending on players' actions so far, one of the sides of this conflict may be friendly towards the party. The PCs may storm the place alongside \npcHighmarshal{} or they may decide to help defend the place, hoping the newly-earned trust of the Ardents will help them achieve their goals.

If the characters were hostile to \enemyCultistOfMoments{}s earlier in the story, they might be recognized, turning peaceful encounter into hostile one.


\spoilerBox{
	\npcHighmarshal{} attacking the low monastery by the eastern gates is referenced in \bookOB{}, Chapter 73: Telling Which Stories.
}



\subsection{Monastery Yard}
\label{ssec:monasteryYard}

When the characters enter the Monastery, read the following:

\quoteBox{
	You are surrounded by serenity, as though this place was oblivious to the chaos raging behind its walls. You see two figures in white robes approaching you: \\ \\
	"Hello, child!", one of them says. "What are you looking for in this place?"
}

Two Ardents (use \enemyCultist{}'s stat blocks) guard the entrance. They are not hostile, unless they sense an incoming danger. If the party decides to attack them, two more \enemyCultist{}s will join the fight after the first round of combat.

The PCs may attempt to talk their way in. Run this as a conversation.
\conversationDefence{\enemyCultist}{11}{16}{3}
They live their lives devoted to the Almighty, and recently - the spren. They will respond positively to arguments suggesting the characters want to take part in the religious rituals.

\conversationEnd{\enemyCultist}{1}

If the players ask about the Unmade artifacts, the Ardents will deny existence of such items, calling it a heresy and a blasphemy. They will cease any further conversation and will turn hostile if the characters will press the topic.

From here, the characters can enter \fullref{ssec:monasteryHalls}.

\subsubsection{\npcHighmarshal{}'s Assault}

If \npcHighmarshal{} is storming the Monastery, there will be 4 \enemyCultist{}s and 3 \enemyWallGuard{}s fighting in here.




\subsection{Long Halls}
\label{ssec:monasteryHalls}

When the PCs enter the halls, read the following:

\quoteBox{
	Long, dark halls connect the whole complex. The walls of cold stone are decorated only with the sparse glow of torchlight. A few ardents walk in here.
}

Sometimes an Ardent or \enemyCultistOfMoments{} can be found here, but they will ignore the characters. The halls lead to \fullref{sec:monasteryChapel}. One of the closed doors hides \fullref{sec:monasteryFeast}. At the end of the corridors, there is \fullref{sec:monasteryStair}. The PCs can also reach \fullref{sec:monasteryCells} in the farthest parts of the Monastery.

\subsubsection{\npcHighmarshal{}'s Assault}

If \npcHighmarshal{} is storming the Monastery, there will be 2 \enemyCultist{}s and 2 \enemyWallGuard{}s fighting in here.



\subsection{Monastery Chapel}
\label{sec:monasteryChapel}

On the walls of the chapel there are paintings of spren, before them a group of kneeling people is praying - ardents in white robes lead the incantations, while the common people repeat after them:

\quoteBox{
	\centering
	"Oh, bringers of joy, remember us!" \\ "Remember us!" \\
	"Oh, dancers with flames, warm us!" \\ "Warm us!" \\
	"Oh, tenders of life, tend to us!" \\ "Tend to us!" \\
	"Oh, whispers of wind, whisper to us!" \\ "Whisper to us!" \\
}

Several \enemyCultist{}s (each \enemyCultistOfMoments{} of a different kind, no two repeating) pray in here with common people and brighteyes like. All of them ignore the PCs, but if they attack them, they will defend themselves. The \enemyCultist{}s will fight to the end, without any regard for the common people, who will attempt to run away.




\subsection{Lavish Feast}
\label{sec:monasteryFeast}

The door to this location is closed. If a character wishes to enter despite that, they will need to pass \skillCheck{15}{\skillStrength{} or \skillThievery{}}. In that case, read the following:

\quoteBox{
	You see a long table full of delights - meat, vegetables, cakes, exotic fruit - illuminated with spherelight from many chalices. More of the food lies on the floor and besides the walls. Some of it starts to rot. \\ \\
	A group of people in white robes feast on the delights. "You are not supposed to be here!", one of them shouts.
}

A \enemyRevelerDrinking{} and eight \enemyCultist{}s (of random kinds) feast in here. They will turn hostile unless a characters manages to quickly convince them to stand down - they would need to pass a \skillDeception{} or \skillPersuasion{} test against \enemyRevelerMasked{}'s Spiritual Defense with disadvantage.

If a combat starts, the enemies will fight to the end.

\subsubsection{\npcHighmarshal{}'s Assault}

If \npcHighmarshal{} is storming the Monastery, her forces will ignore this room, but some of \enemyWallGuard{}s can be called for help.

\subsubsection{Treasure}

In the chalices, there is 5d10 marks of spheres in total. \enemyRevelerDrinking{} carries a key to \fullref{sec:monasteryCells}.

The characters can also help themselves with the food or even bring something back home.

\corruptedBox{
	Participating in a lavish feast in the honor of \npcHeartRevel{}, the \npcHeartRevelTitle{}, may expedite an Enlightened Willshaper.
}



\newpage
\subsection{Locked Cells}
\label{sec:monasteryCells}

If the characters enter this area, read the following:

\quoteBox{
	This area of the Monastery seems abandoned. The halls are dark and nobody can be seen in here. \\ \\
	Suddenly, you hear a faint voice from one of the cells: "Please, have mercy... I am so hungry..."
}

Ardent \npcLockedArdent[s]{} is locked in one of the cells. She is imprisoned by \npcFractionCult{}. She hasn't seen anyone since she was put in here.

\subsubsection{Releasing \npcLockedArdent{}}

A character may open the jail using key found on one of the Revelers in \fullref{sec:monasteryFeast}. If they don't have it, they can attempt \skillCheck{20}{\skillThievery}.

\subsubsection{Talking with \npcLockedArdent{}}

\npcLockedArdent{} is too weak and hungry for a proper conversation. If fed, she will gladly answer any questions:

\scriptedOption{Who are you?}{
	I am \npcLockedArdent{}, an ardent from Devotary of Denial.
}

\scriptedOption{How long have you been locked in here?}{
	Hard to say, I lost track of time... What day do have...? Anyway, they came for me a day after \npcRebelArdent{} got assigned to Queen's Retinue... Did she told them something about me? I thought we were friends...
}

\scriptedOption{Can you help us navigate the Monastery?}{
	It isn't the one I've spent most of my life in, but it should be similar. I can be your guide, just please, don't leave me here!
}

\scriptedOption{Do you know about an Artifacts of the Unmade?}{
	The Voidbringers are destroyed, nothing left from them. There is no such item, and if there were, you wouldn't find them in here, this is a holy place. You are wasting your time... And please, don't pursue such unholy items, they will only curse your soul... Trust in the Almighty, He will guide your souls!
}




\subsection{Stairways}
\label{sec:monasteryStair}

When the PCs reach this place, read the following:

\quoteBox{
	You see a spiral stairs cut from the stone, descending into a darkness. Several people in white robes are standing nearby. "This area is for ardents only. Return to the chapel", one of them says.
}

Six \enemyCultist{}s (each \enemyCultistOfMoments{} of random kind) guard the stairway. They will turn hostile unless the PCs quickly go back. 

From here, the PCs can descend to \fullref{ssec:monasterySoulcasters}.

\subsubsection{\npcHighmarshal{}'s Assault}

If \npcHighmarshal{} is storming the Monastery, four \enemyWallGuard{} will fight the \enemyCultist{}s. The party can help in combat or sneak downstairs.




\subsection{\npcSoulcaster{} and Her Sister}
\label{ssec:monasterySoulcasters}

When the PCs reach this place, read the following:

\quoteBox{
	You see two female ardents sitting in the middle of the room. Green vines pierce through their pale skins, entangling their frail bodies. One of them wears a Soulcaster on her hand.
}

\npcSoulcaster{} and her sisters are \enemySoulcaster{}s, but only one of them has the Fabrial required for Soulcasting. They will not attack any aggressors - in a case of combat, they will attempt to flee or slow down their enemies. They will use Soulcaster as a weapon only when they will be left with no other choice.

No matter the cost, they will not part with the Fabrial. They are not part of the \npcFractionCult{} and they are not familiar with current events or political forces.

At the end of the room, the door leads to \fullref{ssec:monasteryReliquary}. Any character who bonded an Enlightened spren will feel a slight pull towards that area.

\spoilerBox{
	\npcSoulcaster{} is met in \bookOB{}, Chapter 81: Ithi and Her Sister.
}

\subsubsection{\npcHighmarshal{}'s Assault}

If \npcHighmarshal{} is storming the Monastery, she can be found in this room, attempting to persuade the Soulcaster sisters to join her and help the falling city.




\subsection{Forbidden Reliquary}
\label{ssec:monasteryReliquary}

When the PCs reach this area, read the following:

\quoteBox{
	The room is full of small chests, each standing on its own stone shelf and containing an ancient relic of ardents long gone. Two of the relics catch your attention - the artifacts that \npcSjaAnat{} described to you.
}

The party found \lootDustcaster{} and \lootGateOpener{}, securing their objective. Other items in this room have no practical use.

\reasonBox{
	As the characters get hold of the fabrials from the reliquary, don't reveal all their secrets just yet. Let there be some mystery around them. Don't worry, the book will provide explanations when they are needed.
}

\corruptedBox{
	Seeing \lootDustcaster{} for the first time, an artifact of \npcDustmother{}, the \npcDustmotherTitle{}, can expedite the progression of an Enlightened Dustbringer \seeCorruptedRules{}.
}

\corruptedBox{
	Seeing \lootGateOpener{} for the first time, an artifact of \npcBlackFisher{}, the \npcBlackFisherTitle{}, can expedite the progression of an Enlightened Elsecaller \seeCorruptedRules{}.
}




\subsection{Aftermath}

When the party secured the artifacts of the Unmade, trigger the events of \fullref{sec:enemyReborn} when they exit the monastery. The party will still be able to pursue other goals of this chapter, but the conditions in Kholinar will be much different.
